### 2017-12-14 Paper/cover.tex
added outline for the Paper

%-------------------COVER-------------------------------------------
\begin{center}
\begin{Large}
{\bf Bayesian Guided Optimal Experimental Design for Reactive Multilayers}\\
\end{Large}

\bigskip
%\bigskip

Manav Vohra,$^1$ Xun Huan,$^2$ Omar M. Knio$^{1,3}$ \\

\bigskip
\bigskip

\normalsize
$^1$Department of Mechanical Engineering and Materials Science\\
Duke University\\
Durham, NC 27708\\

\bigskip

$^2$Department of Aeronautics and Astronautics\\
Massachusetts Institute of Technology\\
Cambridge, MA 02139\\

\bigskip

$^3$Computer, Electrical and Mathematical Sciences and Engineering Division \\
King Abdullah University of Science and Technology \\
Thuwal 23955-6900, Kingdom of Saudi Arabia\\

\end{center}

\vspace{6cm}

\begin{tabbing}
Corresponding Author: \hspace{5mm} \= Omar M. Knio\\
       \>  Department of Mechanical Engineering and Materials Science\\
       \>  Duke University\\
       \>  144 Hudson Hall, Box 90300 \\
       \>  Durham, NC 27708 \\
       \> \\
Phone: \> (919) 660-5344 \\
Fax:   \> (919) 660-8963 \\
Email: \>  omar.knio@duke.edu   \\
\\
Submitted to: \> \textit{Journal} \\
\> December 2015\\

\end{tabbing}
\clearpage

### 2017-12-14 Paper/outline.tex

 \documentclass[letter,12pt]{article}
%
\input{def}
\usepackage[table]{xcolor}
\usepackage{relsize}
\usepackage{bm}
\usepackage{mathrsfs}

 \def\ol{\overline}
 \def\no{\noindent}
 \def\qd{\dot{Q}}

%%%%%%%FLOW DIAGRAM%%%%%%%%%%
\usepackage[latin1]{inputenc}
\usepackage{tikz}
%\usepackage[table]{xcolor}
\usetikzlibrary{shapes,arrows}
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
   text width=5.0em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=cyan!20, 
   text width=9.0em, text centered, rounded corners]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
   minimum height=2em]
%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------
\begin{document}

\thispagestyle{empty}

\begin{center}
\begin{Large}
{\bf An Efficient Approach to Surrogate Modeling with Application to Molecular
Dynamics}\\
\end{Large}

\bigskip

Manav Vohra, Alen Alexanderian, Sankaran Mahadevan
\end{center}

\begin{large}
\noindent Outline
\end{large}

\begin{enumerate}

\item Introduction
\begin{enumerate}
\item Need for Surrogates - especially for complex models to enable forward UQ, 
sensitivity studies, calibration, and experimental design (Include citations).
\item Computational Hurdles: Polynomial Chaos and GP can be computationally 
intractable and suffer from the curse of dimensionality (Include plots for PCE
to motivate dimension reduction with citations for both PCE and GP).
\item Sensitivity analyis - a potent tool for dimension reduction. However, SA can be
computationally prohibitive. In fact, there are studies demonstrating the use of 
surrogates to reduce costs associated with SA (include citations). 
\item DGSM - brief introduction and citations. 
\item Key contributions of the paper: 1) Methodology that exploits DGSM to reduce the
dimensionality of the problem and thus enables efficient construction of surrogates.
2) Application of the proposed methodology to investigate relative importance of
parameters in the stillinger-weber potential, commonly used for studying phonon transport in silicon. Further, construct a reasonably accurate PC surrogate in the reduced 
space and demonstrate computational advantage of this approach. .
\end{enumerate}

\item Background
\begin{enumerate}
\item DGSM
\item PCE
\end{enumerate}

\item Methodology/Algorithm

\item Motivating Examples
\begin{enumerate}
\item Borehole: Screening, Convergence, Verification
\item Elliptic PDE: Screening, Convergence, Verification
\item Non-linear Oscillator: Screening, Convergence, Verification
\end{enumerate}

\item Application: Phonon Transport in a Si bar
\begin{enumerate}
\item Include all details pertaining to the MD simulation: system, simulation, 
ensembles, etc. 
\item Results
\end{enumerate}

\item Discussion
\begin{enumerate}
\item Methodology is agnostic to the choice of surrogate.
\item As required for a PCE, the uncertain parameters need not be independent. 
\item Strategy depends on the application - methodology could be implemented 
sequentially or adaptively. 
\end{enumerate}

\end{enumerate}

\end{document}

### 2017-12-16 Paper/outline.tex
changed the outline ...

@@
 \begin{enumerate}
-\item Need for Surrogates - especially for complex models to enable forward UQ, 
+\item Need for efficient Surrogates - especially for complex models to enable forward UQ, 
 sensitivity studies, calibration, and experimental design (Include citations).
@@
 \item DGSM
-\item PCE
+\item Polynomial Chaos Expansions (PCE)
 \end{enumerate}

### 2017-12-16 Paper/DGSM_PCE_MD_paper.tex
paper outline/structure ...

--- 2017-12-16 Paper/outline.tex
@@
 
-\thispagestyle{empty}
+\begin{center}
+\textsc{
+Efficient derivative-based global sensitivity approach to 
+surrogate modeling with application to molecular dynamics
+}
 
-\begin{center}
-\begin{Large}
-{\bf An Efficient Approach to Surrogate Modeling with Application to Molecular
-Dynamics}\\
-\end{Large}
+\bigskip
 
@@
 Manav Vohra, Alen Alexanderian, Sankaran Mahadevan
+
 \end{center}
 
-\begin{large}
-\noindent Outline
-\end{large}
+\vspace{10cm}
 
-\begin{enumerate}
+\begin{tabular}{ll}
+Corresponding Author:  & TBA \\
+                       & Vanderbilt University \\ 
+                       & Nashville, TN\\ 
+                       & Phone: \\ 
+                       & Email: 
+\end{tabular}
 
-\item Introduction
+\bigskip
+
+Submitted to: \emph{Journal of Computational Physics}
+
+\clearpage
+
+\tableofcontents
+
+\section{Introduction}
 \begin{enumerate}
@@
 
-\item Background
-\begin{enumerate}
-\item DGSM
-\item Polynomial Chaos Expansions (PCE)
-\end{enumerate}
+\section{Background}
+\subsection{DGSM}
+\[ 
+    \mu_i = E\left(\left( \frac{\partial \mathcal{G}}{\partial \theta_i}\right)^2\right)
+          \approx \hat\mu_i := \frac1N\sum_{j = 1}^N 
+                  \left(\frac{\partial \mathcal{G}(x_j)}{\partial \theta_i}\right)^2
+\]
+Can consider variance of $\hat\mu_i$.
 
-\item Methodology/Algorithm
+\subsection{Polynomial chaos}
+\section{Method}
 
-\item Motivating Examples
-\begin{enumerate}
-\item Borehole: Screening, Convergence, Verification
-\item Elliptic PDE: Screening, Convergence, Verification
-\item Non-linear Oscillator: Screening, Convergence, Verification
-\end{enumerate}
+\section{Motivating examples}
+\subsection{Borehole: Screening, Convergence, Verification}
+\subsection{Semilinear elliptic PDE: Screening, Convergence, Verification}
+\subsection{Nonlinear Oscillator: Screening, Convergence, Verification}
 
-\item Application: Phonon Transport in a Si bar
+\section{Application: Phonon Transport in a Si bar}
+
+Seven uncertain parameters; well-established nominal values exist;
+\[
+   \theta_i \sim U(\bar\theta_i - \epsilon_i, \bar\theta_i + \epsilon_i), 
+   \quad \epsilon_i = 0.1 \bar\theta_i. 
+\]
 \begin{enumerate}
@@
 
-\item Discussion
+\section{Discussion}
 \begin{enumerate}
@@
 
-\end{enumerate}
-
 \end{document}

### 2017-12-18 Paper/gen_outline.sh
updated to change the target filename for paper

@@ -1,5 +1,5 @@
 #!/bin/sh
 
-pdflatex outline.tex
-pdflatex outline.tex
-rm *.aux *.log
+pdflatex DGSM_PCE_MD_paper.tex
+pdflatex DGSM_PCE_MD_paper.tex
+rm *.aux *.log *.toc

### 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
moved cover to a separate file

@@
 
-\begin{center}
-\textsc{
-Efficient derivative-based global sensitivity approach to 
-surrogate modeling with application to molecular dynamics
-}
-
-\bigskip
-
-\bigskip
-
-Manav Vohra, Alen Alexanderian, Sankaran Mahadevan
-
-\end{center}
-
-\vspace{10cm}
-
-\begin{tabular}{ll}
-Corresponding Author:  & TBA \\
-                       & Vanderbilt University \\ 
-                       & Nashville, TN\\ 
-                       & Phone: \\ 
-                       & Email: 
-\end{tabular}
-
-\bigskip
-
-Submitted to: \emph{Journal of Computational Physics}
-
-\clearpage
+\input{cover}
 

### 2017-12-19 Paper/cover.tex
moved cover to a separate file

@@
-%-------------------COVER-------------------------------------------
 \begin{center}
-\begin{Large}
-{\bf Bayesian Guided Optimal Experimental Design for Reactive Multilayers}\\
-\end{Large}
-
-\bigskip
-%\bigskip
-
-Manav Vohra,$^1$ Xun Huan,$^2$ Omar M. Knio$^{1,3}$ \\
-
-\bigskip
-\bigskip
-
-\normalsize
-$^1$Department of Mechanical Engineering and Materials Science\\
-Duke University\\
-Durham, NC 27708\\
+\textsc{
+Derivative-based global sensitivity approach to 
+efficient surrogate modeling with application to molecular dynamics
+}
 
@@
 
-$^2$Department of Aeronautics and Astronautics\\
-Massachusetts Institute of Technology\\
-Cambridge, MA 02139\\
+\bigskip
+
+Manav Vohra, Alen Alexanderian, Sankaran Mahadevan
+
+\end{center}
+
+\vspace{10cm}
+
+\begin{tabular}{ll}
+Corresponding Author:  & TBA \\
+                       & Vanderbilt University \\ 
+                       & Nashville, TN\\ 
+                       & Phone: \\ 
+                       & Email: 
+\end{tabular}
 
@@
 
-$^3$Computer, Electrical and Mathematical Sciences and Engineering Division \\
-King Abdullah University of Science and Technology \\
-Thuwal 23955-6900, Kingdom of Saudi Arabia\\
+Submitted to: \emph{Journal of Computational Physics}
 
-\end{center}
-
-\vspace{6cm}
-
-\begin{tabbing}
-Corresponding Author: \hspace{5mm} \= Omar M. Knio\\
-       \>  Department of Mechanical Engineering and Materials Science\\
-       \>  Duke University\\
-       \>  144 Hudson Hall, Box 90300 \\
-       \>  Durham, NC 27708 \\
-       \> \\
-Phone: \> (919) 660-5344 \\
-Fax:   \> (919) 660-8963 \\
-Email: \>  omar.knio@duke.edu   \\
-\\
-Submitted to: \> \textit{Journal} \\
-\> December 2015\\
-
-\end{tabbing}
 \clearpage

### 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
moved intro to a separate file

@@
 
-\section{Introduction}
-\begin{enumerate}
-\item Need for efficient Surrogates - especially for complex models to enable forward UQ, 
-sensitivity studies, calibration, and experimental design (Include citations).
-\item Computational Hurdles: Polynomial Chaos and GP can be computationally 
-intractable and suffer from the curse of dimensionality (Include plots for PCE
-to motivate dimension reduction with citations for both PCE and GP).
-\item Sensitivity analyis - a potent tool for dimension reduction. However, SA can be
-computationally prohibitive. In fact, there are studies demonstrating the use of 
-surrogates to reduce costs associated with SA (include citations). 
-\item DGSM - brief introduction and citations. 
-\item Key contributions of the paper: 1) Methodology that exploits DGSM to reduce the
-dimensionality of the problem and thus enables efficient construction of surrogates.
-2) Application of the proposed methodology to investigate relative importance of
-parameters in the stillinger-weber potential, commonly used for studying phonon transport in silicon. Further, construct a reasonably accurate PC surrogate in the reduced 
-space and demonstrate computational advantage of this approach. .
-\end{enumerate}
+\input{intro}
 

### 2017-12-19 Paper/intro.tex
moved intro to a separate file

\section{Introduction}
\label{sec:intro}

%\begin{enumerate}
%\item Need for efficient Surrogates - especially for complex models to enable forward UQ, 
%sensitivity studies, calibration, and experimental design (Include citations).
%\item Computational Hurdles: Polynomial Chaos and GP can be computationally 
%intractable and suffer from the curse of dimensionality (Include plots for PCE
%to motivate dimension reduction with citations for both PCE and GP).
%\item Sensitivity analyis - a potent tool for dimension reduction. However, SA can be
%computationally prohibitive. In fact, there are studies demonstrating the use of 
%surrogates to reduce costs associated with SA (include citations). 
%\item DGSM - brief introduction and citations. 
%\item Key contributions of the paper: 1) Methodology that exploits DGSM to reduce the
%dimensionality of the problem and thus enables efficient construction of surrogates.
%2) Application of the proposed methodology to investigate relative importance of
%parameters in the stillinger-weber potential, commonly used for studying phonon transport in silicon. Further, construct a reasonably accurate PC surrogate in the reduced 
%space and demonstrate computational advantage of this approach. .
%\end{enumerate}

### 2017-12-19 Paper/app.tex
individual sections in the paper

--- 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
@@
- \documentclass[letter,12pt]{article}
-%
-\input{def}
-\usepackage[table]{xcolor}
-\usepackage{relsize}
-\usepackage{bm}
-\usepackage{mathrsfs}
-
- \def\ol{\overline}
- \def\no{\noindent}
- \def\qd{\dot{Q}}
-
-%%%%%%%FLOW DIAGRAM%%%%%%%%%%
-\usepackage[latin1]{inputenc}
-\usepackage{tikz}
-%\usepackage[table]{xcolor}
-\usetikzlibrary{shapes,arrows}
-% Define block styles
-\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
-   text width=5.0em, text badly centered, node distance=3cm, inner sep=0pt]
-\tikzstyle{block} = [rectangle, draw, fill=cyan!20, 
-   text width=9.0em, text centered, rounded corners]
-\tikzstyle{line} = [draw, -latex']
-\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
-   minimum height=2em]
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%-------------------------------------------------------------------
-\begin{document}
-
-\input{cover}
-
-\tableofcontents
-
-\input{intro}
-
-\section{Background}
-\subsection{DGSM}
-\[ 
-    \mu_i = E\left(\left( \frac{\partial \mathcal{G}}{\partial \theta_i}\right)^2\right)
-          \approx \hat\mu_i := \frac1N\sum_{j = 1}^N 
-                  \left(\frac{\partial \mathcal{G}(x_j)}{\partial \theta_i}\right)^2
-\]
-Can consider variance of $\hat\mu_i$.
-
-\subsection{Polynomial chaos}
-\section{Method}
-
-\section{Motivating examples}
-\subsection{Borehole: Screening, Convergence, Verification}
-\subsection{Semilinear elliptic PDE: Screening, Convergence, Verification}
-\subsection{Nonlinear Oscillator: Screening, Convergence, Verification}
-
 \section{Application: Phonon Transport in a Si bar}
-
-Seven uncertain parameters; well-established nominal values exist;
-\[
-   \theta_i \sim U(\bar\theta_i - \epsilon_i, \bar\theta_i + \epsilon_i), 
-   \quad \epsilon_i = 0.1 \bar\theta_i. 
-\]
-\begin{enumerate}
-\item Include all details pertaining to the MD simulation: system, simulation, 
-ensembles, etc. 
-\item Results
-\end{enumerate}
-
-\section{Discussion}
-\begin{enumerate}
-\item Methodology is agnostic to the choice of surrogate.
-\item As required for a PCE, the uncertain parameters need not be independent. 
-\item Strategy depends on the application - methodology could be implemented 
-sequentially or adaptively. 
-\end{enumerate}
-
-\end{document}
+\label{sec:app}

### 2017-12-19 Paper/disc.tex
individual sections in the paper

\section{Discussion}
\label{sec:disc}

%\begin{enumerate}
%\item Methodology is agnostic to the choice of surrogate.
%\item As required for a PCE, the uncertain parameters need not be independent. 
%\item Strategy depends on the application - methodology could be implemented 
%sequentially or adaptively. 
%\end{enumerate}

### 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
separate background section
separate space for abstract

@@
 
+\thispagestyle{empty}
 \input{cover}
+
+\baselineskip=22pt
 
@@
 
+\input{abstract}
+\clearpage
+
 \input{intro}
+\bigskip
+\bigskip
 
-\section{Background}
-\subsection{DGSM}
-\[ 
-    \mu_i = E\left(\left( \frac{\partial \mathcal{G}}{\partial \theta_i}\right)^2\right)
-          \approx \hat\mu_i := \frac1N\sum_{j = 1}^N 
-                  \left(\frac{\partial \mathcal{G}(x_j)}{\partial \theta_i}\right)^2
-\]
-Can consider variance of $\hat\mu_i$.
+\input{bg}
+\bigskip
+\bigskip
 
-\subsection{Polynomial chaos}
-\section{Method}
+\input{method}
+\bigskip
+\bigskip
 
-\section{Motivating examples}
-\subsection{Borehole: Screening, Convergence, Verification}
-\subsection{Semilinear elliptic PDE: Screening, Convergence, Verification}
-\subsection{Nonlinear Oscillator: Screening, Convergence, Verification}
+\input{examples}
+\bigskip
+\bigskip
 
-\section{Application: Phonon Transport in a Si bar}
+\input{app}
+\bigskip
+\bigskip
 
-Seven uncertain parameters; well-established nominal values exist;
-\[
-   \theta_i \sim U(\bar\theta_i - \epsilon_i, \bar\theta_i + \epsilon_i), 
-   \quad \epsilon_i = 0.1 \bar\theta_i. 
-\]
-\begin{enumerate}
-\item Include all details pertaining to the MD simulation: system, simulation, 
-ensembles, etc. 
-\item Results
-\end{enumerate}
+\input{disc}
+\bigskip
+\bigskip
 
-\section{Discussion}
-\begin{enumerate}
-\item Methodology is agnostic to the choice of surrogate.
-\item As required for a PCE, the uncertain parameters need not be independent. 
-\item Strategy depends on the application - methodology could be implemented 
-sequentially or adaptively. 
-\end{enumerate}
+\input{ack}
+\bigskip
+\bigskip
+
+\bibliographystyle{unsrt}
+\bibliography{REFER}
+
+\clearpage
+
+\input{figures}
 

### 2017-12-19 Paper/bg.tex
working on dgsm background

\section{Background}
\label{sec:bg}

In this section, we provide a brief theoretical background to the
derivative-based global sensitivity approach and the polynomial chaos
expansion.

\subsection{Derivative-based global sensitivity}

The derivative-based global sensitivity analysis (DGSA) is performed by 
estimating a sensitivity measure~\cite{Kucherenko:2009} for each stochastic
parameter in a model or a function. The
sensitivity measure associated with a parameter, $\theta_i$, based on
the observable, $\mathcal{Y}$ is given as follows:

\be
\mu_i = \mathbb{E}\left[\left(\frac{\partial \mathcal{Y}(\bm{x})}{\partial \theta_i}\right)^{2}\right]
\label{eq:mu}
\ee

\noindent The derivative in the above equation is estimated using finite
difference as given below, and averaged using pseudo-random samples in
the uncertain parameter domain.

\be
\frac{\partial \mathcal{Y}(\bm{\theta}^{\ast})}{\partial \theta_i} =
 \lim_{\Delta\theta_i^{*}\to 0}
\frac{[\mathcal{Y}(\theta_1^{*},\ldots,\theta_{i-1}^{*},
\theta_i^{*}+\Delta\theta_i^{*},
\theta_{i+1}^{*},\ldots,\theta_d^{*}) - 
\mathcal{Y}(\bm{\theta}^{*})]}{\Delta\theta_i^{*}} 
\ee

\noindent The total number of model realizations or function evaluations
needed to
compute $\mu_i$ in a Euclidian space $\mathbb{R}^d$ using $N$ samples is
therefore, $N\times(d+1)$.

### 2017-12-23 Paper/bg.tex
working on the background section

@@
 In this section, we provide a brief theoretical background to the
-derivative-based global sensitivity approach and the polynomial chaos
+derivative-based global sensitivity measure and the polynomial chaos
 expansion.
@@
 
-\noindent The derivative in the above equation is estimated using finite
+The derivative in the above equation is estimated using finite
 difference as given below, and averaged using pseudo-random samples in
@@
 \mathcal{Y}(\bm{\theta}^{*})]}{\Delta\theta_i^{*}} 
+\label{eq:partial}
 \ee
 
-\noindent The total number of model realizations or function evaluations
+The total number of model realizations or function evaluations
 needed to
 compute $\mu_i$ in a Euclidian space $\mathbb{R}^d$ using $N$ samples is
-therefore, $N\times(d+1)$.
+therefore, $N\times(d+1)$. The derivative in Eq.~\ref{eq:partial} could be evaluated
+analytically in case the functional dependence of $\mathcal{Y}$ and $\theta_i$
+is known. Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
+compared to the uncertainty in $\theta_i$ which leads to a significant improvement
+over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
+using large increments.
+
+For parameters with continuous distributions, the upper bound on the total Sobol' sensitivity index
+can be expressed in terms of $\mu_i$, the Poincar\'e constant ($\mathcal{C}_i$) and the total 
+variance of the model output ($V$)~\cite{Lamboni:2013}:
+
+\be
+ST_i \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
+\label{eq:bound}
+\ee
+
+The upper bound in the above inequality is proportional to the product of $\mathcal{C}_i$
+and $\mu_i$. However, for the purpose of parameter screening as discussed later in
+Section~\ref{sec:method}, we consider a normalized product, $\hat{\mathcal{C}_i\mu_i}$:
+
+\be
+\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
+\ee
+
+The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability distribution of $\theta_i$.
+Table~\ref{tab:poincare} provides its value in the case of uniform and normal
+distributions.
+\bigskip
+
+\begin{table}[htbp]
+\renewcommand*{\arraystretch}{1.2}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+Distribution & $\mathcal{C}_i$ \\ \hline \hline 
+Uniform, $\mathcal{U}[a, b]$ & $(b-a)^{2}/\pi^2$ \\ 
+Normal, $\mathcal{N}(\mu,\sigma^2)$ & $\sigma^2$ \\ 
+\hline
+\end{tabular}
+\end{center}
+
+\caption{Poincare constant for the case of uniformly and normally distributed random
+parameters~\cite{Roustant:2014}.}
+\label{tab:poincare}
+\end{table}
+
+\subsection{Polynomial Chaos Expansion}
+
+As discussed earlier in Section~\ref{sec:intro}, the Polynomial Chaos Expansion (PCE)
+is one of the most commonly used surrogates for representing the dependence of a random
+observable ($\mathcal{Y}$) on independent uncertain or stochastic model parameters ($\bm{\theta}$).
+Considering a joint probability distribution of the components of ($\bm{\theta}$) as $\mathbb{P}(\bm{\theta})$,
+the following condition is imposed on $\mathcal{Y}$:
+
+\be
+\mathbb{E}[\mathcal{Y}^2] = \int_{\mathcal{D}_{\bm{\theta}}} \mathcal{Y}^2 \mathbb{P}(\bm{\theta}) 
+d\bm{\theta} < \infty
+\ee
+
+\noindent where $\mathcal{D}_{\bm{\theta}}$ is the domain of the input parameter space. The PCE of
+$\mathcal{Y}$ is a mean-square convergent truncated summation given as
+follows~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}:
+
+\be
+\mathcal{Y} = \sum_{\alpha\in\mathcal{I}} c_{\alpha}\Psi_{\alpha}(\bm{\xi(\theta)}) 
+\ee
+
+Note that the set of parameters, $\bm{\theta}$ are parameterized in terms of canonical random
+variables, $\bm{\xi}$ in the above expansion. $\Psi_{\alpha}$'s are multivariate polynomial
+basis, orthonormal with respect to the joint probability distribution of $\bm{\xi}$, $\mathcal{I}$
+is the multi-index set which identifies the degree of individual polynomials in each term in the
+multivariate basis.
+
+Computational strategies available for estimating the PC coefficients ($c_\alpha$'s) typically involve
+techniques based on projection or regression. Projection-based methods rely on numerical
+quadrature for estimating the following expectation:
+
+\be
+\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\mathcal{Y}]
+\approx
+\sum_{i=1}^{N} \mathcal{Y}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
+\ee
+
+Regression-based methods such as least angle regression (LAR)~\cite{Efron:2004} and least absolute shrinkage
+and selection operator (LASSO)~\cite{Tibshirani:1996} aim to construct a sparse PCE~\cite{Blatman:2008}
+by solving a regularized optimization problem:
+
+\be
+\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{x}) -
+\mathcal{M}(\bm{x})\right)^{2}\right]  + \lambda\norm{\bm{c}}
+\ee
+
+In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
+a general purpose Uncertainty Quantification software developed at ETH Zurich in Switzerland.

### 2017-12-23 Paper/bg.tex
working on background

@@
 
+The regularization term forces the minimization towards low-rank solutions.
 In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
-a general purpose Uncertainty Quantification software developed at ETH Zurich in Switzerland.
+a general purpose uncertainty quantification software developed at ETH Zurich in Switzerland.

### 2017-12-25 Codes/Elliptic_PDE/ub1_conv.m
updated files in the elliptic pde example

@@ -20,15 +20,16 @@ for i = 1:dim
 end
 
 % Construct the set of samples based on the highest number i.e. 20
-S = zeros(20,dim);
+tsams = 20;
+S = zeros(tsams,dim);
  for j = 1:dim
-        S(:,j) = unifrnd(L(j,1),U(j,1),20,1);
+        S(:,j) = unifrnd(L(j,1),U(j,1),tsams,1);
  end
 
  % Evaluate model for the set S offline
  G = model_elliptic(S);
  
-for nsams = 5:5:20
+for nsams = 5:5:tsams
     Gdx = zeros(nsams,dim);
     
     for i = 1:dim

### 2017-12-25 Codes/MD/plot_time_lx.py
script for plotting length as a function of time for npt

@@ -1,0 +1,40 @@
+import argparse
+import numpy as np
+import matplotlib
+matplotlib.use('pdf')
+from matplotlib import pyplot as plt
+from matplotlib import mlab
+from matplotlib import rc
+
+rc('text', usetex=True)
+
+def main():
+  parser = argparse.ArgumentParser()
+  parser.add_argument('log_sw_file',help='name of sw log-file')
+  args = parser.parse_args()
+  f1 = open(args.log_sw_file,'r')
+  f2 = open(args.log_sw_file,'r') # total number of rows in the log file
+
+# Extract lx from the log file
+  data_1 = f2.readlines()
+  lx_npt = np.zeros((50,2))
+  for i in range(np.array(data_1).shape[0]):
+    row = f1.readline()
+    if "{tnpt}" in row:
+      for n_skip in range(4):
+        line_skip = f1.readline()
+      for k in range(lx_npt.shape[0]):
+        lx_data = f1.readline()
+        p  = lx_data.split()
+        lx_npt[k,0] = float(p[0])
+        lx_npt[k,1] = float(p[1])
+
+  fig = plt.figure()
+  ax = fig.add_subplot(111)
+  ax.plot(lx_npt[:,0],lx_npt[:,1],lw=2.0)
+  ax.set_xlabel(r'$\mathrm{Number~of~Steps}$',fontsize=15)
+  ax.set_ylabel(r'$\mathrm{L_x (\AA)}$',fontsize=15)
+  fig.savefig('lx_npt.pdf')
+
+if __name__ == "__main__":
+  main()

### 2017-12-26 Codes/MD/compute_k.m
working on the MD app

@@ -1,0 +1,31 @@
+close all;
+clear all;
+
+q1_1 = -17406.122;
+q1_2 = 17396.757;
+q2_1 = -19072.368;
+q2_2 = 19058.147;
+
+q1_avg = (abs(q1_1)+abs(q1_2))./2.0;
+q2_avg = (abs(q2_1)+abs(q2_2))./2.0;
+dt = 0.0005;
+ps2s = 1e-12;
+lc = 5.43;
+ang2m = 1e-10;
+w = 22.*lc;
+l1 = 50.*lc;
+l2 = 50.*lc;
+ld = 500000;
+ev2j = 1.609e-19;
+
+q1 = (q1_avg*ev2j)./(2.0.*dt.*ld.*ps2s.*w.*w.*ang2m.*ang2m);
+%dTdx1 = 50./((l1./2).*ang2m);
+cte1 = 1.5938;
+dTdx1 = cte1./(lc.*ang2m);
+cte2 = 1.5938;
+dTdx2 = cte2./(lc.*ang2m);
+q2 = (q2_avg*ev2j)./(2.0.*dt.*ld.*ps2s.*w.*w.*ang2m.*ang2m);
+%dTdx2 = 50./((l2./2).*ang2m);
+
+k1 = q1./dTdx1;
+k2 = q2./dTdx2;

### 2017-12-26 Codes/MD/k_from_MD.py

@@ -1,0 +1,70 @@
+import numpy as np
+import matplotlib
+matplotlib.use('pdf')
+from matplotlib import pyplot as plt
+from matplotlib import mlab
+from matplotlib import rc
+
+import yaml
+import argparse
+import math
+
+rc('text', usetex=True)
+
+if __name__ == "__main__":
+
+  parser = argparse.ArgumentParser()
+  parser.add_argument('input_params',help='name of yml input file')
+  parser.add_argument('energy_file',help='data file with exchange energies')
+  args = parser.parse_args()
+  input_params = yaml.load(open(args.input_params).read())
+  lc = 5.43 # Lattice constant in Ang
+  dt = input_params["dt"]
+  ld = input_params["ld"]
+  W = input_params["w"]
+  W = W*lc
+  L = 50*lc
+  dTdx = 1.5938/lc
+  eV_to_J = 1.602e-19
+  ang_to_m = 1.0e-10
+  ps_to_s = 1.0e-12
+  energy_file = args.energy_file
+  f1 = open(energy_file,'r')
+  data = f1.readlines()
+  nr = np.array(data).shape[0]
+  idx,e1,e2 = [],[],[]
+  k_data = np.zeros((nr,2))
+  for line in data:
+    p = line.split()
+    idx.append(float(p[0]))
+    e1.append(float(p[1]))
+    e2.append(float(p[2]))
+    idxv,e1v,e2v = np.array(idx),np.array(e1),np.array(e2)
+  k_data[:,0] = idxv
+
+  e_avg,k = np.zeros((nr,1)),np.zeros((nr,1))
+  e_avg[:,0] = [0.5*(abs(e1v[i])+abs(e2v[i])) for i in range(nr)]
+
+  for i in range(nr):
+   dq = float((e_avg[i,0]*eV_to_J))/float(2.0*dt*ld*ps_to_s*W*W*pow(ang_to_m,2))
+   k[i,0] = float(dq*ang_to_m)/float(dTdx)
+
+  k_data[:,1] = k[:,0]
+  np.savetxt('k_data.txt',k_data,fmt='%d %5.4f')
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2017-12-26 Codes/MD/ub.m

@@ -1,0 +1,38 @@
+close all;
+clear all;
+rng(100);
+
+dim = 7;
+dX = zeros(dim,1); pc = zeros(dim,1);
+mu = zeros(dim,1); ub = zeros(dim,1);
+L = zeros(dim,1); U = zeros(dim,1);
+
+% Nominal values of the parameters
+A = 7.049556277; B = 0.6022245584;
+p = 4.0; q = 0.0; alpha = 1.80;
+lambda = 21.0; gamma = 1.20;
+
+N = [A;B;p;q;alpha;lambda;gamma];
+L(:,1) = 0.9.*N(:); % lower-bound
+U(:,1) = 1.1.*N(:); % upper-bound
+
+for j = 1:dim
+  dX(i) = 1e-5.*(U(i,1)-L(i,1));
+  pc(j) = ((U(i,1)-L(i,1)).^2)./(pi.^2);
+end
+
+nsams = 5;
+G = zeros(nsams,1); Gdx = zeros(nsams,dim);
+G(:,1) = k_data(1:nsams,2);
+
+for j = 1:dim
+  Gdx(:,j) = k_data(j*nsams+1:(j+1)*nsams,2);
+  dGdx = (Gdx(:,j) - G(:,1))./dX(j);
+  dGdx2 = dGdx.^2;
+  T = sum(dGdx2);
+  nu(j) = T./nsams;
+  ub(j) = pc(j).*nu(j);
+end
+
+ub(1:dim) = ub(1:dim)./sum(ub);
+

### 2017-12-26 Codes/MD/compute_k.m
working on the MD app

@@ -16,7 +16,7 @@ w = 22.*lc;
 l1 = 50.*lc;
 l2 = 50.*lc;
 ld = 500000;
-ev2j = 1.609e-19;
+ev2j = 1.602e-19;
 
 q1 = (q1_avg*ev2j)./(2.0.*dt.*ld.*ps2s.*w.*w.*ang2m.*ang2m);
 %dTdx1 = 50./((l1./2).*ang2m);

### 2017-12-26 Codes/MD/gen_samples.m

@@ -15,7 +15,7 @@ N = [A;B;p;q;alpha;lambda;gamma];
 L(:,1) = 0.9.*N(:); % lower-bound
 U(:,1) = 1.1.*N(:); % upper-bound
 ts = 20; % total number of samples
-ns = 5; % subset of samples
+ns = 10; % subset of samples
 U(4,1) = 0.1;
 
 S = zeros(ts,dim);

### 2017-12-26 Codes/MD/k_from_MD.py

@@ -48,6 +48,8 @@ if __name__ == "__main__":
   for i in range(nr):
    dq = float((e_avg[i,0]*eV_to_J))/float(2.0*dt*ld*ps_to_s*W*W*pow(ang_to_m,2))
    k[i,0] = float(dq*ang_to_m)/float(dTdx)
+  
+  print (k)
 
   k_data[:,1] = k[:,0]
   np.savetxt('k_data.txt',k_data,fmt='%d %5.4f')

### 2017-12-26 Codes/MD/ub.m

@@ -1,38 +1,0 @@
-close all;
-clear all;
-rng(100);
-
-dim = 7;
-dX = zeros(dim,1); pc = zeros(dim,1);
-mu = zeros(dim,1); ub = zeros(dim,1);
-L = zeros(dim,1); U = zeros(dim,1);
-
-% Nominal values of the parameters
-A = 7.049556277; B = 0.6022245584;
-p = 4.0; q = 0.0; alpha = 1.80;
-lambda = 21.0; gamma = 1.20;
-
-N = [A;B;p;q;alpha;lambda;gamma];
-L(:,1) = 0.9.*N(:); % lower-bound
-U(:,1) = 1.1.*N(:); % upper-bound
-
-for j = 1:dim
-  dX(i) = 1e-5.*(U(i,1)-L(i,1));
-  pc(j) = ((U(i,1)-L(i,1)).^2)./(pi.^2);
-end
-
-nsams = 5;
-G = zeros(nsams,1); Gdx = zeros(nsams,dim);
-G(:,1) = k_data(1:nsams,2);
-
-for j = 1:dim
-  Gdx(:,j) = k_data(j*nsams+1:(j+1)*nsams,2);
-  dGdx = (Gdx(:,j) - G(:,1))./dX(j);
-  dGdx2 = dGdx.^2;
-  T = sum(dGdx2);
-  nu(j) = T./nsams;
-  ub(j) = pc(j).*nu(j);
-end
-
-ub(1:dim) = ub(1:dim)./sum(ub);
-

### 2017-12-26 Codes/MD/write_params.m

@@ -1,0 +1,10 @@
+
+fid = fopen('params_2_5.txt','w');
+fmt = '%14.8f %14.8f %14.8f %14.8f %14.8f %14.8f %14.8f\n';
+
+for i = 1:40
+  fprintf(fid,fmt,params_2_5(i,1),params_2_5(i,2),params_2_5(i,3),params_2_5(i,4),...
+                  params_2_5(i,5),params_2_5(i,6),params_2_5(i,7));  
+end
+
+fclose(fid);

### 2017-12-26 Codes/MD/screen.m
working on MD app

@@ -1,0 +1,40 @@
+close all;
+clear all;
+rng(100);
+
+dim = 7;
+dX = zeros(dim,1); pc = zeros(dim,1);
+mu = zeros(dim,1); ub = zeros(dim,1);
+L = zeros(dim,1); U = zeros(dim,1);
+k_data = load('k_data.txt');
+
+% Nominal values of the parameters
+A = 7.049556277; B = 0.6022245584;
+p = 4.0; q = 0.0; alpha = 1.80;
+lambda = 21.0; gamma = 1.20;
+
+N = [A;B;p;q;alpha;lambda;gamma];
+L(:,1) = 0.9.*N(:); % lower-bound
+U(:,1) = 1.1.*N(:); % upper-bound
+U(4,1) = 0.1;
+
+for j = 1:dim
+  dX(j) = 1e-5.*(U(j,1)-L(j,1));
+  pc(j) = ((U(j,1)-L(j,1)).^2)./(pi.^2);
+end
+
+nsams = 5;
+G = zeros(nsams,1); Gdx = zeros(nsams,dim);
+G(:,1) = k_data(1:nsams,2);
+
+for j = 1:dim
+  Gdx(:,j) = k_data(j*nsams+1:(j+1)*nsams,2);
+  dGdx = (Gdx(:,j) - G(:,1))./dX(j);
+  dGdx2 = dGdx.^2;
+  T = sum(dGdx2);
+  mu(j) = T./nsams;
+  ub(j) = pc(j).*mu(j);
+end
+
+ub(1:dim) = ub(1:dim)./sum(ub);
+

### 2017-12-27 Codes/Elliptic_PDE/elliptic.m
compare PCE convergence using same set of samples

@@ -70,19 +70,19 @@ cpu_time = cputime - t;
 % Generate a set of pdf evaluations of the observable for comparison with
 % the 3D case
 
-dim = 4; % dimension
-nsams = 1e6; % number of points at which the pdf needs to be evaluated
-
-S = zeros(nsams,dim);
-for j = 1:dim
-    L = IOpts.Marginals(j).Parameters(1);
-    U = IOpts.Marginals(j).Parameters(2);
-    S(:,j) = unifrnd(L,U,nsams,1);
-end
-
-Y_PCE4D = uq_evalModel(S);
-save('valpts_pdf.mat','S');
-save('y4d.mat','Y_PCE4D');
+%dim = 4; % dimension
+%nsams = 1e6; % number of points at which the pdf needs to be evaluated
+%
+%S = zeros(nsams,dim);
+%for j = 1:dim
+%    L = IOpts.Marginals(j).Parameters(1);
+%    U = IOpts.Marginals(j).Parameters(2);
+%    S(:,j) = unifrnd(L,U,nsams,1);
+%end
+%
+%Y_PCE4D = uq_evalModel(S);
+%save('valpts_pdf.mat','S');
+%save('y4d.mat','Y_PCE4D');
 
 
 

### 2017-12-28 Paper/bg.tex
working on the borehole subsection

@@
 \noindent where $\mathcal{D}_{\bm{\theta}}$ is the domain of the input parameter space. The PCE of
-$\mathcal{Y}$ is a mean-square convergent truncated summation given as
+$\mathcal{Y}$ ($\mathcal{Y}^{\mbox{\tiny {PC}}}$) is a mean-square 
+convergent truncated summation given as
 follows~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}:
@@
 \be
-\mathcal{Y} = \sum_{\alpha\in\mathcal{I}} c_{\alpha}\Psi_{\alpha}(\bm{\xi(\theta)}) 
+\mathcal{Y}^{\mbox{\tiny M}} \approx \mathcal{Y}^{\mbox{\tiny PC}} = 
+\sum_{\alpha\in\mathcal{I}} c_{\alpha}\Psi_{\alpha}(\bm{\xi(\theta)}) 
 \ee
 
+\noindent where $\mathcal{Y}^{\mbox{\tiny M}}$ corresponds to realizations of the
+observable using the original (typically physics-based) model. 
 Note that the set of parameters, $\bm{\theta}$ are parameterized in terms of canonical random
@@
 
+\noindent where $w^{(i)}$ denotes the weight associated with the quadrature node $i$. 
 Regression-based methods such as least angle regression (LAR)~\cite{Efron:2004} and least absolute shrinkage
@@
 \hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{x}) -
-\mathcal{M}(\bm{x})\right)^{2}\right]  + \lambda\norm{\bm{c}}
+\mathcal{M}(\bm{x})\right)^{2}\right]  + \lambda\normone{\bm{c}}
 \ee
 
+\noindent where $\normone{\bm{c}}$ = $\sum_{\alpha\in \mathcal{I}} |c_\alpha |$.
 The regularization term forces the minimization towards low-rank solutions.

### 2017-12-28 Paper/examples.tex
working on the borehole subsection

\section{Motivating Examples}
\label{sec:examples}

In Section~\ref{sec:method}, we presented a methodology for screening model
parameters using an approximate estimate of the upper bound on the Sobol'
total effect sensitivity index. The screening process helped identify parameters
that are relatively insignificant with respect to the observable. These insignificant
parameters could thus be fixed at their nominal values thereby reducing the
dimensionality of the problem.

In this section, we motivate this approach based
on parameter screening to construct low-dimensional PC surrogates by 
applying it to simple test problems: (1) Borehole function, (2) Non-linear Oscillator, and
(3) Semi-linear Elliptic PDE. Since model evaluations in all these test
problems are not expensive, it allows us to compare relative importance of
model parameters,
obtained using the derivative-based sensitivity approach with that obtained
using converged estimates of Sobol' total effect sensitivity index~\cite{Sobol:2001}.
Additionally, we compare convergence of the PC Surrogates, constructed in
the full and the reduced space, based on the 
leave-one-out-cross-validation error ($\epsilon_{\mbox{\tiny LOO}}$), defined
as follows~\cite{Blatman:2010}:

\be
\epsilon_{\mbox{\tiny LOO}} = 
\frac{\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
 \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\theta}_i)\right)^2}
{\sum_{i=1}^N
\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
\label{eq:loo}
\ee

\noindent where $\widetilde{\mu}~=~\frac{1}{N}\sum_{i=1}^N \mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i)$
is the sample mean of the model response, and $ \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$
is the PCE surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
From Eq.~\ref{eq:loo}, it appears that $N$ PCE's are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
independent of $\mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$ is used.

\subsection{Borehole function}

The borehole function is a benchmark reference problem in sensitivity analysis. It models the discharge
of water ($\mathcal{Q}$) through a borehole in terms of geometrical and physical parameters:

\be
\mathcal{Q} = \frac{2\pi T_u(H_u - H_l)}{\ln\left(\frac{r}{r_w}\right)\left(1 +
\frac{2LT_u}{\ln\left(\frac{r}{r_w}\right)r_w^2K_w} + \frac{T_u}{T_l}\right)}
\label{eq:bore}
\ee

\noindent The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the RHS of Eq.~\ref{eq:bore} are considered as uncertain. Table~\ref{tab:bore} provides
marginal distributions of the uncertain parameters.

\begin{table}[htbp]
\renewcommand*{\arraystretch}{1.2}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Parameter & Distribution \\ \hline \hline
$r_w$ (Borehole radius, m) & $\mathcal{N}$(0.1,0.016) \\
$L$ (Borehole length, m) & $\mathcal{U}$[1120,1680] \\
$T_u$ (Transmissivity of upper aquifer, m$^2$/yr) & $\mathcal{U}$[63070,115600] \\
$H_u$ (Potentiometric head of upper aquifer, m) & $\mathcal{U}$[990,1110] \\
$T_l$ (Transmissivity of lower aquifer, m$^2$/yr) & $\mathcal{U}$[63.1,116] \\
$H_l$ (Potentiometric head of lower aquifer, m) & $\mathcal{U}$[700,820] \\
$K_w$ (Borehole hydraulic conductivity, m/yr) & $\mathcal{U}$[9855,12045] \\
\hline
\end{tabular}
\end{center}

\caption{Description and marginal distributions of uncertain parameters in the borehole function
given by Eq.~\ref{eq:bore}.}
\label{tab:bore}
\end{table}

Since function evaluations of the discharge using Eq.~\ref{eq:bore} are quite cheap, the converged
estimates of Sobol' total effect sensitivity index can be easily computed.

### 2017-12-28 Codes/Borehole/test_borehole.m
added a fig on total sensitivity for borehole

@@ -55,22 +55,41 @@ PCESobolAnalysis = uq_createAnalysis(SobolOpts);
 PCESobolResults = PCESobolAnalysis.Results;
 STi = PCESobolResults.Total;
 
+% Plot Sobol indices
+uq_figure('Position', [50 50 500 400])
+cm = colormap;
+uq_bar(1:7,PCESobolResults.Total, 0.25,'facecolor', cm(1,:), 'edgecolor', 'none');
+ylabel('$$\mathrm{Sobol~Total~Effect~Index}$$','interpreter','latex');
+xlabel('$$\mathrm{Parameter}$$','interpreter','latex');
+ylim([0 1]);
+xlim([0 8]);
+xticklabels({'$$\mathrm{r_w}$$','$$\mathrm{T_u}$$','$$\mathrm{H_u}$$','$$\mathrm{T_l}$$',...
+                '$$\mathrm{H_l}$$','$$\mathrm{L}$$','$$\mathrm{K_w}$$'});
+set(gca, 'xtick', 1:length(IOpts.Marginals), 'xticklabel',...
+    xticklabels, 'fontsize',14);
+set(gca,'TickLabelInterpreter','latex');
+grid off;
+set(gcf,'color',[1,1,1]);
+box on;
+
+print -depsc sense_borehole.eps
+
 % Compute UB1 for all variables
-X = myPCE.ExpDesign.X;
-dim = size(X,2);
-nsam = size(X,1);
-V = myPCE.PCE.Moments.Var;
-dX = zeros(dim,1); pc = zeros(dim,1);
-dX(1) = 1e-6; pc(1) = 0.0161812.^2;
-for i = 2:dim
-    lim = IOpts.Marginals(i).Parameters;
-    dX(i) = 1e-5.*(lim(2) - lim(1));
-    pc(i) = (1./(pi.^2)).*((lim(2)-lim(1)).^2);
-end
+%X = myPCE.ExpDesign.X;
+%dim = size(X,2);
+%nsam = size(X,1);
+%V = myPCE.PCE.Moments.Var;
+%dX = zeros(dim,1); pc = zeros(dim,1);
+%dX(1) = 1e-6; pc(1) = 0.0161812.^2;
+%for i = 2:dim
+%    lim = IOpts.Marginals(i).Parameters;
+%    dX(i) = 1e-5.*(lim(2) - lim(1));
[…]

### 2017-12-28 Codes/Elliptic_PDE/elliptic.m

@@ -32,10 +32,16 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 25;
+PCEOpts.ExpDesign.NSamples = 20;
 t = cputime;
 myPCE = uq_createModel(PCEOpts);
 cpu_time = cputime - t;
+
+X = myPCE.ExpDesign.X;
+Y = myPCE.ExpDesign.Y;
+XS = X(:,2:4);
+save('X20.dat','XS','-ASCII');
+save('Y20.dat','Y','-ASCII');
 
 % ========================================================================
 % Compute Sobol Indices

### 2017-12-28 Paper/examples.tex
working on the borehole example

@@
 obtained using the derivative-based sensitivity approach with that obtained
-using converged estimates of Sobol' total effect sensitivity index~\cite{Sobol:2001}.
-Additionally, we compare convergence of the PC Surrogates, constructed in
-the full and the reduced space, based on the 
+using converged estimates of Sobol' total effect sensitivity index, $\mathcal{T}(\theta_i)$~\cite{Sobol:2001}:
+
+\be
+\mathcal{T}(\theta_i) = 
+\frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})}
+\ee
+
+\noindent $\mathcal{T}(\theta_i)$ is essentially the ratio of the contribution to the variance of an
+observable $\mathcal{G}$ by the parameter $\theta_i$ to the total variance of $\mathcal{G}$.
+Additionally, we compare convergence of the PCE constructed in
+the full parameter space with those constructed in the reduced space. To assess convergence, 
+we rely on the 
 leave-one-out-cross-validation error ($\epsilon_{\mbox{\tiny LOO}}$), defined
@@
 
-Since function evaluations of the discharge using Eq.~\ref{eq:bore} are quite cheap, the converged
-estimates of Sobol' total effect sensitivity index can be easily computed.
+As mentioned earlier in this section, cheap function evaluations of the discharge using 
+Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
+Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
+parameters in the borehole function.

### 2017-12-28 Codes/Borehole/test_borehole.m
sensitivity plot y-label updated

@@ -59,7 +59,7 @@ STi = PCESobolResults.Total;
 uq_figure('Position', [50 50 500 400])
 cm = colormap;
 uq_bar(1:7,PCESobolResults.Total, 0.25,'facecolor', cm(1,:), 'edgecolor', 'none');
-ylabel('$$\mathrm{Sobol~Total~Effect~Index}$$','interpreter','latex');
+ylabel('$$\mathrm{\mathcal{T}(\theta_i)}$$','interpreter','latex');
 xlabel('$$\mathrm{Parameter}$$','interpreter','latex');
 ylim([0 1]);
 xlim([0 8]);

### 2017-12-28 Paper/bg.tex
working on the borehole example
work in progess

@@
 
-For parameters with continuous distributions, the upper bound on the total Sobol' sensitivity index
+For parameters with continuous distributions, the upper bound on the total 
+Sobol' sensitivity index ($\mathcal{T}(\theta_i)$)
 can be expressed in terms of $\mu_i$, the Poincar\'e constant ($\mathcal{C}_i$) and the total 
@@
 \be
-ST_i \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
+\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
 \label{eq:bound}
@@
 \hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
+\label{eq:cmu}
 \ee
@@
 \be
-\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\mathcal{Y}]
+\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\mathcal{Y}^{\mbox{\tiny{M}}}]
 \approx
-\sum_{i=1}^{N} \mathcal{Y}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
+\sum_{i=1}^{N} \mathcal{Y}^{\mbox{\tiny{M}}}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
 \ee
@@
 \be
-\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{x}) -
-\mathcal{M}(\bm{x})\right)^{2}\right]  + \lambda\normone{\bm{c}}
+\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{\bm{\xi(\theta)}}) -
+\mathcal{Y}^{\mbox{\tiny{M}}}(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
 \ee

### 2017-12-29 Codes/Borehole/gen_plots_borehole.m
ub vs samples plot for borehole

@@ -1,7 +1,52 @@
 close all;
 clear all;
+addpath(genpath('./line_fewer_markers_v4/'));
 
-err_samples();
+%err_samples();
+ub_conv();
+
+function ubc = ub_conv()
+data_ub = load('nsams_ub.txt');
+%data_sti = load('STi_conv.mat');
+col = ['c','r','b','m','g','k'];
+ls = ['-','-.','--','-s','-d',':','-*'];
+
+figure
+hold on;
+%for i = 1:7
+%plot(data_ub(:,1),data_ub(:,i+1),'LineWidth',2,'color',col(i));
+%plot(data_ub(:,1),data_ub(:,2),'LineWidth',1.5,'color',[0 0 0]);
+%plot(data_ub(:,1),data_ub(:,3),':','LineWidth',1.5,'color',[0 0 0]);
+%plot(data_ub(:,1),data_ub(:,4),'-.','LineWidth',1.5,'color',[0 0 0]);
+%plot(data_ub(:,1),data_ub(:,5),':','LineWidth',1.5,'color',[0 0 0]);
+%plot(data_ub(:,1),data_ub(:,6),'-.','LineWidth',1.5,'color',[0 0 0]);
+%plot(data_ub(:,1),data_ub(:,7),'-.','LineWidth',1.5,'color',[0 0 0]);
+line_fewer_markers(data_ub(:,1),data_ub(:,2),20,':ko','MarkerSize',6,'MarkerFaceColor','k');
+plot(data_ub(:,1),data_ub(:,3),'--k');
+line_fewer_markers(data_ub(:,1),data_ub(:,4),20,':ks','MarkerSize',6,'MarkerFaceColor','k');
+plot(data_ub(:,1),data_ub(:,5),'--k');
+line_fewer_markers(data_ub(:,1),data_ub(:,6),20,':ks','MarkerSize',6,'MarkerFaceColor','k');
+%line_fewer_markers(data_ub(:,1),data_ub(:,7),10,':kd','MarkerSize',4,'MarkerFaceColor','k');
+plot(data_ub(:,1),data_ub(:,7),'-.k');
+line_fewer_markers(data_ub(:,1),data_ub(:,8),20,':k*','MarkerSize',6);
+%line_fewer_markers(t, sin(3*t).*cos(t/2), 10, 'p-');
+%end
+
+hold off;
+xlabel('$$\mathrm{Number~of~Samples}$$','interpreter','latex');
[…]

### 2017-12-29 Codes/Borehole/test_borehole.m

@@ -44,41 +44,41 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 300;
+PCEOpts.ExpDesign.NSamples = 500;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices
-SobolOpts.Type = 'Sensitivity';
-SobolOpts.Method = 'Sobol';
-SobolOpts.Sobol.SampleSize = 1e5;
-PCESobolAnalysis = uq_createAnalysis(SobolOpts);
-PCESobolResults = PCESobolAnalysis.Results;
-STi = PCESobolResults.Total;
-
-% Plot Sobol indices
-uq_figure('Position', [50 50 500 400])
-cm = colormap;
-uq_bar(1:7,PCESobolResults.Total, 0.25,'facecolor', cm(1,:), 'edgecolor', 'none');
-ylabel('$$\mathrm{\mathcal{T}(\theta_i)}$$','interpreter','latex');
-xlabel('$$\mathrm{Parameter}$$','interpreter','latex');
-ylim([0 1]);
-xlim([0 8]);
-xticklabels({'$$\mathrm{r_w}$$','$$\mathrm{T_u}$$','$$\mathrm{H_u}$$','$$\mathrm{T_l}$$',...
-                '$$\mathrm{H_l}$$','$$\mathrm{L}$$','$$\mathrm{K_w}$$'});
-set(gca, 'xtick', 1:length(IOpts.Marginals), 'xticklabel',...
-    xticklabels, 'fontsize',14);
-set(gca,'TickLabelInterpreter','latex');
-grid off;
-set(gcf,'color',[1,1,1]);
-box on;
-
-print -depsc sense_borehole.eps
+%SobolOpts.Type = 'Sensitivity';
+%SobolOpts.Method = 'Sobol';
+%SobolOpts.Sobol.SampleSize = 1e5;
+%PCESobolAnalysis = uq_createAnalysis(SobolOpts);
+%PCESobolResults = PCESobolAnalysis.Results;
+%STi = PCESobolResults.Total;
+%
+%% Plot Sobol indices
+%uq_figure('Position', [50 50 500 400])
+%cm = colormap;
[…]

### 2017-12-29 Codes/Borehole/ub1_conv.m

@@ -1,0 +1,53 @@
+% This script computes and writes ubber bounds on total sobol indices for a
+% range of sample size.
+
+close all;
+clear all;
+rng(100);
+
+fid = fopen('nsams_ub.txt','w');
+fmt = '%d %5.4f %5.4f %5.4f %5.4f %5.4f %5.4f %5.4f\n';
+dim = 7;
+dX = zeros(dim,1); pc = zeros(dim,1);
+nu = zeros(dim,1); ub1 = zeros(dim,1);
+L = [0.1;63070;990;63.1;700;1120;9855];
+U = [0.2;115600;1110;116;820;1680;12045];
+
+for i = 1:dim
+    dX(i) = 1e-5.*(U(i)-L(i));
+    pc(i) = ((U(i)-L(i)).^2)./(pi.^2);
+end
+
+pc(1) = 0.0161812.^2;
+
+% Construct the set of samples based on the highest number i.e. 20
+tsams = 500;
+%S = zeros(tsams,dim);
+% for j = 1:dim
+%        S(:,j) = unifrnd(L(j,1),U(j,1),tsams,1);
+% end
+
+S = load('S.mat');
+
+ % Evaluate model for the set S offline
+G = uq_borehole(S.X);
+ 
+for nsams = 5:5:tsams
+    Gdx = zeros(nsams,dim);
+    
+    for i = 1:dim
+        S_new = S.X(1:nsams,:);
+        S_new(:,i) = S_new(:,i) + dX(i);
+        Gdx(:,i) = uq_borehole(S_new);
+        dGdx = (Gdx(:,i) - G(1:nsams,1))./dX(i);
+        dGdx2 = dGdx.^2;
+        T = sum(dGdx2);
+        nu(i) = T./nsams;
+        ub1(i) = pc(i).*nu(i);
+    end
+    ub1(1:dim) = ub1(1:dim)./sum(ub1);
+    fprintf(fid,fmt,nsams,ub1(1),ub1(2),ub1(3),ub1(4),ub1(5),ub1(6),ub1(7));
+    %fprintf(fid,'\n');
+end
+
+fclose(fid);

### 2017-12-29 Paper/examples.tex
work in progess
added screening plot for borehole

@@
 Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
-parameters in the borehole function.
+parameters in the borehole function using 10$^6$ pseudo-random
+samples in the input parameter domain. These estimates are used to verify fidelity of
+parameter screening based on the methodology presented in Section~\ref{sec:method}. 
+In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
+for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.
+Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
+even when small number of samples are used to estimate the expectation in Eq.~\ref{eq:mu}. 
+Consequently, the relative importance of uncertain 
+parameters in the borehole function is found to be consistent with predictions based on the Sobol' index.

### 2017-12-30 Paper/examples.tex
work in progress

@@
 Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
-even when small number of samples are used to estimate the expectation in Eq.~\ref{eq:mu}. 
+even when small number of samples (5 -- 10) are used to estimate the expectation in Eq.~\ref{eq:mu}. 
 Consequently, the relative importance of uncertain 
 parameters in the borehole function is found to be consistent with predictions based on the Sobol' index. 
+In the considered intervals for the uncertain parameters, it is clear that the discharge is insensitive to
+$T_u$ and $T_l$. Moreover, the sensitivity towards $K_w$ is also small. We exploit this result by 
+discounting the uncertainties in $T_u$, $T_l$, and $K_w$ while using nominal values for these
+parameters instead.

### 2017-12-30 Paper/examples.tex
work in progress

@@
 parameters in the borehole function using 10$^6$ pseudo-random
-samples in the input parameter domain. These estimates are used to verify fidelity of
+samples\footnote{Although $\mathcal{T}(\theta_i)$ 
+might converge with much fewer samples depending upon the model, we consider a large number that
+typically ensures a converged estimate for the purpose of illustration.} in the input parameter domain. 
+These estimates are used to verify fidelity of
 parameter screening based on the methodology presented in Section~\ref{sec:method}. 
@@
 Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
-even when small number of samples (5 -- 10) are used to estimate the expectation in Eq.~\ref{eq:mu}. 
+even when small number of samples (5 -- 10) are used. 
 Consequently, the relative importance of uncertain 
@@
 In the considered intervals for the uncertain parameters, it is clear that the discharge is insensitive to
-$T_u$ and $T_l$. Moreover, the sensitivity towards $K_w$ is also small. We exploit this result by 
-discounting the uncertainties in $T_u$, $T_l$, and $K_w$ while using nominal values for these
+$T_u$ and $T_l$. Moreover, the sensitivity towards $K_w$ is also small. We exploit this result to reduce
+the dimensionality of the problem by 
+discounting the uncertainties in $T_u$, $T_l$, and $K_w$, while using nominal values for these
 parameters instead.
+
+Our goal as discussed is to gain computational advantage by constructing surrogates in a 
+reduced input parameter space. To this end, we construct PCE's in 5D and 4D spaces by
+fixing $\{T_u,T_l\}$ in the former and additionally fixing $K_w$ in the latter at their respective
+mean values. In Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed
+in the full space (7D) with those constructed in the two reduced spaces (4D and 5D) using
+$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). As expected, it is observed that the PCE
+constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
+$\mathcal{O}(10^{-6})$ accuracy is sought, we need

### 2017-12-30 Codes/Borehole/borehole4D/borehole4D.m
PCE convergence plot updated

@@ -32,16 +32,16 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 10;
+PCEOpts.ExpDesign.NSamples = 80;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices
-SobolOpts.Type = 'Sensitivity';
-SobolOpts.Method = 'Sobol';
-SobolOpts.Sobol.SampleSize = 1e5;
-PCESobolAnalysis = uq_createAnalysis(SobolOpts);
-PCESobolResults = PCESobolAnalysis.Results;
-STi = PCESobolResults.Total;
+%SobolOpts.Type = 'Sensitivity';
+%SobolOpts.Method = 'Sobol';
+%SobolOpts.Sobol.SampleSize = 1e5;
+%PCESobolAnalysis = uq_createAnalysis(SobolOpts);
+%PCESobolResults = PCESobolAnalysis.Results;
+%STi = PCESobolResults.Total;
 
 % Compute UB1 for all variables
 X = myPCE.ExpDesign.X;

### 2017-12-30 Codes/Borehole/borehole5D/borehole5D.m

@@ -36,16 +36,16 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 60;
+PCEOpts.ExpDesign.NSamples = 80;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices
-SobolOpts.Type = 'Sensitivity';
-SobolOpts.Method = 'Sobol';
-SobolOpts.Sobol.SampleSize = 1e5;
-PCESobolAnalysis = uq_createAnalysis(SobolOpts);
-PCESobolResults = PCESobolAnalysis.Results;
-STi = PCESobolResults.Total;
+%SobolOpts.Type = 'Sensitivity';
+%SobolOpts.Method = 'Sobol';
+%SobolOpts.Sobol.SampleSize = 1e5;
+%PCESobolAnalysis = uq_createAnalysis(SobolOpts);
+%PCESobolResults = PCESobolAnalysis.Results;
+%STi = PCESobolResults.Total;
 
 % Compute UB1 for all variables
 X = myPCE.ExpDesign.X;

### 2017-12-30 Codes/Borehole/gen_plots_borehole.m

@@ -2,8 +2,8 @@ close all;
 clear all;
 addpath(genpath('./line_fewer_markers_v4/'));
 
-%err_samples();
-ub_conv();
+err_samples();
+%ub_conv();
 
 function ubc = ub_conv()
 data_ub = load('nsams_ub.txt');
@@ -49,7 +49,11 @@ print -depsc ub_conv_borehole.eps
 end
 
 function err = err_samples()
+%ns = [10;20;30;40;50;60;70;80];
 ns = [10;20;30;40;50];
+%err7D = [1.836;2.958e-1;1.864e-2;1.632e-2;1.934e-2;2.374e-3;2.319e-3;1.184e-3];
+%err5D = [4.018e-1;3.136e-1;1.629e-2;2.955e-2;2.345e-3;2.770e-3;4.879e-4;4.331e-4];
+%err4D = [1.135e-1;1.603e-1;7.151e-3;1.571e-3;1.519e-4;5.217e-5;3.378e-4;4.286e-6];
 err7D = [1.836;2.958e-1;1.864e-2;1.632e-2;1.934e-2];
 err5D = [4.018e-1;3.136e-1;1.629e-2;2.955e-2;2.345e-3];
 err4D = [1.135e-1;1.603e-1;7.151e-3;1.571e-3;1.519e-4];
@@ -60,9 +64,9 @@ err(:,3) = log10(err4D(:));
 
 figure
 hold on;
-plot(ns,err(:,1),'-o','color','k','linewidth',2);
-plot(ns,err(:,2),'-d','color','b','linewidth',2);
-plot(ns,err(:,3),'-s','color','r','linewidth',2);
+plot(ns,err(:,1),':ko','MarkerFaceColor','k');
+plot(ns,err(:,2),':kd','MarkerFaceColor','k');
+plot(ns,err(:,3),':ks','MarkerFaceColor','k');
 xlabel('$$\mathrm{Number~of~Samples}$$','interpreter','latex');
 ylabel('$$\mathrm{log_{10}(\epsilon_{LOO})}$$','interpreter','latex');
 xlim([8,52]);

### 2017-12-30 Codes/Borehole/test_borehole.m

@@ -44,7 +44,7 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 500;
+PCEOpts.ExpDesign.NSamples = 80;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices

### 2017-12-30 Paper/examples.tex
borehole in progress

@@
 
-In Section~\ref{sec:method}, we presented a methodology for screening model
+In section~\ref{sec:method}, we presented a methodology for screening model
 parameters using an approximate estimate of the upper bound on the Sobol'
@@
 \frac{\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
- \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\theta}_i)\right)^2}
+ \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
 {\sum_{i=1}^N
@@
 independent of $\mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
+
+The converged low-dimensional PCE is assessed
+for predictive accuracy. While several techniques could be used, we consider predictive verification
+in an L-2 sense as well as a probabilistic sense. In the former case, we estimate a relative L-2 norm
+of the error ($\epsilon_{\mbox{\tiny{L-2}}}$) as follows:
+
+\be
+\epsilon_{\mbox{\tiny{L-2}}} = 
+\frac{\left[\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
+ \mathcal{Y}^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
+{\left[\sum_{i=1}^N
+\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
+\label{eq:l2}
+\ee
+
+\noindent As discussed earlier in section~\ref{sec:method}, computational cost associated with
+L-2 verification is negligible since function evaluations or model realizations obtained during the
+screening step could be re-used.
+However, since the test problems are computationally inexpensive, we generate an independent
+set of samples ($\bm{\theta_i}$) to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}
+in each case.
+For the purpose of probabilistic verification, we compare the probability density function of
+the observable obtained using PCE's in the full space and the reduced space in the following
+test problems. In situations where model runs are computationally expensive, probabilistic verification might
+not be feasible.
 
@@
 constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
-$\mathcal{O}(10^{-6})$ accuracy is sought, we need
+$\mathcal{O}(10^{-4})$ accuracy is sought, we need function evaluations at only about
+50 sample points in the 4D parameter space whereas the number of samples needed in the full 
+7D space seems much higher.

### 2018-01-01 Codes/Borehole/borehole4D/borehole4D.m
L2 error computed for the  orehole example

@@ -32,7 +32,7 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 80;
+PCEOpts.ExpDesign.NSamples = 50;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices
@@ -58,6 +58,17 @@ end
 
 %ub1 = dgsm(dim,nsam,X,V,dX,pc);
 
+X7 = load('X7.mat');
+Y7 = load('Y7.mat');
+X7 = X7.X;
+Y7 = Y7.Y;
+X4 = zeros(size(X7,1),4);
+X4(:,1) = X7(:,1);
+X4(:,2) = X7(:,3);
+X4(:,3:4) = X7(:,5:6);
+
+errL2 = validate(X4,X7,Y7);
+
 function ub1 = dgsm(dim,nsam,X,V,dX,pc)
 G = uq_borehole(X);
 Gdx = zeros(nsam,dim);
@@ -76,7 +87,12 @@ for i = 1:dim
 end
 end
 
-
+function errv = validate(X4,X7,Y7)
+Y_PCE = uq_evalModel(X4);
+NR = sum(((Y7-Y_PCE).^2)).^(0.5);
+DR = sum((Y7.^2)).^(0.5);
+errv = double(NR)./double(DR);
+end
 
 
 

### 2018-01-01 Codes/Borehole/borehole5D/borehole5D.m

@@ -36,7 +36,7 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 80;
+PCEOpts.ExpDesign.NSamples = 50;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices
@@ -62,6 +62,17 @@ end
 
 %ub1 = dgsm(dim,nsam,X,V,dX,pc);
 
+X7 = load('X7.mat');
+Y7 = load('Y7.mat');
+X7 = X7.X;
+Y7 = Y7.Y;
+X5 = zeros(size(X7,1),5);
+X5(:,1) = X7(:,1);
+X5(:,2) = X7(:,3);
+X5(:,3:5) = X7(:,5:7);
+
+errL2 = validate(X5,X7,Y7);
+
 function ub1 = dgsm(dim,nsam,X,V,dX,pc)
 G = uq_borehole(X);
 Gdx = zeros(nsam,dim);
@@ -80,12 +91,12 @@ for i = 1:dim
 end
 end
 
-
-
-
-
-
-
+function errv = validate(X5,X7,Y7)
+Y_PCE = uq_evalModel(X5);
+NR = sum(((Y7-Y_PCE).^2)).^(0.5);
+DR = sum((Y7.^2)).^(0.5);
+errv = double(NR)./double(DR);
+end
 
 
 

### 2018-01-01 Codes/Borehole/test_borehole.m

@@ -44,7 +44,7 @@ PCEOpts.MetaType = 'PCE';
 PCEOpts.FullModel = myModel;
 PCEOpts.Degree = 1:10;
 PCEOpts.Method = 'LARS';
-PCEOpts.ExpDesign.NSamples = 80;
+PCEOpts.ExpDesign.NSamples = 50;
 myPCE = uq_createModel(PCEOpts);
 
 % Compute Sobol Indices

### 2018-01-01 Codes/Borehole/borehole4D/borehole4D.m
pdf compare for borehole

@@ -43,6 +43,17 @@ myPCE = uq_createModel(PCEOpts);
 %PCESobolResults = PCESobolAnalysis.Results;
 %STi = PCESobolResults.Total;
 
+% PCE Evaluations for pdf comp
+
+data_pts = load('../valpts_pdf.mat');
+X7 = data_pts.S;
+X4 = zeros(size(X7,1),4);
+X4(:,1) = X7(:,1);
+X4(:,2) = X7(:,3);
+X4(:,3:4) = X7(:,5:6);
+Y_PCE4D = uq_evalModel(X4);
+save('y4d.mat','Y_PCE4D');
+
 % Compute UB1 for all variables
 X = myPCE.ExpDesign.X;
 dim = size(X,2);

### 2018-01-01 Codes/Borehole/borehole5D/borehole5D.m

@@ -47,6 +47,17 @@ myPCE = uq_createModel(PCEOpts);
 %PCESobolResults = PCESobolAnalysis.Results;
 %STi = PCESobolResults.Total;
 
+% PCE Evaluations for pdf comp
+
+data_pts = load('../valpts_pdf.mat');
+X7 = data_pts.S;
+X5 = zeros(size(X7,1),5);
+X5(:,1) = X7(:,1);
+X5(:,2) = X7(:,3);
+X5(:,3:5) = X7(:,5:7);
+Y_PCE5D = uq_evalModel(X5);
+save('y5d.mat','Y_PCE5D');
+
 % Compute UB1 for all variables
 X = myPCE.ExpDesign.X;
 dim = size(X,2);

### 2018-01-01 Codes/Borehole/test_borehole.m

@@ -91,6 +91,71 @@ myPCE = uq_createModel(PCEOpts);
 %data = load('val_pts.mat');
 %E = validate(data.val_pts);
 
+%========================================================================
+% Generate a set of pdf evaluations of the observable for comparison with
+% the 3D case
+
+dim = 7; % dimension
+nsams = 1e6; % number of points at which the pdf needs to be evaluated
+
+S = zeros(nsams,dim);
+S(:,1) = normrnd(IOpts.Marginals(1).Parameters(1),IOpts.Marginals(1).Parameters(2),nsams,1);
+for j = 2:dim
+    L = IOpts.Marginals(j).Parameters(1);
+    U = IOpts.Marginals(j).Parameters(2);
+    S(:,j) = unifrnd(L,U,nsams,1);
+end
+
+Y_PCE7D = uq_evalModel(S);
+save('valpts_pdf.mat','S');
+save('y7d.mat','Y_PCE7D');
+
+%========================================================================
+%Plot comparison of 7D, 5D, and 4D PDFs
+
+data7 = load('y7d.mat');
+data5 = load('y5d.mat');
+data4 = load('y4d.mat');
+
+Y_PCE7D = data7.Y_PCE7D;
+Y_PCE5D = data5.Y_PCE5D;
+Y_PCE4D = data4.Y_PCE4D;
+
+step = (max(Y_PCE7D) - min(Y_PCE7D)).*(1e-4);
+pts_PCE7D = min(Y_PCE7D):step:max(Y_PCE7D);
+
+step = (max(Y_PCE5D) - min(Y_PCE5D)).*(1e-4);
+pts_PCE5D = min(Y_PCE5D):step:max(Y_PCE5D);
+
+step = (max(Y_PCE4D) - min(Y_PCE4D)).*(1e-4);
+pts_PCE4D = min(Y_PCE4D):step:max(Y_PCE4D);
+
+[density_PCE7D,xmesh_PCE7D] = ksdensity(Y_PCE7D,pts_PCE7D);
+[density_PCE5D,xmesh_PCE5D] = ksdensity(Y_PCE5D,pts_PCE5D);
+[density_PCE4D,xmesh_PCE4D] = ksdensity(Y_PCE4D,pts_PCE4D);
+
+figure;
+hold on;
+plot(xmesh_PCE7D,density_PCE7D,'Linewidth',2,'color','k');
[…]

### 2018-01-01 Paper/examples.tex
work in progress
added oscillator schematic

@@
 L-2 verification is negligible since function evaluations or model realizations obtained during the
-screening step could be re-used.
-However, since the test problems are computationally inexpensive, we generate an independent
-set of samples ($\bm{\theta_i}$) to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}
-in each case.
+screening step could be re-used to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}.
 For the purpose of probabilistic verification, we compare the probability density function of
@@
 7D space seems much higher.
+
+As discussed earlier in this section, the reduced order PCE's are verified for predictive accuracy in 
+a least-squares sense and a probabilistic sense. Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$
+based on 50 samples and corresponding function evaluations in the original 7D parameter space
+were found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other words, the 4D
+PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within 1.12$\%$ of predictions based on
+the borehole function. It is interesting to note that although the order of convergence in the case of a 5D
+PCE is lower (Figure~\ref{fig:conv_bore}), its predictive accuracy is higher than the 4D PCE. A possible
+explanation for this observation is that above a certain order of convergence, the uncertainty in $k_w$ 
+contributes much more towards predictive accuracy of the reduced order PCE. It is therefore critical
+to account for the order of PCE convergence as well as its predictive accuracy for a given application,
+as highlighted earlier in section~\ref{sec:method}.
+
+Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the discharge, $\mathcal{Q}$
+obtained by propagating 10$^6$ Monte-Carlo (MC) samples through the 7D PCE in the
+original input parameter domain as well as the reduced order PCE's constructed in 4 and 5 dimensions. 
+It is evident from this plot, that the PDF's agree quite favorably with each other. Consequently, it can
+be said that the reduced order PCE is verified in a probabilistic sense. In other words, the mode as
+well as the uncertainty in the observable is reliably captured and predicted by the reduced order PCE.
+
+\subsection{Non-linear Oscillator}

### 2018-01-02 Codes/MD/combine_energy.m
working on results for the MD application

@@ -1,0 +1,28 @@
+close all
+clear all
+
+set1 = load('energy_set1.txt');
+set2 = load('energy_set2.txt');
+com = zeros(80,3);
+np = 5; % N for each set where N(d+1) computations were performed
+
+f = 1; % counter for the combined energy file
+k = 1; % counter for individual energy files
+
+while f <= 80
+  com(f:f+(np-1),1) = f:f+(np-1);
+  com(f:f+(np-1),2:3) = set1(k:k+(np-1),2:3);
+  com(f+np:(f+np)+(np-1),1) = f+np:(f+np)+(np-1);
+  com(f+np:(f+np)+(np-1),2:3) = set2(k:k+(np-1),2:3);
+  f = f+2*np;
+  k = k+np;
+end
+
+fid = fopen('energy_combined.txt','w');
+fmt = '%02d %10.3f %10.3f\n';
+
+for i = 1:80
+  fprintf(fid,fmt,com(i,1),com(i,2),com(i,3));
+end
+
+fclose(fid);

### 2018-01-02 Codes/MD/gen_samples.m

@@ -15,7 +15,7 @@ N = [A;B;p;q;alpha;lambda;gamma];
 L(:,1) = 0.9.*N(:); % lower-bound
 U(:,1) = 1.1.*N(:); % upper-bound
 ts = 20; % total number of samples
-ns = 10; % subset of samples
+ns = 15; % subset of samples
 U(4,1) = 0.1;
 
 S = zeros(ts,dim);

### 2018-01-02 Codes/MD/screen.m

@@ -23,7 +23,7 @@ for j = 1:dim
   pc(j) = ((U(j,1)-L(j,1)).^2)./(pi.^2);
 end
 
-nsams = 5;
+nsams = 10;
 G = zeros(nsams,1); Gdx = zeros(nsams,dim);
 G(:,1) = k_data(1:nsams,2);
 

### 2018-01-02 Codes/MD/write_params.m

@@ -1,10 +1,10 @@
 
-fid = fopen('params_2_5.txt','w');
+fid = fopen('params_3_5.txt','w');
 fmt = '%14.8f %14.8f %14.8f %14.8f %14.8f %14.8f %14.8f\n';
 
 for i = 1:40
-  fprintf(fid,fmt,params_2_5(i,1),params_2_5(i,2),params_2_5(i,3),params_2_5(i,4),...
-                  params_2_5(i,5),params_2_5(i,6),params_2_5(i,7));  
+  fprintf(fid,fmt,params_3_5(i,1),params_3_5(i,2),params_3_5(i,3),params_3_5(i,4),...
+                  params_3_5(i,5),params_3_5(i,6),params_3_5(i,7));  
 end
 
 fclose(fid);

### 2018-03-31 Codes/MD/PCE5D/build_pce.m
syncing dgsm dir

@@ -12,6 +12,9 @@ MetaOpts.ExpDesign.Y = Y;
 L = [6.3446 0 1.62 18.90 1.08];
 U = [7.7545 0.1 1.98 23.10 1.32];
 
+% nominal parameter values
+nom = [7.0496 0.0 1.80 21.0 1.20];
+
 for ii = 1:5
     IOpts.Marginals(ii).Type = 'Uniform';
     IOpts.Marginals(ii).Parameters = [L(ii), U(ii)];
@@ -40,6 +43,43 @@ qoic(24:nsams-1,1) = qoi(25:nsams,2);
 %E1 = verify_L2(nsams,qoic);
 %verify_pdf(qoic);
 %gsa();
+gridded_likelihood(L,U,nom);
+
+%lx = linspace(L(3),U(3),4);
+%ly = linspace(L(5),U(5),4);
+%[XX,YY] = meshgrid(lx,ly);
+%sXX = size(XX(:),1);
+%nomc = zeros(sXX,5);
+%nomc(1:end,1) = nom(1);
+%nomc(1:end,3) = XX(:);
+%nomc(1:end,4) = nom(4);
+%nomc(1:end,5) = YY(:);
+%data_pce = uq_evalModel(nomc);
+%data_pce_surf = reshape(data_pce,size(XX));
+%km = 149; %experimental estimate of kappa at 300 K
+%like = zeros(size(XX));
+%diff = (km - data_pce_surf).^2;
+%sig2 = (0.15*km).^2;
+%pre = 1./sqrt(2.*pi.*sig2);
+%like = pre.*exp(-diff./(2.*sig2));
+%[M,I] = max(like(:));
+%[I_row,I_col] = ind2sub(size(like),I);
+%
+%figure;
+%hold on;
+%pcolor(XX,YY,like);
+%shading interp;
+%plot(lx(I_row,I_col),ly(I_row,I_col),'*','MarkerSize',10,'MarkerFaceColor','m');
+%c = colorbar();
+%xlabel('$$\mathrm{\alpha}$$','interpreter','latex','fontsize',18);
+%ylabel('$$\mathrm{\gamma}$$','interpreter','latex','fontsize',18);
+%set(gca,'fontsize',14);
+%set(gca,'TickLabelInterpreter','latex')
+%set(c,'TickLabelInterpreter','latex')
+%set(gcf,'color',[1,1,1]);
+%print -depsc gl.eps
+
+% Function definitions
 
 % Sobol Sensitivity Indices
[…]

### 2018-03-31 Codes/MD/active_subspace/init_1D.m

@@ -18,7 +18,7 @@ rn1 = Nr./Dr;
 
 
 % SSP 1D
-ssp1D(eta,xpr,G);
+%ssp1D(eta,xpr,G);
 
 % Generate a million random samples in the 7D space
 ts = 1e5;

### 2018-03-31 Codes/MD/active_subspace/init_2D.m

@@ -1,4 +1,4 @@
-function rn2 = init_2D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1);
+function [rn2,xmesh_PCE2,density_PCE2] = init_2D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1);
 
 % 2D Polynomial surface fit
 y1 = eta(:,1)'*xpr';
@@ -15,11 +15,11 @@ end
 
 Nr = (sum((G-Y_surr_data).^2)).^(0.5);
 Dr = (sum((G).^2)).^(0.5);
-%rn2 = Nr./Dr; 
-rn2 = max(Y_surr_data);
+rn2 = Nr./Dr; 
 
 % SSP 2D
-ssp2D(y1,y2,G,sf);
+%ssp2D(y1,y2,G,sf); % 3D plot with surface fit
+ssp2D_2(y1,y2,G); % 2D plot showing trends in k along first two active variables
 
 % compare pdf with the histogram'
 ts = 1e5;
@@ -47,7 +47,7 @@ for i = 1:ts
   Y_surr_rs(i) = sf(y1_rs(i),y2_rs(i));
 end
 
-pdf_comp_ssp2D(G,Y_surr_rs);
+%pdf_comp_ssp2D(G,Y_surr_rs);
 
 % Function Definitions
 
@@ -66,18 +66,34 @@ box on;
 print -depsc ssp2D.eps
 end
 
-% compare pdf of kappa using 1D SSP
+function ssp2_2 = ssp2D_2(y1,y2,G);
+figure;
+ps = 100; % size of the point
+scatter(y1,y2,ps,G,'filled');
+shading interp;
+xlabel('$$\mathrm{\eta_1^{T}\xi}$$','interpreter','latex','fontsize',18);
+ylabel('$$\mathrm{\eta_2^{T}\xi}$$','interpreter','latex','fontsize',18);
+set(gca,'TickLabelInterpreter','latex','fontsize',14);
+set(gcf,'color',[1,1,1]);
+box on;
+c = colorbar();
+set(c,'TickLabelInterpreter','latex');
+print -depsc ssp2D_2.eps
+end
+
+
+% compare pdf of kappa using 2D SSP
 function comp2 = pdf_comp_ssp2D(G,Y_PCE)
 step = (max(Y_PCE) - min(Y_PCE)).*(1e-4);
 pts_PCE = min(Y_PCE):step:max(Y_PCE);
[…]

### 2018-03-31 Codes/MD/active_subspace/init_3D.m

@@ -1,0 +1,109 @@
+function rn3 = init_3D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1,xmesh_PCE2,density_PCE2);
+
+% 3D Polynomial surface fit
+
+y1 = eta(:,1)'*xpr';
+y2 = eta(:,2)'*xpr';
+y3 = eta(:,3)'*xpr';
+
+s = size(y1,2);
+Y = zeros(s,3);
+Y(:,1) = y1;
+Y(:,2) = y2;
+Y(:,3) = y3;
+
+reg=MultiPolyRegress(Y,G,3);
+
+% compute rel L-2 norm of error
+np = size(xpr,1);
+Y_surr_data = zeros(np,1);
+
+for i = 1:np
+  np=Y(i,:);
+  ns=repmat(np,[length(reg.PowerMatrix) 1]).^reg.PowerMatrix;
+  es=ones(length(reg.PowerMatrix),1);
+  for ii=1:size(reg.PowerMatrix,2)
+    es=es.*ns(:,ii);
+  end
+  Y_surr_data(i) = reg.Coefficients'*es; % The estimate for the new data point.
+end
+
+Nr = (sum((G-Y_surr_data).^2)).^(0.5);
+Dr = (sum((G).^2)).^(0.5);
+rn3 = Nr./Dr;
+
+% compare pdf with histogram
+
+ts = 1e5;
+samples = zeros(ts,dim);
+
+for j = 1:dim
+  samples(:,j) = unifrnd(L(j,1),U(j,1),ts,1);
+end
+
+% project those samples in [-1,1]
+
+xrand = zeros(ts,dim);
+
+for i = 1:ts
+  for j = 1:dim
+    xrand(i,j) = 2.0.*(samples(i,j)-L(j))./(U(j)-L(j)) - 1.0;
+  end
+end
+
+Y_surr_rs = zeros(ts,1);
+
+y1_rs = eta(:,1)'*xrand';
+y2_rs = eta(:,2)'*xrand';
+y3_rs = eta(:,3)'*xrand';
+sn = size(y1_rs,2);
+Y_rs = zeros(sn,3);
+Y_rs(:,1) = y1_rs;
+Y_rs(:,2) = y2_rs;
+Y_rs(:,3) = y3_rs;
+
+for i = 1:ts
+  np=Y_rs(i,:);
+  %np = [-0.4716   -0.2264    0.6605];
[…]

### 2018-03-31 Codes/MD/active_subspace/test_sub.m

@@ -73,16 +73,28 @@ eta(:,1) = W(:,1);
 eta(:,2) = W(:,2);
 eta(:,3) = W(:,3);
 
+
+% Computing activity scores
+
+as = zeros(7,1);
+
+for i = 1:dim
+  for j=1:3
+    as(i) = as(i) + lambda(j).*(W(i,j).^2);
+  end
+end
+
 % Eigvalue plot
 %eigv(lambda);
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 [rn1,xmesh_PCE1,density_PCE1] = init_1D(eta,xpr,G,dim,L,U); % 1D active var analysis, 
-rn2 = init_2D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1); % 2D active var analysis
-%rn: rel L2 norm of error
-rn3 = init_3D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1); % 2D active var analysis
+%[rn2,xmesh_PCE2,density_PCE2] = init_2D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1); 
+% 2D active var analysis, rn: rel L2 norm of error
+%rn3 = init_3D(eta,xpr,G,dim,L,U,xmesh_PCE1,density_PCE1,xmesh_PCE2,density_PCE2); % 2D active var analysis
 
+%plot_rn(rn1,rn2,rn3);
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@ -98,5 +110,18 @@ set(gcf,'color',[1,1,1]);
 box on;
 grid on;
 print -depsc eigv.eps
+end
+
+function prn = plot_rn(rn1,rn2,rn3);
+figure;
+plot([1 2 3],[rn1 rn2 rn3],'o--','MarkerFaceColor','k');
+xlabel('$$\mathrm{Active~Subspace~Dimension}$$','interpreter','latex','fontsize',18);
+ylabel('$$\mathrm{Relative~L-2~Norm~of~Error}$$','interpreter','latex','fontsize',18);
+xticks([1 2 3]);
+xlim([0,4]);
+set(gca,'TickLabelInterpreter','latex');
+set(gcf,'color',[1,1,1]);
+box on;
+print -depsc rn.eps
 end
 

### 2018-04-28 Paper/cover.tex
files added

@@
 \textsc{
-Derivative-based global sensitivity approach to 
-efficient surrogate modeling with application to molecular dynamics
+Derivative-based global sensitivity approach to efficient surrogate modelling
+with Polynomial Chaos
 }
@@
 \bigskip 
+\bigskip
+
+Manav Vohra$^{1}$, Alen Alexanderian$^{2}$, Cosmin Safta$^{3}$, Sankaran Mahadevan$^{1}$
+
+\bigskip
+\bigskip
+
+\normalsize
+$^1$Department of Civil and Environmental Engineering\\
+Vanderbilt University\\
+Nashville, TN 37235\\
 
@@
 
-Manav Vohra, Alen Alexanderian, Sankaran Mahadevan
+$^2$Department of Mathematics\\
+North Carolina State University\\
+Raleigh, NC 27695\\
+
+\bigskip
+
+$^3$Sandia National Laboratories\\
+Livermore, CA 94550\\
 
@@
 
-\vspace{10cm}
+\vspace{6cm}
 
-\begin{tabular}{ll}
-Corresponding Author:  & TBA \\
-                       & Vanderbilt University \\ 
-                       & Nashville, TN\\ 
-                       & Phone: \\ 
-                       & Email: 
-\end{tabular}
+\begin{tabbing}
+Corresponding Author: \hspace{5mm} \= Sankaran Mahadevan\\
+       \>  Department of Civil and Environmental Engineering\\
+       \>  Vanderbilt University\\
+       \>  272 Jacobs Hall, VU Mailbox: PMB 351831 \\
+       \>  Nashville, TN 37235 \\
+       \> \\
+Phone: \> (615) 322-3040 \\
+Fax:   \> (615) 343-3773 \\
+Email: \>  sankaran.mahadevan@vanderbilt.edu   \\
+\\
+Submitted to: \> \textit{Reliability Engineering and System Safety} \\
+\>  May 2018\\
 
 \bigskip
-
-Submitted to: \emph{Journal of Computational Physics}
+\end{tabbing}
 

### 2018-04-28 Paper/intro.tex
files added

@@
 %\end{enumerate}
+
+The emerging field of uncertainty quantification (UQ) aims at methodologies for 
+incorporating, characterizing, quantifying, propagating, and reducing the 
+uncertainties associated with predictive models and simulations. For situations
+involving complex physical models and compute-intensive simulations, an
+efficient approach to construction of model surrogates is sought to enable UQ
+in a tractable manner. Polynomial chaos expansion 
+(PCE)~\cite{Xiu:2002,Ghanem:2003,Eldred:2008,Olivier:2010} and 
+Gaussian Process (GP)~\cite{Rasmussen:2004} or Kriging~\cite{Stein:2012} are
+among the most commonly used surrogates for scientific applications. However,
+both approaches quickly become prohibitive when the set of uncertain model
+inputs and parameters is large-dimensional. Specifically, in the case of a PCE,
+a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
+requires model realizations at $(p+1)^d$ quadrature nodes to estimate the PC
+coefficients using a fully-tensorized Gauss quadrature. This trend is 
+illustrated below in Figure~\ref{fig:curse}.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.70\textwidth]{./Figures/quad_comp}
+\caption{Number of fully-tensorized Gauss quadrature nodes ($(p+1)^d$) is plotted against PCE total order truncation, $p$ for $d$ = 2,3, and 4.}
+\label{fig:curse}
+\end{center}
+\end{figure}

### 2018-04-28 Paper/intro.tex
..

@@
 a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
-requires model realizations at $(p+1)^d$ quadrature nodes to estimate the PC
+requires model realizations at $(p+1)^d$ quadrature nodes to ecactly determine the PC
 coefficients using a fully-tensorized Gauss quadrature. This trend is 
@@
  \begin{center}
-  \includegraphics[width=0.70\textwidth]{./Figures/quad_comp}
-\caption{Number of fully-tensorized Gauss quadrature nodes ($(p+1)^d$) is plotted against PCE total order truncation, $p$ for $d$ = 2,3, and 4.}
+  \includegraphics[width=0.70\textwidth]{./Figures/curse}
+\caption{Number of multi-dimensional Gauss quadrature nodes, $(p+1)^d$ is plotted against the PCE
+ total order truncation, $p$ for 2, 3, and 4 dimensional polynomial basis functions.}
 \label{fig:curse}

### 2018-04-29 Paper/bg.tex
..

@@
 The derivative-based global sensitivity analysis (DGSA) is performed by 
-estimating a sensitivity measure~\cite{Kucherenko:2009} for each stochastic
+estimating a sensitivity measure~\cite{Sobol:2009} for each stochastic
 parameter in a model or a function. The
@@
 
-The derivative in the above equation is estimated using finite
+\noindent The derivative in the above equation is estimated using finite
 difference as given below, and averaged using pseudo-random samples in
@@
 
-The upper bound in the above inequality is proportional to the product of $\mathcal{C}_i$
+\noindent The upper bound in the above inequality is proportional to the product of $\mathcal{C}_i$
 and $\mu_i$. However, for the purpose of parameter screening as discussed later in
@@
 
-The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability distribution of $\theta_i$.
+\noindent The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability distribution of $\theta_i$.
 Table~\ref{tab:poincare} provides its value in the case of uniform and normal

### 2018-04-29 Paper/examples.tex
update ...
..

@@
 parameter screening based on the methodology presented in Section~\ref{sec:method}.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.65\textwidth]{./Figures/sense_borehole}
+\caption{Sobol' total effect sensitivity index for uncertain parameters in the borehole
+function (Eq.~\ref{eq:bore}).}
+\label{fig:sense_bore}
+\end{center}
+\end{figure}
+
 In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
 for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.
-Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.65\textwidth]{./Figures/ub_conv_borehole}
+\caption{Estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted 
+against number of samples considered for evaluating $\mu_i$. Corresponding estimates
+for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
+legend.}
+\label{fig:screen_bore}
+\end{center}
+\end{figure}
+
+\noindent Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
 even when small number of samples (5 -- 10) are used. 
@@
 in the full space (7D) with those constructed in the two reduced spaces (4D and 5D) using
-$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). As expected, it is observed that the PCE
+$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}).
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.65\textwidth]{./Figures/err_samples_borehole}
+\caption{A comparison of order of the leave-one-out-error 
+($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
+used for constructing the PCE in 4, 5, and 7 dimensions.}
+\label{fig:conv_bore}
+\end{center}
+\end{figure}
+
+\noindent As expected, it is observed that the PCE
 constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
@@
 original input parameter domain as well as the reduced order PCE's constructed in 4 and 5 dimensions.
-It is evident from this plot, that the PDF's agree quite favorably with each other. Consequently, it can
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.65\textwidth]{./Figures/pdf_comp_borehole}
+\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
+by propagating
+parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
+were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
+\label{fig:pdfcomp_bore}
+\end{center}
+\end{figure}
+
+\noindent It is evident from this plot, that the PDF's agree quite favorably with each other. Consequently, it can
 be said that the reduced order PCE is verified in a probabilistic sense. In other words, the mode as
@@
 \subsection{Non-linear Oscillator}
+
+\subsection{Semilinear elliptic PDE with random source term}
+
+We consider the semilinear elliptic PDE,
+\begin{equation}\label{equ:semilinear}
+\begin{aligned}
+-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
+ u &= 0. \quad \text{on } \partial \Omega
+\end{aligned}
+\end{equation}
+We model the source term as 
+\begin{equation}
+q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
+\cos(i \pi y),
+\quad N = 8.
+\end{equation}
+Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
+and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
+the following QoI,
+\[
+     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
+\]
+where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.

### 2018-04-29 Paper/intro.tex
..

--- 2018-04-28 Paper/intro.tex
@@
 a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
-requires model realizations at $(p+1)^d$ quadrature nodes to estimate the PC
-coefficients using a fully-tensorized Gauss quadrature. This trend is 
-illustrated below in Figure~\ref{fig:curse}.
+requires model realizations at $(p+1)^d$ quadrature nodes to exactly determine the PC
+coefficients using a fully-tensorized Gauss quadrature. Consider a case where $d$ = 8 which
+could be a regarded as a low-dimensional problem, and $p$ = 5, requires model evaluations at
+roughly 1.7 million quadrature nodes. However, the degree of exactness in numerical estimation 
+of the coefficients as made possible with a fully-tensored quadrature might not be desired. In that
+case, computational effort can be reduced considerably by using nested
+quadratures~\cite{Gentleman:1972a,Gentleman:1972b,Novak:1999,Waldvogel:2006} which allow 
+model realizations at a given level to be used at higher levels of accuracy as well as sparse grids
+based on Smolyak tensorization~\cite{Smolyak:1963}. Additonally, sparse basis 
+techniques~\cite{Peng:2014,Hampton:2015,Blatman:2011} have been used to reduce  the required
+computational effort for constructing a reasonably accurate PC surrogate.
 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.70\textwidth]{./Figures/quad_comp}
-\caption{Number of fully-tensorized Gauss quadrature nodes ($(p+1)^d$) is plotted against PCE total order truncation, $p$ for $d$ = 2,3, and 4.}
-\label{fig:curse}
-\end{center}
-\end{figure}
+One of the primary objectives for constructing a model surrogate is to be able to perform 
+parametric sensitivity analysis tractably. Sensitivity analysis provides an insight into the
+relative contributions of the uncertain model parameters and inputs to the uncertainty in
+predictions. The analysis could potentially reduce the dimensionality of the problem.
+However, as discussed earlier, constructing the surrogate might still require a large amount
+of computational resources. It can thus be understood that dimension reduction prior to
+constructing the surrogate might lead to enormous computational savings. In this work,
+we present a strategy for identifying and screening uncertain model parameters that 
+are significantly less important that the rest, thereby reducing the dimensionality of the
+problem and enabling the construction of a reduced-order surrogate. As discussed in
+section~\ref{sec:method}, parameter ranks are determined using a \textit{screening-metric}
+based on derivative-based global sensitivity 
+measures~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016}. 
+The strategy is agnostic to the choice of methodology for constructing the surrogate. However, 
+we will be using PCE to demonstrate the suitability of the proposed strategy. Below, in 
+section~\ref{sec:bg}, we provide a brief introduction to derivative-based global sensitivity analysis
+in the present context as well as the polynomial chaos methodology. Later, in section~\ref{sec:examples},
+we motivate the proposed strategy by implementing it to a suite of simple applications, namely, the 
+classic borehole function, a non-linear oscillator, and a semi-linear elliptic PDE. Finally, we demonstrate
+suitability of our approach by using it to reduce the dimensionality of a H$_2$/O$_2$ kinetics problem
+involving 19 reactions in section~\ref{sec:app}.
+
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=0.70\textwidth]{./Figures/curse}
+%\caption{Number of multi-dimensional Gauss quadrature nodes, $(p+1)^d$ is plotted against the PCE
+% total order truncation, $p$ for 2, 3, and 4 dimensional polynomial basis functions.}
+%\label{fig:curse}
+%\end{center}
+%\end{figure}

### 2018-04-30 Paper/bg.tex
work in progress ...

@@
 
-In this section, we provide a brief theoretical background to the
-derivative-based global sensitivity measure and the polynomial chaos
-expansion.
+In this section, we introduce the notations used in the rest of
+the article, and present the requisite background material on 
+derivative-based global sensitivity measures and surrogate modeling 
+using polynomial chaos expansion.
 
-\subsection{Derivative-based global sensitivity}
-
-The derivative-based global sensitivity analysis (DGSA) is performed by 
-estimating a sensitivity measure~\cite{Sobol:2009} for each stochastic
-parameter in a model or a function. The
-sensitivity measure associated with a parameter, $\theta_i$, based on
-the observable, $\mathcal{Y}$ is given as follows:
-
+\subsection{Derivative-based global sensitivity analysis}  
+Let $\mathcal{Y}$ be a mathematical model that is a function of $\Np$ uncertain 
+parameters, $\theta_1, \theta_2, \ldots, \theta_\Np$. The goal of sensitivity analysis
+is measuring the influence of each component of the parameter vector 
+$\bm{\theta}$ on the model output. 
+\alennote{We consider the case of statistically independent parameters, right? 
+Should we make this precise?}
+Derivative-based global sensitivity analysis (DGSA) is performed by 
+computing derivative based global sensitivity measures (DGSMs)~\cite{Sobol:2009} 
+for each uncertain parameter in the model. 
+Specifically, we consider the following DGSMs, 
 \be
-\mu_i = \mathbb{E}\left[\left(\frac{\partial \mathcal{Y}(\bm{x})}{\partial \theta_i}\right)^{2}\right]
+\mu_i = 
+\mathbb{E}\left[\left(\frac{\partial \mathcal{Y}(\bm{\bm{\theta}})}{\partial \theta_i}\right)^{2}\right], \quad i = 1, \ldots, \Np.
 \label{eq:mu}
 \ee
+Here $\mathbb{E}$ denotes expectation over the uncertain parameters.
+Notice that this formulation assumes that the function $\mathcal{Y}$ is differentiable
+with respect to $\theta_i$, $i = 1, \ldots, \Np$, almost surely.
 
-\noindent The derivative in the above equation is estimated using finite
-difference as given below, and averaged using pseudo-random samples in
-the uncertain parameter domain.
+The derivative in the above equation can be estimated using finite
+differences as given below, and averaged using Monte Carlo sampling in
+the uncertain parameter space.
 
@@
 over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
-using large increments.
+using large increments.  It is noted by many authors~[REFS], and also observed
+in the numerical experiments in the present work, that a modest Monte Carlo
+sample size is often sufficient for computing~\eqref{eq:mu} with reasonable
+accuracy.
 
@@
 \be
-\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
+\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \widehat{\mathcal{C}_i\mu_i})
 \label{eq:bound}
@@
 and $\mu_i$. However, for the purpose of parameter screening as discussed later in
-Section~\ref{sec:method}, we consider a normalized product, $\hat{\mathcal{C}_i\mu_i}$:
+Section~\ref{sec:method}, we consider a normalized product, $\widehat{\mathcal{C}_i\mu_i}$:
 
 \be
-\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
+\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
 \label{eq:cmu}

### 2018-05-01 Paper/method.tex
..

\section{Method}
\label{sec:method}

%Stage1: QoI selection for accurate estimation of derivatives and PCE, Stage 2: Parameter Screening, Stage 3: Reduced-order Surrogate Verification
%
%1. Goal is to estimate the upper bound on Sobol total-effect index using DGSM. 
%2. QoI should be differentiable w.r.t all the parameters. 
%3. Derivative could be estimated analytically or numerically.
%4. The expected value of the partial derivative w.r.t a given parameter is approximated over a few samples.
%5. Gradually enhance the sample size until some degree of convergence is established.
%6. Note that model runs at the full parameter space will be used for verification of the ROS. However, one could consider
%relaxing the convergence criterion to reduce computational costs. 
%7. Consider the product of Ci and mu_i to screen parameters.

### 2018-05-02 Paper/bg.tex
work in progress ...

@@
 \subsection{Derivative-based global sensitivity analysis}
-Let $\mathcal{Y}$ be a mathematical model that is a function of $\Np$ uncertain 
+
+\alennote{1. Remove $G^M$; use $G$ and $G^{PC}$. 2. Start with $G$ in $\xi$ and
+the, in one sentence connect to physical range. 3. Equation (9) should be moved up to 
+2.1.}
+Let $\GG$ be a mathematical model that is a function of $\Np$ uncertain 
 parameters, $\theta_1, \theta_2, \ldots, \theta_\Np$. The goal of sensitivity analysis
@@
 $\bm{\theta}$ on the model output. 
-\alennote{We consider the case of statistically independent parameters, right? 
-Should we make this precise?}
+In the present work, we consider the case where the input parameters are statistically 
+independent.
+
 Derivative-based global sensitivity analysis (DGSA) is performed by 
@@
 \mu_i = 
-\mathbb{E}\left[\left(\frac{\partial \mathcal{Y}(\bm{\bm{\theta}})}{\partial \theta_i}\right)^{2}\right], \quad i = 1, \ldots, \Np.
+\mathbb{E}\left[\left(\frac{\partial \GG(\bm{\bm{\theta}})}{\partial \theta_i}\right)^{2}\right], \quad i = 1, \ldots, \Np.
 \label{eq:mu}
@@
 Here $\mathbb{E}$ denotes expectation over the uncertain parameters.
-Notice that this formulation assumes that the function $\mathcal{Y}$ is differentiable
+Notice that this formulation assumes that the function $\GG$ is differentiable
 with respect to $\theta_i$, $i = 1, \ldots, \Np$, almost surely.
@@
 \be
-\frac{\partial \mathcal{Y}(\bm{\theta}^{\ast})}{\partial \theta_i} =
+\frac{\partial \GG(\bm{\theta}^{\ast})}{\partial \theta_i} =
  \lim_{\Delta\theta_i^{*}\to 0}
-\frac{[\mathcal{Y}(\theta_1^{*},\ldots,\theta_{i-1}^{*},
+\frac{[\GG(\theta_1^{*},\ldots,\theta_{i-1}^{*},
 \theta_i^{*}+\Delta\theta_i^{*},
 \theta_{i+1}^{*},\ldots,\theta_d^{*}) - 
-\mathcal{Y}(\bm{\theta}^{*})]}{\Delta\theta_i^{*}} 
+\GG(\bm{\theta}^{*})]}{\Delta\theta_i^{*}} 
 \label{eq:partial}
@@
 therefore, $N\times(d+1)$. The derivative in Eq.~\ref{eq:partial} could be evaluated
-analytically in case the functional dependence of $\mathcal{Y}$ and $\theta_i$
+analytically in case the functional dependence of $\GG$ and $\theta_i$
 is known. Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
@@
 
-\subsection{Polynomial Chaos Expansion}
+\subsection{Polynomial chaos expansion}
 
-As discussed earlier in Section~\ref{sec:intro}, the Polynomial Chaos Expansion (PCE)
-is one of the most commonly used surrogates for representing the dependence of a random
-observable ($\mathcal{Y}$) on independent uncertain or stochastic model parameters ($\bm{\theta}$).
-Considering a joint probability distribution of the components of ($\bm{\theta}$) as $\mathbb{P}(\bm{\theta})$,
-the following condition is imposed on $\mathcal{Y}$:
+%As discussed earlier in Section~\ref{sec:intro}, the 
+%Polynomial chaos expansion
+%(PCE) is a commonly used tool for surrogate modeling.
+We consider models with $\Np$ random inputs, 
+$\theta_1, \ldots, \theta_\Np$ that are modeled
+as statistically independent random variables. The 
+variables $\theta_i$ will take in physically meaningful
+ranges; it is common to parameterize input uncertainties
+with canonical random variables $\xi_1, \ldots, \xi_\Np$,
+which can be then shifted and scaled to obtain the corresponding $\theta_i's$.
+Typical choices for distribution of $\xi_i$ include standard normal 
+and uniform distribution on the interval $[-1, 1]$.
+Let 
+\[
+   \bm{f}(\bm{x}) = \prod_{i=1}^\Np f_i(x_i), \quad \bm{x} \in \mathbb{R}^\Np
+\]
+where $f_i$ are probability density functions of $\xi_i$, $i = 1, \ldots, \Np$.
+We consider a square integrable random variable $\GG:\R^\Np \to \R$; 
+that is,
+\[
+\int_{\mathcal{D}} \GG(\bm{\xi})^2 \, \bm{f}(\bm{\xi})d\bm{\xi} < \infty,
+\]
+where $\mathcal{D}$ is the support of the distribution law of the random vector
+$\bm{\xi}$. In applications, 
+the random variable $\GG$ is the mathematical model of interest.
+
+% for representing the
+%dependence of a random observable ($\GG$) on independent uncertain or
+%stochastic model parameters ($\bm{\theta}$).  Considering a joint probability
+%distribution of the components of ($\bm{\theta}$) as
+%$\mathbb{P}(\bm{\theta})$, the following condition is imposed on
+%$\GG$:
 
 \be
-\mathbb{E}[\mathcal{Y}^2] = \int_{\mathcal{D}_{\bm{\theta}}} \mathcal{Y}^2 \mathbb{P}(\bm{\theta}) 
+\mathbb{E}[\GG^2] = \int_{\mathcal{D}_{\bm{\theta}}} \GG^2 \mathbb{P}(\bm{\theta}) 
 d\bm{\theta} < \infty
@@
 \noindent where $\mathcal{D}_{\bm{\theta}}$ is the domain of the input parameter space. The PCE of
-$\mathcal{Y}$ ($\mathcal{Y}^{\mbox{\tiny {PC}}}$) is a mean-square 
+$\GG$ ($\GG^{\mbox{\tiny {PC}}}$) is a mean-square 
 convergent truncated summation given as
@@
 \be
-\mathcal{Y}^{\mbox{\tiny M}} \approx \mathcal{Y}^{\mbox{\tiny PC}} = 
+\GG^{\mbox{\tiny M}} \approx \GG^{\mbox{\tiny PC}} = 
 \sum_{\alpha\in\mathcal{I}} c_{\alpha}\Psi_{\alpha}(\bm{\xi(\theta)}) 
@@
 
-\noindent where $\mathcal{Y}^{\mbox{\tiny M}}$ corresponds to realizations of the
+\noindent where $\GG^{\mbox{\tiny M}}$ corresponds to realizations of the
 observable using the original (typically physics-based) model. 
@@
 \be
-\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\mathcal{Y}^{\mbox{\tiny{M}}}]
+\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\GG^{\mbox{\tiny{M}}}]
 \approx
-\sum_{i=1}^{N} \mathcal{Y}^{\mbox{\tiny{M}}}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
+\sum_{i=1}^{N} \GG^{\mbox{\tiny{M}}}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
 \ee
@@
 \hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{\bm{\xi(\theta)}}) -
-\mathcal{Y}^{\mbox{\tiny{M}}}(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
+\GG^{\mbox{\tiny{M}}}(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
 \ee

### 2018-05-05 Paper/method.tex
..

@@
-\section{Method}
+\section{Methodology}
 \label{sec:method}
@@
 %relaxing the convergence criterion to reduce computational costs. 
-%7. Consider the product of Ci and mu_i to screen parameters.
+%7. Consider the product of Ci and mu_i to screen parameters.i
+
+In this section, we outline the underlying methodology for constructing a 
+reduced-order surrogate using sensitivity analysis. The term `reduced-order'
+in the present context implies that the surrogate is constructed in a 
+subspace that sufficiently captures the uncertainty in the model output. 
+In other words, the dimensionality of the polynomial basis functions in
+the case of PC surrogates is effectively reduced. A possible approach to 
+constructing a reduced-order surrogate involves sensitivity analysis of the
+uncertain model parameters with respect to a given output, and thereby
+disregard parameters considered as unimportant. For this purpose, global
+sensitivity analysis based on Sobol indices could be pursued. However,
+as discussed earlier in section~\ref{sec:intro}, determining converged 
+estimates of Sobol sensitivity indices typically requires tens of thousands
+of model evaluations. Consequently, the exercise becomes prohibitive in
+situations where the model runs are compute-intensive.

### 2018-05-05 Paper/bg.tex
work in progress ...

@@
 
-The derivative in the above equation can be estimated using finite
-differences as given below, and averaged using Monte Carlo sampling in
-the uncertain parameter space.
-
+If an analytic expression for $\GG$ is available the derivative in the above
+expression can be computed directly. In applications, however, $\GG$ is often
+defined in terms of a solution of a mathematical model. In some cases, 
+one has access to appropriate adjoint solvers that enable efficient
+adjoint-based gradient computations. In the present work, we consider
+a generic computational model and only assume that the model
+output depends differentiablly to the parameter $\bm{\theta}$. Thus, 
+we consider finite-difference gradient computation: 
 \be
-\frac{\partial \GG(\bm{\theta}^{\ast})}{\partial \theta_i} =
- \lim_{\Delta\theta_i^{*}\to 0}
-\frac{[\GG(\theta_1^{*},\ldots,\theta_{i-1}^{*},
-\theta_i^{*}+\Delta\theta_i^{*},
-\theta_{i+1}^{*},\ldots,\theta_d^{*}) - 
-\GG(\bm{\theta}^{*})]}{\Delta\theta_i^{*}} 
+\frac{\partial \GG(\bm{\theta})}{\partial \theta_i} 
+\approx
+\frac{\GG(\theta_1,\ldots,\theta_{i-1},
+\theta_i+\Delta\theta_i,
+\theta_{i+1},\ldots,\theta_d) - 
+\GG(\bm{\theta})}{\Delta\theta_i}, \quad i = 1, \ldots, \Np. 
 \label{eq:partial}
 \ee
-
+Then,~\eqref{eq:mu} can be evaluated by Monte Carlo sampling in
+the uncertain parameter space. 
 The total number of model realizations or function evaluations
 needed to
-compute $\mu_i$ in a Euclidian space $\mathbb{R}^d$ using $N$ samples is
-therefore, $N\times(d+1)$. The derivative in Eq.~\ref{eq:partial} could be evaluated
-analytically in case the functional dependence of $\GG$ and $\theta_i$
-is known. Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
-compared to the uncertainty in $\theta_i$ which leads to a significant improvement
-over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
-using large increments.  It is noted by many authors~[REFS], and also observed
+compute $\mu_i$ for a function $G$ of $\Np$ random inputs and using $N$ samples is
+therefore, $N\times(\Np+1)$. 
+%The derivative in Eq.~\ref{eq:partial} could be evaluated
+%analytically in case the functional dependence of $\GG$ and $\theta_i$
+%is known. 
+%Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
+%compared to the uncertainty in $\theta_i$ which leads to a significant improvement
+%over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
+%using large increments.  
+It is noted by many authors~[REFS], and also observed
 in the numerical experiments in the present work, that a modest Monte Carlo
@@
 
-%As discussed earlier in Section~\ref{sec:intro}, the 
-%Polynomial chaos expansion
-%(PCE) is a commonly used tool for surrogate modeling.
 We consider models with $\Np$ random inputs, 
@@
 where $\mathcal{D}$ is the support of the distribution law of the random vector
-$\bm{\xi}$. In applications, 
-the random variable $\GG$ is the mathematical model of interest.
+$\bm{\xi}$.
 
@@
 %$\GG$:
+%\be
+%\mathbb{E}[\GG^2] = \int_{\mathcal{D}_{\bm{\theta}}} \GG^2 \mathbb{P}(\bm{\theta}) 
+%d\bm{\theta} < \infty
+%\ee
 
+%\noindent where $\mathcal{D}_{\bm{\theta}}$ is the domain of the input parameter space.
+
+As mentioned in Section~\ref{sec:intro}, the 
+polynomial chaos expansion
+(PCE) is a commonly used tool for surrogate modeling. 
+The PCE of
+$\GG$ is a mean-square 
+convergent series expansion~\cite{Xiu:2002,Ghanem:2003,Olivier:2010} of the form:
 \be
-\mathbb{E}[\GG^2] = \int_{\mathcal{D}_{\bm{\theta}}} \GG^2 \mathbb{P}(\bm{\theta}) 
-d\bm{\theta} < \infty
+\GG(\bm\xi) = \sum_{k=0}^\infty c_k\Psi_k(\bm{\xi}),
 \ee
+where $\Psi_k$'s form a multivariate orthogonal polynomial
+basis---orthogonal with respect to the joint probability distribution of $\bm{\xi}$.
+%
+In practice, a truncated expansion is used.  Moreover, in applications, $\GG$
+is a mathematical model of interest that takes a parameter vector $\bm{\theta}$
+(with components in physically meaningful ranges) as input. Therefore, we 
+write the truncated PC representation of a model $\GG$ as follows:
+\be 
+\GG(\bm\theta) \approx \GG^{\mbox{\tiny PC}}(\bm\theta) := \sum_{k=0}^{\Npc}
+c_k\Psi_k (\bm\xi(\bm\theta)), 
+\ee
+where $\bm\xi(\bm\theta)$ is found by a simple linear transformation.
 
-\noindent where $\mathcal{D}_{\bm{\theta}}$ is the domain of the input parameter space. The PCE of
-$\GG$ ($\GG^{\mbox{\tiny {PC}}}$) is a mean-square 
-convergent truncated summation given as
-follows~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}:
-
-\be
-\GG^{\mbox{\tiny M}} \approx \GG^{\mbox{\tiny PC}} = 
-\sum_{\alpha\in\mathcal{I}} c_{\alpha}\Psi_{\alpha}(\bm{\xi(\theta)}) 
-\ee
-
-\noindent where $\GG^{\mbox{\tiny M}}$ corresponds to realizations of the
-observable using the original (typically physics-based) model. 
-Note that the set of parameters, $\bm{\theta}$ are parameterized in terms of canonical random
-variables, $\bm{\xi}$ in the above expansion. $\Psi_{\alpha}$'s are multivariate polynomial
-basis, orthonormal with respect to the joint probability distribution of $\bm{\xi}$, $\mathcal{I}$
-is the multi-index set which identifies the degree of individual polynomials in each term in the
-multivariate basis.
-
-Computational strategies available for estimating the PC coefficients ($c_\alpha$'s) typically involve
-techniques based on projection or regression. Projection-based methods rely on numerical
-quadrature for estimating the following expectation:
-
-\be
-\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\GG^{\mbox{\tiny{M}}}]
-\approx
-\sum_{i=1}^{N} \GG^{\mbox{\tiny{M}}}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
-\ee
-
-\noindent where $w^{(i)}$ denotes the weight associated with the quadrature node $i$. 
+Computational strategies available for estimating the PC coefficients
+($c_k$'s) typically involve techniques based on projection or regression.
+Projection-based methods consider the orthogonal projection of 
+$\GG$ on the PC basis $\{\Psi_k\}_{k=0}^\Npc$ and compute
+the resulting expansion coefficients via quadrature~\cite{Olivier:2010}.
+%on numerical quadrature for estimating the
+%following expectation:
+%\be
+%\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\GG^{\mbox{\tiny{M}}}]
+%\approx
+%\sum_{i=1}^{N} \GG^{\mbox{\tiny{M}}}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
+%\ee
+%\noindent where $w^{(i)}$ denotes the weight associated with the quadrature node $i$. 
 Regression-based methods such as least angle regression (LAR)~\cite{Efron:2004} and least absolute shrinkage
@@
 by solving a regularized optimization problem:
-
 \be
-\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{\bm{\xi(\theta)}}) -
+\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}_{\bm\theta}
+\left[\left(\sum_{k=0}^\Npc c_k \Psi_k(\bm\xi(\bm\theta)) -
 \GG^{\mbox{\tiny{M}}}(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
 \ee
-
-\noindent where $\normone{\bm{c}}$ = $\sum_{\alpha\in \mathcal{I}} |c_\alpha |$.
-The regularization term forces the minimization towards low-rank solutions.
+where $\normone{\bm{c}}$ = $\sum_{k=0}^\Npc |c_k |$.
+The regularization term forces the minimization towards sparse coefficient vectors resulting
+in sparse PC representations.
 In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
-a general purpose uncertainty quantification software developed at ETH Zurich in Switzerland.
+a general purpose uncertainty quantification software developed at ETH Zurich.
+% in Switzerland.

### 2018-05-05 Paper/examples.tex
work in progress ...

@@
 obtained using the derivative-based sensitivity approach with that obtained
-using converged estimates of Sobol' total effect sensitivity index, $\mathcal{T}(\theta_i)$~\cite{Sobol:2001}:
+using converged estimates of Sobol' total effect sensitivity index, $\mathcal{T}(\theta_i)$.
 
-\be
-\mathcal{T}(\theta_i) = 
-\frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})}
-\ee
+%\cite{Sobol:2001}:
+%\be
+%\mathcal{T}(\theta_i) = 
+%\frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})}
+%\ee
 

### 2018-05-05 Paper/bg.tex
sec 2, first pass ...

@@
 
-\alennote{1. Remove $G^M$; use $G$ and $G^{PC}$. 2. Start with $G$ in $\xi$ and
-the, in one sentence connect to physical range. 3. Equation (9) should be moved up to 
-2.1.}
 Let $\GG$ be a mathematical model that is a function of $\Np$ uncertain 
@@
 
-For parameters with continuous distributions, the upper bound on the total 
-Sobol' sensitivity index ($\mathcal{T}(\theta_i)$)
+Consider the total 
+Sobol' sensitivity index~\cite{Sobol:2001},
+\be
+\mathcal{T}(\theta_i) = 1 - 
+\frac{\mathbb{V}[\mathbb{E}(\GG|\bm{\theta}_{\sim i})]}{\mathbb{V}(\GG)},
+\ee
+where $\bm{\theta}_{\sim i}$ is the random vector $\bm\theta$ with $i$th component removed, 
+and $\mathbb{V}$ denotes the variance. The total Sobol' index quantifies the total contribution 
+of $\theta_i$ to variance of the model $\GG$. Components of $\bm\theta$ with small 
+total Sobol' index can be considered inessential and can be fixed at nominal values. However, 
+computing the total Sobol' index is a computationally expensive task for expensive-to-evaluate 
+models with large number of uncertain parameters. Fortunately, 
+for parameters with continuous distributions, an upper bound on $\mathcal{T}_i$  
 can be expressed in terms of $\mu_i$, the Poincar\'e constant ($\mathcal{C}_i$) and the total 
-variance of the model output ($V$)~\cite{Lamboni:2013}:
-
+variance of the model output ($\mathbb{V}(\GG)$)~\cite{Lamboni:2013}:
 \be
-\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \widehat{\mathcal{C}_i\mu_i})
+\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)}~(\propto \widehat{\mathcal{C}_i\mu_i})
 \label{eq:bound}

### 2018-05-06 Paper/method.tex
..

--- 2018-05-01 Paper/method.tex
@@
 %relaxing the convergence criterion to reduce computational costs. 
-%7. Consider the product of Ci and mu_i to screen parameters.
+%7. Consider the product of Ci and mu_i to screen parameters.i
+
+In this section, we outline the underlying methodology for constructing a 
+reduced-order surrogate using sensitivity analysis. The term `reduced-order'
+in the present context implies that the surrogate is constructed in a 
+subspace that sufficiently captures the uncertainty in the model output. 
+For instance, in the case of PC surrogates, the dimensionality of the polynomial
+basis functions is effectively reduced. A possible approach to 
+constructing a reduced-order surrogate involves sensitivity analysis of the
+uncertain model parameters with respect to a given output, and thereby
+disregarding the uncertainty associated with parameters considered as unimportant.
+For this purpose, a global sensitivity analysis based on Sobol indices could be pursued.
+However, as discussed earlier in sections~\ref{sec:intro} and~\ref{sec:bg}, determining converged 
+estimates of Sobol sensitivity indices typically requires tens of thousands
+of model evaluations. Consequently, the exercise becomes prohibitive in
+situations where the model runs are compute-intensive. Instead, we estimate a normalized
+upper-bound ($\widehat{\mathcal{C}_i\mu_i}$, see Eq.~\ref{eq:bound}) on the Sobol total
+effect index ($\mathcal{T}(\theta_i)$) for each parameter, $\theta_i$, and use it as a 
+metric to identify the unimportant parameters. Below, we provide an algorithm for 
+parameter screening. It is assumed that the partial derivatives in Eq.~\ref{eq:mu}
+are estimated using finite difference.
+
+\bigskip
+
+\begin{breakablealgorithm}
+  \caption{Parameter screening with derivative-based sensitivity measures.}
+  \begin{algorithmic}[1]
+    \Procedure{Screening}{}
+      \State Generate $n_1$ points in $\mathbb{R}^{d}$.\Comment{$d$: 
+             Number of uncertain model parameters.}
+      \State Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.
+      \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
+      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\widehat{\mathcal{C}_i\mu_i}$ values for $\theta_i$.
+      \State set $k$ = 1\Comment{Iteration counter}
+      \Do
+        \State Generate $n_k$ new points in $\mathbb{R}^{d}$.
+        \State Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.
+        \State Compute and store model evaluations at the $n_k(d+1)$ points.
+        \State Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.
+        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
+        \State Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - 
+               \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.\Comment{$max\_pdev$:
+               Maximum percentage deviation in $\mu_i$ between successive iterations.}
+        \State set $k$ = $k$ + 1
+      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
+               $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
+    \EndProcedure
+  \end{algorithmic}
+\end{breakablealgorithm}
+
+\bigskip
+
+Based on the steps outlined in the above algorithm, it can be said that the set of sample points used for
+estimating the screening metric, $\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks
+between successive iterations as well as a certain degree of convergence in estimates of the screening 
+metric for each uncertain parameter is accomplished. Parameter
+screening is an integral part of the overall strategy for constructing the reduced-order surrogate as 
+depicted below using a flow-diagram.

### 2018-05-06 Paper/bg.tex
..

@@
 \frac{\mathbb{V}[\mathbb{E}(\GG|\bm{\theta}_{\sim i})]}{\mathbb{V}(\GG)},
+\label{eq:total}
 \ee
@@
 %\noindent where $w^{(i)}$ denotes the weight associated with the quadrature node $i$. 
-Regression-based methods such as least angle regression (LAR)~\cite{Efron:2004} and least absolute shrinkage
+Regression-based methods such as least angle regression (LAR)~\cite{Efron:2004}, and least absolute shrinkage
 and selection operator (LASSO)~\cite{Tibshirani:1996} aim to construct a sparse PCE~\cite{Blatman:2008}
-by solving a regularized optimization problem:
+by solving a regularized optimization problem. Specifically in the case of LAR, a penalty term comprising the L-1
+norm of the PC coefficients is used:
+
 \be

### 2018-05-06 Paper/method.tex
..

@@
 depicted below using a flow-diagram.
+
+\bigskip
+
+\begin{center}
+\begin{tikzpicture}[node distance=1.5cm]
+
+\node (start) [startstop] {Start};
+
+\node (qoi) [io, below of=start,align=left] {Select an appropriate model output};
+
+\draw [line] (start) -- (qoi);
+
+\node (tol) [process, below of=qoi, text width=8em] {Set an initial tolerance, $\tau$};
+
+\draw [line] (qoi) -- (tol);
+
+\node (screen) [process, below of=tol, text width=9.5em] {Parameter Screening};
+
+\draw [line] (tol) -- (screen);
+
+\node (dr) [draw, diamond, aspect=2.0] {Is \\ Dimension-reduction \\ possible$?$};
+
+\end{tikzpicture}
+\end{center}

### 2018-05-07 Paper/method.tex
..

@@
 
+\begin{figure}[htbp]
 \begin{center}
@@
 
-\node (dr) [draw, diamond, aspect=2.0] {Is \\ Dimension-reduction \\ possible$?$};
+\node (dr) [draw, diamond, aspect=1.5,yshift=-6.7cm, text width=4.5em, text centered] {Is DR possible$?$};
+
+\draw [line] (screen) -- (dr);
+
+%\node (dr_mean) [right of=dr, xshift=5cm] {DR: Dimension Reduction};
 
@@
 \end{center}
+
+\caption{Flow-diagram outlining the overall strategy for constructing reduced-order surrogates using
+the derivative-based sensitivity measures. Note that DR is an abbreviation for dimension reduction.}
+\end{figure}

### 2018-05-07 Paper/examples.tex
..
borehole, first pass ...

@@
 \noindent The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
-in the RHS of Eq.~\ref{eq:bore} are considered as uncertain. Table~\ref{tab:bore} provides
-marginal distributions of the uncertain parameters.
+in the right hand side of~\eqref{eq:bore} are considered 
+as uncertain. Thus, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
+\[
+   \vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T.
+\] 
+Table~\ref{tab:bore} provides distributions of the uncertain inputparameters.
 
@@
 
-\caption{Description and marginal distributions of uncertain parameters in the borehole function
-given by Eq.~\ref{eq:bore}.}
+\caption{Description and distributions of uncertain parameters in the borehole function
+given by~\eqref{eq:bore}.}
 \label{tab:bore}
@@
 
-As mentioned earlier in this section, cheap function evaluations of the discharge using 
-Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
-Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
-parameters in the borehole function using 10$^6$ pseudo-random
-samples\footnote{Although $\mathcal{T}(\theta_i)$ 
-might converge with much fewer samples depending upon the model, we consider a large number that
-typically ensures a converged estimate for the purpose of illustration.} in the input parameter domain. 
+Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ using
+enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
+sampling, with a sufficiently large Monte Carlo sample size.  Shown in
+Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
+uncertain parameters in the borehole function using 10$^6$ pseudo-random
+samples in the input parameter space. 
+%\footnote{Although $\mathcal{T}(\theta_i)$ might converge with much fewer
+%samples depending upon the model, we consider a large number that typically
+%ensures a converged estimate for the purpose of illustration.} 
 These estimates are used to verify fidelity of
@@
  \begin{center}
-  \includegraphics[width=0.65\textwidth]{./Figures/sense_borehole}
-\caption{Sobol' total effect sensitivity index for uncertain parameters in the borehole
-function (Eq.~\ref{eq:bore}).}
+  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
+  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_borehole}
+\caption{
+Left: Sobol' total sensitivity index for uncertain parameters in the borehole
+function. Right: 
+estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted
+against number of samples considered for evaluating $\mu_i$. Corresponding estimates
+for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
+legend. \alennote{Can we have larger fontsizes for the right image? Also the y-axis label
+needs to be modified with a widehat as done in the text now.}}
 \label{fig:sense_bore}
@@
 \end{figure}
+In Figure~\ref{fig:sense_bore}~(right), we plot estimates of the screening parameter 
+$\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
+samples used for approximating $\mu_i$ using~\eqref{eq:mu}.
+Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
+Consequently, the relative importance of uncertain 
+parameters in the borehole function is found to be consistent 
+with predictions based on the Sobol' index. 
+In the considered intervals for the uncertain parameters, it is clear 
+that the discharge is insensitive to $T_u$ and $T_l$. 
+Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
+the dimensionality of the problem by 
+discounting the uncertainties in $T_u$, $T_l$, and $K_w$ by fixing 
+them at their respective nominal values.
 
-In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
-for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.
-
+Our goal as discussed is to gain computational advantage by constructing
+surrogates in a reduced input parameter space. To this end, we construct PCE's
+in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
+fixing $K_w$ in the latter at their respective mean values. In
+Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed in the
+full space (7D) with those constructed in the two reduced spaces (4D and 5D)
+using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). 
 \begin{figure}[htbp]
  \begin{center}
-  \includegraphics[width=0.65\textwidth]{./Figures/ub_conv_borehole}
-\caption{Estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted 
-against number of samples considered for evaluating $\mu_i$. Corresponding estimates
-for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
-legend.}
-\label{fig:screen_bore}
-\end{center}
-\end{figure}
-
-\noindent Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
-even when small number of samples (5 -- 10) are used. 
-Consequently, the relative importance of uncertain 
-parameters in the borehole function is found to be consistent with predictions based on the Sobol' index. 
-In the considered intervals for the uncertain parameters, it is clear that the discharge is insensitive to
-$T_u$ and $T_l$. Moreover, the sensitivity towards $K_w$ is also small. We exploit this result to reduce
-the dimensionality of the problem by 
-discounting the uncertainties in $T_u$, $T_l$, and $K_w$, while using nominal values for these
-parameters instead.
-
-Our goal as discussed is to gain computational advantage by constructing surrogates in a 
-reduced input parameter space. To this end, we construct PCE's in 5D and 4D spaces by
-fixing $\{T_u,T_l\}$ in the former and additionally fixing $K_w$ in the latter at their respective
-mean values. In Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed
-in the full space (7D) with those constructed in the two reduced spaces (4D and 5D) using
-$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}).
-
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.65\textwidth]{./Figures/err_samples_borehole}
+  \includegraphics[width=0.6\textwidth]{./Figures/err_samples_borehole}
 \caption{A comparison of order of the leave-one-out-error 
 ($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
-used for constructing the PCE in 4, 5, and 7 dimensions.}
+used for constructing the PCE in 4, 5, and 7 dimensions. \alennote{Use different line styles
+and colors. Also use thicker lines. Instead of taking log of the error, just use a 
+semilogy in Matlab to use logarithmic scale on the y-axis.}}
 \label{fig:conv_bore}
@@
 
-\noindent As expected, it is observed that the PCE
-constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
-$\mathcal{O}(10^{-4})$ accuracy is sought, we need function evaluations at only about
-50 sample points in the 4D parameter space whereas the number of samples needed in the full 
-7D space seems much higher.
+As expected, it is observed that the PCE constructed in the 4D space converges
+at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
+accuracy is sought, we need function evaluations at only about 50 sample points
+in the 4D parameter space whereas the number of samples needed in the full 7D
+space seems much higher.~\alennote{How are these samples used? Are we doing 
+Latin Hypercube sample, or some other QMC approach?}
 
-As discussed earlier in this section, the reduced order PCE's are verified for predictive accuracy in 
-a least-squares sense and a probabilistic sense. Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$
-based on 50 samples and corresponding function evaluations in the original 7D parameter space
-were found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other words, the 4D
-PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within 1.12$\%$ of predictions based on
-the borehole function. It is interesting to note that although the order of convergence in the case of a 5D
-PCE is lower (Figure~\ref{fig:conv_bore}), its predictive accuracy is higher than the 4D PCE. A possible
-explanation for this observation is that above a certain order of convergence, the uncertainty in $k_w$ 
-contributes much more towards predictive accuracy of the reduced order PCE. It is therefore critical
-to account for the order of PCE convergence as well as its predictive accuracy for a given application,
-as highlighted earlier in section~\ref{sec:method}.
+As discussed earlier in this section, the reduced order PCE's are verified for
+predictive accuracy in a least-squares sense and a probabilistic sense.
+Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$ based on 50 samples and
+corresponding function evaluations in the original 7D parameter space were
+found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other
+words, the 4D PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within
+1.12$\%$ of predictions based on the borehole function. We note  that although
+the convergence in the case of a 5D PCE is slower (Figure~\ref{fig:conv_bore}),
+its predictive accuracy is higher than the 4D PCE. This illustrates the
+tradeoff between accuracy and computational efficiency for the present 
+problem. Generally, the required level of accuracy is problem dependent. 
+The present framework allows for moving towards higher fidelity 
+reduced order surrogates based on the ranking of the parameter sensitivities.
 
-Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the discharge, $\mathcal{Q}$
-obtained by propagating 10$^6$ Monte-Carlo (MC) samples through the 7D PCE in the
-original input parameter domain as well as the reduced order PCE's constructed in 4 and 5 dimensions.
+%A possible explanation for this observation is that above a certain order
+%of convergence, the uncertainty in $k_w$ contributes much more towards
+%predictive accuracy of the reduced order PCE. It is therefore critical to
+%account for the order of PCE convergence as well as its predictive accuracy for
+%a given application, as highlighted earlier in section~\ref{sec:method}.
 
+Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the
+discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ Monte-Carlo (MC)
+samples through the 7D PCE in the original input parameter domain as well as
+the reduced order PCE's constructed in 4 and 5 dimensions. 
 \begin{figure}[htbp]
  \begin{center}
-  \includegraphics[width=0.65\textwidth]{./Figures/pdf_comp_borehole}
+  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
 \caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
@@
 parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
-were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
+were obtained using 10$^{6}$ MC samples in the input parameter domain.
+\alennote{Use thicker lines, different colors in addition to line styles, larger 
+font size, and also use the x-axis limits to be $[0, 300]$, maybe? 
+Once figures 4, 5 are appropriate reformatted, I would combine them in one line as I did 
+things in figure 2.}
+} 
 \label{fig:pdfcomp_bore}
@@
 \end{figure}
-
-\noindent It is evident from this plot, that the PDF's agree quite favorably with each other. Consequently, it can
-be said that the reduced order PCE is verified in a probabilistic sense. In other words, the mode as
-well as the uncertainty in the observable is reliably captured and predicted by the reduced order PCE.
+It is evident from this plot, that the PDF's agree quite favorably with each
+other. Consequently, it can be said that the reduced order PCE is verified in a
+probabilistic sense. In other words, the mode as well as the uncertainty in the
+observable is reliably captured and predicted by the reduced order PCE.
 

### 2018-05-08 Paper/method.tex
..

@@
 
-\node (tol) [process, below of=qoi, text width=8em] {Set an initial tolerance, $\tau$};
+\node (tol) [io, below of=qoi, text width=7em,align=left,yshift=-0.2cm] {Set an initial tolerance, $\tau$};
 
@@
 
-%\node (dr_mean) [right of=dr, xshift=5cm] {DR: Dimension Reduction};
+\node (res) [draw, diamond, aspect=1.5, xshift=4.5cm,text width=4.5em, text centered, right of=dr] {Resource available$?$};
+
+\draw [line] (dr) -- node[anchor=south] {N} (res);
+
+\node (dtol) [io, above of=res, text width=6em,align=left,yshift=1.2cm,text centered]
+ {\vspace{-5mm}\be\tau = \tau - \delta\tau,~\delta\tau > 0\nonumber\ee};
+
+\draw [line] (dtol) -| (screen);
+
+ \draw [line] (res) -- node[anchor=west,yshift=-0.1cm] {Y} (dtol);
+
+\node (ros) [process, below of=dr, text width=11em,yshift=-1.2cm] {Construct a reduced-order surrogate};
+
+\draw [line] (dr) -- node[anchor=east] {Y}(ros);
+
+\node (verify) [process, below of=ros, text width=9em,yshift=-0.2cm] {Verify accuracy of the surrogate};
+
+\draw [line] (ros) -- (verify);
+
+\node (stop) [startstop, below of=verify] {Stop};
+
+\draw [line] (verify) -- (stop);
+
+\draw [line] (res) |- node[anchor=east,yshift=4.3cm] {N} (stop);
 
@@
 \end{figure}
+
+As illustrated in the above flow-diagram, application of the above methodology to construct a reduced-order
+surrogate relies on the choice of an \textit{appropriate} model output. Since the parameters are screened
+using derivative-based sensitivity measures, the model output should exhibit a smooth dependence on the
+individual uncertain parameters to enable a reasonable approximation of the derivatives in Eq.~\ref{eq:mu}.
+Hence, for a given problem involving multiple outputs or model predictions, it is likely that a reduced-order 
+surrogate might be possible for only selected outputs. Hence, where possible, it is recommended to a priori assess the
+nature of dependence of a given model output on the parameters.

### 2018-05-08 Paper/examples.tex
..

@@
 
-In section~\ref{sec:method}, we presented a methodology for screening model
-parameters using an approximate estimate of the upper bound on the Sobol'
-total effect sensitivity index. The screening process helped identify parameters
-that are relatively insignificant with respect to the observable. These insignificant
-parameters could thus be fixed at their nominal values thereby reducing the
-dimensionality of the problem.
-
-In this section, we motivate this approach based
-on parameter screening to construct low-dimensional PC surrogates by 
-applying it to simple test problems: (1) Borehole function, (2) Non-linear Oscillator, and
-(3) Semi-linear Elliptic PDE. Since model evaluations in all these test
-problems are not expensive, it allows us to compare relative importance of
-model parameters,
-obtained using the derivative-based sensitivity approach with that obtained
-using converged estimates of Sobol' total effect sensitivity index, $\mathcal{T}(\theta_i)$.
-
-%\cite{Sobol:2001}:
-%\be
-%\mathcal{T}(\theta_i) = 
-%\frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})}
-%\ee
-
-\noindent $\mathcal{T}(\theta_i)$ is essentially the ratio of the contribution to the variance of an
-observable $\mathcal{G}$ by the parameter $\theta_i$ to the total variance of $\mathcal{G}$.
-Additionally, we compare convergence of the PCE constructed in
-the full parameter space with those constructed in the reduced space. To assess convergence, 
-we rely on the 
-leave-one-out-cross-validation error ($\epsilon_{\mbox{\tiny LOO}}$), defined
-as follows~\cite{Blatman:2010}:
-
-\be
-\epsilon_{\mbox{\tiny LOO}} = 
-\frac{\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
- \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
-{\sum_{i=1}^N
-\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
-\label{eq:loo}
-\ee
-
-\noindent where $\widetilde{\mu}~=~\frac{1}{N}\sum_{i=1}^N \mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i)$
-is the sample mean of the model response, and $ \mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$
-is the PCE surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
-From Eq.~\ref{eq:loo}, it appears that $N$ PCE's are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
-However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
-independent of $\mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
-
-The converged low-dimensional PCE is assessed
-for predictive accuracy. While several techniques could be used, we consider predictive verification
-in an L-2 sense as well as a probabilistic sense. In the former case, we estimate a relative L-2 norm
-of the error ($\epsilon_{\mbox{\tiny{L-2}}}$) as follows:
-
-\be
-\epsilon_{\mbox{\tiny{L-2}}} = 
-\frac{\left[\sum_{i=1}^N\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i) - 
- \mathcal{Y}^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
-{\left[\sum_{i=1}^N
-\left(\mathcal{Y}^{\mbox{\tiny M}}(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
-\label{eq:l2}
-\ee
-
-\noindent As discussed earlier in section~\ref{sec:method}, computational cost associated with
-L-2 verification is negligible since function evaluations or model realizations obtained during the
-screening step could be re-used to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}.
-For the purpose of probabilistic verification, we compare the probability density function of
-the observable obtained using PCE's in the full space and the reduced space in the following
-test problems. In situations where model runs are computationally expensive, probabilistic verification might
-not be feasible.
+In section~\ref{sec:method}, we presented a methodology for constructing
+an ROS by identifying unimportant parameters based on 
+estimates of the upper bound on the Sobol'
+total effect sensitivity index ($\mathcal{T}(\theta_i)$) for individual parameters.
+In this section, we motivate the methodology by applying it to three test problems,
+namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
+Since model evaluations in all these test
+problems are inexpensive, we compare relative importance of model parameters based
+on DGSMs, obtained using model predictions with 
+converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate, constructed in the
+full parameter space. Additionally, to illustrate computational gains, we compare
+convergence trends as a function of training runs for the ROS with the full-space
+surrogate. Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
+PDFs of the model output, obtained using the ROS and the full-space surrogate for
+the purpose of verification.
 

### 2018-05-08 Paper/intro.tex
..

@@
 in a tractable manner. Polynomial chaos expansion 
-(PCE)~\cite{Xiu:2002,Ghanem:2003,Eldred:2008,Olivier:2010} and 
+(PCE)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010} and 
 Gaussian Process (GP)~\cite{Rasmussen:2004} or Kriging~\cite{Stein:2012} are
@@
 are significantly less important that the rest, thereby reducing the dimensionality of the
-problem and enabling the construction of a reduced-order surrogate. As discussed in
+problem and enabling the construction of a reduced-order surrogate (ROS). As discussed in
 section~\ref{sec:method}, parameter ranks are determined using a \textit{screening-metric}

### 2018-05-08 Paper/method.tex
..

--- 2018-05-06 Paper/method.tex
@@
 In this section, we outline the underlying methodology for constructing a 
-reduced-order surrogate using sensitivity analysis. The term `reduced-order'
+reduced-order surrogate (ROS) using sensitivity analysis. The term `reduced-order'
 in the present context implies that the surrogate is constructed in a 
 subspace that sufficiently captures the uncertainty in the model output. 
-For instance, in the case of PC surrogates, the dimensionality of the polynomial
-basis functions is effectively reduced. A possible approach to 
-constructing a reduced-order surrogate involves sensitivity analysis of the
+In the case of PC surrogates used in this work, it implies that the dimensionality
+of the polynomial basis functions is effectively reduced.
+
+A possible approach to 
+constructing the ROS involves sensitivity analysis of the
 uncertain model parameters with respect to a given output, and thereby
@@
 of model evaluations. Consequently, the exercise becomes prohibitive in
-situations where the model runs are compute-intensive. Instead, we estimate a normalized
-upper-bound ($\widehat{\mathcal{C}_i\mu_i}$, see Eq.~\ref{eq:bound}) on the Sobol total
-effect index ($\mathcal{T}(\theta_i)$) for each parameter, $\theta_i$, and use it as a 
-metric to identify the unimportant parameters. Below, we provide an algorithm for 
-parameter screening. It is assumed that the partial derivatives in Eq.~\ref{eq:mu}
-are estimated using finite difference.
+situations where the model runs are compute-intensive. Instead, we adopt a novel approach
+that focuses on estimating the upper-bound
+upper-bound ($\widehat{\mathcal{C}_i\mu_i}$, see Eq.~\ref{eq:bound}) on Sobol total
+effect index ($\mathcal{T}(\theta_i)$) for each parameter, $\theta_i$, and using it as a 
+metric to screen parameters that are relatively unimportant. Below, we provide a generalized
+strategy for parameter screening.
 
@@
 \begin{breakablealgorithm}
-  \caption{Parameter screening with derivative-based sensitivity measures.}
+  \caption{Parameter screening with DGSMs: A generalized approach.}
   \begin{algorithmic}[1]
     \Procedure{Screening}{}
-      \State Generate $n_1$ points in $\mathbb{R}^{d}$.\Comment{$d$: 
-             Number of uncertain model parameters.}
-      \State Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.
-      \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
-      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\widehat{\mathcal{C}_i\mu_i}$ values for $\theta_i$.
-      \State set $k$ = 1\Comment{Iteration counter}
+      \State Generate $n_1$ samples in $\mathbb{R}^{N_p}$ according to the joint probability density, $\bm{f(\theta)}$.
+      \State Evaluate the gradient vector, $\nabla_{\bm{\theta}}G_k$ at each sample point, $\bm{\theta}_k$.
+      \State Approximate sensitivity measures, $\bm{\mu}$: \be\bm{\mu} \approx \hat{\bm{\mu}} = 
+      \frac{1}{n_1}\sum\limits_{k=1}^{n_1}(\nabla_{\bm{\theta}}G_k)(\nabla_{\bm{\theta}}G_k)^{T}\nonumber\ee
+      \State Estimate $\widehat{\mathcal{C}_i\mu_i}$ for each parameter, $\theta_i$ and determine initial ranks,
+       $\mathcal{R}^{old}$.
+      \State set $s$ = 1\Comment{Iteration counter}
       \Do
-        \State Generate $n_k$ new points in $\mathbb{R}^{d}$.
-        \State Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.
-        \State Compute and store model evaluations at the $n_k(d+1)$ points.
-        \State Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.
+        \State Generate $n_s$ new points in $\mathbb{R}^{N_p}$.
         \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
-        \State Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - 
-               \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.\Comment{$max\_pdev$:
-               Maximum percentage deviation in $\mu_i$ between successive iterations.}
-        \State set $k$ = $k$ + 1
+        \State Compute $\Delta\mu_m$ = max$\left(\frac{|\mu_{i,s} - 
+               \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.\Comment{$\Delta\mu_m$:
+               Maximum deviation in $\mu_i$ between successive iterations.}
+        \State set $s$ = $s$ + 1
       \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
-               $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
+               $\Delta\mu_m$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
     \EndProcedure
@@
 
+In case the gradient, $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically, we could use finite-difference
+to approximate its value as shown in Eq.~\ref{eq:partial}. In that case, the above algorithm could be adapted as
+follows:
+
+\bigskip
+
+\begin{breakablealgorithm}
+  \caption{Parameter screening with DGSMs using finite differences.}
+  \begin{algorithmic}[1]
+    \Procedure{Screening}{}
+      \State Generate $n_1$ samples in $\mathbb{R}^{N_p}$ according to the joint probability density, $\bm{f(\theta)}$.
+      \State Perturb each point along the $N_p$ directions to obtain a set of $n_1(N_p+1)$ samples.
+      \State Estimate $\nabla_{\bm{\theta}}G_k$ using model evaluations at the $n_1$ samples and the corresponding 
+                 neighbouring samples for each component of $\bm{\theta}$.
+      \State Approximate sensitivity measures, $\bm{\mu}$: \be\bm{\mu} \approx \hat{\bm{\mu}} = 
+      \frac{1}{n_1}\sum\limits_{k=1}^{n_1}(\nabla_{\bm{\theta}}G_k)(\nabla_{\bm{\theta}}G_k)^{T}\nonumber\ee
+      \State Estimate $\widehat{\mathcal{C}_i\mu_i}$ for each parameter, $\theta_i$ and determine initial ranks,
+       $\mathcal{R}^{old}$.
+      \State set $s$ = 1\Comment{Iteration counter}
+      \Do
+        \State Generate $n_s$ new points in $\mathbb{R}^{N_p}$.
+        \State Perturb each point along the $N_p$ directions to obtain a set of $n_s(N_p+1)$ points.
+        \State Compute $\mu_i$ using model evaluations at $(N_p+1)(n_1 + \sum\limits_j^s n_j)$ points.
+        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
+        \State Compute $\Delta\mu_m$ = max$\left(\frac{|\mu_{i,s} - 
+               \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.\Comment{$\Delta\mu_m$:
+               Maximum deviation in $\mu_i$ between successive iterations.}
+        \State set $s$ = $s$ + 1
+      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
+               $\Delta\mu_m$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
+    \EndProcedure
+  \end{algorithmic}
+\end{breakablealgorithm}
+
+\bigskip
+
+%\bigskip
+%
+%\begin{breakablealgorithm}
+%  \caption{Parameter screening with derivative-based sensitivity measures.}
+%  \begin{algorithmic}[1]
+%    \Procedure{Screening}{}
+%      \State Generate $n_1$ points in $\mathbb{R}^{d}$.\Comment{$d$: 
+%             Number of uncertain model parameters.}
+%      \State Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.
+%      \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
+%      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\widehat{\mathcal{C}_i\mu_i}$ values for $\theta_i$.
+%      \State set $k$ = 1\Comment{Iteration counter}
+%      \Do
+%        \State Generate $n_k$ new points in $\mathbb{R}^{d}$.
+%        \State Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.
+%        \State Compute and store model evaluations at the $n_k(d+1)$ points.
+%        \State Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.
+%        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
+%        \State Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - 
+%               \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.\Comment{$max\_pdev$:
+%               Maximum percentage deviation in $\mu_i$ between successive iterations.}
+%        \State set $k$ = $k$ + 1
+%      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
+%               $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
+%    \EndProcedure
+%  \end{algorithmic}
+%\end{breakablealgorithm}
+%
+%\bigskip
+
 Based on the steps outlined in the above algorithm, it can be said that the set of sample points used for
@@
 metric for each uncertain parameter is accomplished. Parameter
-screening is an integral part of the overall strategy for constructing the reduced-order surrogate as 
+screening is an integral part of the overall strategy for constructing the ROS as 
 depicted below using a flow-diagram.
@@
 
+\begin{figure}[htbp]
 \begin{center}
+
+\tikzset{
+    arro/.style={{Square[]->}}
+}
+
 \begin{tikzpicture}[node distance=1.5cm]
@@
 
-\draw [line] (start) -- (qoi);
+\draw [arro] (start) -- (qoi);
 
-\node (tol) [process, below of=qoi, text width=8em] {Set an initial tolerance, $\tau$};
+\node (tol) [io, below of=qoi, text width=7em,align=left,yshift=-0.2cm] {Set an initial tolerance, $\tau$};
 
-\draw [line] (qoi) -- (tol);
+\draw [arro] (qoi) -- (tol);
 
@@
 
-\draw [line] (tol) -- (screen);
+\draw [arro] (tol) -- (screen);
 
-\node (dr) [draw, diamond, aspect=2.0] {Is \\ Dimension-reduction \\ possible$?$};
+\node (dr) [draw, diamond, aspect=1.5,yshift=-6.9cm, text width=4.5em, text centered] {Is DR possible$?$};
+
+\draw [arro] (screen) -- (dr);
+
+\node (fss) [process, right of=dr, text width=9em,xshift=3.5cm] {Construct full-space surrogate (FSS)};
+
+\draw [arro] (dr) -- node[anchor=south] {N} (fss);
+
+\node (res) [draw, diamond, aspect=1.5, xshift=3.5cm,text width=4.5em, text centered, right of=fss] {FSS converged$?$};
+
+\draw [arro] (fss) -- (res);
+
+\node (dtol) [io, above of=res, text width=6em,align=left,yshift=1.2cm,text centered]
+ {\vspace{-5mm}\be\tau = \tau - \delta\tau,~\delta\tau > 0\nonumber\ee};
+
+\draw [arro] (dtol) -| (screen);
+
+ \draw [arro] (res) -- node[anchor=west,yshift=-0.1cm] {N} (dtol);
+
+ \node (assess) [process, below of=dr, text width=11em,yshift=-1.2cm] {If applicable, assess $\alpha$ and convergence
+  of FSS};
+
+ \draw [arro] (dr) -- node[anchor=east] {Y}(assess);
+
+ \node (con) [draw, diamond, aspect=1.5,text width=4em, text centered, below of=assess,yshift=-0.7cm] {Continue$?$};
+
+ \draw [arro] (assess) -- (con);
+
+\node (ros) [process, below of=con, text width=6em, yshift=-0.7cm] {Construct the ROS};
+
+ \draw [arro] (con) -- node[anchor=east] {Y}(ros);
+
+\node (verify) [process, below of=ros, text width=9em,yshift=-0.2cm] {Verify accuracy of the surrogate};
+
+\draw [arro] (ros) -- (verify);
+
+\node (stop) [startstop, right of=verify,xshift=3.5cm] {Stop};
+
+\draw [arro] (verify) -- (stop);
+
+\draw [arro] (res) |- node[anchor=east,yshift=6.9cm] {Y} (stop);
+
+\draw [arro] (con) -| node[anchor=south,xshift=-3cm] {N} (stop);
 
@@
 \end{center}
+
+\caption{Flow-diagram outlining the overall strategy for constructing reduced-order surrogates using
+DGSMs. Note that DR is an abbreviation for dimension reduction.}
+\label{fig:flow}
+\end{figure}
+
+As illustrated in the above flow-diagram, application of the above methodology to construct an ROS 
+relies on the choice of an \textit{appropriate} model output. Since the parameters are screened
+using DGSMs, the model output should exhibit a smooth dependence on the
+individual uncertain parameters to enable a reasonable approximation of the derivatives in Eq.~\ref{eq:mu}.
+Thus, for a given problem involving multiple outputs or model predictions, it is likely that a reduced-order 
+surrogate might be possible only for selected outputs. Hence, where possible, it is recommended to a priori assess the
+nature of dependence of a given model output on the parameters.
+
+The amount of computational effort associated with the presented methodology can be mainly attributed to
+two steps: I. Parameter Screening, and II. Constructing a converged ROS. Computational gains are realized
+in situations where constructing the surrogate in the full parameter space is more expensive than the combined cost
+associated with these steps. Determining the optimal allocation of computational resources for these steps, however, 
+is not possible a priori. Hence, we suggest estimating the DGSMs on a small set of samples (say, $n_1$ = 5) 
+initially, and screening with a relatively large value of tolerance, $\tau$ while keeping a track of computational expense.
+Tighter tolerances on $\bm{\mu}$ are
+gradually imposed until the screening process yields conclusive results pertaining to the possibility of dimension-reduction
+or a reasonably converged surrogate is constructed using the available set of model evaluations in the full parameter space. 
+Hence, the combined computational cost associated with steps I and II could be less, equal to, or greater than that needed
+to construct the surrogate in the full parameter space. To avoid the case of greater computational effort, we suggest 
+that the decision to construct the ROS should account for the degree of dimension-reduction predicted at the end of the
+screening step ($\alpha$, defined below in Eq.~\ref{eq:alpha}), and the state of convergence of the full-space surrogate. 
+Enormous computational savings are in fact possible when dealing with complex, 
+compute-intensive models, even if $\alpha$ in the following equation is
+not too large.
+
+\be
+\alpha = \frac{\mbox{Dimensionality of ROS}}{\mbox{Dimensionality of the full surrogate}}
+\label{eq:alpha}
+\ee
+
+In order to assess convergence of the ROS, we estimate the leave-one-out cross validation error as
+follows:
+
+\be
+\epsilon_{\mbox{\tiny LOO}} = 
+\frac{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - G^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
+{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
+\label{eq:loo}
+\ee
+
+\noindent where $N_l$ is the number of training points, 
+$\widetilde{\mu}~=~\frac{1}{N}\sum\limits_{i=1}^N G(\bm{\theta}_i)$
+is the sample mean of the model response, and $ G^{\mbox{\tiny {PC}\textbackslash i}}$
+is the PCE surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
+From Eq.~\ref{eq:loo}, it appears that $N$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
+However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
+independent of $\mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
+
+Finally, as outlined in Figure~\ref{fig:flow}, the converged ROS is verified for predictive accuracy. 
+To this end, we compute a relative L-2 norm of the difference in predictions between the model
+and the ROS ($\epsilon_{\mbox{\tiny{L-2}}}$) as follows:
+
+\be
+\epsilon_{\mbox{\tiny{L-2}}} = \frac{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i) - 
+G^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
+{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
+\label{eq:l2}
+\ee
+
+\noindent where $N_v$ is the number of sampling points in the full parameter space at which model
+evaluations are available. It must be noted that the computational effort associated with estimating
+ $\epsilon_{\mbox{\tiny{L-2}}}$
+is negligible since we exploit the available set of model evaluations in the full parameter space, generated
+during the screening step. Additionally, probability density function (PDF) based on these full-space 
+model evaluations are compared with the PDF generated using a large set of evaluations of the same
+output from the ROS.

### 2018-05-08 Paper/examples.tex
..

@@
 full parameter space. Additionally, to illustrate computational gains, we compare
-convergence trends as a function of training runs for the ROS with the full-space
+convergence trends as a function of training runs for the ROS and the full-space
 surrogate. Furthermore, as discussed earlier in section~\ref{sec:method}, we compare

### 2018-05-09 Paper/method.tex
..

@@
 However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
-independent of $\mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
+independent of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
 

### 2018-05-09 Paper/examples.tex
..

@@
   \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
-  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_borehole}
+  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
 \caption{
@@
 function. Right: 
-estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted
+estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$) is plotted
 against number of samples considered for evaluating $\mu_i$. Corresponding estimates
 for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
-legend. \alennote{Can we have larger fontsizes for the right image? Also the y-axis label
-needs to be modified with a widehat as done in the text now.}}
+legend. }
 \label{fig:sense_bore}

### 2018-05-09 Paper/method.tex
updated alg 1 ...

@@
 
-\bigskip
-
+\clearpage
 \begin{breakablealgorithm}
@@
     \Procedure{Screening}{}
-      \State Generate $n_1$ samples in $\mathbb{R}^{N_p}$ according to the joint probability density, $\bm{f(\theta)}$.
-      \State Evaluate the gradient vector, $\nabla_{\bm{\theta}}G_k$ at each sample point, $\bm{\theta}_k$.
-      \State Approximate sensitivity measures, $\bm{\mu}$: \be\bm{\mu} \approx \hat{\bm{\mu}} = 
-      \frac{1}{n_1}\sum\limits_{k=1}^{n_1}(\nabla_{\bm{\theta}}G_k)(\nabla_{\bm{\theta}}G_k)^{T}\nonumber\ee
-      \State Estimate $\widehat{\mathcal{C}_i\mu_i}$ for each parameter, $\theta_i$ and determine initial ranks,
-       $\mathcal{R}^{old}$.
-      \State set $s$ = 1\Comment{Iteration counter}
-      \Do
-        \State Generate $n_s$ new points in $\mathbb{R}^{N_p}$.
-        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
-        \State Compute $\Delta\mu_m$ = max$\left(\frac{|\mu_{i,s} - 
-               \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.\Comment{$\Delta\mu_m$:
-               Maximum deviation in $\mu_i$ between successive iterations.}
-        \State set $s$ = $s$ + 1
-      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
-               $\Delta\mu_m$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
+      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
+       according to the probability density $\bm{f(\theta)}$.
+      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
+             $k = 1, \ldots, n_1$.
+
+      \State Compute 
+      $\mu_{1, i} = \frac{1}{n_1} \sum_{k = 1}^{n_1} (g^k_i)^2$
+      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
+             $i = 1, \ldots, \Np$. 
+      \State Determine initial ranks: 
+            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{n_1}$ such that 
+\[
+   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
+\]
+      \State Set $s$ = 1.
+      \State Set $\mathrm{done} = \mathrm{false}$.
+      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
+        \State Set $s = s + 1$.
+        \State Draw $n_s$ new samples 
+                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
+        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
+             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
+
+        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
+               $\{\bm{g}_k \}_{k = 1}^{n_{s-1}+n_s}$.
+        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
+        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
+        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
+               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
+      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
+         \State $\mathrm{done} = \mathrm{true}$
+      \Else
+          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
+      \EndIf
+    \EndWhile
     \EndProcedure

### 2018-05-10 Paper/examples.tex
..

@@
 fixing $K_w$ in the latter at their respective mean values. In
-Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed in the
+Figure~\ref{fig:conv_bore}(left), we compare convergence of PCE's constructed in the
 full space (7D) with those constructed in the two reduced spaces (4D and 5D)
@@
  \begin{center}
-  \includegraphics[width=0.6\textwidth]{./Figures/err_samples_borehole}
-\caption{A comparison of order of the leave-one-out-error 
+  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_borehole}
+  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_borehole}
+\caption{Left: A comparison of order of the leave-one-out-error 
 ($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
-used for constructing the PCE in 4, 5, and 7 dimensions. \alennote{Use different line styles
-and colors. Also use thicker lines. Instead of taking log of the error, just use a 
-semilogy in Matlab to use logarithmic scale on the y-axis.}}
+used for constructing the PCE in 4, 5, and 7 dimensions. Right: A comparison of
+PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
+the marginal distributions of the uncertain parameters in each case.} 
 \label{fig:conv_bore}
@@
 
-Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the
-discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ Monte-Carlo (MC)
+Figure~\ref{fig:conv_bore}(right) illustrates a comparison of the PDFs
+of the
+discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ random
 samples through the 7D PCE in the original input parameter domain as well as
-the reduced order PCE's constructed in 4 and 5 dimensions. 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
-\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
-by propagating
-parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
-were obtained using 10$^{6}$ MC samples in the input parameter domain.
-\alennote{Use thicker lines, different colors in addition to line styles, larger 
-font size, and also use the x-axis limits to be $[0, 300]$, maybe? 
-Once figures 4, 5 are appropriate reformatted, I would combine them in one line as I did 
-things in figure 2.}
-} 
-\label{fig:pdfcomp_bore}
-\end{center}
-\end{figure}
-It is evident from this plot, that the PDF's agree quite favorably with each
-other. Consequently, it can be said that the reduced order PCE is verified in a
+the reduced order PCEs constructed in 4 and 5 dimensions. 
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
+%\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
+%by propagating
+%parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
+%were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
+%\label{fig:pdfcomp_bore}
+%\end{center}
+%\end{figure}
+It is evident from this plot, that the PDFs agree quite favorably with each
+other with respect to the modal estimate as well as the uncertainty associated with 
+$\mathcal{Q}$. 
+Consequently, it can be said that the reduced order PCE is verified in a
 probabilistic sense. In other words, the mode as well as the uncertainty in the

### 2018-05-12 Paper/method.tex
minor ...
..

@@
 \clearpage
+
 \begin{breakablealgorithm}
@@
        according to the probability density $\bm{f(\theta)}$.
+       \State $N_t = N_t + n_1$
       \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
@@
       \State Compute 
-      $\mu_{1, i} = \frac{1}{n_1} \sum_{k = 1}^{n_1} (g^k_i)^2$
+      $\mu_{1, i} = \frac{1}{N_t} \sum_{k = 1}^{N_t} (g^k_i)^2$
       \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
@@
       \State Determine initial ranks: 
-            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{n_1}$ such that 
+            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{N_t}$ such that 
 \[
@@
       \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
-        \State Set $s = s + 1$.
+        \State $s = s + 1$
+        \State $N_t = N_t + n_s$
         \State Draw $n_s$ new samples 
-                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
-        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
-             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
-
+                  $\bm{\theta}_k$, $k = 1, \ldots, n_s$
+        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$
         \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
-               $\{\bm{g}_k \}_{k = 1}^{n_{s-1}+n_s}$.
+               $\{\bm{g}_k \}_{k = 1}^{N_t}$.
         \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
@@
     \EndWhile
+    \State $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \nu_i \ni \displaystyle\frac{\nu_i}{\max(\bm{\nu})}> \tau_\text{screen}\}.$
+
     \EndProcedure
   \end{algorithmic}
+  \label{alg:screen}
 \end{breakablealgorithm}
+
+%\begin{breakablealgorithm}
+%  \caption{Parameter screening with DGSMs: A generalized approach.}
+%  \begin{algorithmic}[1]
+%    \Procedure{Screening}{}
+%      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
+%       according to the probability density $\bm{f(\theta)}$.
+%      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
+%             $k = 1, \ldots, n_1$. 
+%
+%      \State Compute 
+%      $\mu_{1, i} = \frac{1}{n_1} \sum_{k = 1}^{n_1} (g^k_i)^2$
+%      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
+%             $i = 1, \ldots, \Np$. 
+%      \State Determine initial ranks: 
+%            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{n_1}$ such that 
+%\[
+%   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
+%\]
+%      \State Set $s$ = 1.
+%      \State Set $\mathrm{done} = \mathrm{false}$.
+%      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
+%        \State Set $s = s + 1$.
+%        \State Draw $n_s$ new samples 
+%                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
+%        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
+%             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
+%
+%        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
+%               $\{\bm{g}_k \}_{k = 1}^{n_{s-1}+n_s}$.
+%        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
+%        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
+%        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
+%               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
+%      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
+%         \State $\mathrm{done} = \mathrm{true}$
+%      \Else
+%          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
+%      \EndIf
+%    \EndWhile
+%    \State Let $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \nu_i \ni \displaystyle\frac{\nu_i}{\max(\bm{\nu})}> \tau_\text{screen}\}.$
+%    
+%    \EndProcedure
+%  \end{algorithmic}
+%  \label{alg:screen}
+%\end{breakablealgorithm}
 
@@
 In case the gradient, $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically, we could use finite-difference
-to approximate its value as shown in Eq.~\ref{eq:partial}. In that case, the above algorithm could be adapted as
-follows:
-
-\bigskip
-
-\begin{breakablealgorithm}
-  \caption{Parameter screening with DGSMs using finite differences.}
-  \begin{algorithmic}[1]
-    \Procedure{Screening}{}
-      \State Generate $n_1$ samples in $\mathbb{R}^{N_p}$ according to the joint probability density, $\bm{f(\theta)}$.
-      \State Perturb each point along the $N_p$ directions to obtain a set of $n_1(N_p+1)$ samples.
-      \State Estimate $\nabla_{\bm{\theta}}G_k$ using model evaluations at the $n_1$ samples and the corresponding 
-                 neighbouring samples for each component of $\bm{\theta}$.
-      \State Approximate sensitivity measures, $\bm{\mu}$: \be\bm{\mu} \approx \hat{\bm{\mu}} = 
-      \frac{1}{n_1}\sum\limits_{k=1}^{n_1}(\nabla_{\bm{\theta}}G_k)(\nabla_{\bm{\theta}}G_k)^{T}\nonumber\ee
-      \State Estimate $\widehat{\mathcal{C}_i\mu_i}$ for each parameter, $\theta_i$ and determine initial ranks,
-       $\mathcal{R}^{old}$.
-      \State set $s$ = 1\Comment{Iteration counter}
-      \Do
-        \State Generate $n_s$ new points in $\mathbb{R}^{N_p}$.
-        \State Perturb each point along the $N_p$ directions to obtain a set of $n_s(N_p+1)$ points.
-        \State Compute $\mu_i$ using model evaluations at $(N_p+1)(n_1 + \sum\limits_j^s n_j)$ points.
-        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
-        \State Compute $\Delta\mu_m$ = max$\left(\frac{|\mu_{i,s} - 
-               \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.\Comment{$\Delta\mu_m$:
-               Maximum deviation in $\mu_i$ between successive iterations.}
-        \State set $s$ = $s$ + 1
-      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
-               $\Delta\mu_m$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
-    \EndProcedure
-  \end{algorithmic}
-\end{breakablealgorithm}
-
-\bigskip
-
-%\bigskip
-%
-%\begin{breakablealgorithm}
-%  \caption{Parameter screening with derivative-based sensitivity measures.}
-%  \begin{algorithmic}[1]
-%    \Procedure{Screening}{}
-%      \State Generate $n_1$ points in $\mathbb{R}^{d}$.\Comment{$d$: 
-%             Number of uncertain model parameters.}
-%      \State Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.
-%      \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
-%      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\widehat{\mathcal{C}_i\mu_i}$ values for $\theta_i$.
-%      \State set $k$ = 1\Comment{Iteration counter}
-%      \Do
-%        \State Generate $n_k$ new points in $\mathbb{R}^{d}$.
-%        \State Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.
-%        \State Compute and store model evaluations at the $n_k(d+1)$ points.
-%        \State Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.
-%        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\widehat{\mathcal{C}_i\mu_i}$ values.
-%        \State Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - 
-%               \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.\Comment{$max\_pdev$:
-%               Maximum percentage deviation in $\mu_i$ between successive iterations.}
-%        \State set $k$ = $k$ + 1
-%      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
-%               $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
-%    \EndProcedure
-%  \end{algorithmic}
-%\end{breakablealgorithm}
-%
-%\bigskip
+to approximate its value as shown in Eq.~\ref{eq:partial} in Algorithm~\ref{alg:screen}. However, as discussed earlier
+in section 2.1, estimating $\bm{\mu}$  using $\mathcal{N}$ samples in the full parameter space requires 
+model evaluations at model evaluations at $(N_p+1)\mathcal{N}$ samples, compared to only $\mathcal{N}$ samples in 
+situations where the derivative is available analytically. Hence, computational effort when using finite differences
+is increased by a factor of $(N_p+1)$.
 
@@
 between successive iterations as well as a certain degree of convergence in estimates of the screening 
-metric for each uncertain parameter is accomplished. Parameter
+metric for each uncertain parameter is accomplished. However, the amount of computational effort associated
+the screening process is limited by the choice of maximum number of iterations Parameter
 screening is an integral part of the overall strategy for constructing the ROS as 
@@
 
-\node (tol) [io, below of=qoi, text width=7em,align=left,yshift=-0.2cm] {Set an initial tolerance, $\tau$};
+\node (tol) [io, below of=qoi, text width=9em,align=left,yshift=-0.2cm] {Initialize: $\tau$, $\tau_\text{screen}$, 
+$s_\text{max}$, $N_t$ = 0};
 
@@
 
-\node (dr) [draw, diamond, aspect=1.5,yshift=-6.9cm, text width=4.5em, text centered] {Is DR possible$?$};
+\node (output) [process, below of=screen, text width=9.5em] {Compute $\alpha$ based on $\mathcal{I}_\text{active}$};
 
-\draw [arro] (screen) -- (dr);
+\draw [arro] (screen) -- (output);
+
+\node (dr) [draw, diamond, aspect=1.5,yshift=-8.4cm, text width=4.5em, text centered] {If $\alpha < 1$};
+
+\draw [arro] (output) -- (dr);
 
@@
 
-\node (dtol) [io, above of=res, text width=6em,align=left,yshift=1.2cm,text centered]
- {\vspace{-5mm}\be\tau = \tau - \delta\tau,~\delta\tau > 0\nonumber\ee};
+\node (dtol) [io, above of=res, text width=8.7em,align=left,yshift=2.8cm] {Update: $\tau$, $s_\text{max}$, $N_t$};
 
@@
 
- \draw [arro] (res) -- node[anchor=west,yshift=-0.1cm] {N} (dtol);
+ \draw [arro] (res) -- node[anchor=east,yshift=-0.6cm] {N} (dtol);
 
@@
 
-\caption{Flow-diagram outlining the overall strategy for constructing reduced-order surrogates using
-DGSMs. Note that DR is an abbreviation for dimension reduction.}
+\caption{Flow-diagram outlining the adaptive strategy for constructing reduced-order surrogates using
+DGSMs.}
 \label{fig:flow}

### 2018-05-13 Paper/method.tex
...
..

@@
 \clearpage
-
+\iffalse
 \begin{breakablealgorithm}
@@
 \end{breakablealgorithm}
+\fi
 
-%\begin{breakablealgorithm}
-%  \caption{Parameter screening with DGSMs: A generalized approach.}
-%  \begin{algorithmic}[1]
-%    \Procedure{Screening}{}
+%%%%%%%%%%%
+
+\begin{breakablealgorithm}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \caption{Parameter screening with DGSMs: A generalized approach.}
+  \begin{algorithmic}[1]
+\Require $\tau > 0$, $\tau_\text{screen} > 0$,
+$s_\text{max}$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$. 
+\Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
+    \Procedure{Screening}{}
     %  \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
      %  according to the probability density $\bm{f(\theta)}$.
-%      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
-%             $k = 1, \ldots, n_1$. 
-%
-%      \State Compute 
-%      $\mu_{1, i} = \frac{1}{n_1} \sum_{k = 1}^{n_1} (g^k_i)^2$
-%      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
-%             $i = 1, \ldots, \Np$. 
-%      \State Determine initial ranks: 
-%            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{n_1}$ such that 
-%\[
-%   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
-%\]
-%      \State Set $s$ = 1.
-%      \State Set $\mathrm{done} = \mathrm{false}$.
-%      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
-%        \State Set $s = s + 1$.
-%        \State Draw $n_s$ new samples 
-%                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
-%        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
-%             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
-%
-%        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
-%               $\{\bm{g}_k \}_{k = 1}^{n_{s-1}+n_s}$.
-%        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
-%        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
-%        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
-%               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
-%      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
-%         \State $\mathrm{done} = \mathrm{true}$
-%      \Else
-%          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
-%      \EndIf
-%    \EndWhile
-%    \State Let $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \nu_i \ni \displaystyle\frac{\nu_i}{\max(\bm{\nu})}> \tau_\text{screen}\}.$
-%    
-%    \EndProcedure
-%  \end{algorithmic}
-%  \label{alg:screen}
-%\end{breakablealgorithm}
+     %   \State $N_\text{total} = N_\text{total} + n_1$.
+      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
+             $k = 1, \ldots, n_1$.
+
+      \State Compute 
+      $\mu_{1, i} = \frac{1}{N_\text{total}} \sum_{k = 1}^{N_\text{total}} (g^k_i)^2$
+      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
+             $i = 1, \ldots, \Np$. 
+      \State Determine initial ranks: 
+            let $\mathcal{R}^{old} = \{ \nu_{i_1}, \nu_{i_2}, \ldots, \nu_{i_\Np}\}$ such that 
+\[
+   \nu_{i_1} \geq \nu_{i_2} \geq \cdots \geq \nu_{i_\Np}. 
+\]
+      \State Set $s$ = 1.
+      \State Set $\mathrm{done} = \mathrm{false}$.
+      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
+        \State $s = s + 1$.
+        \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
+                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
+       \State $N_\text{total} = N_\text{total} + n_s$.
+        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
+             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
+
+        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
+               $\{\bm{g}_k \}_{k = 1}^{N_\text{total}}$.
+        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
+        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
+        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
+               \left(\frac{|\mu_{s,i} - \mu_{s-1,i}|}{ \mu_{s-1,i}}\right)$.
+      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
+         \State $\mathrm{done} = \mathrm{true}$
+      \Else
+          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
+      \EndIf
+    \EndWhile
+    \State $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \displaystyle\frac{\nu_i}
+        {\|\bm{\nu}\|_\infty} > \tau_\text{screen}\}.$
+
+    \EndProcedure
+  \end{algorithmic}
+  \label{alg:screen}
+\end{breakablealgorithm}
 
@@
 
-\node (qoi) [io, below of=start,align=left] {Select an appropriate model output};
+\node (val) [process, below of=start, text width=14.5em] {Construct a validation test suite using
+pre-allocated resources.};
 
-\draw [arro] (start) -- (qoi);
+\draw [arro] (start) -- (val);
+
+\node (qoi) [io, below of=val,align=left,yshift=-0.2cm] {Select an appropriate model output};
+
+\draw [arro] (val) -- (qoi);
 
 \node (tol) [io, below of=qoi, text width=9em,align=left,yshift=-0.2cm] {Initialize: $\tau$, $\tau_\text{screen}$, 
-$s_\text{max}$, $N_t$ = 0};
+$s_\text{max}$, $\beta$, $N_\text{total}$ = 0};
 
@@
 
-\node (screen) [process, below of=tol, text width=9.5em] {Parameter Screening};
+\node (sam0) [process, below of=tol, text width=12.5em, yshift=-0.3cm] {Draw $n_0$ samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
+     according to $\bm{f(\theta)}$};
 
-\draw [arro] (tol) -- (screen);
+\draw [arro] (tol) -- (sam0);
 
-\node (output) [process, below of=screen, text width=9.5em] {Compute $\alpha$ based on $\mathcal{I}_\text{active}$};
+\node (counter) [process, below of=sam0, text width=9.5em, yshift=-0.21cm] {\vspace{-6mm}\be N_\text{total} = N_\text{total} + n_0 \nonumber\ee};
 
-\draw [arro] (screen) -- (output);
+\draw [arro] (sam0) -- (counter);
 
-\node (dr) [draw, diamond, aspect=1.5,yshift=-8.4cm, text width=4.5em, text centered] {If $\alpha < 1$};
+\node (fss) [process, below of=counter, text width=14.5em, yshift=-0.28cm] {Construct regression-based 
+surrogate in full-space (FSS) uing $N_\text{total}$ model evaluations};
 
-\draw [arro] (output) -- (dr);
+\draw [arro] (counter) -- (fss);
 
-\node (fss) [process, right of=dr, text width=9em,xshift=3.5cm] {Construct full-space surrogate (FSS)};
+\node (chk) [process, below of=fss, text width=12.5em, yshift=-0.5cm] {Assess accuracy of FSS using the
+validation test suite};
 
-\draw [arro] (dr) -- node[anchor=south] {N} (fss);
+\draw [arro] (fss) -- (chk);
 
-\node (res) [draw, diamond, aspect=1.5, xshift=3.5cm,text width=4.5em, text centered, right of=fss] {FSS converged$?$};
+\node (res) [draw, diamond, aspect=1.5, text width=7.5em, text centered, below of=chk,yshift=-1.5cm] {Is \\ FSS, 
+sufficiently accurate$?$};
 
-\draw [arro] (fss) -- (res);
+\draw [arro] (chk) -- (res);
 
-\node (dtol) [io, above of=res, text width=8.7em,align=left,yshift=2.8cm] {Update: $\tau$, $s_\text{max}$, $N_t$};
+\node (screen) [process, right of=res, text width=9.5em, xshift=4.5cm] {Parameter Screening};
 
-\draw [arro] (dtol) -| (screen);
+\draw [arro] (res) -- node[anchor=north] {N} (screen);
 
- \draw [arro] (res) -- node[anchor=east,yshift=-0.6cm] {N} (dtol);
+\node (dr) [draw, diamond, aspect=1.8, text width=7.5em, text centered, right of=screen,xshift=4cm] {Is $\alpha$
+small enough$?$};
 
- \node (assess) [process, below of=dr, text width=11em,yshift=-1.2cm] {If applicable, assess $\alpha$ and convergence
-  of FSS};
+\draw [arro] (screen) -- (dr);
 
- \draw [arro] (dr) -- node[anchor=east] {Y}(assess);
+\node (dtol) [io, above of=dr, text width=8.7em,align=left,yshift=3.2cm] {Update: $\tau$, $\tau_\text{screen}$, 
+$s_\text{max}$, $\beta$};
 
- \node (con) [draw, diamond, aspect=1.5,text width=4em, text centered, below of=assess,yshift=-0.7cm] {Continue$?$};
+\draw [arro] (dr) -- node[anchor=east,yshift=-0.8cm] {N} (dtol);
 
- \draw [arro] (assess) -- (con);
+\draw [arro] (dtol) |- (sam0);
 
-\node (ros) [process, below of=con, text width=6em, yshift=-0.7cm] {Construct the ROS};
+\node (ros) [process, below of=dr, text width=11.5em, yshift=-1.5cm] {Construct a reduced-order surrogate (ROS)};
 
- \draw [arro] (con) -- node[anchor=east] {Y}(ros);
+\draw [arro] (dr) -- node[anchor=east,yshift=0.1cm] {Y} (ros);
 
-\node (verify) [process, below of=ros, text width=9em,yshift=-0.2cm] {Verify accuracy of the surrogate};
+\node (ver) [process, left of=ros, text width=14.5em, xshift=-5cm] {Verify ROS using evaluations at $N_\text{total}$
+$\&$ the validation test suite};
 
-\draw [arro] (ros) -- (verify);
+\draw [arro] (ros) -- (ver);
 
-\node (stop) [startstop, right of=verify,xshift=3.5cm] {Stop};
+\node (stop) [startstop, below of=chk,yshift=-4.5cm] {Stop};
 
-\draw [arro] (verify) -- (stop);
+\draw [arro] (res) -- node[anchor=east,yshift=0.0cm] {Y} (stop);
 
-\draw [arro] (res) |- node[anchor=east,yshift=6.9cm] {Y} (stop);
-
-\draw [arro] (con) -| node[anchor=south,xshift=-3cm] {N} (stop);
+\draw [arro] (ver) -- (stop);
 

### 2018-05-14 Paper/method.tex
..

@@
 \Require $\tau > 0$, $\tau_\text{screen} > 0$,
-$s_\text{max}$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$. 
+$s_\text{max}$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
 \Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
@@
 
-\node (val) [process, below of=start, text width=14.5em] {Construct a validation test suite using
+\node (val) [process, below of=start, text width=14.5em] {Create a validation test suite using
 pre-allocated resources.};
@@
 
-\node (dtol) [io, above of=dr, text width=8.7em,align=left,yshift=3.2cm] {Update: $\tau$, $\tau_\text{screen}$, 
-$s_\text{max}$, $\beta$};
+\node (dtol) [io, above of=dr, text width=10.5em,align=left,yshift=3.2cm,inner sep=0.2pt] {\vspace{1mm}Update: $\tau$, 
+$\tau_\text{screen}$, $s_\text{max}$, $\beta$; Input: $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$\vspace{1mm}};
 
@@
 
-\caption{Flow-diagram outlining the adaptive strategy for constructing reduced-order surrogates using
-DGSMs.}
+\caption{Flow-diagram outlining the adaptive strategy for constructing reduced-order surrogates.}
 \label{fig:flow}

### 2018-05-14 Paper/method.tex
..

@@
 
-In this section, we outline the underlying methodology for constructing a 
-reduced-order surrogate (ROS) using sensitivity analysis. The term `reduced-order'
-in the present context implies that the surrogate is constructed in a 
+In this section, we outline the underlying framework for ``adaptively" constructing a 
+reduced-order surrogate (ROS) using sensitivity analysis.  The proposed methodology
+is described as adaptive since the ROS is constructed only in situations where
+it is expected to yield computational dividend as discussed further below. 
+The term `reduced-order' implies that the surrogate is constructed in a 
 subspace that sufficiently captures the uncertainty in the model output. 
-In the case of PC surrogates used in this work, it implies that the dimensionality
+In the context of PC surrogates used in this work, it implies that the dimensionality
 of the polynomial basis functions is effectively reduced.
 
-A possible approach to 
-constructing the ROS involves sensitivity analysis of the
-uncertain model parameters with respect to a given output, and thereby
-disregarding the uncertainty associated with parameters considered as unimportant.
-For this purpose, a global sensitivity analysis based on Sobol indices could be pursued.
-However, as discussed earlier in sections~\ref{sec:intro} and~\ref{sec:bg}, determining converged 
+Dimension-reduction is guided by global sensitivity analysis (GSA) of the uncertain model parameters. 
+A typical approach to GSA involves estimating the Sobol sensitivity indices~\cite{Sobol:2001}
+in the case of non-linear mathematical models. However, as discussed earlier in 
+sections~\ref{sec:intro} and~\ref{sec:bg}, determining converged 
 estimates of Sobol sensitivity indices typically requires tens of thousands
-of model evaluations. Consequently, the exercise becomes prohibitive in
-situations where the model runs are compute-intensive. Instead, we adopt a novel approach
-that focuses on estimating the upper-bound
-upper-bound ($\widehat{\mathcal{C}_i\mu_i}$, see Eq.~\ref{eq:bound}) on Sobol total
-effect index ($\mathcal{T}(\theta_i)$) for each parameter, $\theta_i$, and using it as a 
-metric to screen parameters that are relatively unimportant. Below, we provide a generalized
-strategy for parameter screening.
+of model evaluations. Consequently, the exercise becomes prohibitive especially in
+situations where the model runs are compute-intensive. In the proposed framework,
+we adopt a novel approach for constructing an ROS by estimating the upper-bound 
+($\widehat{\mathcal{C}_i\mu_i}$, see Eq.~\ref{eq:bound}) on Sobol total
+effect index ($\mathcal{T}(\theta_i)$) for each parameter, $\theta_i$, and use it
+as a metric to screen parameters that are relatively unimportant. A generalized
+methodology for parameter screening is provided below in Algorithm~\ref{alg:screen}.
 
-\clearpage
-\iffalse
-\begin{breakablealgorithm}
-  \caption{Parameter screening with DGSMs: A generalized approach.}
-  \begin{algorithmic}[1]
-    \Procedure{Screening}{}
-      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
-       according to the probability density $\bm{f(\theta)}$.
-      \State $N_t = N_t + n_1$
-      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
-             $k = 1, \ldots, n_1$.
-
-      \State Compute 
-      $\mu_{1, i} = \frac{1}{N_t} \sum_{k = 1}^{N_t} (g^k_i)^2$
-      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
-             $i = 1, \ldots, \Np$. 
-      \State Determine initial ranks: 
-            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{N_t}$ such that 
-\[
-   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
-\]
-      \State Set $s$ = 1.
-      \State Set $\mathrm{done} = \mathrm{false}$.
-      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
-        \State $s = s + 1$
-        \State $N_t = N_t + n_s$
-        \State Draw $n_s$ new samples 
-                  $\bm{\theta}_k$, $k = 1, \ldots, n_s$
-        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$
-        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
-               $\{\bm{g}_k \}_{k = 1}^{N_t}$.
-        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
-        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
-        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
-               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
-      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
-         \State $\mathrm{done} = \mathrm{true}$
-      \Else
-          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
-      \EndIf
-    \EndWhile
-    \State $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \nu_i \ni \displaystyle\frac{\nu_i}{\max(\bm{\nu})}> \tau_\text{screen}\}.$
-
-    \EndProcedure
-  \end{algorithmic}
-  \label{alg:screen}
-\end{breakablealgorithm}
-\fi
-
-%%%%%%%%%%%
-
+%%%%%%%%%%% Revised %%%%%%%%%%%
+\bigskip
 \begin{breakablealgorithm}
@@
 \end{breakablealgorithm}
-
 \bigskip
 
-In case the gradient, $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically, we could use finite-difference
-to approximate its value as shown in Eq.~\ref{eq:partial} in Algorithm~\ref{alg:screen}. However, as discussed earlier
-in section 2.1, estimating $\bm{\mu}$  using $\mathcal{N}$ samples in the full parameter space requires 
-model evaluations at model evaluations at $(N_p+1)\mathcal{N}$ samples, compared to only $\mathcal{N}$ samples in 
-situations where the derivative is available analytically. Hence, computational effort when using finite differences
-is increased by a factor of $(N_p+1)$.
+In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically, we could use finite-difference
+to approximate its value as shown in Eq.~\ref{eq:partial}. However, as discussed earlier
+in section 2.1, estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires 
+model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in 
+case the derivative is available analytically. Hence, computational effort when using finite differences
+is expected to increase by a factor of $(N_p+1)$.
 
@@
 metric for each uncertain parameter is accomplished. However, the amount of computational effort associated
-the screening process is limited by the choice of maximum number of iterations Parameter
-screening is an integral part of the overall strategy for constructing the ROS as 
-depicted below using a flow-diagram.
-
-\bigskip
+the screening process is limited by the choice of maximum number of iterations, $s_\text{max}$. Key inputs
+include a limiting value of the maximum relative change in the sensitivity measure between succesive iterations
+($\tau$), a limiting ratio ($\tau_\text{screen}$) of the sensitivity metric relative to its maximum value,
+ a fraction $\beta$ to guide the number of new samples 
+($ \lceil \beta n_1 \rceil$ denotes an integer $\leq~\beta n_1$) at each iteration,
+a new set of samples ($\{ \bm{\theta}_k \}_{k = 1}^{n_0}$) for the initial screening step in the algorithm,
+and the set of all the available gradient evaluations ($\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$). The outputs
+include the set of active indices ($\mathcal{I}_\text{active}$) corresponding to the important parameters,
+the total number of available model evaluations ($N_\text{total}$), and the enriched set of gradient evaluations
+(($\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$)). Parameter screening is an integral part of the overall framework,
+illustrated using a flow-diagram in Figure~\ref{fig:flow}.
 
 \begin{figure}[htbp]
-\begin{center}
-
 \tikzset{
@@
 \end{tikzpicture}
-\end{center}
 
@@
 \end{figure}
+%\clearpage
 
-As illustrated in the above flow-diagram, application of the above methodology to construct an ROS 
-relies on the choice of an \textit{appropriate} model output. Since the parameters are screened
-using DGSMs, the model output should exhibit a smooth dependence on the
-individual uncertain parameters to enable a reasonable approximation of the derivatives in Eq.~\ref{eq:mu}.
-Thus, for a given problem involving multiple outputs or model predictions, it is likely that a reduced-order 
-surrogate might be possible only for selected outputs. Hence, where possible, it is recommended to a priori assess the
-nature of dependence of a given model output on the parameters.
+We begin by setting aside computational resources for constructing a 
+validation test suite to be used for assessing the accuracy of the resulting
+surrogate. Obviously, the resources allocated for this purpose
+depend upon the application as well as total amount of available resource. The applicability
+of the proposed framework depends upon the choice of the model output. Since the screening metric
+involves computation of partial derivatives in the full parameter space, the output must exhibit
+a smooth dependence on each parameter for the approximation to be reasonable. It is therefore likely
+that for a given application involving multiple outputs, the ROS can only be constructed for a 
+selected few. Hence, where possible, it is prudent to assess the nature of the input-output
+relationship for a given model prior to implementing the present framework. The set of required inputs
+for parameter screening are initialized, and model evaluations at $n_0$ random samples in the full-space
+are computed. These evaluations are used to construct a surrogate in the full-space (FSS) using regression-based
+techniques. If the surrogate is found to be sufficiently accurate for the given application, the process
+is terminated. However, it is highly unlikely that a full-space surrogate, constructed using a reasonably 
+small number of model evaluations would result in a faithful representation of the input-output relationship. 
+The available set of model evaluations are utlized and further enhanced during parameter screening as
+discussed earlier. At the end of screening, the set of active indices, $\mathcal{I}_\text{active}$ is used
+to evaluate $\alpha$ in the following equation:
+
+\be
+\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p}
+\label{eq:alpha}
+\ee
+
+\noindent where $|\mathcal{I}_\text{active}|$ denotes the cardinality of $\mathcal{I}_\text{active}$.
+Scope for dimension-reduction increases as $\alpha$ decreases. Hence, if $\alpha$ is
+considered to be small and computational gains are expected owing to dimension reduction, the ROS
+is constructed and verified for accuracy using a combination of model evaluations used for screening
+and those associated with the validation test suite. On the other hand, if $\alpha$ is considerably
+large, the set of inputs required for screening are updated as needed, and a new set of $n_0$ samples
+and corresponding model evaluations are generated. The FSS is re-constructed using the enriched set
+of evaluations and the aforementioned analysis is repeated as illustrated in the flow-diagram.
 
@@
 associated with these steps. Determining the optimal allocation of computational resources for these steps, however, 
-is not possible a priori. Hence, we suggest estimating the DGSMs on a small set of samples (say, $n_1$ = 5) 
-initially, and screening with a relatively large value of tolerance, $\tau$ while keeping a track of computational expense.
-Tighter tolerances on $\bm{\mu}$ are
-gradually imposed until the screening process yields conclusive results pertaining to the possibility of dimension-reduction
-or a reasonably converged surrogate is constructed using the available set of model evaluations in the full parameter space. 
-Hence, the combined computational cost associated with steps I and II could be less, equal to, or greater than that needed
-to construct the surrogate in the full parameter space. To avoid the case of greater computational effort, we suggest 
-that the decision to construct the ROS should account for the degree of dimension-reduction predicted at the end of the
-screening step ($\alpha$, defined below in Eq.~\ref{eq:alpha}), and the state of convergence of the full-space surrogate. 
-Enormous computational savings are in fact possible when dealing with complex, 
-compute-intensive models, even if $\alpha$ in the following equation is
-not too large.
+is not possible a priori. Hence, in the proposed framework, we exploit the set of model evaluations used
+in parameter screening to simultaneously construct the FSS while keeping a track of its accuracy using the
+validation test suite. This would help address situations where significant dimension
+reduction is not possible, and hence, constructing the ROS might result in a computational disadvantage. We
+suggest using a small number of samples in the initial screening step (say, $n_0$ = 5) and a relatively large
+$\tau$ (say, $\mathcal{O}(10^{-1})$) as a starting point with possible reduction in $\tau$ during
+subsequent screenings.
 
-\be
-\alpha = \frac{\mbox{Dimensionality of ROS}}{\mbox{Dimensionality of the full surrogate}}
-\label{eq:alpha}
-\ee
-
-In order to assess convergence of the ROS, we estimate the leave-one-out cross validation error as
-follows:
+In order to assess convergence of the resulting surrogate, one could estimate the leave-one-out cross 
+validation error as follows:
 
@@
 \noindent where $N_l$ is the number of training points, 
-$\widetilde{\mu}~=~\frac{1}{N}\sum\limits_{i=1}^N G(\bm{\theta}_i)$
+$\widetilde{\mu}~=~\frac{1}{N_l}\sum\limits_{i=1}^{N_l} G(\bm{\theta}_i)$
 is the sample mean of the model response, and $ G^{\mbox{\tiny {PC}\textbackslash i}}$
-is the PCE surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
-From Eq.~\ref{eq:loo}, it appears that $N$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
+is the PC surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
+From Eq.~\ref{eq:loo}, it appears that $N_l$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
 However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
-independent of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
-
-Finally, as outlined in Figure~\ref{fig:flow}, the converged ROS is verified for predictive accuracy. 
-To this end, we compute a relative L-2 norm of the difference in predictions between the model
-and the ROS ($\epsilon_{\mbox{\tiny{L-2}}}$) as follows:
+independent of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used. Accuracy of the
+surrogate could be assessed by evaluating the relative L-2 norm of the difference in predictions
+between the model and the surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
 
@@
 \noindent where $N_v$ is the number of sampling points in the full parameter space at which model
-evaluations are available. It must be noted that the computational effort associated with estimating
- $\epsilon_{\mbox{\tiny{L-2}}}$
-is negligible since we exploit the available set of model evaluations in the full parameter space, generated
-during the screening step. Additionally, probability density function (PDF) based on these full-space 
-model evaluations are compared with the PDF generated using a large set of evaluations of the same
-output from the ROS.
+evaluations are available. Accuracy of the surrogate could be further investigated by comparing
+probability density functions (PDFs) of the model output based on model evaluations in the full
+parameter space and surrogate predictions corresponding to a large number of samples.
+
+%\newpage
+\iffalse
+\begin{breakablealgorithm}
+  \caption{Parameter screening with DGSMs: A generalized approach.}
+  \begin{algorithmic}[1]
+    \Procedure{Screening}{}
+      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
+       according to the probability density $\bm{f(\theta)}$.
+      \State $N_t = N_t + n_1$
+      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
+             $k = 1, \ldots, n_1$.
+
+      \State Compute 
+      $\mu_{1, i} = \frac{1}{N_t} \sum_{k = 1}^{N_t} (g^k_i)^2$
+      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
+             $i = 1, \ldots, \Np$. 
+      \State Determine initial ranks: 
+            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{N_t}$ such that 
+\[
+   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
+\]
+      \State Set $s$ = 1.
+      \State Set $\mathrm{done} = \mathrm{false}$.
+      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
+        \State $s = s + 1$
+        \State $N_t = N_t + n_s$
+        \State Draw $n_s$ new samples 
+                  $\bm{\theta}_k$, $k = 1, \ldots, n_s$
+        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$
+        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
+               $\{\bm{g}_k \}_{k = 1}^{N_t}$.
+        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
+        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
+        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
+               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
+      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
+         \State $\mathrm{done} = \mathrm{true}$
+      \Else
+          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
+      \EndIf
+    \EndWhile
+    \State $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \nu_i \ni \displaystyle\frac{\nu_i}{\max(\bm{\nu})}> \tau_\text{screen}\}.$
+
+    \EndProcedure
+  \end{algorithmic}
+  \label{alg:screen}
+\end{breakablealgorithm}
+\fi
+
+%\newpage

### 2018-05-14 Paper/examples.tex
..

@@
 
-In section~\ref{sec:method}, we presented a methodology for constructing
-an ROS by identifying unimportant parameters based on 
-estimates of the upper bound on the Sobol'
-total effect sensitivity index ($\mathcal{T}(\theta_i)$) for individual parameters.
-In this section, we motivate the methodology by applying it to three test problems,
+In section~\ref{sec:method}, we presented a framework for constructing
+an ROS (if deemed advantageous) by identifying unimportant parameters based on 
+estimates of the screening metric, $\widehat{\mathcal{C}_i\mu_i}$
+for individual parameters.
+In this section, we motivate the underlying methodology by applying it to three test problems,
 namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
@@
 problems are inexpensive, we compare relative importance of model parameters based
-on DGSMs, obtained using model predictions with 
-converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate, constructed in the
-full parameter space. Additionally, to illustrate computational gains, we compare
-convergence trends as a function of training runs for the ROS and the full-space
-surrogate. Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
+on the screening metric, obtained using model evaluations with 
+converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate constructed in the
+full parameter space (FSS). Additionally, to illustrate computational gains, we compare
+convergence trends as a function of training runs for the ROS and the FSS using 
+$\epsilon_{\mbox{\tiny LOO}}$ in Eq.~\ref{eq:loo}. 
+Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
 PDFs of the model output, obtained using the ROS and the full-space surrogate for

### 2018-05-15 Paper/examples.tex
..

@@
 samples used for approximating $\mu_i$ using~\eqref{eq:mu}.
-Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
+Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement
+with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
 Consequently, the relative importance of uncertain 
@@
 Our goal as discussed is to gain computational advantage by constructing
-surrogates in a reduced input parameter space. To this end, we construct PCE's
+surrogates in a reduced input parameter space. To this end, we use LAR to 
+construct PCEs
 in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
 fixing $K_w$ in the latter at their respective mean values. In
-Figure~\ref{fig:conv_bore}(left), we compare convergence of PCE's constructed in the
+Figure~\ref{fig:conv_bore}(left), we compare convergence of PCEs constructed in the
 full space (7D) with those constructed in the two reduced spaces (4D and 5D)
 using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}).
+
 \begin{figure}[htbp]
@@
 in the 4D parameter space whereas the number of samples needed in the full 7D
-space seems much higher.~\alennote{How are these samples used? Are we doing 
-Latin Hypercube sample, or some other QMC approach?}
+space seems much higher. Latin hypercube sampling (LHS) was used in
+each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(left)
+is not expected to decrease monotonically with the increase in sample size
+owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}.
 
@@
 the reduced order PCEs constructed in 4 and 5 dimensions. 
-%\begin{figure}[htbp]
-% \begin{center}
-%  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
-%\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
-%by propagating
-%parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
-%were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
-%\label{fig:pdfcomp_bore}
-%\end{center}
-%\end{figure}
 It is evident from this plot, that the PDFs agree quite favorably with each

### 2018-05-15 Paper/method.tex

@@
 
-In this section, we outline the underlying framework for ``adaptively" constructing a 
-reduced-order surrogate (ROS) using sensitivity analysis.  The proposed methodology
-is described as adaptive since the ROS is constructed only in situations where
-it is expected to yield computational dividend as discussed further below. 
-The term `reduced-order' implies that the surrogate is constructed in a 
-subspace that sufficiently captures the uncertainty in the model output. 
-In the context of PC surrogates used in this work, it implies that the dimensionality
-of the polynomial basis functions is effectively reduced.
+In this section, we outline the underlying framework for \emph{adaptively}
+constructing a reduced-order surrogate (ROS) using sensitivity analysis.  The
+proposed methodology is described as adaptive since the ROS is constructed only
+in situations where it is expected to yield computational dividend as discussed
+further below.  The term reduced-order implies that the surrogate is
+constructed in a subspace that sufficiently captures the uncertainty in the
+model output.~\alennote{The next sentence seems unneeded, and 
+might be confusing; consider removing it, or clarify that in 
+the case of PCE, we construct PC bases as multivariate polynomials
+on a parameter space with reduced dimension.}
+In the context of PC surrogates used in this work, it implies
+that the dimensionality of the polynomial basis functions is effectively
+reduced.
 
-Dimension-reduction is guided by global sensitivity analysis (GSA) of the uncertain model parameters. 
-A typical approach to GSA involves estimating the Sobol sensitivity indices~\cite{Sobol:2001}
-in the case of non-linear mathematical models. However, as discussed earlier in 
-sections~\ref{sec:intro} and~\ref{sec:bg}, determining converged 
-estimates of Sobol sensitivity indices typically requires tens of thousands
-of model evaluations. Consequently, the exercise becomes prohibitive especially in
-situations where the model runs are compute-intensive. In the proposed framework,
-we adopt a novel approach for constructing an ROS by estimating the upper-bound 
-($\widehat{\mathcal{C}_i\mu_i}$, see Eq.~\ref{eq:bound}) on Sobol total
-effect index ($\mathcal{T}(\theta_i)$) for each parameter, $\theta_i$, and use it
-as a metric to screen parameters that are relatively unimportant. A generalized
-methodology for parameter screening is provided below in Algorithm~\ref{alg:screen}.
+Dimension reduction is guided by global sensitivity analysis (GSA).  A typical
+approach to GSA involves estimating the Sobol sensitivity
+indices~\cite{Sobol:2001} in the case of non-linear mathematical models.
+However, as discussed earlier in sections~\ref{sec:intro} and~\ref{sec:bg},
+determining accurate estimates of Sobol sensitivity indices typically requires
+tens of thousands of model evaluations. Consequently, the exercise becomes
+prohibitive for expensive-to-evaluate models.  In the proposed framework, we
+adopt a novel approach for constructing an ROS based on estimating the
+upper-bound $\widehat{\mathcal{C}_i\mu_i}$, given in~\eqref{eq:bound}, on 
+Sobol total effect index ($\mathcal{T}(\theta_i)$) for each 
+parameter, $\theta_i$, and use it as a metric to screen 
+parameters that are relatively unimportant. A general
+methodology for parameter screening is provided below in
+Algorithm~\ref{alg:screen}.
 
@@
 
-In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically, we could use finite-difference
-to approximate its value as shown in Eq.~\ref{eq:partial}. However, as discussed earlier
-in section 2.1, estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires 
-model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in 
-case the derivative is available analytically. Hence, computational effort when using finite differences
-is expected to increase by a factor of $(N_p+1)$.
+In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically,
+we could use finite-difference to approximate its value as shown in
+Eq.~\ref{eq:partial}. However, as discussed earlier in section 2.1,
+~\alennote{Don't hard code section numbers, use labels, and refer to them.}
+estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires
+model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in case
+the derivative is available analytically. Hence, computational effort when
+using finite differences is expected to increase by a factor of $(N_p+1)$.
+Another possible approach, suitable in certain cases, is the use of
+adjoint-based gradient computation. In such cases, each gradient computation,
+which is more efficient than finite-differences---each gradient
+evaluation requires a forward model solve and adjoint solve---but 
+requires the availability of adjoint solvers.
+\alennote{I will put some references there ...}
 
-Based on the steps outlined in the above algorithm, it can be said that the set of sample points used for
-estimating the screening metric, $\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks
-between successive iterations as well as a certain degree of convergence in estimates of the screening 
-metric for each uncertain parameter is accomplished. However, the amount of computational effort associated
-the screening process is limited by the choice of maximum number of iterations, $s_\text{max}$. Key inputs
-include a limiting value of the maximum relative change in the sensitivity measure between succesive iterations
-($\tau$), a limiting ratio ($\tau_\text{screen}$) of the sensitivity metric relative to its maximum value,
- a fraction $\beta$ to guide the number of new samples 
-($ \lceil \beta n_1 \rceil$ denotes an integer $\leq~\beta n_1$) at each iteration,
-a new set of samples ($\{ \bm{\theta}_k \}_{k = 1}^{n_0}$) for the initial screening step in the algorithm,
-and the set of all the available gradient evaluations ($\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$). The outputs
-include the set of active indices ($\mathcal{I}_\text{active}$) corresponding to the important parameters,
-the total number of available model evaluations ($N_\text{total}$), and the enriched set of gradient evaluations
-(($\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$)). Parameter screening is an integral part of the overall framework,
-illustrated using a flow-diagram in Figure~\ref{fig:flow}.
+Based on the steps outlined in the above algorithm, it can be said that the set
+of sample points used for estimating the screening metric,
+$\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks between
+successive iterations as well as a certain degree of convergence in estimates
+of the screening metric for each uncertain parameter is accomplished. However,
+the amount of computational effort associated the screening process is limited
+by the choice of maximum number of iterations, $s_\text{max}$. Key inputs
+include a limiting value of the maximum relative change in the sensitivity
+measure between succesive iterations $\tau$, a limiting ratio
+$\tau_\text{screen}$ of the sensitivity metric relative to its maximum value,
+a fraction $\beta$ to guide the number of new samples $ \lceil \beta n_1
+\rceil$ denotes an integer $\leq~\beta n_1$ at each iteration, a set of
+samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ for the initial screening step in
+the algorithm, and the set of available gradient evaluations $\{
+\bm{g}^k \}_{k=1}^{n_0}$. The outputs include the set of active
+indices $\mathcal{I}_\text{active}$ corresponding to the 
+\emph{important parameters}, the total number of available model 
+evaluations $N_\text{total}$, and the enriched set of gradient evaluations 
+$\{ \bm{g}^k
+\}_{k=1}^{N_\text{total}}$. Parameter screening is an integral part of the
+overall framework, illustrated using a flow-diagram in Figure~\ref{fig:flow}.
 
@@
 
-We begin by setting aside computational resources for constructing a 
-validation test suite to be used for assessing the accuracy of the resulting
-surrogate. Obviously, the resources allocated for this purpose
-depend upon the application as well as total amount of available resource. The applicability
-of the proposed framework depends upon the choice of the model output. Since the screening metric
-involves computation of partial derivatives in the full parameter space, the output must exhibit
-a smooth dependence on each parameter for the approximation to be reasonable. It is therefore likely
-that for a given application involving multiple outputs, the ROS can only be constructed for a 
-selected few. Hence, where possible, it is prudent to assess the nature of the input-output
-relationship for a given model prior to implementing the present framework. The set of required inputs
-for parameter screening are initialized, and model evaluations at $n_0$ random samples in the full-space
-are computed. These evaluations are used to construct a surrogate in the full-space (FSS) using regression-based
-techniques. If the surrogate is found to be sufficiently accurate for the given application, the process
-is terminated. However, it is highly unlikely that a full-space surrogate, constructed using a reasonably 
-small number of model evaluations would result in a faithful representation of the input-output relationship. 
-The available set of model evaluations are utlized and further enhanced during parameter screening as
-discussed earlier. At the end of screening, the set of active indices, $\mathcal{I}_\text{active}$ is used
-to evaluate $\alpha$ in the following equation:
+We begin by setting aside computational resources for constructing a validation
+test suite to be used for assessing the accuracy of the resulting surrogate.
+Naturally, the resources allocated for this purpose depend upon the application
+as well as total amount of available resources. 
+%
+%The applicability of the
+%proposed framework depends upon the choice of the model output. 
+%
+Since the
+screening metric involves computation of partial derivatives in the full
+parameter space, the output must exhibit differentiable 
+dependence on each parameter. It is therefore likely that for a given
+application involving multiple outputs, the ROS can only be constructed for a
+selected few. Hence, where possible, it is important to assess the nature of the
+input-output relationship for a given model prior to implementing the present
+framework. The set of required inputs for parameter screening are initialized,
+and model evaluations at $n_0$ random samples in the full-space are computed.
+These evaluations are used to construct a surrogate in the full-space (FSS)
+using regression-based techniques. If the surrogate is found to be sufficiently
+accurate for the given application, the process is terminated. However, it is
+likely that a full-space surrogate constructed using a 
+small number of model evaluations would not provide a 
+faithful representation of the input-output relationship.
 
+The available set of model evaluations are utlized and further enhanced during
+parameter screening as discussed earlier.  At the end of screening, the set of
+active indices, $\mathcal{I}_\text{active}$, is used to evaluate $\alpha$ in the
+following equation: 
 \be
-\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p}
+\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p},
 \label{eq:alpha}
 \ee
+\alennote{I noticed in the latex code the use of the \textbf{noindent} command;
+please remove those, we will use latext setting to formation paragraphs.} where
+$|\mathcal{I}_\text{active}|$ denotes the cardinality of
+$\mathcal{I}_\text{active}$.  Scope for dimension-reduction increases as
+$\alpha$ decreases.  Hence, if $\alpha$ is considered to be small and
+computational gains are expected owing to dimension reduction, the ROS is
+constructed and verified for accuracy using a combination of model evaluations
+used for screening and those associated with the validation test suite.  On the
+other hand, if $\alpha$ is considerably large (~\alennote{You mean close to
+one?}), the set of inputs required for screening are updated as needed, and a
+new set of $n_0$ samples and corresponding model evaluations are generated. The
+FSS is re-constructed using the enriched set of evaluations and the
+aforementioned analysis is repeated as illustrated in the flow-diagram.
 
-\noindent where $|\mathcal{I}_\text{active}|$ denotes the cardinality of $\mathcal{I}_\text{active}$.
-Scope for dimension-reduction increases as $\alpha$ decreases. Hence, if $\alpha$ is
-considered to be small and computational gains are expected owing to dimension reduction, the ROS
-is constructed and verified for accuracy using a combination of model evaluations used for screening
-and those associated with the validation test suite. On the other hand, if $\alpha$ is considerably
-large, the set of inputs required for screening are updated as needed, and a new set of $n_0$ samples
-and corresponding model evaluations are generated. The FSS is re-constructed using the enriched set
-of evaluations and the aforementioned analysis is repeated as illustrated in the flow-diagram.
+The amount of computational effort associated with the presented methodology
+can be mainly attributed to two steps: I.~Parameter Screening, and 
+II.~Constructing a converged ROS. Computational gains are realized in situations
+where constructing the surrogate in the full parameter space is more expensive
+than the combined cost associated with these steps. Determining the optimal
+allocation of computational resources for these steps, however, is not possible
+a priori. Hence, in the proposed framework, we exploit the set of model
+evaluations used in parameter screening to simultaneously construct the FSS
+while keeping a track of its accuracy using the validation test suite. This
+would help address situations where significant dimension reduction is not
+possible, and hence, constructing the ROS might result in a computational
+disadvantage. We suggest using a small number of samples in the initial
+screening step (say, $n_0$ = 5) and a relatively large $\tau$ (say,
+$\mathcal{O}(10^{-1})$) as a starting point with possible reduction in $\tau$
+during subsequent screenings.
 
-The amount of computational effort associated with the presented methodology can be mainly attributed to
-two steps: I. Parameter Screening, and II. Constructing a converged ROS. Computational gains are realized
-in situations where constructing the surrogate in the full parameter space is more expensive than the combined cost
-associated with these steps. Determining the optimal allocation of computational resources for these steps, however, 
-is not possible a priori. Hence, in the proposed framework, we exploit the set of model evaluations used
-in parameter screening to simultaneously construct the FSS while keeping a track of its accuracy using the
-validation test suite. This would help address situations where significant dimension
-reduction is not possible, and hence, constructing the ROS might result in a computational disadvantage. We
-suggest using a small number of samples in the initial screening step (say, $n_0$ = 5) and a relatively large
-$\tau$ (say, $\mathcal{O}(10^{-1})$) as a starting point with possible reduction in $\tau$ during
-subsequent screenings.
-
-In order to assess convergence of the resulting surrogate, one could estimate the leave-one-out cross 
-validation error as follows:
-
+To assess convergence of the resulting surrogate, one could estimate the
+leave-one-out cross validation error as follows:
 \be
@@
 \ee
-
-\noindent where $N_l$ is the number of training points, 
+where $N_l$ is the number of training points, 
 $\widetilde{\mu}~=~\frac{1}{N_l}\sum\limits_{i=1}^{N_l} G(\bm{\theta}_i)$
-is the sample mean of the model response, and $ G^{\mbox{\tiny {PC}\textbackslash i}}$
-is the PC surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
-From Eq.~\ref{eq:loo}, it appears that $N_l$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
-However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
-independent of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used. Accuracy of the
-surrogate could be assessed by evaluating the relative L-2 norm of the difference in predictions
-between the model and the surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
-
+is the sample mean of the model response, and $ G^{\mbox{\tiny
+{PC}\textbackslash i}}$ is the PC surrogate constructed using all but the
+$i^{\mbox{\tiny{th}}}$ model realization.  From~\eqref{eq:loo}, it appears
+that $N_l$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.  However,
+in practice a modified formulation for $\epsilon_{\mbox{\tiny
+LOO}}$~\cite{Blatman:2009}, independent of $G^{\mbox{\tiny {PC}\textbackslash
+i}}$ is used. Accuracy of the surrogate could be assessed by evaluating the
+relative $\ell_2$-norm of the difference in predictions between the model and the
+surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
 \be
@@
 \ee
-
-\noindent where $N_v$ is the number of sampling points in the full parameter space at which model
-evaluations are available. Accuracy of the surrogate could be further investigated by comparing
-probability density functions (PDFs) of the model output based on model evaluations in the full
-parameter space and surrogate predictions corresponding to a large number of samples.
+where $N_v$ is the number of sampling points in the full parameter space at
+which model evaluations are available. Accuracy of the surrogate could be
+further investigated by comparing probability density functions (PDFs) of the
+model output based on model evaluations in the full parameter space and
+surrogate predictions corresponding to a large number of samples.
 

### 2018-05-16 Paper/examples.tex
..
.

@@
 
+In this test problem, we consider an undamped non-linear oscillator with only one degree of
+freedom as illustrated below in Figure~\ref{fig:osc}.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.6\textwidth]{./Figures/oscillator}
+\caption{Schematic illustration of an undamped non-linear oscillator system with one degree of freedom.}
+\label{fig:osc}
+\end{center}
+\end{figure}
+
+The above system has been studied extensively for its reliability using the following state function~\cite{Bucher:1989, 
+Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:
+
+\be
+g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - \left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|
+\ee
+
 \subsection{Semilinear elliptic PDE with random source term}

### 2018-05-16 Paper/method.tex
pass through method section ...

@@
 
+\textbf{Parameter screening.}
 Dimension reduction is guided by global sensitivity analysis (GSA).  A typical
@@
 the amount of computational effort associated the screening process is limited
-by the choice of maximum number of iterations, $s_\text{max}$. Key inputs
-include a limiting value of the maximum relative change in the sensitivity
-measure between succesive iterations $\tau$, a limiting ratio
-$\tau_\text{screen}$ of the sensitivity metric relative to its maximum value,
-a fraction $\beta$ to guide the number of new samples $ \lceil \beta n_1
-\rceil$ denotes an integer $\leq~\beta n_1$ at each iteration, a set of
-samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ for the initial screening step in
-the algorithm, and the set of available gradient evaluations $\{
-\bm{g}^k \}_{k=1}^{n_0}$. The outputs include the set of active
+by the choice of maximum number of iterations, $s_\text{max}$. 
+Key inputs
+are as follows: (1) 
+a limiting value $\tau$ of the maximum relative change in the sensitivity
+measure between succesive iterations; (2) 
+a limiting ratio $\tau_\text{screen}$ of the sensitivity metric 
+relative to its maximum value;
+(3) a real number $\beta \in (0, 1)$ to 
+guide the number of new samples $\lceil \beta n_1 \rceil$ 
+at each iteration ($\lceil \beta n_1
+\rceil$ 
+is the smallest integer greater than or equal to $\beta n_1$); 
+(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
+for the initial screening step in
+the algorithm and the corresponding gradient evaluations 
+$\{ \bm{g}^k \}_{k=1}^{n_0}$, where
+$\bm{g}^k = \nabla_{\bm{\theta}} G(\bm{\theta}_k)$. 
+The outputs are the set of active
 indices $\mathcal{I}_\text{active}$ corresponding to the 
@@
 evaluations $N_\text{total}$, and the enriched set of gradient evaluations 
-$\{ \bm{g}^k
-\}_{k=1}^{N_\text{total}}$. Parameter screening is an integral part of the
-overall framework, illustrated using a flow-diagram in Figure~\ref{fig:flow}.
+$\{ \bm{g}^k\}_{k=1}^{N_\text{total}}$. 
+Parameter screening is an integral part of the
+overall surrogate model construction framework 
+detailed below.
 
@@
 
+\textbf{Adaptive surrogate model construction.}
 We begin by setting aside computational resources for constructing a validation
@@
 as well as total amount of available resources. 
-%
-%The applicability of the
-%proposed framework depends upon the choice of the model output. 
-%
-Since the
-screening metric involves computation of partial derivatives in the full
-parameter space, the output must exhibit differentiable 
-dependence on each parameter. It is therefore likely that for a given
-application involving multiple outputs, the ROS can only be constructed for a
-selected few. Hence, where possible, it is important to assess the nature of the
-input-output relationship for a given model prior to implementing the present
-framework. The set of required inputs for parameter screening are initialized,
+The set of required inputs for parameter screening are initialized,
 and model evaluations at $n_0$ random samples in the full-space are computed.
@@
 FSS is re-constructed using the enriched set of evaluations and the
-aforementioned analysis is repeated as illustrated in the flow-diagram.
+aforementioned analysis is repeated as illustrated in the flow-diagram
+in Figure~\ref{fig:flow} that shows the overall 
+parameter screening and surrogate model construction method.
 
+\textbf{Validation metrics.}
+To assess convergence of the resulting surrogate, one could estimate the
+leave-one-out cross validation error as follows:
+\be
+\epsilon_{\mbox{\tiny LOO}} = 
+\frac{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - G^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
+{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
+\label{eq:loo}
+\ee
+where $N_l$ is the number of training points, 
+$\widetilde{\mu}~=~\frac{1}{N_l}\sum\limits_{i=1}^{N_l} G(\bm{\theta}_i)$
+is the sample mean of the model response, and $ G^{\mbox{\tiny
+{PC}\textbackslash i}}$ is the PC surrogate constructed using all but the
+$i^{\mbox{\tiny{th}}}$ model realization.  From~\eqref{eq:loo}, it appears
+that $N_l$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.  However,
+in practice a modified formulation for $\epsilon_{\mbox{\tiny
+LOO}}$~\cite{Blatman:2009}, independent of $G^{\mbox{\tiny {PC}\textbackslash
+i}}$ is used.~\alennote{What is that modified formulation? Need to specify.}
+Accuracy of the surrogate could be assessed by evaluating the
+relative $\ell_2$-norm of the difference in predictions between the model and the
+surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
+\be
+\epsilon_{\mbox{\tiny{L-2}}} = \frac{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i) - 
+G^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
+{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
+\label{eq:l2}
+\ee
+where $N_v$ is the number of sampling points in the full parameter space at
+which model evaluations are available. 
+\alennote{You mean to do L2 error study in 
+addition to the leave-one-out error studies?}
+Accuracy of the surrogate could be
+further investigated by comparing probability density functions (PDFs) of the
+model output based on model evaluations in the full parameter space and
+surrogate predictions corresponding to a large number of samples.  
+\alennote{I don't think you can construct the PDF in full parameter 
+space, in real applications, as you need a large number of 
+expensive model evaluations. Maybe we should say that  
+we compare the PDF of the surrogate to a histogram of true model
+evaluations?}
+
+\textbf{Remarks.}
 The amount of computational effort associated with the presented methodology
@@
 
-To assess convergence of the resulting surrogate, one could estimate the
-leave-one-out cross validation error as follows:
-\be
-\epsilon_{\mbox{\tiny LOO}} = 
-\frac{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - G^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
-{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
-\label{eq:loo}
-\ee
-where $N_l$ is the number of training points, 
-$\widetilde{\mu}~=~\frac{1}{N_l}\sum\limits_{i=1}^{N_l} G(\bm{\theta}_i)$
-is the sample mean of the model response, and $ G^{\mbox{\tiny
-{PC}\textbackslash i}}$ is the PC surrogate constructed using all but the
-$i^{\mbox{\tiny{th}}}$ model realization.  From~\eqref{eq:loo}, it appears
-that $N_l$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.  However,
-in practice a modified formulation for $\epsilon_{\mbox{\tiny
-LOO}}$~\cite{Blatman:2009}, independent of $G^{\mbox{\tiny {PC}\textbackslash
-i}}$ is used. Accuracy of the surrogate could be assessed by evaluating the
-relative $\ell_2$-norm of the difference in predictions between the model and the
-surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
-\be
-\epsilon_{\mbox{\tiny{L-2}}} = \frac{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i) - 
-G^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
-{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
-\label{eq:l2}
-\ee
-where $N_v$ is the number of sampling points in the full parameter space at
-which model evaluations are available. Accuracy of the surrogate could be
-further investigated by comparing probability density functions (PDFs) of the
-model output based on model evaluations in the full parameter space and
-surrogate predictions corresponding to a large number of samples.
+The applicability of the proposed framework depends upon the choice of the
+model output.  Since the screening metric involves computation of partial
+derivatives in the full parameter space, the output must exhibit differentiable
+dependence on each parameter. It is therefore likely that for a given
+application involving multiple outputs, the ROS can only be constructed for a
+selected few, using the approach presented above.  Hence, it is important to
+assess the nature of the input-output relationship for a given model prior to
+implementing the present framework.
 

### 2018-05-16 Paper/examples.tex
..

@@
 \begin{center}
-\begin{tabular}{|c|c|}
+\begin{tabular}{|l||l|}
 \hline
-Parameter & Distribution \\ \hline \hline
-$r_w$ (Borehole radius, m) & $\mathcal{N}$(0.1,0.016) \\
-$L$ (Borehole length, m) & $\mathcal{U}$[1120,1680] \\
-$T_u$ (Transmissivity of upper aquifer, m$^2$/yr) & $\mathcal{U}$[63070,115600] \\
-$H_u$ (Potentiometric head of upper aquifer, m) & $\mathcal{U}$[990,1110] \\
-$T_l$ (Transmissivity of lower aquifer, m$^2$/yr) & $\mathcal{U}$[63.1,116] \\
-$H_l$ (Potentiometric head of lower aquifer, m) & $\mathcal{U}$[700,820] \\
-$K_w$ (Borehole hydraulic conductivity, m/yr) & $\mathcal{U}$[9855,12045] \\
+\textbf{Parameter Description} & \textbf{Distribution} \\ \hline \hline
+Borehole radius, $r_w$ (m) & $\mathcal{N}$(0.1,0.016) \\
+Borehole length, $L$ (m) & $\mathcal{U}$[1120,1680] \\
+Transmissivity of upper aquifer, $T_u$ (m$^2$/yr) & $\mathcal{U}$[63070,115600] \\
+Potentiometric head of upper aquifer, $H_u$ (m) & $\mathcal{U}$[990,1110] \\
+Transmissivity of lower aquifer, $T_l$ (m$^2$/yr) & $\mathcal{U}$[63.1,116] \\
+Potentiometric head of lower aquifer, $H_l$ (m) & $\mathcal{U}$[700,820] \\
+Borehole hydraulic conductivity, $K_w$ (m/yr) & $\mathcal{U}$[9855,12045] \\
 \hline
@@
 \caption{Description and distributions of uncertain parameters in the borehole function
-given by~\eqref{eq:bore}.}
+given by~\eqref{eq:bore}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
+mean, $\mu$ and variance, $\sigma^2$. $\mathcal{U}[a,b]$ denotes a uniform distribution
+with limits $a$ and $b$.}
 \label{tab:bore}
 \end{table}
-
+%
 Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ using
@@
 \caption{
-Left: Sobol' total sensitivity index for uncertain parameters in the borehole
-function. Right: 
-estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$) is plotted
-against number of samples considered for evaluating $\mu_i$. Corresponding estimates
-for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
-legend. }
+Left:Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
+borehole discharge function in~\eqref{eq:bore}. Right: 
+Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
+against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
+in each case in the legend.}
 \label{fig:sense_bore}
@@
 \end{figure}
+
 In Figure~\ref{fig:sense_bore}~(right), we plot estimates of the screening parameter 
@@
 fixing $K_w$ in the latter at their respective mean values. In
-Figure~\ref{fig:conv_bore}(left), we compare convergence of PCEs constructed in the
+Figure~\ref{fig:conv_bore}~(left), we compare convergence of PCEs constructed in the
 full space (7D) with those constructed in the two reduced spaces (4D and 5D)
@@
 \end{figure}
-
+%
 As expected, it is observed that the PCE constructed in the 4D space converges
@@
 space seems much higher. Latin hypercube sampling (LHS) was used in
-each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(left)
+each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}~(left)
 is not expected to decrease monotonically with the increase in sample size
@@
 
-Figure~\ref{fig:conv_bore}(right) illustrates a comparison of the PDFs
+Figure~\ref{fig:conv_bore}~(right) illustrates a comparison of the PDFs
 of the
@@
 observable is reliably captured and predicted by the reduced order PCE. 
-
+% 
 \subsection{Non-linear Oscillator}
@@
 
-The above system has been studied extensively for its reliability using the following state function~\cite{Bucher:1989, 
-Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:
+The above system has been studied extensively for its reliability using
+the following state function~\cite{Bucher:1989,Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:
+%
+\be
+g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - 
+\left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|
+\label{eq:limit}
+\ee
 
-\be
-g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - \left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|
-\ee
+\noindent where $z_\text{max}$ is the maximum displacement response of the system, $r$ denotes the displacement at
+which either spring yields, $\bm{X}:~\{m,k_1,k_2,r,F,t_1\}$ is a set of uncertain parameters, and   
+$\omega_0~=~\sqrt{\frac{k_1+k_2}{m}}$. The uncertain parameters are considered to be normally distributed with mean
+and variance as provided below in Table~\ref{tab:osc}.
+
+\begin{table}[htbp]
+\renewcommand*{\arraystretch}{1.2}
+\begin{center}
+\begin{tabular}{|l||l|}
+\hline
+\textbf{Parameter Description} & \textbf{Distribution} \\ \hline \hline
+Mass, $m$ (kg) & $\mathcal{N}$(1,0.05) \\
+Time, $t_1$ (s) & $\mathcal{N}$(1,0.2) \\
+Force, $F$ (N) & $\mathcal{N}$(1,0.2) \\
+Displacement, $r$ (m) & $\mathcal{N}$(0.5,0.05) \\
+Spring Constant, $k_1$ (Nm$^{-1}$) & $\mathcal{N}$(1,0.1) \\
+Spring Constant, $k_2$ (Nm$^{-1}$) & $\mathcal{N}$(0.1,0.01) \\
+\hline
+\end{tabular}
+\end{center}
+
+\caption{Description and distributions of uncertain parameters in the limit state function
+given by~\eqref{eq:limit}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
+mean, $\mu$ and variance, $\sigma^2$. $\mathcal{U}[a,b]$ denotes a uniform distribution
+with limits $a$ and $b$.}
+\label{tab:osc}
+\end{table}
+
+Converged estimates of $\mathcal{T}(\theta_i)$ are once again obtained easily by
+evaluating $g(\bm{X})$ for a large set of samples in $\mathbb{R}^{|\bm{X}|}$ as
+shown in Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
+$\widehat{\mathcal{C}_i\mu_i}$ are plotted against the number of samples in 
+Figure~\ref{fig:sense_osc}~(right).
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.48\textwidth]{./Figures/sense_oscillator}
+  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_oscillator}
+\caption{
+Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the limit 
+state function in~\eqref{eq:limit}. Right: 
+Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
+against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
+in each case in the legend.}
+\label{fig:sense_osc}
+\end{center}
+\end{figure}
 

### 2018-05-16 Paper/examples.tex
..

@@
 
+From the above figure, it can be said that the Sobol sensitivity indices are in excellent
+agreement with the screening metric estimates. Consequently, the parameter ranks are
+found to be consistent in the two plots. It is observed that the limit state function is
+predominantly sensitive towards three parameters: $r$, $F$, and $t_1$. Hence, it seems
+likely that an ROS in three dimensions is able to capture the uncertainty
+in $g(\bm{X})$ due to uncertainty in the six parameters. To illustrate computational gains
+as a result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the uncertainty
+in $k_1$ as well), and the original 6D parameter domain. In Figure~\ref{fig:conv_osc}~(left), we
+compare the rate of convergence of the PCEs. As expected, the third-order PCE converges much faster
+than the other two. Consequently, the number of model evaluations required for a converged
+PCE is expected to be relatively much smaller in this case.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_oscillator}
+  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
+\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is against sample size for 
+PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
+Right: PDF of the limit state function is plotted using the actual function in~\eqref{eq:limit}
+and the third-order PCE.}
+\label{fig:conv_osc}
+\end{center}
+\end{figure}
+
 \subsection{Semilinear elliptic PDE with random source term}

### 2018-05-17 Paper/examples.tex
..

@@
 
+In order to verify the accuracy of the third-order PCE, we estimate the relative L-2 norm of the
+difference between predictions of  $g(\bm{X})$, obtained using the actual function in ~\eqref{eq:limit}
+and the PCE using~\eqref{eq:l2}.  The value of $\epsilon_{\mbox{\tiny{L-2}}}$ using evaluations at
+100 points was found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$. Furthermore, 
+the accuracy is assessed in a probabilistic sense by comparing PDFs
+of $g(\bm{X})$, obtained using the function and the 3D PCE as illustrated in Figure~\ref{fig:conv_osc}~(right).
+Clearly, the two PDFs are in excellent agreement with each other. Hence, the ROS constructed 
+using the methodology presented in section~\ref{sec:method} could be used reliably to characterize
+as well as quantify the uncertainty in $g(\bm{X})$ due to parametric uncertainty associated with
+its functional description in~\eqref{eq:limit}, efficiently.
+
 \subsection{Semilinear elliptic PDE with random source term}

### 2018-05-17 Paper/method.tex
..

@@
 constructed in a subspace that sufficiently captures the uncertainty in the
-model output.~\alennote{The next sentence seems unneeded, and 
-might be confusing; consider removing it, or clarify that in 
-the case of PCE, we construct PC bases as multivariate polynomials
-on a parameter space with reduced dimension.}
-In the context of PC surrogates used in this work, it implies
-that the dimensionality of the polynomial basis functions is effectively
-reduced.
+model output. We begin by outlining an algorithm for parameter screening
+to assess the importance of individual parameters for potential dimension
+reduction and construction of an ROS. The overall adaptive framework 
+which incorporates parameter screening as an integral step is thereafter
+presented. Finally, we present validation metrics used for assessing the
+convergence and accuracy of the ROS followed by a brief discussion on
+salient features of the proposed framework.
 
@@
 we could use finite-difference to approximate its value as shown in
-Eq.~\ref{eq:partial}. However, as discussed earlier in section 2.1,
-~\alennote{Don't hard code section numbers, use labels, and refer to them.}
+Eq.~\ref{eq:partial}. However, as discussed earlier in~\ref{sub:dgsm},
 estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires
@@
 used for screening and those associated with the validation test suite.  On the
-other hand, if $\alpha$ is considerably large (~\alennote{You mean close to
-one?}), the set of inputs required for screening are updated as needed, and a
+other hand, if $\alpha$ is close to 1, the set of inputs required for screening are
+ updated as needed, and a
 new set of $n_0$ samples and corresponding model evaluations are generated. The
@@
 model output based on model evaluations in the full parameter space and
-surrogate predictions corresponding to a large number of samples.  
-\alennote{I don't think you can construct the PDF in full parameter 
-space, in real applications, as you need a large number of 
-expensive model evaluations. Maybe we should say that  
-we compare the PDF of the surrogate to a histogram of true model
-evaluations?}
+the ROS predictions corresponding to a large number of samples (say, 10$^6$). 
+However, in realistic problems involving complex, compute-intensive 
+simulations, the PDF based on model evaluations would be intractable.
+A practical alternative would be to compare a histogram
+based on sparse model evaluations with the surrogate-based PDF
+in order to gain some insight into the quality of the comparison.
 

### 2018-05-17 Paper/method.tex
another comment on the algorithm ...

@@
 \Require $\tau > 0$, $\tau_\text{screen} > 0$,
-$s_\text{max}$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
+$s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
 \Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
@@
              $k = 1, \ldots, n_1$. 
-
+\alennote{Should we have $n_1 = n_0$? Also, there is an issue with this 
+algorithm: when you call this first time according to the flow diagram, you will
+not actually have the gradients $\bm{g}^k$, $k = 1, \ldots, N_\text{total}$;
+moreover, we need to explicitly augment the gradient samples with the ones 
+passed to the method. Moreover, I think the step $N_\text{total} = N_\text{total} + n_0$
+should be in the body of this algorithm, as opposed to where it is in the flow 
+diagram.}
       \State Compute 

### 2018-05-17 Paper/examples.tex
.
..

@@
 \caption{
-Left:Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
+Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
 borehole discharge function in~\eqref{eq:bore}. Right: 
@@
 given by~\eqref{eq:limit}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
-mean, $\mu$ and variance, $\sigma^2$. $\mathcal{U}[a,b]$ denotes a uniform distribution
-with limits $a$ and $b$.}
+mean, $\mu$ and variance, $\sigma^2$.}
 \label{tab:osc}

### 2018-05-18 Paper/method.tex
...

@@
 where $N_l$ is the number of training points,
-$\widetilde{\mu}~=~\frac{1}{N_l}\sum\limits_{i=1}^{N_l} G(\bm{\theta}_i)$
-is the sample mean of the model response, and $ G^{\mbox{\tiny
-{PC}\textbackslash i}}$ is the PC surrogate constructed using all but the
-$i^{\mbox{\tiny{th}}}$ model realization.  From~\eqref{eq:loo}, it appears
-that $N_l$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.  However,
-in practice a modified formulation for $\epsilon_{\mbox{\tiny
-LOO}}$~\cite{Blatman:2009}, independent of $G^{\mbox{\tiny {PC}\textbackslash
-i}}$ is used.~\alennote{What is that modified formulation? Need to specify.}
-Accuracy of the surrogate could be assessed by evaluating the
-relative $\ell_2$-norm of the difference in predictions between the model and the
-surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
+$\widetilde{\mu}~=~\frac{1}{N_l}\sum\limits_{i=1}^{N_l} G(\bm{\theta}_i)$ is
+the sample mean of the model response, and $ G^{\mbox{\tiny {PC}\textbackslash
+i}}$ is the PC surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$
+model realization.  From~\eqref{eq:loo}, it appears that $N_l$ PCEs are needed
+to evaluate $\epsilon_{\mbox{\tiny LOO}}$.  However, in practice a modified
+formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009}, independent
+of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used; for an easy reference,
+see~\cite[Eq.~(1.27)]{Marelli:2014}.  Accuracy of the surrogate could also 
+be assessed by evaluating the relative $\ell_2$-norm of the difference in
+predictions between the model and the surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
 \be
@@
 which model evaluations are available. 
-\alennote{You mean to do L2 error study in 
-addition to the leave-one-out error studies?}
-Accuracy of the surrogate could be
-further investigated by comparing probability density functions (PDFs) of the
-model output based on model evaluations in the full parameter space and
-the ROS predictions corresponding to a large number of samples (say, 10$^6$). 
-However, in realistic problems involving complex, compute-intensive 
-simulations, the PDF based on model evaluations would be intractable.
-A practical alternative would be to compare a histogram
-based on sparse model evaluations with the surrogate-based PDF
-in order to gain some insight into the quality of the comparison.
+%
+Accuracy of the surrogate could be further investigated by comparing
+probability density functions (PDFs) of the model output based on model
+evaluations in the full parameter space and the ROS predictions corresponding
+to a large number of samples (say, 10$^6$).  However, in realistic problems
+involving complex, compute-intensive simulations, the PDF based on model
+evaluations would be intractable.  A practical alternative would be to compare
+a histogram based on sparse model evaluations with the surrogate-based PDF in
+order to gain some insight into the quality of the comparison.
 

### 2018-05-18 Paper/bg.tex
..
...

@@
 \subsection{Derivative-based global sensitivity analysis}  
+\label{sub:dgsm}
 
@@
 \ee
-
-\noindent The upper bound in the above inequality is proportional to the product of $\mathcal{C}_i$
-and $\mu_i$. However, for the purpose of parameter screening as discussed later in
-Section~\ref{sec:method}, we consider a normalized product, $\widehat{\mathcal{C}_i\mu_i}$:
+The upper bound in the above inequality is proportional to the product of
+$\mathcal{C}_i$ and $\mu_i$. However, for the purpose of parameter screening as
+discussed later in Section~\ref{sec:method}, we consider a normalized product,
+$\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies between 0 and 1:
 
@@
 \left[\left(\sum_{k=0}^\Npc c_k \Psi_k(\bm\xi(\bm\theta)) -
-\GG^{\mbox{\tiny{M}}}(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
+\GG(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
+\label{eq:reg}
 \ee

### 2018-05-18 Paper/method.tex
..

@@
       \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
-             $k = 1, \ldots, n_1$. 
-\alennote{Should we have $n_1 = n_0$? Also, there is an issue with this 
-algorithm: when you call this first time according to the flow diagram, you will
-not actually have the gradients $\bm{g}^k$, $k = 1, \ldots, N_\text{total}$;
-moreover, we need to explicitly augment the gradient samples with the ones 
-passed to the method. Moreover, I think the step $N_\text{total} = N_\text{total} + n_0$
-should be in the body of this algorithm, as opposed to where it is in the flow 
-diagram.}
+             $k~=~N_\text{total}+1, \ldots, N_\text{total}+n_1$. 
+      \State $N_\text{total} = N_\text{total} + n_1$
       \State Compute 
@@
 
-\node (sam0) [process, below of=tol, text width=12.5em, yshift=-0.3cm] {Draw $n_0$ samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
+\node (sam0) [process, below of=tol, text width=12.5em, yshift=-0.3cm] {Draw $n_1$ samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
      according to $\bm{f(\theta)}$};
@@
 
-\node (counter) [process, below of=sam0, text width=9.5em, yshift=-0.21cm] {\vspace{-6mm}\be N_\text{total} = N_\text{total} + n_0 \nonumber\ee};
+%\node (counter) [process, below of=sam0, text width=9.5em, yshift=-0.21cm] {\vspace{-6mm}\be N_\text{total} = N_\text{total} + n_0 \nonumber\ee};
 
-\draw [arro] (sam0) -- (counter);
+%\draw [arro] (sam0) -- (counter);
 
-\node (fss) [process, below of=counter, text width=14.5em, yshift=-0.28cm] {Construct regression-based 
-surrogate in full-space (FSS) uing $N_\text{total}$ model evaluations};
+\node (fss) [process, below of=sam0, text width=14.5em, yshift=-0.5cm] {Construct regression-based 
+surrogate in full-space (FSS) uing ($N_\text{total}$+$n_1$) model evaluations};
 
-\draw [arro] (counter) -- (fss);
+\draw [arro] (sam0) -- (fss);
 
@@
 
-\node (ver) [process, left of=ros, text width=14.5em, xshift=-5cm] {Verify ROS using evaluations at $N_\text{total}$
-$\&$ the validation test suite};
+\node (ver) [process, left of=ros, text width=13.0em, xshift=-5cm] {Test ROS accuracy using
+ evaluations at $N_\text{total}$ $\&$ the validation test suite};
 
@@
 following equation: 
+%
 \be
@@
 \ee
-\alennote{I noticed in the latex code the use of the \textbf{noindent} command;
-please remove those, we will use latext setting to formation paragraphs.} where
-$|\mathcal{I}_\text{active}|$ denotes the cardinality of
+%
+where $|\mathcal{I}_\text{active}|$ denotes the cardinality of
 $\mathcal{I}_\text{active}$.  Scope for dimension-reduction increases as
@@
 where $N_v$ is the number of sampling points in the full parameter space at
-which model evaluations are available. 
+which model evaluations are available. In the case of an ROS, it is the
+augmented set of model evaluations used for validation and screening.  
 %
@@
 implementing the present framework.
+
+Using the framework proposed in this section, we aim to construct a reliable
+surrogate in the most efficient manner within the constraints of the computational
+budget. However, it is likely that for a given application, the ROS is not
+found to be sufficiently accurate. In such a scenario, we suggest enriching the
+set of important parameters by incorporating the least unimportant parameter
+as determined after a series of screening steps, and re-constructing the ROS. 
+This process could be repeated depending upon the availability of resources
+and the desired accuracy of the surrogate.
 

### 2018-05-20 Paper/bg.tex
update ...

@@
 \ee
+The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability
+distribution of $\theta_i$. For $\theta_i \sim \mathcal{U}[a, b]$,
+$\mathcal{C}_i = (b-a)^{2}/\pi^2$, and for  
+$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$. 
+Here $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with mean $\mu$
+and variance $\sigma^2$, and $\mathcal{U}[a,b]$ denotes a uniform distribution
+on the interval $[a, b]$.
 
-\noindent The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability distribution of $\theta_i$.
-Table~\ref{tab:poincare} provides its value in the case of uniform and normal
-distributions.
-\bigskip
-
-\begin{table}[htbp]
-\renewcommand*{\arraystretch}{1.2}
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-Distribution & $\mathcal{C}_i$ \\ \hline \hline 
-Uniform, $\mathcal{U}[a, b]$ & $(b-a)^{2}/\pi^2$ \\ 
-Normal, $\mathcal{N}(\mu,\sigma^2)$ & $\sigma^2$ \\ 
-\hline
-\end{tabular}
-\end{center}
-
-\caption{Poincare constant for the case of uniformly and normally distributed random
-parameters~\cite{Roustant:2014}.}
-\label{tab:poincare}
-\end{table}
+%Table~\ref{tab:poincare} provides its value in the
+%case of uniform and normal distributions.
+%
+%\begin{table}[htbp]
+%\renewcommand*{\arraystretch}{1.2}
+%\begin{center}
+%\begin{tabular}{|c|c|}
+%\hline
+%Distribution & $\mathcal{C}_i$ \\ \hline \hline 
+%Uniform, $\mathcal{U}[a, b]$ & $(b-a)^{2}/\pi^2$ \\ 
+%Normal, $\mathcal{N}(\mu,\sigma^2)$ & $\sigma^2$ \\ 
+%\hline
+%\end{tabular}
+%\end{center}
+%\caption{Poincare constant for the case of 
+%uniformly and normally distributed random
+%parameters~\cite{Roustant:2014}.}
+%\label{tab:poincare}
+%\end{table}
 

### 2018-05-20 Paper/examples.tex
update ...

--- 2018-05-16 Paper/examples.tex
@@
 \begin{center}
-\begin{tabular}{|l||l|}
-\hline
-\textbf{Parameter Description} & \textbf{Distribution} \\ \hline \hline
+\begin{tabular}{ll}
+\toprule
+\textbf{Parameter} & \textbf{Distribution} \\ 
+\bottomrule
 Borehole radius, $r_w$ (m) & $\mathcal{N}$(0.1,0.016) \\
@@
 Borehole hydraulic conductivity, $K_w$ (m/yr) & $\mathcal{U}$[9855,12045] \\
-\hline
+\bottomrule
 \end{tabular}
@@
 \caption{Description and distributions of uncertain parameters in the borehole function
-given by~\eqref{eq:bore}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
-mean, $\mu$ and variance, $\sigma^2$. $\mathcal{U}[a,b]$ denotes a uniform distribution
-with limits $a$ and $b$.}
+given by~\eqref{eq:bore}.}
 \label{tab:bore}
@@
 % 
-\subsection{Non-linear Oscillator}
-
-In this test problem, we consider an undamped non-linear oscillator with only one degree of
-freedom as illustrated below in Figure~\ref{fig:osc}.
-
+\subsection{Nonlinear Oscillator}
+We consider an undamped nonlinear oscillator with only one degree of
+freedom as illustrated in Figure~\ref{fig:osc}. 
 \begin{figure}[htbp]
  \begin{center}
-  \includegraphics[width=0.6\textwidth]{./Figures/oscillator}
+  \includegraphics[width=0.5\textwidth]{./Figures/oscillator}
 \caption{Schematic illustration of an undamped non-linear oscillator system with one degree of freedom.}
@@
 \end{figure}
-
-The above system has been studied extensively for its reliability using
+This system has been studied extensively for its reliability using
 the following state function~\cite{Bucher:1989,Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:
@@
 g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - 
-\left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|
+\left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|,
 \label{eq:limit}
 \ee
-
 \noindent where $z_\text{max}$ is the maximum displacement response of the system, $r$ denotes the displacement at
-which either spring yields, $\bm{X}:~\{m,k_1,k_2,r,F,t_1\}$ is a set of uncertain parameters, and   
-$\omega_0~=~\sqrt{\frac{k_1+k_2}{m}}$. The uncertain parameters are considered to be normally distributed with mean
+which either spring yields, $\bm{X}=(m,k_1,k_2,r,F,t_1)^T$ is the vector 
+of uncertain parameters, and   
+$\omega_0~=~\sqrt{(k_1+k_2)/m}$. The uncertain parameters are considered to be normally distributed with mean
 and variance as provided below in Table~\ref{tab:osc}.
@@
 \begin{center}
-\begin{tabular}{|l||l|}
-\hline
-\textbf{Parameter Description} & \textbf{Distribution} \\ \hline \hline
+\begin{tabular}{ll}
+\toprule
+\textbf{Parameter} & \textbf{Distribution} \\ 
+\bottomrule
 Mass, $m$ (kg) & $\mathcal{N}$(1,0.05) \\
@@
 Spring Constant, $k_2$ (Nm$^{-1}$) & $\mathcal{N}$(0.1,0.01) \\
-\hline
+\bottomrule
 \end{tabular}
@@
 
-\caption{Description and distributions of uncertain parameters in the limit state function
-given by~\eqref{eq:limit}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
-mean, $\mu$ and variance, $\sigma^2$. $\mathcal{U}[a,b]$ denotes a uniform distribution
-with limits $a$ and $b$.}
+\caption{Description and distributions of uncertain parameters in the limit state function~\eqref{eq:limit}.}
 \label{tab:osc}
@@
 Converged estimates of $\mathcal{T}(\theta_i)$ are once again obtained easily by
-evaluating $g(\bm{X})$ for a large set of samples in $\mathbb{R}^{|\bm{X}|}$ as
-shown in Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
+evaluating $g(\bm{X})$ for a large set of samples in the uncertain 
+parameter space; see Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
 $\widehat{\mathcal{C}_i\mu_i}$ are plotted against the number of samples in 
 Figure~\ref{fig:sense_osc}~(right). 
-
 \begin{figure}[htbp]
@@
 \end{figure}
-
-From the above figure, it can be said that the Sobol sensitivity indices are in excellent
-agreement with the screening metric estimates. Consequently, the parameter ranks are
-found to be consistent in the two plots. It is observed that the limit state function is
-predominantly sensitive towards three parameters: $r$, $F$, and $t_1$. Hence, it seems
-likely that an ROS in three dimensions is able to capture the uncertainty
-in $g(\bm{X})$ due to uncertainty in the six parameters. To illustrate computational gains
-as a result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the uncertainty
-in $k_1$ as well), and the original 6D parameter domain. In Figure~\ref{fig:conv_osc}~(left), we
-compare the rate of convergence of the PCEs. As expected, the third-order PCE converges much faster
-than the other two. Consequently, the number of model evaluations required for a converged
-PCE is expected to be relatively much smaller in this case.
-
+We note that the total Sobol sensitivity indices are in excellent agreement
+with the screening metric estimates. 
+Consequently, the parameter ranks are found to be consistent in the
+two plots in  
+Figure~\ref{fig:sense_osc}.
+It is observed that the limit state function is predominantly sensitive 
+to $r$, $F$, and $t_1$. Hence, it seems likely that an ROS in
+three dimensions is able to capture the overall uncertainty in $g(\bm{X})$.
+% due to uncertainty in the six parameters. 
+To illustrate computational gains as a
+result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the
+uncertainty in $k_1$ as well), and the original 6D parameter domain. In
+Figure~\ref{fig:conv_osc}~(left), we compare the convergence of the
+PCEs. As expected, the third-order PCE converges much faster than the other
+two. Consequently, the number of model evaluations required for a converged PCE
+is expected to be relatively much smaller in this case.  
 \begin{figure}[htbp]
@@
 \end{figure}
+
+To verify the accuracy of the third-order PCE, we estimate the relative L-2
+norm of the difference between predictions of  $g(\bm{X})$, obtained using the
+actual function in ~\eqref{eq:limit} and the 
+PCE using~\eqref{eq:l2}~\alennote{Do we use a validation set?}  The
+value of $\epsilon_{\mbox{\tiny{L-2}}}$ using evaluations 
+at 100 points~\alennote{How are these points generated? Monte Carlo? QMC?}
+was
+found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
+Furthermore, the accuracy is assessed in a probabilistic sense by comparing
+PDFs of $g(\bm{X})$, obtained using the function and the 3D PCE as illustrated
+in Figure~\ref{fig:conv_osc}~(right).  Clearly, the two PDFs are in excellent
+agreement with each other. Hence, the ROS constructed using the methodology
+presented in section~\ref{sec:method} could be used reliably to 
+quantify the uncertainty in $g(\bm{X})$.
+% due to parametric uncertainty
+%associated with its functional description in~\eqref{eq:limit}, efficiently.
 

### 2018-05-20 Paper/examples.tex
...

@@
 
-The borehole function is a benchmark reference problem in sensitivity analysis. It models the discharge
-of water ($\mathcal{Q}$) through a borehole in terms of geometrical and physical parameters:
-
+The borehole function is a benchmark reference problem in sensitivity analysis.
+It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
+geometrical and physical parameters:
 \be
-\mathcal{Q} = \frac{2\pi T_u(H_u - H_l)}{\ln\left(\frac{r}{r_w}\right)\left(1 +
-\frac{2LT_u}{\ln\left(\frac{r}{r_w}\right)r_w^2K_w} + \frac{T_u}{T_l}\right)}
+\mathcal{Q} = \frac{\displaystyle
+2\pi T_u(H_u - H_l)}{\displaystyle
+\ln({r}/{r_w})\Big[1 +
+\frac{2LT_u}{
+\ln({r}/{r_w})r_w^2K_w} + \frac{T_u}{T_l}\Big]}
 \label{eq:bore}
 \ee
-
-\noindent The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
+The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
 in the right hand side of~\eqref{eq:bore} are considered 

### 2018-05-21 Paper/examples.tex
..

@@
 norm of the difference between predictions of  $g(\bm{X})$, obtained using the
-actual function in ~\eqref{eq:limit} and the 
-PCE using~\eqref{eq:l2}~\alennote{Do we use a validation set?}  The
-value of $\epsilon_{\mbox{\tiny{L-2}}}$ using evaluations 
-at 100 points~\alennote{How are these points generated? Monte Carlo? QMC?}
-was
-found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
+actual function in \eqref{eq:limit} and the 
+PCE using \eqref{eq:l2}, and a validation test suite. The test suite comprised
+model evaluations at 100 independent Monte-Carlo samples in the full 
+parameter space. The value of $\epsilon_{\mbox{\tiny{L-2}}}$ 
+was found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
 Furthermore, the accuracy is assessed in a probabilistic sense by comparing

### 2018-05-22 Paper/examples.tex
..

@@
 in the right hand side of~\eqref{eq:bore} are considered 
-as uncertain. Thus, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
-\[
-   \vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T.
-\] 
-Table~\ref{tab:bore} provides distributions of the uncertain inputparameters.
+as uncertain. Hence, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
+ $\vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T$, a vector of
+ uncertain parameters. Table~\ref{tab:bore} provides distributions of the
+ uncertain input parameters.
 
@@
 
-\subsection{Semilinear elliptic PDE with random source term}
+\subsection{Semi-linear elliptic PDE with random source term}
 
-We consider the semilinear elliptic PDE,
-\begin{equation}\label{equ:semilinear}
+We consider the following semi-linear elliptic PDE on a 2D square domain ([0,1]$\times$[0,1]):
+
+\begin{equation}\label{eq:semilinear}
 \begin{aligned}
@@
 \end{equation}
-We model the source term as 
-\begin{equation}
-q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
-\cos(i \pi y),
-\quad N = 8.
-\end{equation}
-Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
-and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
-the following QoI,
-\[
-     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
-\]
-where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.
+%
+where $u$ is referred to as the velocity, $\kappa$ and $c$ are coefficients of the diffusion term
+and the non-linear term in the above equation respectively. The velocity, $u$ is random since the
+source term, $q$ in RHS is modelled as a truncated summation with random coefficients:
+
+\be
+q = \sum\limits_{i=1}^{N=8}\alpha_i\sin\left(\frac{i\pi x}{8}\right)\cos\left(\frac{i\pi y}{8}\right)
+\label{eq:source}
+\ee
+%
+Hence, $u~=~u(\vec{\theta})$ with $\vec{\theta} = (\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$, a vector
+of uncertain parameters. Table~\ref{tab:elliptic} provides distributions of the uncertain
+input parameters. The solution of~\eqref{eq:semilinear} for
+a particular set of values of the uncertain parameters is illustrated below in Figure~\ref{fig:usoln}.
+
+\begin{table}[htbp]\label{tab:elliptic}
+\renewcommand*{\arraystretch}{1.2}
+\begin{center}
+\begin{tabular}{cl}
+\toprule
+\textbf{Parameter} & \textbf{Distribution} \\ 
+\bottomrule
+$\kappa$ & $\mathcal{U}$[0.05,0.1] \\
+$c$ & $\mathcal{U}$[1.0,2.0] \\
+$\alpha_i$ & $\mathcal{U}$[0.0,4.0] \\
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{Description and distributions of uncertain parameters in the 
+semi-linear elliptic PDE in~\eqref{eq:semilinear}.}
+\end{table}
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.6\textwidth]{./Figures/u_soln}
+  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at fixed values
+  of $\kappa$, $c$, and $\alpha_i$ as provided. The color-bar indicates the range of $u$.}
+\label{fig:usoln}
+\end{center}
+\end{figure}
+
+%We consider the semilinear elliptic PDE,
+%\begin{equation}\label{equ:semilinear}
+%\begin{aligned}
+%-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
+% u &= 0. \quad \text{on } \partial \Omega
+%\end{aligned}
+%\end{equation}
+%We model the source term as 
+%\begin{equation}
+%q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
+%\cos(i \pi y),
+%\quad N = 8.
+%\end{equation}
+%Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
+%and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
+%the following QoI,
+%\[
+%     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
+%\]
+%where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.

### 2018-05-22 Paper/examples.tex
..

@@
 borehole discharge function in~\eqref{eq:bore}. Right: 
-Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
+Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
 against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
@@
 state function in~\eqref{eq:limit}. Right: 
-Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
+Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
 against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
@@
   \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
-\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is against sample size for 
+\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
 PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
@@
   \includegraphics[width=0.6\textwidth]{./Figures/u_soln}
-  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at fixed values
-  of $\kappa$, $c$, and $\alpha_i$ as provided. The color-bar indicates the range of $u$.}
+  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at 
+  of $\kappa$~=~0.075, $c$~=~1.5, and $\alpha_i$~=~4.0.}
 \label{fig:usoln}
@@
 
-%We consider the semilinear elliptic PDE,
-%\begin{equation}\label{equ:semilinear}
-%\begin{aligned}
-%-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
-% u &= 0. \quad \text{on } \partial \Omega
-%\end{aligned}
-%\end{equation}
-%We model the source term as 
-%\begin{equation}
-%q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
-%\cos(i \pi y),
-%\quad N = 8.
-%\end{equation}
-%Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
-%and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
-%the following QoI,
-%\[
-%     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
-%\]
-%where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.
+We aim to construct a reduced-order surrogate for the following quantity of interest (QoI):
+
+\be
+\mathcal{F}(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
+\label{eq:qoi}
+\ee
+%
+where $D$ is the region: $[2/5, 3/5] \times [2/5, 3/5]$. Once again, the availability of
+cheap model evaluations allow us to obtain converged estimates of the Sobol
+total-effect index ($\mathcal{T}(\theta_i)$), plotted in Figure~\ref{fig:sense_elliptic}.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.46\textwidth]{./Figures/sense_elliptic}
+  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_elliptic}
+\caption{
+Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the 
+semi-linear elliptic PDE~\eqref{eq:semilinear}. Right: 
+Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each uncertain parameter,
+obtained using $N$ = 5, 10, 15, and 20 samples in the full parameter space.}
+\label{fig:sense_elliptic}
+\end{center}
+\end{figure}
+%
+Sensitivity predictions based on the screening metric, $\widehat{\mathcal{C}_i\mu_i}$ are found to
+be in close agreement with $\mathcal{T}(\theta_i)$, even for the case when $N$ = 5. Moreover, 
+the uncertainty in the QoI in \eqref{eq:qoi} is observed to be largely dependent on $c$, 
+$\alpha_2$, $\alpha_3$, $\alpha_4$, and $\alpha_5$. These observations underscore the
+potential for computational gains by constructing an ROS in the 5D parameter space. We 
+illustrate the comparison of convergence characteristics of the PCEs constructed in the
+full parameter space (10D) and the reduced space (5D) in Figure~\ref{fig:conv_elliptic} (left). 
+As expected, the ROS converges at a much faster rate. Using model evaluations at 90
+sample points, $\epsilon_{\mbox{\tiny{LOO}}}$ is found to be two orders of magnitude
+smaller than that in the case of full-surrogate ($\mathcal{O}(10^{-4}$) vs. $\mathcal{O}(10^{-2}$)). 
+Consequently, the computational effort for constructing the ROS in the present test problem
+is expected to be much smaller.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_elliptic}
+  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_elliptic}
+\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
+PCEs constructed in 10 and 5 dimensions to compare their convergence characteristics. 
+Right: PDF of the QoI, $\mathcal{F}(\kappa, c, \theta)$ in~\eqref{eq:semilinear} is
+plotted using the full-surrogate and the reduced-order PC surrogate.}
+\label{fig:conv_elliptic}
+\end{center}
+\end{figure}

### 2018-05-22 Paper/examples.tex
..

@@
 for individual parameters.
-In this section, we motivate the underlying methodology by applying it to three test problems,
+In this section, we motivate the underlying methodology by applying it to three
+test problems,
 namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
@@
 \caption{
-Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
+Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain
+parameters in the
 borehole discharge function in~\eqref{eq:bore}. Right: 
 Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
-against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
-in each case in the legend.}
+against number of samples. Also included in the legend are estimates of
+$\mathcal{T}(\theta_i)$ in each case in the legend.}
 \label{fig:sense_bore}
@@
 
-We consider the following semi-linear elliptic PDE on a 2D square domain ([0,1]$\times$[0,1]):
+We consider the following semi-linear elliptic PDE on a 2D square domain ([0,1]$\times$[0,1])
+with Dirichlet boundary conditions:
 
@@
 and the non-linear term in the above equation respectively. The velocity, $u$ is random since the
-source term, $q$ in RHS is modelled as a truncated summation with random coefficients:
+source term, $q$ in the RHS is modelled as a truncated summation with random coefficients:
 
@@
 %
-Hence, $u~=~u(\vec{\theta})$ with $\vec{\theta} = (\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$, a vector
-of uncertain parameters. Table~\ref{tab:elliptic} provides distributions of the uncertain
-input parameters. The solution of~\eqref{eq:semilinear} for
-a particular set of values of the uncertain parameters is illustrated below in Figure~\ref{fig:usoln}.
+Hence, $u~=~u(\vec{\theta})$ with $\vec{\theta} = 
+(\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$, a vector
+of uncertain parameters. Distributions of the uncertain
+input parameters are tabulated below in Figure~\ref{fig:elliptic}~(left).
+The solution of~\eqref{eq:semilinear} for
+a fixed set of values of the uncertain parameters is also 
+illustrated.
 
-\begin{table}[htbp]\label{tab:elliptic}
-\renewcommand*{\arraystretch}{1.2}
+\begin{figure}[htbp]
 \begin{center}
+\begin{minipage}[htbp]{.25\linewidth}
+\vspace{0pt}
+%\centering
+\hspace{-25mm}
 \begin{tabular}{cl}
 \toprule
-\textbf{Parameter} & \textbf{Distribution} \\ 
+$\theta_i$ & \textbf{Distribution} \\ 
 \bottomrule
@@
 \end{tabular}
+\end{minipage}
+\hspace{-20mm}
+\begin{minipage}[htbp]{.25\linewidth}
+\vspace{0pt}
+%\centering
+\includegraphics[width=3.0in]{./Figures/u_soln.png}
+\end{minipage}%
 \end{center} 
-\caption{Description and distributions of uncertain parameters in the 
-semi-linear elliptic PDE in~\eqref{eq:semilinear}.}
-\end{table}
+\caption{Left: Table providing distributions of the individual
+uncertain parameters in~\eqref{eq:semilinear}. Right: Solution
+of the 2D semi-linear elliptic PDE~\eqref{eq:semilinear} using
+$\kappa$~=~0.075, $c$~=~1.5, and $\alpha_i$~=~4.0}
+\label{fig:elliptic}
+\end{figure}
 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.6\textwidth]{./Figures/u_soln}
-  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at 
-  of $\kappa$~=~0.075, $c$~=~1.5, and $\alpha_i$~=~4.0.}
-\label{fig:usoln}
-\end{center}
-\end{figure}
+%\begin{table}[htbp]
+%\begin{tabular}{cc}
+%
+%  \includegraphics[width=0.45\textwidth]{./Figures/u_soln.png} &
+%\begin{tabular}{cl}
+%\toprule
+%$\theta_i$ & \textbf{Distribution} \\ 
+%\bottomrule
+%$\kappa$ & $\mathcal{U}$[0.05,0.1] \\
+%$c$ & $\mathcal{U}$[1.0,2.0] \\
+%$\alpha_i$ & $\mathcal{U}$[0.0,4.0] \\
+%\bottomrule
+%\end{tabular}
+%\\
+%\end{tabular}
+%\end{table}
 
@@
 %
-where $D$ is the region: $[2/5, 3/5] \times [2/5, 3/5]$. Once again, the availability of
+where $D$ is the region: $[2/5, 3/5] \times [2/5, 3/5]$ in $\mathbb{R}^{x\times y}$. 
+The availability of
 cheap model evaluations allow us to obtain converged estimates of the Sobol
-total-effect index ($\mathcal{T}(\theta_i)$), plotted in Figure~\ref{fig:sense_elliptic}.
+total-effect index ($\mathcal{T}(\theta_i)$), plotted in Figure~\ref{fig:sense_elliptic}~(left),
+with reasonable effort.
 
@@
 %
-Sensitivity predictions based on the screening metric, $\widehat{\mathcal{C}_i\mu_i}$ are found to
-be in close agreement with $\mathcal{T}(\theta_i)$, even for the case when $N$ = 5. Moreover, 
-the uncertainty in the QoI in \eqref{eq:qoi} is observed to be largely dependent on $c$, 
+Sensitivity predictions based on the screening metric, $\widehat{\mathcal{C}_i\mu_i}$,
+plotted in Figure~\ref{fig:sense_elliptic}~(right), are found to
+be in close agreement with $\mathcal{T}(\theta_i)$, even for the case when $N$ = 5. As $N$
+is increased from 5 to 20, estimates of the screening metric are observed to converge.
+Based on the trends observed in Figure~\ref{fig:sense_elliptic}, it can be said that
+the uncertainty in the QoI in \eqref{eq:qoi} is largely dependent on $c$, 
 $\alpha_2$, $\alpha_3$, $\alpha_4$, and $\alpha_5$. These observations underscore the
@@
 \end{figure}
+
+Once again, we verify the accuracy of the ROS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
+using model evaluations at 100 independent Monte-Carlo samples in the 10D parameter
+space. The L-2 norm was estimated to be 0.05 i.e. the ROS was found to be accurate
+within 5$\%$. Additionally, we compare PDFs of the QoI, $\mathcal{F}(\kappa,c,\theta)$,
+generated using the full-space and the reduced-space surrogates in 
+Figure~\ref{fig:conv_elliptic}~(right). The two PDFs are observed to be in excellent 
+agrement with each other. Hence, the ROS is successfully verified and could be
+used in lieu of the full-space surrogate to reduce computational effort.

### 2018-05-22 Paper/examples.tex
PDE example ...

@@
 test problems,
-namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
+namely, the borehole function, a non-linear oscillator, and a semilinear elliptic PDE.
 Since model evaluations in all these test
@@
 
-\subsection{Semi-linear elliptic PDE with random source term}
+\subsection{Semilinear elliptic PDE with random source term}
 
-We consider the following semi-linear elliptic PDE on a 2D square domain ([0,1]$\times$[0,1])
-with Dirichlet boundary conditions:
-
+We consider the following semilinear elliptic PDE: 
 \begin{equation}\label{eq:semilinear}
 \begin{aligned}
--\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
- u &= 0. \quad \text{on } \partial \Omega
+-\kappa \Delta u + c u^3 &= q \quad \text{in } \Omega,\\
+ u &= 0 \quad \text{on } \partial \Omega.
 \end{aligned}
 \end{equation}
-%
-where $u$ is referred to as the velocity, $\kappa$ and $c$ are coefficients of the diffusion term
-and the non-linear term in the above equation respectively. The velocity, $u$ is random since the
-source term, $q$ in the RHS is modelled as a truncated summation with random coefficients:
-
+Here $\Omega = (0, 1)\times(0,1)$, 
+$u$ is the state variable, and $\kappa$ and $c$ are coefficients of the diffusion term
+and the nonlinear term in the above equation respectively. 
+We consider uncertainties in $\kappa$, $c$, and the source term. 
+The right hand side function $q$ is defined by 
 \be
-q = \sum\limits_{i=1}^{N=8}\alpha_i\sin\left(\frac{i\pi x}{8}\right)\cos\left(\frac{i\pi y}{8}\right)
+q(x, y) = 
+\sum\limits_{i=1}^{N=8}\alpha_i\sin\left(\frac{i\pi x}{8}\right)
+                               \cos\left(\frac{i\pi y}{8}\right),
 \label{eq:source}
 \ee
+where $\alpha_i$, $i = 1, \ldots, 8$ are random coefficients.
 %
-Hence, $u~=~u(\vec{\theta})$ with $\vec{\theta} = 
-(\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$, a vector
+Hence, $u~=~u(\vec{\theta})$, where $\vec{\theta} = 
+(\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$ is the vector
 of uncertain parameters. Distributions of the uncertain
-input parameters are tabulated below in Figure~\ref{fig:elliptic}~(left).
+input parameters are tabulated in Figure~\ref{fig:elliptic}~(left).
 The solution of~\eqref{eq:semilinear} for
@@
 uncertain parameters in~\eqref{eq:semilinear}. Right: Solution
-of the 2D semi-linear elliptic PDE~\eqref{eq:semilinear} using
+of the 2D semilinear elliptic PDE~\eqref{eq:semilinear} using
 $\kappa$~=~0.075, $c$~=~1.5, and $\alpha_i$~=~4.0}
@@
 
-We aim to construct a reduced-order surrogate for the following quantity of interest (QoI):
-
+We aim to construct a reduced-order surrogate for the following QoI:
 \be
@@
 %
-where $D$ is the region: $[2/5, 3/5] \times [2/5, 3/5]$ in $\mathbb{R}^{x\times y}$. 
-The availability of
-cheap model evaluations allow us to obtain converged estimates of the Sobol
-total-effect index ($\mathcal{T}(\theta_i)$), plotted in Figure~\ref{fig:sense_elliptic}~(left),
-with reasonable effort.
-
+where $D$ is the region $[2/5, 3/5] \times [2/5, 3/5] \subset \Omega$, 
+and $|D|$ denotes the area of $D$. 
+While this model is considerably more complex than the previous numerical
+examples, it can still be solved efficiently.
+The equation was discretized using finite-differences and Newton's method
+was used to solve the resulting nonlinear system.~\alennote{Give the
+number of degrees of freedom.} 
+We computed converged estimates of the Sobol
+total-effect index $\mathcal{T}(\theta_i)$, reported 
+in Figure~\ref{fig:sense_elliptic}~(left).~\alennote{Say how many PDE solves
+were used.}
 \begin{figure}[htbp]
@@
 Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the 
-semi-linear elliptic PDE~\eqref{eq:semilinear}. Right: 
+semilinear elliptic PDE~\eqref{eq:semilinear}. Right: 
 Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each uncertain parameter,
@@
 full parameter space (10D) and the reduced space (5D) in Figure~\ref{fig:conv_elliptic} (left). 
-As expected, the ROS converges at a much faster rate. Using model evaluations at 90
+As expected, the ROS converges considerably faster. Using model evaluations at 90
 sample points, $\epsilon_{\mbox{\tiny{LOO}}}$ is found to be two orders of magnitude
-smaller than that in the case of full-surrogate ($\mathcal{O}(10^{-4}$) vs. $\mathcal{O}(10^{-2}$)). 
+smaller than that in the case of full-surrogate ($\mathcal{O}(10^{-4}$) versus
+$\mathcal{O}(10^{-2}$)). 
 Consequently, the computational effort for constructing the ROS in the present test problem
 is expected to be much smaller. 
-
+%
 \begin{figure}[htbp]
@@
 using model evaluations at 100 independent Monte-Carlo samples in the 10D parameter
-space. The L-2 norm was estimated to be 0.05 i.e. the ROS was found to be accurate
-within 5$\%$. Additionally, we compare PDFs of the QoI, $\mathcal{F}(\kappa,c,\theta)$,
+space, and the ROS was found to be accurate
+within 5$\%$. 
+%The L-2 norm was estimated to be 0.05 i.e. 
+Additionally, we compare PDFs of the QoI, $\mathcal{F}(\kappa,c,\theta)$,
 generated using the full-space and the reduced-space surrogates in
-Figure~\ref{fig:conv_elliptic}~(right). The two PDFs are observed to be in excellent 
-agrement with each other. Hence, the ROS is successfully verified and could be
-used in lieu of the full-space surrogate to reduce computational effort.
+Figure~\ref{fig:conv_elliptic}~(right). The two PDFs are observed to be in
+excellent agrement with each other. Hence, the ROS is successfully verified and
+could be used in lieu of the full-space surrogate to reduce computational
+effort. 
+\alennote{Regarding the PDFs reported in figures 3, 6, 9: I think since we 
+are sampling the model at a large number of points to compute the
+total Sobol indices, we might as well save those sames, and then
+use them to compute a KDE of the ``true'' PDF; that way, each of these
+PDF comparison plots will report: true, FSS, ROS PDFs. I think that will
+make the case 
+for the presented method stronger, given we remain close to the true PDF.}

### 2018-05-23 Paper/examples.tex

@@
 examples, it can still be solved efficiently.
-The equation was discretized using finite-differences and Newton's method
+The equation was discretized using finite-differences, and Newton's method
 was used to solve the resulting nonlinear system.~\alennote{Give the

### 2018-05-23 Paper/examples.tex
..

--- 2018-05-22 Paper/examples.tex
@@
 predictive accuracy in a least-squares sense and a probabilistic sense.
-Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$ based on 50 samples and
-corresponding function evaluations in the original 7D parameter space were
+Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$ based on 50 samples in the
+validation test suite were
 found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other
@@
 samples through the 7D PCE in the original input parameter domain as well as
-the reduced order PCEs constructed in 4 and 5 dimensions. 
+the reduced order PCEs constructed in 4 and 5 dimensions. A normalized histogram
+plot using model evaluations in the validation test suite is also included.
 It is evident from this plot, that the PDFs agree quite favorably with each
-other with respect to the modal estimate as well as the uncertainty associated with 
-$\mathcal{Q}$. 
+other as well as the model-based histogram with respect to the modal estimate
+as well as the uncertainty associated with $\mathcal{Q}$. 
 Consequently, it can be said that the reduced order PCE is verified in a
@@
 Furthermore, the accuracy is assessed in a probabilistic sense by comparing
-PDFs of $g(\bm{X})$, obtained using the function and the 3D PCE as illustrated
-in Figure~\ref{fig:conv_osc}~(right).  Clearly, the two PDFs are in excellent
-agreement with each other. Hence, the ROS constructed using the methodology
+in Figure~\ref{fig:conv_osc}~(right),
+PDFs of $g(\bm{X})$, obtained using the full-surrogate, reduced-order 
+surrogates constructed 3 and 4 dimensions, and a normalized histogram based
+on model evaluation in the validation test suite. The three PDFs are observed
+to be in excellent agreement with each other as well as the model-based
+histogram. Hence, the ROS constructed using the methodology
 presented in section~\ref{sec:method} could be used reliably to 
-quantify the uncertainty in $g(\bm{X})$.
-% due to parametric uncertainty
-%associated with its functional description in~\eqref{eq:limit}, efficiently.
+quantify the uncertainty in $g(\bm{X})$ with reduced effort.
 
@@
 
-%\begin{table}[htbp]
-%\begin{tabular}{cc}
-%
-%  \includegraphics[width=0.45\textwidth]{./Figures/u_soln.png} &
-%\begin{tabular}{cl}
-%\toprule
-%$\theta_i$ & \textbf{Distribution} \\ 
-%\bottomrule
-%$\kappa$ & $\mathcal{U}$[0.05,0.1] \\
-%$c$ & $\mathcal{U}$[1.0,2.0] \\
-%$\alpha_i$ & $\mathcal{U}$[0.0,4.0] \\
-%\bottomrule
-%\end{tabular}
-%\\
-%\end{tabular}
-%\end{table}
-
 We aim to construct a reduced-order surrogate for the following QoI:
@@
 examples, it can still be solved efficiently.
-The equation was discretized using finite-differences and Newton's method
-was used to solve the resulting nonlinear system.~\alennote{Give the
+The equation was discretized using finite-differences, and Newton's method
+was used to solve the resulting nonlinear system on a (100$\times$100) 2D
+cartesian grid.~\alennote{Give the
 number of degrees of freedom.} 
@@
 total-effect index $\mathcal{T}(\theta_i)$, reported 
-in Figure~\ref{fig:sense_elliptic}~(left).~\alennote{Say how many PDE solves
-were used.}
+in Figure~\ref{fig:sense_elliptic}~(left) by solving the above non-linear
+system at 500 samples in the 10D parameter space. 
+%
 \begin{figure}[htbp]
@@
 using model evaluations at 100 independent Monte-Carlo samples in the 10D parameter
-space, and the ROS was found to be accurate
-within 5$\%$. 
-%The L-2 norm was estimated to be 0.05 i.e. 
-Additionally, we compare PDFs of the QoI, $\mathcal{F}(\kappa,c,\theta)$,
-generated using the full-space and the reduced-space surrogates in
-Figure~\ref{fig:conv_elliptic}~(right). The two PDFs are observed to be in
-excellent agrement with each other. Hence, the ROS is successfully verified and
-could be used in lieu of the full-space surrogate to reduce computational
-effort. 
-\alennote{Regarding the PDFs reported in figures 3, 6, 9: I think since we 
-are sampling the model at a large number of points to compute the
-total Sobol indices, we might as well save those sames, and then
-use them to compute a KDE of the ``true'' PDF; that way, each of these
-PDF comparison plots will report: true, FSS, ROS PDFs. I think that will
-make the case 
-for the presented method stronger, given we remain close to the true PDF.}
+space. The ROS was found to be accurate
+within 5$\%$. In order to bolster confidence in the ROS, we compare PDFs of the QoI
+as well as a normalized histogram plot based on sparse model evaluations in the  
+validation test-suite, in 
+Figure~\ref{fig:conv_elliptic}~(right). While the two PDFs are in favorable agreement,
+the modal estimate and the spread in the QoI based on the histogram is also captured
+by them. Hence, the ROS could be used with a reasonable degree of confidence to
+quantify the uncertainty in $\mathcal{F}(\kappa, c, \theta)$ thereby leading to
+a computational advantage in this case.

### 2018-05-23 Paper/app.tex
.
..

@@
-\section{Application: Phonon Transport in a Si bar}
+\section{Application: H$_2$/O$_2$ Reaction Kinetics}
 \label{sec:app}
+
+%Problem set-up: something about the reaction - why is it important?
+%different reactions, reaction rate definition, uncertain parameters,
+%quantity of interest. 
+%
+%Implementation of the proposed methodology for two scenarios: lean
+%mix and rich mix. Describe what we mean by lean and rich using
+%stoichiometry. 
+%
+%Define all the inputs as per the framework and illustrate its
+%implementation to this application for both scenarios
+
+The proposed framework in section~\ref{sec:method} is implemented to 
+the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
+The mechanism comprises of 19 reactions including chain reactions,
+dissociation/recombination reactions, and formation and consumption
+of intermediate species: HO$_2$ and H$_2$O$_2$, as provided below
+in Table~\ref{tab:kinetics}.
+
+\begin{table}[htbp]
+\renewcommand*{\arraystretch}{1.2}
+\begin{center}
+\begin{tabular}{ll}
+\toprule
+$\mathcal{R}_1$ & H + O$_2$ $\Longleftrightarrow$ O + OH \\
+$\mathcal{R}_2$ & O + H$_2$ $\Longleftrightarrow$ H + OH \\
+$\mathcal{R}_3$ & H$_2$ + OH $\Longleftrightarrow$ H$_2$O + H \\
+$\mathcal{R}_4$ & OH + OH $\Longleftrightarrow$ O + H$_2$O \\
+$\mathcal{R}_5$ & H$_2$ + M $\Longleftrightarrow$ H + H + M \\
+$\mathcal{R}_6$ & O + O + M $\Longleftrightarrow$ O$_2$ + M \\
+$\mathcal{R}_7$ & O + H + M $\Longleftrightarrow$ OH + M \\
+$\mathcal{R}_8$ & H + OH +M $\Longleftrightarrow$ H$_2$O + M \\
+$\mathcal{R}_9$ & H + O$_2$ + M $\Longleftrightarrow$ HO$_2$ + M \\
+$\mathcal{R}_{10}$ & HO$_2$ + H $\Longleftrightarrow$ H$_2$ + O$_2$ \\
+$\mathcal{R}_{11}$ & HO$_2$ + H $\Longleftrightarrow$ OH + OH \\
+$\mathcal{R}_{12}$ & HO$_2$ + O $\Longleftrightarrow$ O$_2$ + OH \\
+$\mathcal{R}_{13}$ & HO$_2$ + OH $\Longleftrightarrow$ H$_2$O + O$_2$ \\
+$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ $\Longleftrightarrow$ H$_2$O$_2$ + O$_2$ \\
+$\mathcal{R}_{15}$ & H$_2$O$_2$ + M $\Longleftrightarrow$ OH + OH + M \\
+$\mathcal{R}_{16}$ & H$_2$O$_2$ + H $\Longleftrightarrow$ H$_2$O + OH \\
+$\mathcal{R}_{17}$ & H$_2$O$_2$ + H $\Longleftrightarrow$ HO$_2$ + H$_2$ \\
+$\mathcal{R}_{18}$ & H$_2$O$_2$ + O $\Longleftrightarrow$ OH + HO$_2$ \\
+$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH $\Longleftrightarrow$ HO$_2$ + H$_2$O \\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\caption{Reaction mechanism for H$_2$/O$_2$~\cite{Yetter:1991}.}
+\label{tab:kinetics}
+\end{table}
+
+The reaction rate for the $i^{th}$ reaction as a function of temperature
+is given as follows:
+
+\be
+k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT) 
+\label{eq:rate}
+\ee
+%
+where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$
+is the activation energy corresponding to the $i^{th}$ reaction, and
+$R$ is the universal gas constant. We focus our attention on 
+quantifying the uncertainty in the `ignition delay' due to uncertainty
+associated with the pre-exponent, $A_i$ for each reaction. Hence, the
+total number of uncertain parameters in the present case is 19. 
+While the dimensionality of the problem is relatively moderate,
+constructing a surrogate in the 19D parameter space could still be
+expensive. Hence, we explore the possibility of constructing a
+reduce-order surrogate (ROS) using the framework presented earlier
+in section~\ref{sec:method}. To this end, the $A_i$'s are considered
+to be uniformly distributed in the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$;
+$A_i^\ast$ being the nominal estimate corresponding to the $i^{th}$
+reaction. TChem~\cite{Safta:2011}, an open source C package was used
+for simulating temperature and concentration evolution during the
+progress of reactions ($\mathcal{R}_1$ -- $\mathcal{R}_{19}$), and determining
+the ignition delay. The set of nominal values used in the computations,
+for parameters in~\eqref{eq:rate} are provided in~\cite{Yetter:1991}.
+
+In this study, we focus on two scenarios: fuel(H$_2$) rich, and fuel(H$_2$)
+lean. Consider the global reaction:
+
+\be
+2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2O
+\label{eq:global}
+\ee 
+%
+The equivalence ratio ($\phi$) is defined as follows:
+%
+\be
+\phi = \frac{(M_{\text{H}_2}/M_{\text{O}_2})_\text{obs}}{(M_{\text{H}_2}/M_{\text{O}_2})_\text{st}}
+\ee
+%
+The numerator in the RHS represents the fuel-oxygen mass ratio at a given condition
+and the denominator represents the stoichiometric ratio of the same quantity. Hence,
+$\phi$ = 1 at stoichiometric conditions. The equivalence ratio can be altered
+by changing the amount of O$_2$ in the mixture. Essentially, $\phi>1$ corresponds to
+a rich mixture, and $\phi<1$ corresponds to a lean mixture. The above
+reaction~\eqref{eq:global} could thus be generalized as follows:
+
+\be
+2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\min(1,\alpha)\text{H}_2\text{O} + 
+\max(\alpha-1,0)\text{O}_2 + \max(0,2-2\alpha)\text{H}_2
+\label{eq:gen}
+\ee

### 2018-05-24 Paper/app.tex
..

@@
 lean. Consider the global reaction:
-
+%
 \be
-2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2O
+2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
 \label{eq:global}
@@
 \phi = \frac{(M_{\text{H}_2}/M_{\text{O}_2})_\text{obs}}{(M_{\text{H}_2}/M_{\text{O}_2})_\text{st}}
+\label{eq:phi}
 \ee
@@
 $\phi$ = 1 at stoichiometric conditions. The equivalence ratio can be altered
-by changing the amount of O$_2$ in the mixture. Essentially, $\phi>1$ corresponds to
-a rich mixture, and $\phi<1$ corresponds to a lean mixture. The above
-reaction~\eqref{eq:global} could thus be generalized as follows:
-
+by changing the amount of O$_2$ in the mixture. In the case of a lean
+mixture,~\eqref{eq:global} can be written as follows:
+%
+\be
+2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\text{H}_2\text{O} + (\alpha-1)\text{O}_2 
+\hspace{3mm} (\alpha>1)
+\label{eq:lean}
+\ee 
+%
+Similarly, for the case when the mixture if fuel rich,~\eqref{eq:global} is modified
+as follows:
+%
+\be
+2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\alpha\text{H}_2\text{O} + 2(1-\alpha)\text{H}_2
+\hspace{3mm} (\alpha<1)
+\label{eq:rich}
+\ee 
+%
+Eqs.~\eqref{eq:lean} and~\eqref{eq:rich} can be generalized as follows:
+%
 \be
@@
 \ee 
+%
+From the above set of chemical equations, the relationship between $\phi$
+and $\alpha$ can be easily obtained as $\left(\phi~=~\frac{1}{\alpha}\right)$.
+Since $\phi>1$ corresponds to a rich mixture, and $\phi<1$ corresponds to a
+lean mixture, we consider $\phi$ = 2.0 and 0.5 to investigate the two scenarios
+respectively.

### 2018-05-25 Paper/app.tex
..

@@
 lean mixture, we consider $\phi$ = 2.0 and 0.5 to investigate the two scenarios
-respectively.
+respectively. The set of inputs for parameter screening: $\tau_\text{screen}$,
+$s_\text{max}$, $\beta$ are fixed at 0.2, 10, and 1.0 respectively for both cases.
+Additionally, the value of $\tau$ is considered to be 1.0$\times 10^{-17}$ and
+5.0$\times 10^{-17}$ in the rich and lean case respectively.
+
+A full-space surrogate based on the initial set of model evaluations at 5 samples
+did not result in an accurate representation of the input-output relationship. 
+Hence, unlike the test problems presented in section~\ref{sec:examples},we do not
+have converged estimates of the Sobol total-effect index in this case. However,
+the screening procedure in Algorithm~\ref{alg:screen} is implemented to evaluate
+the screening metric for the uncertain pre-exponents ($A_i$'s) as plotted below
+in Figure~\ref{fig:sense_kinetics}~(top row) for both cases. Furthermore, we illustrate
+the decay in the value of $\Delta\mu_s$ with iterations in 
+Figure~\ref{fig:sense_kinetics}~(bottom row).
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_kinetics_rich}
+  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_kinetics_lean}
+  \\ \vspace{2mm}
+  \includegraphics[width=0.48\textwidth]{./Figures/mu_rich}
+  \includegraphics[width=0.48\textwidth]{./Figures/mu_lean}
+\caption{Top: Estimates of $\widehat{\mathcal{C}_i\mu_i}$ for $A_i$'s in the case
+of fuel-rich mixture~(left) and fuel-lean mixture~(right). Bottom: The value of
+$\Delta\mu_s$ during three iterations within the screening step are plotted for
+the case of fuel-rich mixture~(left) and fuel-lean mixture~(right).}
+\label{fig:sense_kinetics}
+\end{center}
+\end{figure}
+%
+The screening metric estimates in the above plots are observed to converge with
+only a few samples (5 -- 10). Moreover, out of the 19 uncertain pre-exponents,
+only $A_1$, $A_9$, $A_{15}$, and $A_{17}$ seem to be important in the fuel-rich
+case, whereas, only $A_1$, $A_9$, and $A_{15}$ seem important in the fuel-lean
+case, based on the value of $\tau_\text{screen}$. These observations are indicative
+of potential for severe reduction in the dimensionality of this problem. A reduced-order
+surrogate, constructed using the proposed framework could thus lead to large computational
+gains. The decay of $\Delta\mu_s$ with iterations is expected and provides a sanity check
+for the screening procedure in both cases.
+
+A reduced-order surrogate (ROS) was constructed in 4D for the fuel-rich case, and in 3D for
+the fuel-lean case. Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the validation
+test suite, the ROS was found to be accurate within 1.8$\%$ in the fuel-rich case, and
+within 3.1$\%$ in the fuel-lean case. Model evaluations at 1000 samples in the test suite
+are further used to plot a normalized histogram of the ignition time in 
+Figure~\ref{fig:pdf_kinetics}. In order to verify the accuracy of the ROS in a 
+probabilistic-sense, we compare the histogram plot with a PDF of ignition time
+using surrogate predictions at 10$^{6}$ samples in the reduced space in both cases. 
+%
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_rich}
+  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_lean}
+\caption{A normalized histogram based on model evaluations at 1000 samples is plotted
+along with a PDF of ignition delay for the fuel-rich case (left) and the fuel-lean
+case (right).}
+\label{fig:pdf_kinetics}
+\end{center}
+\end{figure}
+%
+Clearly, the ROS captures the spread as well as the model estimate of
+the ignition delay in both scenarios. Hence, the proposed framework 
+has enabled severe dimension-reduction and construction of an accurate
+ROS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
+mechanism.

### 2018-05-25 Paper/bg.tex
..

@@
 a generic computational model and only assume that the model
-output depends differentiablly to the parameter $\bm{\theta}$. Thus, 
+output depends differentiably to the parameter $\bm{\theta}$. Thus, 
 we consider finite-difference gradient computation: 

### 2018-05-25 Paper/examples.tex
..

@@
 test problems,
-namely, the borehole function, a non-linear oscillator, and a semilinear elliptic PDE.
+namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
 Since model evaluations in all these test
@@
 its predictive accuracy is higher than the 4D PCE. This illustrates the
-tradeoff between accuracy and computational efficiency for the present 
+trade-off between accuracy and computational efficiency for the present 
 problem. Generally, the required level of accuracy is problem dependent. 
@@
 the reduced order PCEs constructed in 4 and 5 dimensions. A normalized histogram
-plot using model evaluations in the validation test suite is also included.
+plot using 1000 model evaluations in the validation test suite is also included.
 It is evident from this plot, that the PDFs agree quite favorably with each
@@
 PCE using \eqref{eq:l2}, and a validation test suite. The test suite comprised
-model evaluations at 100 independent Monte-Carlo samples in the full 
+model evaluations at 1000 independent Monte-Carlo samples in the full 
 parameter space. The value of $\epsilon_{\mbox{\tiny{L-2}}}$ 
@@
 
-\subsection{Semilinear elliptic PDE with random source term}
+\subsection{Semi-linear elliptic PDE with random source term}
 
-We consider the following semilinear elliptic PDE: 
+We consider the following semi-linear elliptic PDE: 
 \begin{equation}\label{eq:semilinear}
@@
 Once again, we verify the accuracy of the ROS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
-using model evaluations at 100 independent Monte-Carlo samples in the 10D parameter
+using model evaluations at 1000 independent Monte-Carlo samples in the 10D parameter
 space. The ROS was found to be accurate

### 2018-05-25 Paper/intro.tex
..

@@
 model realizations at a given level to be used at higher levels of accuracy as well as sparse grids
-based on Smolyak tensorization~\cite{Smolyak:1963}. Additonally, sparse basis 
+based on Smolyak tensorization~\cite{Smolyak:1963}. Additionally, sparse basis 
 techniques~\cite{Peng:2014,Hampton:2015,Blatman:2011} have been used to reduce  the required

### 2018-05-25 Paper/method.tex
..

@@
 \Require $\tau > 0$, $\tau_\text{screen} > 0$,
-$s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
+$s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
 \Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
@@
 a limiting value $\tau$ of the maximum relative change in the sensitivity
-measure between succesive iterations; (2) 
+measure between successive iterations; (2) 
 a limiting ratio $\tau_\text{screen}$ of the sensitivity metric 
@@
 \node (fss) [process, below of=sam0, text width=14.5em, yshift=-0.5cm] {Construct regression-based 
-surrogate in full-space (FSS) uing ($N_\text{total}$+$n_1$) model evaluations};
+surrogate in full-space (FSS) using ($N_\text{total}$+$n_1$) model evaluations};
 
@@
 
-The available set of model evaluations are utlized and further enhanced during
+The available set of model evaluations are utilized and further enhanced during
 parameter screening as discussed earlier.  At the end of screening, the set of

### 2018-05-26 Paper/app.tex
comments on application problem ...

@@
 in Table~\ref{tab:kinetics}.
+\alennote{Are all these reactions, reversible? The notation $\Longleftrightarrow$ suggests
+that. Also, 
+for reversible reactions, I prefer the notation $\rightleftharpoons$.}
 
@@
 \begin{center}
-\begin{tabular}{ll}
+\begin{tabular}{llll}
 \toprule
-$\mathcal{R}_1$ & H + O$_2$ $\Longleftrightarrow$ O + OH \\
-$\mathcal{R}_2$ & O + H$_2$ $\Longleftrightarrow$ H + OH \\
-$\mathcal{R}_3$ & H$_2$ + OH $\Longleftrightarrow$ H$_2$O + H \\
-$\mathcal{R}_4$ & OH + OH $\Longleftrightarrow$ O + H$_2$O \\
-$\mathcal{R}_5$ & H$_2$ + M $\Longleftrightarrow$ H + H + M \\
-$\mathcal{R}_6$ & O + O + M $\Longleftrightarrow$ O$_2$ + M \\
-$\mathcal{R}_7$ & O + H + M $\Longleftrightarrow$ OH + M \\
-$\mathcal{R}_8$ & H + OH +M $\Longleftrightarrow$ H$_2$O + M \\
-$\mathcal{R}_9$ & H + O$_2$ + M $\Longleftrightarrow$ HO$_2$ + M \\
-$\mathcal{R}_{10}$ & HO$_2$ + H $\Longleftrightarrow$ H$_2$ + O$_2$ \\
-$\mathcal{R}_{11}$ & HO$_2$ + H $\Longleftrightarrow$ OH + OH \\
-$\mathcal{R}_{12}$ & HO$_2$ + O $\Longleftrightarrow$ O$_2$ + OH \\
-$\mathcal{R}_{13}$ & HO$_2$ + OH $\Longleftrightarrow$ H$_2$O + O$_2$ \\
-$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ $\Longleftrightarrow$ H$_2$O$_2$ + O$_2$ \\
-$\mathcal{R}_{15}$ & H$_2$O$_2$ + M $\Longleftrightarrow$ OH + OH + M \\
-$\mathcal{R}_{16}$ & H$_2$O$_2$ + H $\Longleftrightarrow$ H$_2$O + OH \\
-$\mathcal{R}_{17}$ & H$_2$O$_2$ + H $\Longleftrightarrow$ HO$_2$ + H$_2$ \\
-$\mathcal{R}_{18}$ & H$_2$O$_2$ + O $\Longleftrightarrow$ OH + HO$_2$ \\
-$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH $\Longleftrightarrow$ HO$_2$ + H$_2$O \\
+Reaction \#     & Reaction &&\\
+\bottomrule
+$\mathcal{R}_1$ & H + O$_2$          & $\Longleftrightarrow$ & O + OH \\
+$\mathcal{R}_2$ & O + H$_2$          & $\Longleftrightarrow$ & H + OH \\
+$\mathcal{R}_3$ & H$_2$ + OH         & $\Longleftrightarrow$ & H$_2$O + H \\
+$\mathcal{R}_4$ & OH + OH            & $\Longleftrightarrow$ & O + H$_2$O \\
+$\mathcal{R}_5$ & H$_2$ + M          & $\Longleftrightarrow$ & H + H + M \\
+$\mathcal{R}_6$ & O + O + M          & $\Longleftrightarrow$ & O$_2$ + M \\
+$\mathcal{R}_7$ & O + H + M          & $\Longleftrightarrow$ & OH + M \\
+$\mathcal{R}_8$ & H + OH +M          & $\Longleftrightarrow$ & H$_2$O + M \\
+$\mathcal{R}_9$ & H + O$_2$ + M      & $\Longleftrightarrow$ & HO$_2$ + M \\
+$\mathcal{R}_{10}$ & HO$_2$ + H      & $\Longleftrightarrow$ & H$_2$ + O$_2$ \\
+$\mathcal{R}_{11}$ & HO$_2$ + H      & $\Longleftrightarrow$ & OH + OH \\
+$\mathcal{R}_{12}$ & HO$_2$ + O      & $\Longleftrightarrow$ & O$_2$ + OH \\
+$\mathcal{R}_{13}$ & HO$_2$ + OH     & $\Longleftrightarrow$ & H$_2$O + O$_2$ \\
+$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ & $\Longleftrightarrow$ & H$_2$O$_2$ + O$_2$ \\
+$\mathcal{R}_{15}$ & H$_2$O$_2$ + M  & $\Longleftrightarrow$ & OH + OH + M \\
+$\mathcal{R}_{16}$ & H$_2$O$_2$ + H  & $\Longleftrightarrow$ & H$_2$O + OH \\
+$\mathcal{R}_{17}$ & H$_2$O$_2$ + H  & $\Longleftrightarrow$ & HO$_2$ + H$_2$ \\
+$\mathcal{R}_{18}$ & H$_2$O$_2$ + O  & $\Longleftrightarrow$ & OH + HO$_2$ \\
+$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH & $\Longleftrightarrow$ & HO$_2$ + H$_2$O \\
 \bottomrule
@@
 \end{center}
-
-\caption{Reaction mechanism for H$_2$/O$_2$~\cite{Yetter:1991}.}
+\caption{Reaction mechanism for H$_2$/O$_2$ from~\cite{Yetter:1991}}.
 \label{tab:kinetics}
@@
 is given as follows:
-
 \be
-k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT) 
+k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
 \label{eq:rate}
@@
 %
-where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$
-is the activation energy corresponding to the $i^{th}$ reaction, and
-$R$ is the universal gas constant. We focus our attention on 
-quantifying the uncertainty in the `ignition delay' due to uncertainty
-associated with the pre-exponent, $A_i$ for each reaction. Hence, the
-total number of uncertain parameters in the present case is 19. 
+where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
+activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
+universal gas constant. We focus on quantifying the uncertainty in the
+\emph{ignition delay} due to uncertainty associated with the pre-exponent,
+$A_i$ for each reaction. Hence, the total number of uncertain parameters in the
+present case is 19.  The $A_i$'s are considered to be uniformly distributed in
+the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
+estimate corresponding to the $i^{th}$ reaction. TChem~\cite{Safta:2011}, an
+open source C package was used for simulating temperature and concentration
+evolution during the progress of reactions $\mathcal{R}_1$--$\mathcal{R}_{19}$,
+and determining the ignition delay. The set of nominal values used in the
+computations, for parameters in~\eqref{eq:rate} are provided
+in~\cite{Yetter:1991}.
+
 While the dimensionality of the problem is relatively moderate,
-constructing a surrogate in the 19D parameter space could still be
+constructing a surrogate in the 19-dimensional parameter space could still be
 expensive. Hence, we explore the possibility of constructing a
-reduce-order surrogate (ROS) using the framework presented earlier
-in section~\ref{sec:method}. To this end, the $A_i$'s are considered
-to be uniformly distributed in the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$;
-$A_i^\ast$ being the nominal estimate corresponding to the $i^{th}$
-reaction. TChem~\cite{Safta:2011}, an open source C package was used
-for simulating temperature and concentration evolution during the
-progress of reactions ($\mathcal{R}_1$ -- $\mathcal{R}_{19}$), and determining
-the ignition delay. The set of nominal values used in the computations,
-for parameters in~\eqref{eq:rate} are provided in~\cite{Yetter:1991}.
-
-In this study, we focus on two scenarios: fuel(H$_2$) rich, and fuel(H$_2$)
+reduced-order surrogate (ROS) using the framework presented 
+in section~\ref{sec:method}. 
+In the present study, we focus on two scenarios: fuel(H$_2$) rich, and fuel(H$_2$)
 lean. Consider the global reaction:
@@
 %
-The equivalence ratio ($\phi$) is defined as follows:
+The equivalence ratio $\phi$ is defined as follows:
 %
@@
 %
-The numerator in the RHS represents the fuel-oxygen mass ratio at a given condition
+The numerator in the right hand side represents the fuel-oxygen mass ratio at a given condition
+(\alennote{What does the subscript \emph{obs} stand for?}) 
 and the denominator represents the stoichiometric ratio of the same quantity. Hence,
@@
 From the above set of chemical equations, the relationship between $\phi$
-and $\alpha$ can be easily obtained as $\left(\phi~=~\frac{1}{\alpha}\right)$.
+and $\alpha$ can be easily obtained as $\phi~=~\frac{1}{\alpha}$.
 Since $\phi>1$ corresponds to a rich mixture, and $\phi<1$ corresponds to a
 lean mixture, we consider $\phi$ = 2.0 and 0.5 to investigate the two scenarios
-respectively. The set of inputs for parameter screening: $\tau_\text{screen}$,
+respectively.
+
+We apply the parameter screening algorithm with the following
+parameters: $\tau_\text{screen}$,
 $s_\text{max}$, $\beta$ are fixed at 0.2, 10, and 1.0 respectively for both cases.
@@
 5.0$\times 10^{-17}$ in the rich and lean case respectively.
+~\alennote{What is the rationale behind such small numbers? These are smaller
+than the unit round-off.}
 
@@
 did not result in an accurate representation of the input-output relationship. 
+\alennote{This is hardly surprising, five samples in a 19D parameter space
+is going to get us so far; I suggest removing or rewording this statement, 
+as a careful referee will jump on this.}
 Hence, unlike the test problems presented in section~\ref{sec:examples},we do not
-have converged estimates of the Sobol total-effect index in this case. However,
+have converged estimates of the Sobol total-effect index in this case. 
+\alennote{I don't understand; did we not sample the system to death to get 
+total Sobol' indices, or we are saying that's too difficult, and 
+we just use DGSMs and our screening approach?}
+However,
 the screening procedure in Algorithm~\ref{alg:screen} is implemented to evaluate
-the screening metric for the uncertain pre-exponents ($A_i$'s) as plotted below
+the screening metric for the uncertain pre-exponents $A_i$'s as plotted below
 in Figure~\ref{fig:sense_kinetics}~(top row) for both cases. Furthermore, we illustrate
@@
 The screening metric estimates in the above plots are observed to converge with
-only a few samples (5 -- 10). Moreover, out of the 19 uncertain pre-exponents,
+only a few samples (5--10). Moreover, out of the 19 uncertain pre-exponents,
 only $A_1$, $A_9$, $A_{15}$, and $A_{17}$ seem to be important in the fuel-rich
@@
 case, based on the value of $\tau_\text{screen}$. These observations are indicative
-of potential for severe reduction in the dimensionality of this problem. A reduced-order
-surrogate, constructed using the proposed framework could thus lead to large computational
+of potential for significant reduction in the dimensionality of this problem. A reduced-order
+surrogate constructed using the proposed framework could thus lead to large computational
 gains. The decay of $\Delta\mu_s$ with iterations is expected and provides a sanity check
@@
 are further used to plot a normalized histogram of the ignition time in 
-Figure~\ref{fig:pdf_kinetics}. In order to verify the accuracy of the ROS in a 
+Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the ROS in a 
 probabilistic-sense, we compare the histogram plot with a PDF of ignition time
@@
 the ignition delay in both scenarios. Hence, the proposed framework 
-has enabled severe dimension-reduction and construction of an accurate
+has enabled significant dimension-reduction and construction of an accurate
 ROS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction

### 2018-05-26 Paper/disc.tex
..
.

@@
-\section{Discussion}
+\section{Summary and Discussion}
 \label{sec:disc}
@@
 %\item Methodology is agnostic to the choice of surrogate.
+%\item Outcome of parameter screening is QoI dependent. 
 %\item As required for a PCE, the uncertain parameters need not be independent. 
-%\item Strategy depends on the application - methodology could be implemented 
-%sequentially or adaptively. 
+% When working with a computational budget, consider relaxing the tolerance. 
+% Higher the dimension reduction, greater the gains. However, in case of intensive models, even a small reduction could be
+%advantageous. 
+% In general, computational advantage is not guaranteed. Nevertheless, the proposed methodology is promising. 
+% Gains with a reduced order surrogate are multiplied several time when evaluating the posterior distribution of the parameters
+%since several surrogates are needed. 
 %\end{enumerate}
+
+Constructing model surrogates in a large-dimensional setting can be computationally
+challenging especially if the simulations are compute-intensive. In this study, we
+have presented a framework that aims to exploit parametric sensitivity to identify
+\textit{unimportant} parameters in the model. The uncertainty associated with the
+parameters deemed unimportant is disregarded, and the surrogate is constructed in a
+low-dimensional subspace. Conventional approaches on the contrary, use a surrogate
+to perform global sensitivity analysis in order to reduce computational costs. However, 
+constructing a reliable surrogate in high dimensions could still impose a great
+deal of computational burden. The proposed framework strives to tackle this challenge by
+estimating the derivative-based global sensitivity measures, shown to converge to the
+upper bound on Sobol total-effect index with fewer computations.
+
+A screening metric is defined in~\eqref{eq:cmu} for a quantitative assessment of 
+parameter importance. The metric is estimated for a small set of model evaluations
+initially. Subsequent estimates are obtained as the number of evaluations increase
+with each iteration of the screening procedure in Algorithm~\ref{alg:screen}. 
+Once the stopping criterion is met, the metric values are assessed for the
+possibility of dimension reduction. In a favorable scenario of possible dimension
+reduction, a reduced-order surrogate (ROS) is constructed and modified for accuracy. 
+Otherwise, the inputs to the screening procedure are updated as needed and the
+process is repeated. Concurrently, a surrogate in the full space (FSS) is constructed
+each time a new set of model evaluations is available. Both, ROS and FSS are
+constructed using regression-based sparse basis methods. Simultaneous construction
+of the FSS ensures that computational effort associated with the proposed framework
+does not overshoot the effort required to construct a converged FSS directly.
+Hence, the ROS is only constructed in situations where computational gains are
+expected.
+
+The proposed framework was implemented to low-to-moderate dimensional test problems
+and a reliable ROS was constructed in each case. Additionally, potential for large
+computational gains were demonstrated for a relatively higher dimensional application
+involving kinetics of the H$_2$/O$_2$ reaction mechanism. Although PC surrogates were
+used in each case, the frameowork is agnostic to the choice of the surrogate. The scope
+for dimension-reduction and associated computational gains are dependent on the
+application as well as the choice of the quantity of interest that must be differentiable
+with respect to each parameter. Substantial gains are possible in situations 
+involving intensive computations even if the scope for dimension reduction is small. 
+Moreover, exponential gains can be realized with the proposed framework when multiple
+surrogates are to be constructed for investigating the uncertainty in the QoI as 
+illustrated in the kinetics application or inverse problems involving parameter
+estimation in a Bayesian setting.

### 2018-05-26 Paper/app.tex
..

@@
 \bottomrule
-$\mathcal{R}_1$ & H + O$_2$          & $\Longleftrightarrow$ & O + OH \\
-$\mathcal{R}_2$ & O + H$_2$          & $\Longleftrightarrow$ & H + OH \\
-$\mathcal{R}_3$ & H$_2$ + OH         & $\Longleftrightarrow$ & H$_2$O + H \\
-$\mathcal{R}_4$ & OH + OH            & $\Longleftrightarrow$ & O + H$_2$O \\
-$\mathcal{R}_5$ & H$_2$ + M          & $\Longleftrightarrow$ & H + H + M \\
-$\mathcal{R}_6$ & O + O + M          & $\Longleftrightarrow$ & O$_2$ + M \\
-$\mathcal{R}_7$ & O + H + M          & $\Longleftrightarrow$ & OH + M \\
-$\mathcal{R}_8$ & H + OH +M          & $\Longleftrightarrow$ & H$_2$O + M \\
-$\mathcal{R}_9$ & H + O$_2$ + M      & $\Longleftrightarrow$ & HO$_2$ + M \\
-$\mathcal{R}_{10}$ & HO$_2$ + H      & $\Longleftrightarrow$ & H$_2$ + O$_2$ \\
-$\mathcal{R}_{11}$ & HO$_2$ + H      & $\Longleftrightarrow$ & OH + OH \\
-$\mathcal{R}_{12}$ & HO$_2$ + O      & $\Longleftrightarrow$ & O$_2$ + OH \\
-$\mathcal{R}_{13}$ & HO$_2$ + OH     & $\Longleftrightarrow$ & H$_2$O + O$_2$ \\
-$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ & $\Longleftrightarrow$ & H$_2$O$_2$ + O$_2$ \\
-$\mathcal{R}_{15}$ & H$_2$O$_2$ + M  & $\Longleftrightarrow$ & OH + OH + M \\
-$\mathcal{R}_{16}$ & H$_2$O$_2$ + H  & $\Longleftrightarrow$ & H$_2$O + OH \\
-$\mathcal{R}_{17}$ & H$_2$O$_2$ + H  & $\Longleftrightarrow$ & HO$_2$ + H$_2$ \\
-$\mathcal{R}_{18}$ & H$_2$O$_2$ + O  & $\Longleftrightarrow$ & OH + HO$_2$ \\
-$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH & $\Longleftrightarrow$ & HO$_2$ + H$_2$O \\
+$\mathcal{R}_1$ & H + O$_2$          & $\rightleftharpoons$ & O + OH \\
+$\mathcal{R}_2$ & O + H$_2$          & $\rightleftharpoons$ & H + OH \\
+$\mathcal{R}_3$ & H$_2$ + OH         & $\rightleftharpoons$ & H$_2$O + H \\
+$\mathcal{R}_4$ & OH + OH            & $\rightleftharpoons$ & O + H$_2$O \\
+$\mathcal{R}_5$ & H$_2$ + M          & $\rightleftharpoons$ & H + H + M \\
+$\mathcal{R}_6$ & O + O + M          & $\rightleftharpoons$ & O$_2$ + M \\
+$\mathcal{R}_7$ & O + H + M          & $\rightleftharpoons$ & OH + M \\
+$\mathcal{R}_8$ & H + OH +M          & $\rightleftharpoons$ & H$_2$O + M \\
+$\mathcal{R}_9$ & H + O$_2$ + M      & $\rightleftharpoons$ & HO$_2$ + M \\
+$\mathcal{R}_{10}$ & HO$_2$ + H      & $\rightleftharpoons$ & H$_2$ + O$_2$ \\
+$\mathcal{R}_{11}$ & HO$_2$ + H      & $\rightleftharpoons$ & OH + OH \\
+$\mathcal{R}_{12}$ & HO$_2$ + O      & $\rightleftharpoons$ & O$_2$ + OH \\
+$\mathcal{R}_{13}$ & HO$_2$ + OH     & $\rightleftharpoons$ & H$_2$O + O$_2$ \\
+$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ & $\rightleftharpoons$ & H$_2$O$_2$ + O$_2$ \\
+$\mathcal{R}_{15}$ & H$_2$O$_2$ + M  & $\rightleftharpoons$ & OH + OH + M \\
+$\mathcal{R}_{16}$ & H$_2$O$_2$ + H  & $\rightleftharpoons$ & H$_2$O + OH \\
+$\mathcal{R}_{17}$ & H$_2$O$_2$ + H  & $\rightleftharpoons$ & HO$_2$ + H$_2$ \\
+$\mathcal{R}_{18}$ & H$_2$O$_2$ + O  & $\rightleftharpoons$ & OH + HO$_2$ \\
+$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH & $\rightleftharpoons$ & HO$_2$ + H$_2$O \\
 \bottomrule
@@
 %
-The numerator in the right hand side represents the fuel-oxygen mass ratio at a given condition
+The numerator in the right hand side represents the observed (obs) fuel-oxygen mass ratio at a given condition
 (\alennote{What does the subscript \emph{obs} stand for?}) 
-and the denominator represents the stoichiometric ratio of the same quantity. Hence,
+and the denominator represents the stoichiometric (st) ratio of the same quantity. Hence,
 $\phi$ = 1 at stoichiometric conditions. The equivalence ratio can be altered
@@
 %
-Clearly, the ROS captures the spread as well as the model estimate of
+Clearly, the ROS captures the spread as well as the modal estimate of
 the ignition delay in both scenarios. Hence, the proposed framework 

### 2018-05-26 Paper/disc.tex
..

--- 2017-12-19 Paper/disc.tex
@@
-\section{Discussion}
+\section{Summary and Conclusion}
 \label{sec:disc}
@@
 %\item Methodology is agnostic to the choice of surrogate.
+%\item Outcome of parameter screening is QoI dependent. 
 %\item As required for a PCE, the uncertain parameters need not be independent. 
-%\item Strategy depends on the application - methodology could be implemented 
-%sequentially or adaptively. 
+% When working with a computational budget, consider relaxing the tolerance. 
+% Higher the dimension reduction, greater the gains. However, in case of intensive models, even a small reduction could be
+%advantageous. 
+% In general, computational advantage is not guaranteed. Nevertheless, the proposed methodology is promising. 
+% Gains with a reduced order surrogate are multiplied several time when evaluating the posterior distribution of the parameters
+%since several surrogates are needed. 
 %\end{enumerate}
+
+In this work, we have presented a systematic approach for constructed a reduced-order
+surrogate for scientific and engineering applications. dimension reduction is accomplished
+by identifying uncertain parameters that contribute relatively less towards the uncertainty
+in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
+using a screening metric, defined in~\eqref{eq:cmu}. Initially, the metric is estimated
+using model evaluations at a small set of samples in the parameter domain. However, these
+estimates are refined by subsequent enrichment of the sample set during the screening
+procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
+assessed for the scope of dimension reduction. In a favourable scenario, a reduced-order
+surrogate (ROS) is constructed. The ROS is tested for accuracy in a least-squares sense
+as well as a probabilistic sense using a validation test suite. In the proposed framework,
+a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
+the available set of model evaluations. Both, ROS and FSS are
+constructed using regression-based sparse basis methods. Simultaneous construction
+of the FSS ensures that the computational effort associated with the proposed framework
+does not overshoot the effort required to construct the FSS directly.
+Hence, the ROS is constructed only in situations where computational gains are
+expected.
+
+Parameter screening methodology was implemented to low-to-moderate dimensional test problems
+and an accurate ROS was constructed to demonstrate potential for computational gains in
+each case. Furthermore, the overall framework was implemented  to a relatively higher 
+dimensional application involving kinetics of the H$_2$/O$_2$ reaction mechanism. 
+Significant dimension reduction was accomplished for two different scenarios involving
+a fuel-rich and a fuel-lean mixture. In both cases, the resulting ROS was able to capture
+the input-output relationship as well as the uncertainty in the quantity of interest with 
+reasonable accuracy. Additional highlights of the proposed framework are as follows:
+
+\begin{enumerate}
+\item Although Polynomial Chaos surrogates were used in this work, the framework is
+agnostic to the choice of the surrogate. 
+\item The scope for dimension reduction and associated computational gains are
+dependent upon the application as well as the quantity of interest. 
+\item The quantity of interest must be differentiable with respect to each uncertain parameter
+to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
+\item Substantial computational gains are expected in situations involving compute-intensive
+simulations even if the scope for dimension reduction is small. Hence, careful judgment 
+is required when implementing the framework. 
+\item Exponential gains can be realized in situations where multiple surrogates need to be
+constructed as illustrated in the kinetics application. Other possible scenarios include
+include inverse problems involving parameter estimation in a Bayesian setting. 
+\end{enumerate}
+
+%Although PC surrogates were
+%used in each case, the frameowork is agnostic to the choice of the surrogate. The scope
+%for dimension-reduction and associated computational gains are dependent on the
+%application as well as the choice of the quantity of interest that must be differentiable
+%with respect to each parameter. Substantial gains are possible in situations 
+%involving intensive computations even if the scope for dimension reduction is small. 
+%Moreover, exponential gains can be realized with the proposed framework when multiple
+%surrogates are to be constructed for investigating the uncertainty in the QoI as 
+%illustrated in the kinetics application or inverse problems involving parameter
+%estimation in a Bayesian setting.

### 2018-05-26 Paper/examples.tex
..

@@
 was used to solve the resulting nonlinear system on a (100$\times$100) 2D
-cartesian grid.~\alennote{Give the
-number of degrees of freedom.} 
+cartesian grid.
 We computed converged estimates of the Sobol

### 2018-05-26 Paper/app.tex
...

@@
 in Table~\ref{tab:kinetics}.
-\alennote{Are all these reactions, reversible? The notation $\Longleftrightarrow$ suggests
-that. Also, 
-for reversible reactions, I prefer the notation $\rightleftharpoons$.}
 
@@
 %
-The numerator in the right hand side represents the observed (obs) fuel-oxygen mass ratio at a given condition
-(\alennote{What does the subscript \emph{obs} stand for?}) 
-and the denominator represents the stoichiometric (st) ratio of the same quantity. Hence,
-$\phi$ = 1 at stoichiometric conditions. The equivalence ratio can be altered
-by changing the amount of O$_2$ in the mixture. In the case of a lean
+The numerator in the right hand side represents the observed (obs) fuel-oxygen
+mass ratio at a given condition and the denominator represents the
+stoichiometric (st) ratio of the same quantity. Hence, $\phi$ = 1 at
+stoichiometric conditions. The equivalence ratio can be altered by changing the
+amount of O$_2$ in the mixture. In the case of a lean
 mixture,~\eqref{eq:global} can be written as follows:

### 2018-05-26 Paper/ack.tex
..

\section*{Acknowledgement}

M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
National Science Foundation (Grant No. 1404823, CDSE Program). M. Vohra
would also like to sincerely thank Dr. Xun Huan at Sandia National Labs for
his guidance pertaining to the usage of TChem for the chemical kinetics application
in this work.

### 2018-05-26 Paper/intro.tex
intro, first pass ...

--- 2018-05-08 Paper/intro.tex
@@
 
-%\begin{enumerate}
-%\item Need for efficient Surrogates - especially for complex models to enable forward UQ, 
-%sensitivity studies, calibration, and experimental design (Include citations).
-%\item Computational Hurdles: Polynomial Chaos and GP can be computationally 
-%intractable and suffer from the curse of dimensionality (Include plots for PCE
-%to motivate dimension reduction with citations for both PCE and GP).
-%\item Sensitivity analyis - a potent tool for dimension reduction. However, SA can be
-%computationally prohibitive. In fact, there are studies demonstrating the use of 
-%surrogates to reduce costs associated with SA (include citations). 
-%\item DGSM - brief introduction and citations. 
-%\item Key contributions of the paper: 1) Methodology that exploits DGSM to reduce the
-%dimensionality of the problem and thus enables efficient construction of surrogates.
-%2) Application of the proposed methodology to investigate relative importance of
-%parameters in the stillinger-weber potential, commonly used for studying phonon transport in silicon. Further, construct a reasonably accurate PC surrogate in the reduced 
-%space and demonstrate computational advantage of this approach. .
-%\end{enumerate}
-
 The emerging field of uncertainty quantification (UQ) aims at methodologies for
 incorporating, characterizing, quantifying, propagating, and reducing the
-uncertainties associated with predictive models and simulations. For situations
-involving complex physical models and compute-intensive simulations, an
-efficient approach to construction of model surrogates is sought to enable UQ
-in a tractable manner. Polynomial chaos expansion 
-(PCE)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010} and 
-Gaussian Process (GP)~\cite{Rasmussen:2004} or Kriging~\cite{Stein:2012} are
-among the most commonly used surrogates for scientific applications. However,
-both approaches quickly become prohibitive when the set of uncertain model
-inputs and parameters is large-dimensional. Specifically, in the case of a PCE,
-a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
-requires model realizations at $(p+1)^d$ quadrature nodes to exactly determine the PC
-coefficients using a fully-tensorized Gauss quadrature. Consider a case where $d$ = 8 which
-could be a regarded as a low-dimensional problem, and $p$ = 5, requires model evaluations at
-roughly 1.7 million quadrature nodes. However, the degree of exactness in numerical estimation 
-of the coefficients as made possible with a fully-tensored quadrature might not be desired. In that
-case, computational effort can be reduced considerably by using nested
-quadratures~\cite{Gentleman:1972a,Gentleman:1972b,Novak:1999,Waldvogel:2006} which allow 
-model realizations at a given level to be used at higher levels of accuracy as well as sparse grids
-based on Smolyak tensorization~\cite{Smolyak:1963}. Additonally, sparse basis 
-techniques~\cite{Peng:2014,Hampton:2015,Blatman:2011} have been used to reduce  the required
-computational effort for constructing a reasonably accurate PC surrogate.
+uncertainties associated with predictive models and simulations.  For
+situations involving complex physical models and computationally intensive
+simulations surrogate modeling often provides orders of magnitude speedups in
+statistical studies. This is done by replacing repeated evaluations of
+computationally expensive models by inexpensive evaluations of a surrogate
+model.  Thus, an efficient approach to construction of surrogate models is of
+central importance in enabling efficient uncertainty quantification for
+computationally intensive models.
 
-One of the primary objectives for constructing a model surrogate is to be able to perform 
-parametric sensitivity analysis tractably. Sensitivity analysis provides an insight into the
-relative contributions of the uncertain model parameters and inputs to the uncertainty in
-predictions. The analysis could potentially reduce the dimensionality of the problem.
-However, as discussed earlier, constructing the surrogate might still require a large amount
-of computational resources. It can thus be understood that dimension reduction prior to
-constructing the surrogate might lead to enormous computational savings. In this work,
-we present a strategy for identifying and screening uncertain model parameters that 
-are significantly less important that the rest, thereby reducing the dimensionality of the
-problem and enabling the construction of a reduced-order surrogate (ROS). As discussed in
-section~\ref{sec:method}, parameter ranks are determined using a \textit{screening-metric}
-based on derivative-based global sensitivity 
-measures~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016}. 
-The strategy is agnostic to the choice of methodology for constructing the surrogate. However, 
-we will be using PCE to demonstrate the suitability of the proposed strategy. Below, in 
-section~\ref{sec:bg}, we provide a brief introduction to derivative-based global sensitivity analysis
-in the present context as well as the polynomial chaos methodology. Later, in section~\ref{sec:examples},
-we motivate the proposed strategy by implementing it to a suite of simple applications, namely, the 
-classic borehole function, a non-linear oscillator, and a semi-linear elliptic PDE. Finally, we demonstrate
-suitability of our approach by using it to reduce the dimensionality of a H$_2$/O$_2$ kinetics problem
-involving 19 reactions in section~\ref{sec:app}.
+Commonly used surrogate modeling approaches use polynomial chaos expansions
+(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
+regression splines (MARS)~\cite{friedman93}, Gaussian processes
+(GPs)~\cite{Rasmussen:2004}, or kriging~\cite{Stein:2012}.  Many real-world
+applications involve a large number of uncertain parameters. This makes
+construction of surrogate models difficult or impossible in some cases.
+However, in many situations, the variability in model observables of interest
+is sensitive to only a small subset of the uncertain inputs.  Hence,
+identifying model inputs that are inessential to variability in model output is
+a key step that can facilitate surrogate model construction.
+
+%However, both approaches
+%quickly become prohibitive when the set of uncertain model inputs and
+%parameters is large-dimensional. Specifically, in the case of a PCE, a
+%$d$-dimensional polynomial basis with a total order of truncation, $p$ requires
+%model realizations at $(p+1)^d$ quadrature nodes to exactly determine the PC
+%coefficients using a fully-tensorized Gauss quadrature. Consider a case where
+%$d$ = 8 which could be a regarded as a low-dimensional problem, and $p$ = 5,
+%requires model evaluations at roughly 1.7 million quadrature nodes. However,
+%the degree of exactness in numerical estimation of the coefficients as made
+%%possible with a fully-tensored quadrature might not be desired. In that case,
+%computational effort can be reduced considerably by using nested
+%quadratures~\cite{Gentleman:1972a,Gentleman:1972b,Novak:1999,Waldvogel:2006}
+%%which allow model realizations at a given level to be used at higher levels of
+%accuracy as well as sparse grids based on Smolyak
+%tensorization~\cite{Smolyak:1963}. Additionally, sparse basis
+%techniques~\cite{Peng:2014,Hampton:2015,Blatman:2011} have been used to reduce
+%the required computational effort for constructing a reasonably accurate PC
+%surrogate.
+
+%One of the primary objectives for constructing a model surrogate is to be able
+%to perform parametric sensitivity analysis tractably.
+
+Variance based global sensitivity analysis based on Sobol indices~\cite{Sobol93,
+Sobol:2001,
+Owen13,
+SaltelliRattoAndresEtAl08} provides
+insight into the relative contributions of the uncertain model inputs to the
+uncertainty in predictions. Specifically, such analysis can help reduce the
+dimensionality of the problem.  Computing Sobol indices, however, is a
+computationally challenging task.  
+Availability of a surrogate model typically
+enables efficient computation 
+of Sobol indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
+on a wide range of applications including in ocean 
+modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
+geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
+and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global}, to name a few.
+
+While surrogate models provide an efficient way of computing sensitivity
+indices, constructing them in the case of models with high-dimensional inputs
+can be as expensive as computing the Sobol indices via sampling.  Hence,
+dimension reduction prior surrogate model construction can lead to enormous
+computational savings.  Derivative based global sensitivity
+analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016}
+often lead to a more tractable approach for global sensitivity
+analysis~\cite{Kucherenko:2016}.  Also, the links between derivative based
+global sensitivity measures (DGSMs) and total Sobol
+indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
+basis for their use in identifying unimportant parameters.
+
+%However, as discussed
+%earlier, constructing the surrogate might still require a large amount of
+%computational resources.
+
+\paragraph{Our approach}
+We present a strategy for identifying and screening uncertain model parameters
+that are significantly less important that the rest, thereby reducing the
+dimensionality of the problem and enabling the construction of a reduced-order
+surrogate (ROS).  Our approach combines DGSMs and surrogate modeling in an
+iterative manner.  To make maximum use of computational resources, batches of
+model evaluations are performed iteratively, and convergence of our DGSM based
+screening metric is tested successively. Moreover, the validation steps built
+in our method enable monitoring the accuracy of the parameter-screening and the
+constructed surrogate model.  Our approach is agnostic to the choice of
+methodology for constructing the surrogate. However, in the present work, we
+rely on sparse PCEs to demonstrate the suitability of the proposed strategy.
+
+%Moreover, the availability of adjoint solvers for
+%efficient gradient computation can enhance the performance of our approach.
+
+\paragraph{Contributions}
+The contributions of this article are as follows: (i) we establish a robust and
+practical framework for dimension reduction and surrogate modeling.  Our
+approach is general in that it is applicable to a wide range of applications.
+(ii) We present comprehensive numerical results demonstrating the viability of
+our strategy in a number of motivating applications: the classic borehole
+function, a nonlinear oscillator, and a semilinear elliptic PDE.  (iii) We
+deploy our strategy in a application problem from chemical kinetics with 19
+uncertain parameters. The application problem is studied in multiple regimes.
+It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
+or 4-dimensional parameter problem.
+
+\paragraph{Paper outline}
+This article is structured as follows. In section~\ref{sec:bg}, we provide a
+brief introduction to DGSMs as well as the polynomial chaos methodology used in
+the present work.  In Section~\ref{sec:method} we present our proposed
+approach. There we also provide a detailed numerical algorithm and a flow
+diagram to aid practitioners in implementing the presented framework.
+Section~\ref{sec:examples} is devoted to a number of numerical examples
+examining various aspects of our approach. This is followed by implementation
+of our framework in an H$_2$/O$_2$ chemical kinetics, in section~\ref{sec:app}.
+Finally, concluding remarks are provided in section~\ref{sec:disc}.
 

### 2018-05-26 Paper/app.tex

@@
 We apply the parameter screening algorithm with the following
-parameters: $\tau_\text{screen}$,
-$s_\text{max}$, $\beta$ are fixed at 0.2, 10, and 1.0 respectively for both cases.
+parameters: $\tau_\text{screen}$, $s_\text{min}$,
+$s_\text{max}$, $\beta$ are fixed at 0.2, 3, 10, and 1.0 respectively for both cases.
 Additionally, the value of $\tau$ is considered to be 1.0$\times 10^{-17}$ and
-5.0$\times 10^{-17}$ in the rich and lean case respectively.
-~\alennote{What is the rationale behind such small numbers? These are smaller
-than the unit round-off.}
+5.0$\times 10^{-17}$ in the rich and lean case respectively. Such a small value
+of $\tau$ for this application is a consequence of the nature of convergence exhibited
+by the sensitivity measures. Moreover, the screening procedure is carried out
+for atleast $s_\text{min}$ number of iterations in order to bolster our confidence
+in the estimates.
 
-A full-space surrogate based on the initial set of model evaluations at 5 samples
-did not result in an accurate representation of the input-output relationship. 
-\alennote{This is hardly surprising, five samples in a 19D parameter space
-is going to get us so far; I suggest removing or rewording this statement, 
-as a careful referee will jump on this.}
-Hence, unlike the test problems presented in section~\ref{sec:examples},we do not
-have converged estimates of the Sobol total-effect index in this case. 
-\alennote{I don't understand; did we not sample the system to death to get 
-total Sobol' indices, or we are saying that's too difficult, and 
-we just use DGSMs and our screening approach?}
-However,
-the screening procedure in Algorithm~\ref{alg:screen} is implemented to evaluate
-the screening metric for the uncertain pre-exponents $A_i$'s as plotted below
+Following the steps outlined in the flow-diagram in Figure~\ref{fig:flow}, model
+evaluations are initially generated at $n_1$ = 5 samples. The evaluations are
+used to construct a regression-based surrogate in the full-space. As
+expected, the surrogate is found to be highly inaccurate. Moreover, unlike the
+test problems in section~\ref{sec:examples}, we do not estimate the Sobol
+total-effect sensitivity indices in the interest of following the overall framework
+closely. Hence, we proceed to the screening step to estimate the screening metric
+for the uncertain pre-exponents, $A_i$'s. Results are plotted below
 in Figure~\ref{fig:sense_kinetics}~(top row) for both cases. Furthermore, we illustrate

### 2018-05-26 Paper/disc.tex
..

@@
 
-In this work, we have presented a systematic approach for constructed a reduced-order
-surrogate for scientific and engineering applications. dimension reduction is accomplished
+In this work, we have presented a systematic approach for constructing a reduced-order
+surrogate for scientific and engineering applications. Dimension reduction is accomplished
 by identifying uncertain parameters that contribute relatively less towards the uncertainty
@@
 the input-output relationship as well as the uncertainty in the quantity of interest with 
-reasonable accuracy. Additional highlights of the proposed framework are as follows:
+reasonable accuracy. Additional highlights and limitations of the proposed framework are as follows:
 
 \begin{enumerate}
-\item Although Polynomial Chaos surrogates were used in this work, the framework is
-agnostic to the choice of the surrogate. 
+\item The proposed framework is agnostic to the choice of the surrogate although PCE's were used
+in this work. 
 \item The scope for dimension reduction and associated computational gains are
@@
 \item Substantial computational gains are expected in situations involving compute-intensive
-simulations even if the scope for dimension reduction is small. Hence, careful judgment 
+simulations even if the scope for dimension reduction is small and vice versa. Hence, careful judgment 
 is required when implementing the framework. 
 \item Exponential gains can be realized in situations where multiple surrogates need to be
-constructed as illustrated in the kinetics application. Other possible scenarios include
+constructed as illustrated in the kinetics application. Other possible scenarios 
 include inverse problems involving parameter estimation in a Bayesian setting. 

### 2018-05-26 Paper/disc.tex
...

@@
 reasonable accuracy. Additional highlights and limitations of the proposed framework are as follows:
-
+\alennote{This is unclear: if we list limitations, we should be specific and
+not mix them with highlights;
+as for limitations, we can mention 
+e.g., we do not account for correlations, and our method applies only to 
+models with differentiable dependence on parameters, etc.; I would not make
+a bulleted list; I would briefly discuss the limitations, and if possible turn 
+them into strengths! e.g., we consider uncorrelated parameters, but that's okay as in 
+many cases correlations are not well understood and assuming independence is reasonable, etc.}
 \begin{enumerate}
@@
 \item The quantity of interest must be differentiable with respect to each uncertain parameter
-to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
+for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
+%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
 \item Substantial computational gains are expected in situations involving compute-intensive

### 2018-05-27 Paper/method.tex
..
minor ...

@@
   \begin{algorithmic}[1]
-\Require $\tau > 0$, $\tau_\text{screen} > 0$,
+\Require $\tau > 0$, $\tau_\text{screen} > 0$, $s_\text{min} \geq 1$,
 $s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
@@
 Another possible approach, suitable in certain cases, is the use of
-adjoint-based gradient computation. In such cases, each gradient computation,
-which is more efficient than finite-differences---each gradient
-evaluation requires a forward model solve and adjoint solve---but 
-requires the availability of adjoint solvers.
-\alennote{I will put some references there ...}
+adjoint-based gradient computation. In particular, for PDE-based
+problems with scalar QoIs, but high-dimensional uncertain parameters, 
+adjoint-based gradient computation is much more efficient than finite-differences.
+In the adjoint approach, each gradient evaluation requires 
+a solution of the state equation (forward solve) and that of the 
+corresponding adjoint equation; 
+see e.g.,~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011}.
+The adjoint method, however, requires the availability of an adjoint solver.
 

### 2018-05-28 Paper/disc.tex
..

--- 2018-05-26 Paper/disc.tex
@@
 the input-output relationship as well as the uncertainty in the quantity of interest with 
-reasonable accuracy. Additional highlights and limitations of the proposed framework are as follows:
-
+reasonable accuracy. Additional highlights of the proposed framework are as follows:
+%\alennote{This is unclear: if we list limitations, we should be specific and
+%not mix them with highlights;
+%as for limitations, we can mention 
+%e.g., we do not account for correlations, and our method applies only to 
+%models with differentiable dependence on parameters, etc.; I would not make
+%a bulleted list; I would briefly discuss the limitations, and if possible turn 
+%them into strengths! e.g., we consider uncorrelated parameters, but that's okay as in 
+%many cases correlations are not well understood and assuming independence is reasonable, etc.}
 \begin{enumerate}
@@
 dependent upon the application as well as the quantity of interest. 
-\item The quantity of interest must be differentiable with respect to each uncertain parameter
-to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
+%\item The quantity of interest must be differentiable with respect to each uncertain parameter
+%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
+%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
 \item Substantial computational gains are expected in situations involving compute-intensive
-simulations even if the scope for dimension reduction is small and vice versa. Hence, careful judgment 
-is required when implementing the framework. 
+simulations even if the scope for dimension reduction is small. 
+%Hence, careful judgment 
+%pertaining to the construction of a reduced-order surrogate as well as resource allocation is needed. is required when implementing the framework. 
 \item Exponential gains can be realized in situations where multiple surrogates need to be
-constructed as illustrated in the kinetics application. Other possible scenarios 
+constructed as illustrated in the kinetics application. Other possible scenarios may
 include inverse problems involving parameter estimation in a Bayesian setting. 
@@
 
-%Although PC surrogates were
-%used in each case, the frameowork is agnostic to the choice of the surrogate. The scope
-%for dimension-reduction and associated computational gains are dependent on the
-%application as well as the choice of the quantity of interest that must be differentiable
-%with respect to each parameter. Substantial gains are possible in situations 
-%involving intensive computations even if the scope for dimension reduction is small. 
-%Moreover, exponential gains can be realized with the proposed framework when multiple
-%surrogates are to be constructed for investigating the uncertainty in the QoI as 
-%illustrated in the kinetics application or inverse problems involving parameter
-%estimation in a Bayesian setting.
+Based on the results presented for a variety of test problems, 
+and a higher-dimensional chemical kinetics application in this work, it can be said that the
+proposed framework seems quite promising in its potential for identifying favourable
+scenarios for constructing a reduced-order surrogate in a computationally efficient manner. 
+However, it is important to remain cognizant about the underlying limitations of the
+framework. For instance, it does not account for the existence of possible correlation 
+between the uncertain parameters of the model, although in many cases, correlations
+between parameters are not well understood, and assuming mutual independence 
+would be reasonable. Similarly, the quantity of interest is required to be differentiable
+with respect to each parameter in the considered domain. This condition, however, must
+anyways be satisfied for the resulting surrogate to be able to represent the input-output
+relationship for a given model with reasonable accuracy. Finally, careful assessment 
+and decision-making is required with regards to proceeding with the
+construction of a reduced-order surrogate based on the outcome of parameter
+screening, and accuracy of the most-recent full-space surrogate as well as 
+allocation of computational resources for parameter screening, and constructing the
+validation test suite. Implementation to more advanced
+applications in the future would enable further development of the proposed framework.

### 2018-05-28 Paper/disc.tex
..

@@
 procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
-assessed for the scope of dimension reduction. In a favourable scenario, a reduced-order
+assessed for the scope of dimension reduction. In a favorable scenario, a reduced-order
 surrogate (ROS) is constructed. The ROS is tested for accuracy in a least-squares sense
@@
 and a higher-dimensional chemical kinetics application in this work, it can be said that the
-proposed framework seems quite promising in its potential for identifying favourable
+proposed framework seems quite promising in its potential for identifying favorable
 scenarios for constructing a reduced-order surrogate in a computationally efficient manner. 

### 2018-05-28 Paper/examples.tex
..

@@
 
-\subsection{Semi-linear elliptic PDE with random source term}
+\subsection{Semilinear elliptic PDE with random source term}
 
-We consider the following semi-linear elliptic PDE: 
+We consider the following semilinear elliptic PDE: 
 \begin{equation}\label{eq:semilinear}

### 2018-05-28 Paper/intro.tex
..

@@
 We present a strategy for identifying and screening uncertain model parameters
-that are significantly less important that the rest, thereby reducing the
+that are significantly less important than the rest, thereby reducing the
 dimensionality of the problem and enabling the construction of a reduced-order

### 2018-05-28 Paper/disc.tex
minor ...

@@
 
-Parameter screening methodology was implemented to low-to-moderate dimensional test problems
-and an accurate ROS was constructed to demonstrate potential for computational gains in
-each case. Furthermore, the overall framework was implemented  to a relatively higher 
-dimensional application involving kinetics of the H$_2$/O$_2$ reaction mechanism. 
-Significant dimension reduction was accomplished for two different scenarios involving
-a fuel-rich and a fuel-lean mixture. In both cases, the resulting ROS was able to capture
-the input-output relationship as well as the uncertainty in the quantity of interest with 
-reasonable accuracy. Additional highlights of the proposed framework are as follows:
-%\alennote{This is unclear: if we list limitations, we should be specific and
-%not mix them with highlights;
-%as for limitations, we can mention 
-%e.g., we do not account for correlations, and our method applies only to 
-%models with differentiable dependence on parameters, etc.; I would not make
-%a bulleted list; I would briefly discuss the limitations, and if possible turn 
-%them into strengths! e.g., we consider uncorrelated parameters, but that's okay as in 
-%many cases correlations are not well understood and assuming independence is reasonable, etc.}
+Parameter screening methodology was implemented to low-to-moderate dimensional
+test problems and an accurate ROS was constructed to demonstrate potential for
+computational gains in each case. Furthermore, the overall framework was
+implemented  to a relatively higher dimensional application involving kinetics
+of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction was
+accomplished for two different scenarios involving a fuel-rich and a fuel-lean
+mixture. In both cases, the resulting ROS was able to capture the input-output
+relationship as well as the uncertainty in the quantity of interest with
+reasonable accuracy. Additional highlights of the proposed framework are as
+follows:
 \begin{enumerate}
@@
 %to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
-\item Substantial computational gains are expected in situations involving compute-intensive
-simulations even if the scope for dimension reduction is small. 
-%Hence, careful judgment 
-%pertaining to the construction of a reduced-order surrogate as well as resource allocation is needed. is required when implementing the framework. 
+\item Substantial computational gains are expected in situations involving
+compute-intensive simulations even if the scope for dimension reduction is
+small. 
+%Hence, careful judgment pertaining to the construction of a reduced-order
+%surrogate as well as resource allocation is needed. is required when
+%implementing the framework.
+
 \item Exponential gains can be realized in situations where multiple surrogates need to be
@@
 
-Based on the results presented for a variety of test problems, 
-and a higher-dimensional chemical kinetics application in this work, it can be said that the
-proposed framework seems quite promising in its potential for identifying favorable
-scenarios for constructing a reduced-order surrogate in a computationally efficient manner. 
-However, it is important to remain cognizant about the underlying limitations of the
-framework. For instance, it does not account for the existence of possible correlation 
-between the uncertain parameters of the model, although in many cases, correlations
-between parameters are not well understood, and assuming mutual independence 
-would be reasonable. Similarly, the quantity of interest is required to be differentiable
-with respect to each parameter in the considered domain. This condition, however, must
-anyways be satisfied for the resulting surrogate to be able to represent the input-output
-relationship for a given model with reasonable accuracy. Finally, careful assessment 
-and decision-making is required with regards to proceeding with the
-construction of a reduced-order surrogate based on the outcome of parameter
-screening, and accuracy of the most-recent full-space surrogate as well as 
-allocation of computational resources for parameter screening, and constructing the
-validation test suite. Implementation to more advanced
-applications in the future would enable further development of the proposed framework.
+Based on the results presented for a variety of test problems, and a
+higher-dimensional chemical kinetics application in this work, it can be said
+that the proposed framework seems quite promising in its potential for
+identifying favorable scenarios for constructing a reduced-order surrogate in a
+computationally efficient manner.  However, it is important to remain cognizant
+about the limitations of the framework as well. For instance, it does not
+account for the existence of possible correlations between the uncertain
+parameters of the model. However, while the assumption of independent
+parameters is not always justified, in many cases, correlations between
+parameters are not well understood a priori, and assuming mutual independence
+could be reasonable at least in an initial screening stage using DGSMs.
+Additionally, the quantity of interest is required to be differentiable with
+respect to each parameter in the considered domain. This condition, however,
+must anyways be satisfied for the resulting surrogate to be able to represent
+the input-output relationship for a given model with reasonable accuracy.
+Finally, careful assessment and decision-making is required with regards to
+proceeding with the construction of a reduced-order surrogate based on the
+outcome of parameter screening, and accuracy of the most-recent full-space
+surrogate as well as allocation of computational resources for parameter
+screening, and constructing the validation test suite. Implementation to more
+advanced applications in the future would enable further development of the
+proposed framework.

### 2018-05-28 Paper/disc.tex
minor ...

@@
 parameters are not well understood a priori, and assuming mutual independence
-could be reasonable at least in an initial screening stage using DGSMs.
+could be reasonable at least in initial screening using DGSMs.
 Additionally, the quantity of interest is required to be differentiable with

### 2018-06-10 Paper/app.tex
..

@@
 expensive. Hence, we explore the possibility of constructing a
-reduced-order surrogate (ROS) using the framework presented 
+reduced-space surrogate (RSS) using the framework presented 
 in section~\ref{sec:method}. 
-In the present study, we focus on two scenarios: fuel(H$_2$) rich, and fuel(H$_2$)
-lean. Consider the global reaction:
+In the present study, we focus on two scenarios: fuel(H$_2$)-rich, and
+fuel(H$_2$)-lean. Consider the global reaction:
 %
@@
 %
-The numerator in the right hand side represents the observed (obs) fuel-oxygen
+The numerator in the right-hand-side represents the observed (obs) fuel-oxygen
 mass ratio at a given condition and the denominator represents the
@@
 case, based on the value of $\tau_\text{screen}$. These observations are indicative
-of potential for significant reduction in the dimensionality of this problem. A reduced-order
+of the potential for significant reduction in the dimensionality of this problem. 
+A reduced-space
 surrogate constructed using the proposed framework could thus lead to large computational
-gains. The decay of $\Delta\mu_s$ with iterations is expected and provides a sanity check
-for the screening procedure in both cases.
+gains. The decay of $\Delta\mu_s$ with iterations is expected and builds our confidence
+in the screening procedure in both cases.
 
-A reduced-order surrogate (ROS) was constructed in 4D for the fuel-rich case, and in 3D for
-the fuel-lean case. Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the validation
-test suite, the ROS was found to be accurate within 1.8$\%$ in the fuel-rich case, and
+A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
+and in 3D for
+the fuel-lean case. Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the 
+cross-validation set, the RSS was found to be accurate within 1.8$\%$ in the
+fuel-rich case, and
 within 3.1$\%$ in the fuel-lean case. Model evaluations at 1000 samples in the test suite
 are further used to plot a normalized histogram of the ignition time in 
-Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the ROS in a 
+Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the RSS in a 
 probabilistic-sense, we compare the histogram plot with a PDF of ignition time
@@
 %
-Clearly, the ROS captures the spread as well as the modal estimate of
+Clearly, the RSS captures the spread as well as the modal estimate of
 the ignition delay in both scenarios. Hence, the proposed framework 
-has enabled significant dimension-reduction and construction of an accurate
-ROS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
+has enabled significant dimension reduction and construction of an accurate
+RSS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
 mechanism.

### 2018-06-10 Paper/bg.tex
..

@@
 Let $\GG$ be a mathematical model that is a function of $\Np$ uncertain 
-parameters, $\theta_1, \theta_2, \ldots, \theta_\Np$. The goal of sensitivity analysis
-is measuring the influence of each component of the parameter vector 
+inputs, $\theta_1, \theta_2, \ldots, \theta_\Np$. The goal of sensitivity analysis
+is measuring the influence of each component of the input vector 
 $\bm{\theta}$ on the model output. 
-In the present work, we consider the case where the input parameters are statistically 
+In the present work, we consider the case where the inputs are statistically 
 independent.
@@
 Notice that this formulation assumes that the function $\GG$ is differentiable
-with respect to $\theta_i$, $i = 1, \ldots, \Np$, almost surely.
+with respect to $\theta_i$, $i = 1, \ldots, \Np$, almost surely~\manavnote {What do
+we mean by ``almost surely"}.
 
 If an analytic expression for $\GG$ is available the derivative in the above
-expression can be computed directly. In applications, however, $\GG$ is often
+expression can be computed directly. In many applications, however, $\GG$ is often
 defined in terms of a solution of a mathematical model. In some cases, 
@@
 a generic computational model and only assume that the model
-output depends differentiably to the parameter $\bm{\theta}$. Thus, 
+output depends differentiably on the parameter $\bm{\theta}$. Thus, 
 we consider finite-difference gradient computation: 

### 2018-06-10 Paper/disc.tex
..

@@
 
-In this work, we have presented a systematic approach for constructing a reduced-order
+In this work, we have presented a systematic approach for constructing a reduced-space
 surrogate for scientific and engineering applications. Dimension reduction is accomplished
@@
 in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
-using a screening metric, defined in~\eqref{eq:cmu}. Initially, the metric is estimated
+using a screening metric~(\eqref{eq:cmu}) involving derivative-based sensitivity
+measures. Initially, the metric is estimated
 using model evaluations at a small set of samples in the parameter domain. However, these
@@
 procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
-assessed for the scope of dimension reduction. In a favorable scenario, a reduced-order
-surrogate (ROS) is constructed. The ROS is tested for accuracy in a least-squares sense
+assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
+surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
 as well as a probabilistic sense using a validation test suite. In the proposed framework,
 a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
-the available set of model evaluations. Both, ROS and FSS are
+the available set of model evaluations. Both, RSS and FSS are
 constructed using regression-based sparse basis methods. Simultaneous construction
@@
 does not overshoot the effort required to construct the FSS directly.
-Hence, the ROS is constructed only in situations where computational gains are
+Hence, the RSS is constructed only in situations where computational gains are
 expected.
@@
 Parameter screening methodology was implemented to low-to-moderate dimensional
-test problems and an accurate ROS was constructed to demonstrate potential for
+test problems and an accurate RSS was constructed to demonstrate potential for
 computational gains in each case. Furthermore, the overall framework was
@@
 accomplished for two different scenarios involving a fuel-rich and a fuel-lean
-mixture. In both cases, the resulting ROS was able to capture the input-output
+mixture. In both cases, the resulting RSS was able to capture the input-output
 relationship as well as the uncertainty in the quantity of interest with
@@
 that the proposed framework seems quite promising in its potential for
-identifying favorable scenarios for constructing a reduced-order surrogate in a
+identifying favorable scenarios for constructing a reduced-space surrogate in a
 computationally efficient manner.  However, it is important to remain cognizant
@@
 account for the existence of possible correlations between the uncertain
-parameters of the model. However, while the assumption of independent
-parameters is not always justified, in many cases, correlations between
-parameters are not well understood a priori, and assuming mutual independence
-could be reasonable at least in initial screening using DGSMs.
+inputs of the model. However, while the assumption of independent
+inputs is not always justified, in many cases, correlations between
+inputs are not well understood a priori, and assuming mutual independence
+could be reasonable at least in initial screening using DGSMs. On the other
+hand, if approximate correlations are known, the PCE could still be 
+constructed using samples from the correlated space or preferably,
+the input-output relationship could be represented using a Gaussian process
+that provides a means for incorporating the correlation between inputs.  
 Additionally, the quantity of interest is required to be differentiable with
@@
 Finally, careful assessment and decision-making is required with regards to
-proceeding with the construction of a reduced-order surrogate based on the
-outcome of parameter screening, and accuracy of the most-recent full-space
+proceeding with the construction of a reduced-space surrogate based on the
+outcome of parameter screening, and accuracy of the most recent full-space
 surrogate as well as allocation of computational resources for parameter

### 2018-06-10 Paper/examples.tex
..

@@
 In section~\ref{sec:method}, we presented a framework for constructing
-an ROS (if deemed advantageous) by identifying unimportant parameters based on 
+an RSS (if deemed advantageous) by identifying unimportant parameters based on 
 estimates of the screening metric, $\widehat{\mathcal{C}_i\mu_i}$
@@
 test problems,
-namely, the borehole function, a non-linear oscillator, and a semilinear elliptic PDE.
+namely, the borehole function, and a semilinear elliptic PDE.
 Since model evaluations in all these test
-problems are inexpensive, we compare relative importance of model parameters based
+problems are inexpensive, we are able to compare the relative importance of
+model parameters based
 on the screening metric, obtained using model evaluations with 
 converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate constructed in the
-full parameter space (FSS). Additionally, to illustrate computational gains, we compare
-convergence trends as a function of training runs for the ROS and the FSS using 
+full parameter space (FSS). Additionally, to illustrate the computational gains, 
+we compare
+convergence trends as a function of training runs for the RSS and the FSS using 
 $\epsilon_{\mbox{\tiny LOO}}$ in Eq.~\ref{eq:loo}. 
 Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
-PDFs of the model output, obtained using the ROS and the full-space surrogate for
+PDFs of the model output, obtained using the RSS and the full-space surrogate for
 the purpose of verification.
@@
 It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
-geometrical and physical parameters:
+geometrical and physical inputs:
 \be
@@
 \renewcommand*{\arraystretch}{1.2}
+\caption{Description and distributions of uncertain inputs in the borehole function
+given by~\eqref{eq:bore}.}
+\label{tab:bore}
+\end{table}
 \begin{center}
@@
 
-\caption{Description and distributions of uncertain parameters in the borehole function
-given by~\eqref{eq:bore}.}
-\label{tab:bore}
-\end{table}
 %
@@
 the dimensionality of the problem by 
-discounting the uncertainties in $T_u$, $T_l$, and $K_w$ by fixing 
+discounting the variabilities in $T_u$, $T_l$, and $K_w$ by fixing 
 them at their respective nominal values.
 
-Our goal as discussed is to gain computational advantage by constructing
+Our goal as discussed earlier is to gain computational advantage by constructing
 surrogates in a reduced input parameter space. To this end, we use LAR to 
@@
 
-As discussed earlier in this section, the reduced order PCE's are verified for
+As discussed earlier in this section, the reduced-space PCE's are verified for
 predictive accuracy in a least-squares sense and a probabilistic sense.
@@
 The present framework allows for moving towards higher fidelity 
-reduced order surrogates based on the ranking of the parameter sensitivities.
+reduced-space surrogates based on the ranking of the parameter sensitivities.
 
@@
 samples through the 7D PCE in the original input parameter domain as well as
-the reduced order PCEs constructed in 4 and 5 dimensions. A normalized histogram
+the reduced-space PCEs constructed in 4 and 5 dimensions. A normalized histogram
 plot using 1000 model evaluations in the validation test suite is also included.
-It is evident from this plot, that the PDFs agree quite favorably with each
-other as well as the model-based histogram with respect to the modal estimate
+It is evident from this plot that the PDFs agree quite favorably with each
+other as well as the original model-based histogram with respect to the modal estimate
 as well as the uncertainty associated with $\mathcal{Q}$. 
-Consequently, it can be said that the reduced order PCE is verified in a
+Consequently, it can be said that the reduced-space PCE is verified in a
 probabilistic sense. In other words, the mode as well as the uncertainty in the
-observable is reliably captured and predicted by the reduced order PCE. 
+output is reliably captured and predicted by the reduced-space PCE. 
 % 
-\subsection{Nonlinear Oscillator}
-We consider an undamped nonlinear oscillator with only one degree of
-freedom as illustrated in Figure~\ref{fig:osc}. 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.5\textwidth]{./Figures/oscillator}
-\caption{Schematic illustration of an undamped non-linear oscillator system with one degree of freedom.}
-\label{fig:osc}
-\end{center}
-\end{figure}
-This system has been studied extensively for its reliability using
-the following state function~\cite{Bucher:1989,Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:
+%\subsection{Nonlinear Oscillator}
+%We consider an undamped nonlinear oscillator with only one degree of
+%freedom as illustrated in Figure~\ref{fig:osc}. 
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=0.5\textwidth]{./Figures/oscillator}
+%\caption{Schematic illustration of an undamped non-linear oscillator system with one degree of freedom.}
+%\label{fig:osc}
+%\end{center}
+%\end{figure}
+%This system has been studied extensively for its reliability using
+%the following state function~\cite{Bucher:1989,Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:
+%%
+%\be
+%g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - 
+%\left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|,
+%\label{eq:limit}
+%\ee
+%\noindent where $z_\text{max}$ is the maximum displacement response of the system, $r$ denotes the displacement at
+%which either spring yields, $\bm{X}=(m,k_1,k_2,r,F,t_1)^T$ is the vector 
+%of uncertain parameters, and   
+%$\omega_0~=~\sqrt{(k_1+k_2)/m}$. The uncertain parameters are considered to be normally distributed with mean
+%and variance as provided below in Table~\ref{tab:osc}.
 %
-\be
-g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - 
-\left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|,
-\label{eq:limit}
-\ee
-\noindent where $z_\text{max}$ is the maximum displacement response of the system, $r$ denotes the displacement at
-which either spring yields, $\bm{X}=(m,k_1,k_2,r,F,t_1)^T$ is the vector 
-of uncertain parameters, and   
-$\omega_0~=~\sqrt{(k_1+k_2)/m}$. The uncertain parameters are considered to be normally distributed with mean
-and variance as provided below in Table~\ref{tab:osc}.
-
-\begin{table}[htbp]
-\renewcommand*{\arraystretch}{1.2}
-\begin{center}
-\begin{tabular}{ll}
-\toprule
-\textbf{Parameter} & \textbf{Distribution} \\ 
-\bottomrule
-Mass, $m$ (kg) & $\mathcal{N}$(1,0.05) \\
-Time, $t_1$ (s) & $\mathcal{N}$(1,0.2) \\
-Force, $F$ (N) & $\mathcal{N}$(1,0.2) \\
-Displacement, $r$ (m) & $\mathcal{N}$(0.5,0.05) \\
-Spring Constant, $k_1$ (Nm$^{-1}$) & $\mathcal{N}$(1,0.1) \\
-Spring Constant, $k_2$ (Nm$^{-1}$) & $\mathcal{N}$(0.1,0.01) \\
-\bottomrule
-\end{tabular}
-\end{center}
-
-\caption{Description and distributions of uncertain parameters in the limit state function~\eqref{eq:limit}.}
-\label{tab:osc}
-\end{table}
-
-Converged estimates of $\mathcal{T}(\theta_i)$ are once again obtained easily by
-evaluating $g(\bm{X})$ for a large set of samples in the uncertain 
-parameter space; see Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
-$\widehat{\mathcal{C}_i\mu_i}$ are plotted against the number of samples in 
-Figure~\ref{fig:sense_osc}~(right). 
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/sense_oscillator}
-  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_oscillator}
-\caption{
-Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the limit 
-state function in~\eqref{eq:limit}. Right: 
-Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
-against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
-in each case in the legend.}
-\label{fig:sense_osc}
-\end{center}
-\end{figure}
-We note that the total Sobol sensitivity indices are in excellent agreement
-with the screening metric estimates. 
-Consequently, the parameter ranks are found to be consistent in the
-two plots in  
-Figure~\ref{fig:sense_osc}.
-It is observed that the limit state function is predominantly sensitive 
-to $r$, $F$, and $t_1$. Hence, it seems likely that an ROS in
-three dimensions is able to capture the overall uncertainty in $g(\bm{X})$.
-% due to uncertainty in the six parameters. 
-To illustrate computational gains as a
-result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the
-uncertainty in $k_1$ as well), and the original 6D parameter domain. In
-Figure~\ref{fig:conv_osc}~(left), we compare the convergence of the
-PCEs. As expected, the third-order PCE converges much faster than the other
-two. Consequently, the number of model evaluations required for a converged PCE
-is expected to be relatively much smaller in this case.  
-\begin{figure}[htbp]
- \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_oscillator}
-  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
-\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
-PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
-Right: PDF of the limit state function is plotted using the actual function in~\eqref{eq:limit}
-and the third-order PCE.}
-\label{fig:conv_osc}
-\end{center}
-\end{figure}
-
-To verify the accuracy of the third-order PCE, we estimate the relative L-2
-norm of the difference between predictions of  $g(\bm{X})$, obtained using the
-actual function in \eqref{eq:limit} and the 
-PCE using \eqref{eq:l2}, and a validation test suite. The test suite comprised
-model evaluations at 1000 independent Monte-Carlo samples in the full 
-parameter space. The value of $\epsilon_{\mbox{\tiny{L-2}}}$ 
-was found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
-Furthermore, the accuracy is assessed in a probabilistic sense by comparing
-in Figure~\ref{fig:conv_osc}~(right),
-PDFs of $g(\bm{X})$, obtained using the full-surrogate, reduced-order 
-surrogates constructed 3 and 4 dimensions, and a normalized histogram based
-on model evaluation in the validation test suite. The three PDFs are observed
-to be in excellent agreement with each other as well as the model-based
-histogram. Hence, the ROS constructed using the methodology
-presented in section~\ref{sec:method} could be used reliably to 
-quantify the uncertainty in $g(\bm{X})$ with reduced effort.
+%\begin{table}[htbp]
+%\renewcommand*{\arraystretch}{1.2}
+%\begin{center}
+%\begin{tabular}{ll}
+%\toprule
+%\textbf{Parameter} & \textbf{Distribution} \\ 
+%\bottomrule
+%Mass, $m$ (kg) & $\mathcal{N}$(1,0.05) \\
+%Time, $t_1$ (s) & $\mathcal{N}$(1,0.2) \\
+%Force, $F$ (N) & $\mathcal{N}$(1,0.2) \\
+%Displacement, $r$ (m) & $\mathcal{N}$(0.5,0.05) \\
+%Spring Constant, $k_1$ (Nm$^{-1}$) & $\mathcal{N}$(1,0.1) \\
+%Spring Constant, $k_2$ (Nm$^{-1}$) & $\mathcal{N}$(0.1,0.01) \\
+%\bottomrule
+%\end{tabular}
+%\end{center}
+%
+%\caption{Description and distributions of uncertain parameters in the limit state function~\eqref{eq:limit}.}
+%\label{tab:osc}
+%\end{table}
+%
+%Converged estimates of $\mathcal{T}(\theta_i)$ are once again obtained easily by
+%evaluating $g(\bm{X})$ for a large set of samples in the uncertain 
+%parameter space; see Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
+%$\widehat{\mathcal{C}_i\mu_i}$ are plotted against the number of samples in 
+%Figure~\ref{fig:sense_osc}~(right). 
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=0.48\textwidth]{./Figures/sense_oscillator}
+%  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_oscillator}
+%\caption{
+%Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the limit 
+%state function in~\eqref{eq:limit}. Right: 
+%Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
+%against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
+%in each case in the legend.}
+%\label{fig:sense_osc}
+%\end{center}
+%\end{figure}
+%We note that the total Sobol sensitivity indices are in excellent agreement
+%with the screening metric estimates. 
+%Consequently, the parameter ranks are found to be consistent in the
+%two plots in  
+%Figure~\ref{fig:sense_osc}.
+%It is observed that the limit state function is predominantly sensitive 
+%to $r$, $F$, and $t_1$. Hence, it seems likely that an RSS in
+%three dimensions is able to capture the overall uncertainty in $g(\bm{X})$.
+%% due to uncertainty in the six parameters. 
+%To illustrate computational gains as a
+%result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the
+%uncertainty in $k_1$ as well), and the original 6D parameter domain. In
+%Figure~\ref{fig:conv_osc}~(left), we compare the convergence of the
+%PCEs. As expected, the third-order PCE converges much faster than the other
+%two. Consequently, the number of model evaluations required for a converged PCE
+%is expected to be relatively much smaller in this case.  
+%\begin{figure}[htbp]
+% \begin{center}
+%  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_oscillator}
+%  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
+%\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
+%PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
+%Right: PDF of the limit state function is plotted using the actual function in~\eqref{eq:limit}
+%and the third-order PCE.}
+%\label{fig:conv_osc}
+%\end{center}
+%\end{figure}
+%
+%To verify the accuracy of the third-order PCE, we estimate the relative L-2
+%norm of the difference between predictions of  $g(\bm{X})$, obtained using the
+%actual function in \eqref{eq:limit} and the 
+%PCE using \eqref{eq:l2}, and a validation test suite. The test suite comprised
+%model evaluations at 1000 independent Monte-Carlo samples in the full 
+%parameter space. The value of $\epsilon_{\mbox{\tiny{L-2}}}$ 
+%was found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$.
+%Furthermore, the accuracy is assessed in a probabilistic sense by comparing
+%in Figure~\ref{fig:conv_osc}~(right),
+%PDFs of $g(\bm{X})$, obtained using the full-surrogate, reduced-order 
+%surrogates constructed 3 and 4 dimensions, and a normalized histogram based
+%on model evaluation in the validation test suite. The three PDFs are observed
+%to be in excellent agreement with each other as well as the model-based
+%histogram. Hence, the RSS constructed using the methodology
+%presented in section~\ref{sec:method} could be used reliably to 
+%quantify the uncertainty in $g(\bm{X})$ with reduced effort.
 
@@
 
-We aim to construct a reduced-order surrogate for the following QoI:
+We aim to construct a reduced-space surrogate for the following QoI:
 \be
@@
 examples, it can still be solved efficiently.
-The equation was discretized using finite-differences, and Newton's method
+The equation was discretized using finite differences, and Newton's method
 was used to solve the resulting nonlinear system on a (100$\times$100) 2D
@@
 in Figure~\ref{fig:sense_elliptic}~(left) by solving the above non-linear
-system at 500 samples in the 10D parameter space. 
+system at 500 samples in the 10-dimensional parameter space. 
 %
@@
 $\alpha_2$, $\alpha_3$, $\alpha_4$, and $\alpha_5$. These observations underscore the
-potential for computational gains by constructing an ROS in the 5D parameter space. We 
+potential for computational gains by constructing an RSS in the 5D parameter space. We 
 illustrate the comparison of convergence characteristics of the PCEs constructed in the
 full parameter space (10D) and the reduced space (5D) in Figure~\ref{fig:conv_elliptic} (left). 
-As expected, the ROS converges considerably faster. Using model evaluations at 90
+As expected, the RSS converges considerably faster. Using model evaluations at 90
 sample points, $\epsilon_{\mbox{\tiny{LOO}}}$ is found to be two orders of magnitude
@@
 $\mathcal{O}(10^{-2}$)). 
-Consequently, the computational effort for constructing the ROS in the present test problem
+Consequently, the computational effort for constructing the RSS in the present test problem
 is expected to be much smaller. 
@@
 Right: PDF of the QoI, $\mathcal{F}(\kappa, c, \theta)$ in~\eqref{eq:semilinear} is
-plotted using the full-surrogate and the reduced-order PC surrogate.}
+plotted using the full-surrogate and the reduced-space PC surrogate.}
 \label{fig:conv_elliptic}
@@
 
-Once again, we verify the accuracy of the ROS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
+Once again, we verify the accuracy of the RSS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
 using model evaluations at 1000 independent Monte-Carlo samples in the 10D parameter
-space. The ROS was found to be accurate
-within 5$\%$. In order to bolster confidence in the ROS, we compare PDFs of the QoI
+space. The RSS was found to be accurate
+within 5$\%$. In order to bolster confidence in the RSS, we compare PDFs of the QoI
 as well as a normalized histogram plot based on sparse model evaluations in the  
@@
 the modal estimate and the spread in the QoI based on the histogram is also captured
-by them. Hence, the ROS could be used with a reasonable degree of confidence to
+by them. Hence, the RSS could be used with a reasonable degree of confidence to
 quantify the uncertainty in $\mathcal{F}(\kappa, c, \theta)$ thereby leading to

### 2018-06-10 Paper/intro.tex
..

@@
 central importance in enabling efficient uncertainty quantification for
-computationally intensive models.
+systems with computationally intensive models.
 
@@
 (GPs)~\cite{Rasmussen:2004}, or kriging~\cite{Stein:2012}.  Many real-world
-applications involve a large number of uncertain parameters. This makes
-construction of surrogate models difficult or impossible in some cases.
+applications involve a large number of model inputs. This makes
+the construction of surrogate models difficult or impossible in some cases.
 However, in many situations, the variability in model observables of interest
@@
 identifying model inputs that are inessential to variability in model output is
-a key step that can facilitate surrogate model construction.
+a key step that can help reduce the dimension and hence, the effort
+associated with surrogate model construction.
 
@@
 dimensionality of the problem.  Computing Sobol indices, however, is a
-computationally challenging task.  
+computationally demanding task.  
 Availability of a surrogate model typically
@@
 geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
-and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global}, to name a few.
+and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014},
+to name a few.
 
@@
 indices, constructing them in the case of models with high-dimensional inputs
-can be as expensive as computing the Sobol indices via sampling.  Hence,
-dimension reduction prior surrogate model construction can lead to enormous
-computational savings.  Derivative based global sensitivity
+can be as expensive as computing the Sobol indices via sampling. This is
+clearly a ``catch-22" situation. In this paper, we aim to address this
+problem in a systematic and efficient manner. Specifically, we reduce
+the dimensionality of the input space using derivative based global sensitivity
 analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016}
-often lead to a more tractable approach for global sensitivity
+that enables a more tractable approach for global sensitivity
 analysis~\cite{Kucherenko:2016}.  Also, the links between derivative based
@@
 that are significantly less important than the rest, thereby reducing the
-dimensionality of the problem and enabling the construction of a reduced-order
-surrogate (ROS).  Our approach combines DGSMs and surrogate modeling in an
-iterative manner.  To make maximum use of computational resources, batches of
+dimensionality of the problem and enabling the construction of a reduced-space
+surrogate (RSS).  Our approach combines DGSMs and surrogate modeling in an
+iterative manner.  To make optimum use of computational resources, batches of
 model evaluations are performed iteratively, and convergence of our DGSM based
-screening metric is tested successively. Moreover, the validation steps built
+screening metric is tested successively. Moreover, the verification steps built
 in our method enable monitoring the accuracy of the parameter-screening and the
@@
 \paragraph{Contributions}
-The contributions of this article are as follows: (i) we establish a robust and
+The contributions of this article are as follows: (i) We establish a robust and
 practical framework for dimension reduction and surrogate modeling.  Our
@@
 (ii) We present comprehensive numerical results demonstrating the viability of
-our strategy in a number of motivating applications: the classic borehole
-function, a nonlinear oscillator, and a semilinear elliptic PDE.  (iii) We
-deploy our strategy in a application problem from chemical kinetics with 19
+our strategy using motivating applications: the classic borehole
+function, and a semilinear elliptic PDE.  (iii) We further
+deploy our strategy in an application problem from chemical kinetics with 19
 uncertain parameters. The application problem is studied in multiple regimes.
 It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
-or 4-dimensional parameter problem.
+or 4-dimensional problem.
 
@@
 examining various aspects of our approach. This is followed by implementation
-of our framework in an H$_2$/O$_2$ chemical kinetics, in section~\ref{sec:app}.
+of our framework in a H$_2$/O$_2$ chemical kinetics problem, in section~\ref{sec:app}.
 Finally, concluding remarks are provided in section~\ref{sec:disc}.

### 2018-06-10 Paper/method.tex
..

@@
 In this section, we outline the underlying framework for \emph{adaptively}
-constructing a reduced-order surrogate (ROS) using sensitivity analysis.  The
-proposed methodology is described as adaptive since the ROS is constructed only
+constructing a reduced-space surrogate (RSS) using sensitivity analysis.  The
+proposed methodology is described as adaptive since the RSS is constructed only
 in situations where it is expected to yield computational dividend as discussed
-further below.  The term reduced-order implies that the surrogate is
+further below.  The term reduced-space implies that the surrogate is
 constructed in a subspace that sufficiently captures the uncertainty in the
@@
 to assess the importance of individual parameters for potential dimension
-reduction and construction of an ROS. The overall adaptive framework 
+reduction and construction of an RSS. The overall adaptive framework 
 which incorporates parameter screening as an integral step is thereafter
-presented. Finally, we present validation metrics used for assessing the
-convergence and accuracy of the ROS followed by a brief discussion on
+presented. Finally, we present metrics used for assessing the
+convergence and accuracy of the RSS followed by a brief discussion on
 salient features of the proposed framework.
@@
 prohibitive for expensive-to-evaluate models.  In the proposed framework, we
-adopt a novel approach for constructing an ROS based on estimating the
+adopt a novel approach for constructing an RSS based on estimating the
 upper-bound $\widehat{\mathcal{C}_i\mu_i}$, given in~\eqref{eq:bound}, on 
@@
 Algorithm~\ref{alg:screen}.
+%\clearpage
 
@@
 \]
-      \State Set $s$ = 1.
-      \State Set $\mathrm{done} = \mathrm{false}$.
+      \State Set $s$ = 1 and $\mathrm{done} = \mathrm{false}$.
       \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
@@
 problems with scalar QoIs, but high-dimensional uncertain parameters, 
-adjoint-based gradient computation is much more efficient than finite-differences.
+adjoint-based gradient computation is much more efficient than finite differences.
 In the adjoint approach, each gradient evaluation requires 
@@
 Based on the steps outlined in the above algorithm, it can be said that the set
-of sample points used for estimating the screening metric,
+of sample points used for estimating the screening metricd
 $\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks between
@@
 of the screening metric for each uncertain parameter is accomplished. However,
-the amount of computational effort associated the screening process is limited
+the amount of computational effort associated with the screening process is limited
 by the choice of maximum number of iterations, $s_\text{max}$. 
@@
 
-\node (val) [process, below of=start, text width=14.5em] {Create a validation test suite using
-pre-allocated resources.};
+\node (val) [process, below of=start, text width=14.5em] {Create a cross-validation
+test suite using pre-allocated resources.};
 
@@
 
-\node (ros) [process, below of=dr, text width=11.5em, yshift=-1.5cm] {Construct a reduced-order surrogate (ROS)};
+\node (ros) [process, below of=dr, text width=11.5em, yshift=-1.5cm] {Construct a reduced-space surrogate (RSS)};
 
@@
 
-\node (ver) [process, left of=ros, text width=13.0em, xshift=-5cm] {Test ROS accuracy using
+\node (ver) [process, left of=ros, text width=13.0em, xshift=-5cm] {Test RSS accuracy using
  evaluations at $N_\text{total}$ $\&$ the validation test suite};
@@
 
-\caption{Flow-diagram outlining the adaptive strategy for constructing reduced-order surrogates.}
+\caption{Flow-diagram outlining the adaptive strategy for constructing reduced-space
+ surrogates.}
 \label{fig:flow}
@@
 \textbf{Adaptive surrogate model construction.}
-We begin by setting aside computational resources for constructing a validation
+We begin by setting aside computational resources for constructing a cross-validation
 test suite to be used for assessing the accuracy of the resulting surrogate.
@@
 $\alpha$ decreases.  Hence, if $\alpha$ is considered to be small and
-computational gains are expected owing to dimension reduction, the ROS is
+computational gains are expected owing to dimension reduction, the RSS is
 constructed and verified for accuracy using a combination of model evaluations
@@
 
-\textbf{Validation metrics.}
+\textbf{Assessment of the surrogate.}
 To assess convergence of the resulting surrogate, one could estimate the
@@
 where $N_v$ is the number of sampling points in the full parameter space at
-which model evaluations are available. In the case of an ROS, it is the
+which model evaluations are available. In the case of an RSS, it is the
 augmented set of model evaluations used for validation and screening.  
@@
 probability density functions (PDFs) of the model output based on model
-evaluations in the full parameter space and the ROS predictions corresponding
-to a large number of samples (say, 10$^6$).  However, in realistic problems
-involving complex, compute-intensive simulations, the PDF based on model
-evaluations would be intractable.  A practical alternative would be to compare
+evaluations in the full parameter space and the RSS predictions corresponding
+to a large number of samples (say, 10$^6$ for a high-dimensional input space).
+However, in realistic problems
+involving complex, compute-intensive simulations, constructing the PDF based on model
+evaluations would be infeasible.  A practical alternative would be to compare
 a histogram based on sparse model evaluations with the surrogate-based PDF in
@@
 can be mainly attributed to two steps: I.~Parameter Screening, and 
-II.~Constructing a converged ROS. Computational gains are realized in situations
+II.~Constructing a converged RSS. Computational gains are realized in situations
 where constructing the surrogate in the full parameter space is more expensive
@@
 would help address situations where significant dimension reduction is not
-possible, and hence, constructing the ROS might result in a computational
+possible, and hence, constructing the RSS might result in a computational
 disadvantage. We suggest using a small number of samples in the initial
@@
 dependence on each parameter. It is therefore likely that for a given
-application involving multiple outputs, the ROS can only be constructed for a
+application involving multiple outputs, the RSS can only be constructed for a
 selected few, using the approach presented above.  Hence, it is important to
@@
 surrogate in the most efficient manner within the constraints of the computational
-budget. However, it is likely that for a given application, the ROS is not
+budget. However, it is likely that for a given application, the RSS is not
 found to be sufficiently accurate. In such a scenario, we suggest enriching the
-set of important parameters by incorporating the least unimportant parameter
-as determined after a series of screening steps, and re-constructing the ROS. 
+set of important inputs by incorporating the least unimportant model input
+as determined after a series of screening steps, and re-constructing the RSS. 
 This process could be repeated depending upon the availability of resources

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/doign.c
..

@@ -1,0 +1,124 @@
+#include "ign.h"
+
+double doIgn(tadvInfo *ad, ioInfo *iod, void *cvode_mem)
+{
+
+  int    i, iter, cvflag, Nvars, foundid2;
+  double tret, der2, time_id1, time_id2, Temp_m1, Temp_m2, time_m1, time_m2, Temp_save ;
+
+  foundid2 = 0 ;
+  time_id1 = time_id2 = 0.0     ;
+  time_m1  = time_m2  = 0.0     ;
+  Temp_m1  = Temp_m2  = NV_Ith_S(ad->y0,0);
+  iter = 0    ;
+
+  Nvars = NV_LENGTH_S(ad->y0) ;
+
+  ad->t = ad->tsta ;
+
+  /* Re-initialize cvode */
+  cvflag = CVodeReInit(cvode_mem, ad->tsta, ad->y0 );
+  Check_CVflag(&cvflag, "CVodeReInit", 1) ;
+  cvflag = CVodeSVtolerances(cvode_mem, ad->relT, ad->absT);
+  Check_CVflag(&cvflag, "CVodeSVtolerances", 1) ;
+  cvflag = CVodeSetStopTime(cvode_mem, ad->tend);
+  Check_CVflag(&cvflag, "CVodeSetStopTime", 1) ;
+
+  //printf("%18.12e\n",ad->relT);
+  // for (i=0; i<Nvars;i++)
+  //  printf("%d %18.12e\n",i,NV_Ith_S(ad->absT,i));
+
+  //exit(0);
+
+  Temp_save = NV_Ith_S(ad->y0,0) ;
+
+#ifdef DEBUGMSG
+  N_Vector ydot = N_VNew_Serial( Nvars );
+  chemrhs(0.0, ad->y0, ydot, NULL);
+  for( i = 0; i < Nvars ; i++) {
+    printf("%d %e %e\n",i,NV_Ith_S(ad->y0,i),NV_Ith_S(ydot,i));
+  }
+  exit(1);
+#endif
+  while ( ( ad->t < ad->tend ) && (iter < (ad->NiterMax) ) ) {
+    /* call cvode */
+    ad->t += (ad->deltat) ;
+    iter  += 1         ;
+    cvflag = CVode(cvode_mem, ad->t, ad->y0, &tret, CV_NORMAL);
+
+    if (cvflag == CV_ROOT_RETURN)
+    {
+      int rootsfound[1] ;
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/doignDtSeq.c

@@ -1,0 +1,68 @@
+#include "ign.h"
+
+double doIgnDtSeq(tadvInfo *ad, ioInfo *iod, void *cvode_mem)
+{
+
+  double tret; 
+  int    i, iter, cvflag, Nvars;
+  double time_id1 = 0.0 ;
+
+  Nvars = NV_LENGTH_S(ad->y0) ;
+
+  ad->t = ad->tsta ;
+  iter = 0    ;
+  while ( iter < ad->getDeltatSeq ) 
+  {
+
+/*#ifdef DONOTDOIT*/
+    /* Re-initialize cvode */
+    cvflag = CVodeReInit(cvode_mem, ad->t, ad->y0 );
+    Check_CVflag(&cvflag, "CVodeReInit", 1) ;
+
+    cvflag = CVodeSVtolerances(cvode_mem, ad->relT, ad->absT);
+    Check_CVflag(&cvflag, "CVodeSVtolerances", 1) ;
+
+    cvflag = CVodeSetStopTime(cvode_mem, ad->tend);
+    Check_CVflag(&cvflag, "CVodeSetStopTime", 1) ;
+/*#endif*/
+
+    /* call cvode */
+    ad->deltat = ad->deltatSeq[iter] ;
+    ad->t     += ad->deltat ;
+    iter += 1 ;
+    cvflag = CVode(cvode_mem, ad->t, ad->y0, &tret, CV_NORMAL);
+
+    if (cvflag == CV_ROOT_RETURN) 
+    {
+      int rootsfound[1] ;
+      int flagroot = CVodeGetRootInfo(cvode_mem, rootsfound);
+      Check_CVflag(&flagroot, "CVodeGetRootInfo", 1) ;
+      printf("Found root : %20.12e\n",tret);
+      time_id1 = tret ;
+      if ( ad->getIgnDel == 1 ) { ad->tend = tret ; (ad->NiterMax) = iter ; return ( time_id1 ) ; }
+    }
+
+    /* reset time based on end time from cvode */
+    ad->t = tret ;
+
+#ifndef NO_OUTPUT
+    /* output solution */
+    if ( iter % (ad->oFreq) == 0 )
+      Output(1, iter, ad, iod) ;
+#endif
+
+    /* re-calculate absolute tolerances based on recent solution */
+    for( i = 0; i < Nvars ; i++)
+    {
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/doignReinit.c

@@ -1,0 +1,66 @@
+#include "ign.h"
+
+double doIgnReinit(tadvInfo *ad, ioInfo *iod, void *cvode_mem)
+{
+
+  double tret, Temp_save, time_id1 = 0.0 ; 
+  int    i, iter, cvflag, Nvars;
+
+  Nvars = NV_LENGTH_S(ad->y0) ;
+
+  ad->t = ad->tsta ;
+  iter = 0    ;
+  time_id1 = -100.0 ;
+
+  /* Re-initialize cvode */
+  cvflag = CVodeReInit(cvode_mem, ad->tsta, ad->y0 );
+  Check_CVflag(&cvflag, "CVodeReInit", 1) ;
+  cvflag = CVodeSVtolerances(cvode_mem, ad->relT, ad->absT);
+  Check_CVflag(&cvflag, "CVodeSVtolerances", 1) ;
+  cvflag = CVodeSetStopTime(cvode_mem, ad->tend);
+  Check_CVflag(&cvflag, "CVodeSetStopTime", 1) ;
+
+  Temp_save = NV_Ith_S(ad->y0,0);
+  while ( ( ad->t < (ad->tend) ) && (iter < (ad->NiterMax) ) )
+  {
+    /* call cvode */
+    ad->t += (ad->deltat) ;
+    iter  += 1         ;
+    cvflag = CVode(cvode_mem, ad->t, ad->y0, &tret, CV_NORMAL);
+
+    if (cvflag == CV_ROOT_RETURN) 
+    {
+      int rootsfound[1] ;
+      int flagroot = CVodeGetRootInfo(cvode_mem, rootsfound);
+      Check_CVflag(&flagroot, "CVodeGetRootInfo", 1) ;
+      /* printf("Found root : %20.12e\n",tret); */
+      time_id1 = tret ;
+      return ( time_id1 ) ; 
+    }
+
+    /* reset time based on end time from cvode */
+    ad->t = tret ;
+
+    /*
+       calculate new time step:
+       - reduce/increase time step if \Delta T >< 0.25K
+     */
+    (ad->deltat) = MIN(
+		    ad->deltaTemp/MAX(fabs(NV_Ith_S(ad->y0,0)-Temp_save),TCSMALL)*(ad->deltat),
+		    2.0*(ad->deltat)
+		);
+    (ad->deltat) = MIN((ad->deltat),ad->deltatMax) ;
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/ign.c

@@ -1,0 +1,297 @@
+#include "ign.h"
+
+void getmeps(double *rtol, double *atol)
+{
+
+  double sml = 1.0 ;
+  while ( 1.0+sml != 1.0 ) sml *= 0.5 ;
+  *rtol = sqrt(2.0*sml) ;
+  *atol = *rtol ;
+  return ;
+
+}
+int main()
+{
+
+  tadvInfo advdata;
+  ioInfo   iodata;
+
+  /* Integer parameters */
+  int Nspec, Nvars, Nreac ;
+
+  /* Character array parameters */
+  int sizecMax = 100, specinno ;
+  char *mechfile, *thermofile ;
+
+  int    lsnm = LENGTHOFSPECNAME;
+  char   *SpecName ;
+  double *SpecMsFr ;
+
+  unsigned int withTab ;  /* tabulation flag */
+
+  /* work parameters */
+  int i ;
+  double time_id1,time_id2 ;
+
+  /* CVODE-related parameters */
+  int iter, ierr ;
+  cdt udata ;
+
+  mechfile   = (char *) malloc( sizecMax * sizeof(char) ) ;
+  thermofile = (char *) malloc( sizecMax * sizeof(char) );
+  memset(mechfile  , 0, sizecMax) ;
+  memset(thermofile, 0, sizecMax) ;
+
+  /* Arrays for input/output species info */
+  SpecName = (char   *) malloc( MAXSPECIN * lsnm *sizeof(char  ) ) ;
+  SpecMsFr = (double *) malloc( MAXSPECIN *       sizeof(double) ) ;
+  memset(SpecName, 0, MAXSPECIN * lsnm) ;
+  for ( i = 0 ; i < MAXSPECIN; i++ ) SpecMsFr[i] = 0.0 ;
+
+  iodata.SpecOutName = (char *) malloc( MAXSPECOUT* lsnm *sizeof(char)) ;
+  memset(iodata.SpecOutName, 0, MAXSPECOUT * lsnm) ;
+
+  setup(&advdata,&iodata,&withTab,SpecName, SpecMsFr, &specinno,
+        mechfile, thermofile) ;
+
+  /*
+                           _
+                  ___  ___| |_ _   _ _ __
+                 / __|/ _ \ __| | | | '_ \
+                 \__ \  __/ |_| |_| | |_) |
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/ign.h

@@ -1,0 +1,101 @@
+#ifndef IGNHSEEN
+#define IGNHSEEN
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h> 
+#include <string.h>
+#include <ctype.h>
+#include <assert.h>
+
+/*  CVODE headers  */
+#include <cvode/cvode.h>             /* prototypes for CVODE fcts., consts.  */
+#include <nvector/nvector_serial.h>  /* serial N_Vector types, fcts., macros */
+#include <cvode/cvode_dense.h>       /* prototype for CVDense                */
+#include <sundials/sundials_dense.h> /* definitions DlsMat DENSE_ELEM        */
+#include <sundials/sundials_types.h> /* definition of type realtype          */
+
+#include "TC_interface.h"
+#include "TC_params.h"
+
+#define MAX(A,B) ( ((A) > (B)) ? (A) : (B) )
+#define MIN(A,B) ( ((A) < (B)) ? (A) : (B) )
+
+#define MAXSPECIN  200
+#define MAXSPECOUT 200
+
+typedef struct {
+  double Tign;
+  int ncalls;
+} cdt;
+
+/* Time stepping/CVode info */
+typedef struct {
+
+  double t;           /* current time */
+  double tsta;        /* start time */
+  double tend;        /* end   time */
+  double deltat;      /* current time step */
+  double deltatMax;   /* maximum time step */
+  double deltaTemp;   /* maximum temperature change per time step*/
+
+  double Tini;        /* initial temperature */   
+  double Temp_id ;    /* temperature threshold for ignition delay */
+
+  double pressure ;   /* atmospheric pressure */  
+  double pfac ;       /* pressure factor */
+
+  int oFreq;          /* Output frequency */
+  int NiterMax;       /* Maximum no. of iterations */
+
+  double *scal ;      /* array, Nspec+1 long with T and Y's */
+  N_Vector y0 ;       /* CVode vector, Nspec+1 long with T and Y's */
+  realtype relT;      /* relative tolerance */
+  N_Vector absT;      /* CVode vector, absolute tolerances */
+
+  int getDeltatSeq;   /* use prescribed time steps ? */
+  double *deltatSeq;  /* array with prescribed time steps*/
+
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/initcvode.c

@@ -1,0 +1,50 @@
+#include "ign.h"
+
+void initCVODE (void **cvode_mem, tadvInfo *ad, cdt *udata) 
+{
+  int cvflag ;
+
+  /* Create cvode solver */
+  (*cvode_mem) = CVodeCreate(CV_BDF, CV_NEWTON);
+  Check_CVflag(*cvode_mem, "CVodeCreate", 0) ;
+
+  /* Allocate memory */
+  cvflag = CVodeInit(*cvode_mem, &chemrhswrapper, ad->tsta, ad->y0);
+  Check_CVflag(&cvflag, "CVodeInit", 1) ;
+  cvflag = CVodeSVtolerances(*cvode_mem, ad->relT, ad->absT);
+  Check_CVflag(&cvflag, "CVodeSVtolerances", 1) ;
+
+  /*  Set dense solver */
+  cvflag = CVDense(*cvode_mem, NV_LENGTH_S(ad->y0) );
+  Check_CVflag(&cvflag, "CVDense", 1) ;
+  
+  /* Set work array */
+  cvflag = CVodeSetUserData(*cvode_mem,  (void *) udata);
+  Check_CVflag(&cvflag, "CVodeSetUserData", 1) ;
+
+#ifdef USEJAC
+  /* Set dense Jacobian */
+  cvflag = CVDlsSetDenseJacFn(*cvode_mem, chemjacwrapper);
+  Check_CVflag(&cvflag, "CVDlsSetDenseJacFn", 1) ;
+#endif
+
+  /* Set maximum order for the integratiom method */
+  cvflag = CVodeSetMaxOrd(*cvode_mem, ad->CVmaxord);
+  Check_CVflag(&cvflag, "CVodeSetMaxOrd", 1) ;
+  
+  /* Set maximum number of steps */
+  cvflag = CVodeSetMaxNumSteps(*cvode_mem, ad->CVmaxnumsteps);
+  Check_CVflag(&cvflag, "CVodeSetMaxNumSteps", 1) ;
+
+  /* Set stop value */
+  cvflag = CVodeSetStopTime(*cvode_mem, ad->tend);
+  Check_CVflag(&cvflag, "CVodeSetStopTime", 1) ;
+
+#ifdef GETTIG
+  /* Call CVodeRootInit to specify the root function g with 1 component */
+  cvflag = CVodeRootInit(*cvode_mem, 1, &g);
+  Check_CVflag(&cvflag, "CVodeRootInit", 1) ;
+#endif
+
+  return ;
+}

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/output.c

@@ -1,0 +1,127 @@
+#include "ign.h"
+
+static double *tempNmsfr=NULL, *rhsvals=NULL ;
+
+void Output(int iflag, int iter, tadvInfo *ad, ioInfo *iod)
+{
+  int i, ierr, Nvars, Nspec, icount, lsnm ;
+  double sumY, *scal;
+
+
+  lsnm  = LENGTHOFSPECNAME;
+  scal  = N_VGetArrayPointer(ad->y0);
+  Nvars = NV_LENGTH_S(ad->y0) ;
+  Nspec = Nvars-1;
+
+  if ( tempNmsfr == NULL ) 
+    tempNmsfr = (double *) malloc( (Nspec+1) * sizeof(double) ) ;
+  if ( rhsvals   == NULL ) 
+    rhsvals   = (double *) malloc( (Nspec+1) * sizeof(double) ) ;
+
+  if ( iflag == 0 ) 
+  {
+    char *snameshdr = (char *) malloc( Nspec * lsnm * sizeof(char) ) ; 
+    ierr = TC_getSnames( Nspec, snameshdr ) ;
+    if (ierr != 0) {
+      printf("ERROR in %s at line %d\n",__FILE__,__LINE__); 
+      exit(1);
+    }
+
+    fprintf(iod->myfile,"# 1: iteration, #2: time, #3: deltat, #4: temperature,\n") ;
+    if (iod->specOutIDs==NULL) {
+      for ( i = 0; i<Nspec; i++ )
+        fprintf(iod->myfile,"#%d: Mass fraction of %s \n",i+5,&snameshdr[i*lsnm]);
+    }
+    else {
+      icount = 0;
+      for ( i = 0; i<Nspec; i++ ) 
+        if (iod->specOutIDs[i]==1) {
+          fprintf(iod->myfile,"#%d: Mass fraction of %s \n",icount+5,&snameshdr[i*lsnm]);
+          icount++;
+	}
+    }
+
+    fprintf(iod->myfile1,"#1: time, #2: temperature,\n") ;
+    if (iod->specOutIDs==NULL) {
+      for ( i = 0; i<Nspec; i++ )
+        fprintf(iod->myfile1,"#%d: Mass fraction of %s \n",
+                i+3,&snameshdr[i*lsnm]);
+    }
+    else {
+      icount = 0;
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/rhsjac.c

@@ -1,0 +1,98 @@
+#include "ign.h"
+
+void chemrhs(realtype t, N_Vector y, N_Vector ydot, void *f_data)
+{
+
+  int Nv,i ;
+
+  Nv = NV_LENGTH_S(y) ;
+
+  realtype *TandYs = N_VGetArrayPointer(y   );
+  realtype *omg    = N_VGetArrayPointer(ydot);
+  TC_getSrc ( TandYs, Nv, omg ) ;
+
+  return ;
+
+}
+
+int chemrhswrapper(realtype t, N_Vector y, N_Vector ydot, void *f_data)
+{
+
+  chemrhs(t,y,ydot,f_data) ;
+  return ( 0 );
+
+}
+
+#ifdef USEJAC
+
+void chemjac(realtype t, N_Vector y, DlsMat Jac, double *jactmp) 
+{
+
+  int Ns,i ;
+  unsigned int useJacAnl = 1 ; /* use analytic Jacobian */
+
+  Ns = NV_LENGTH_S(y)-1 ;
+  realtype *TandYs = N_VGetArrayPointer(y   );
+  TC_getJacTYN ( TandYs, Ns, (Jac->data), useJacAnl ) ;
+
+  //for (i=0; i<1; i++)
+  //  printf("%d %18e \n",i,(Jac->data)[i]);
+
+  return ;
+  
+}
+
+int chemjacwrapper(long int N, realtype t, 
+                   N_Vector y, N_Vector fy, DlsMat J, void *udata,
+		               N_Vector tmp1, N_Vector tmp2, N_Vector tmp3) 
+{
+
+  double *jactmp = (double*) udata ;
+  chemjac( t, y, J, jactmp) ;
+
+  return ( 0 );
+
+}
+
+#endif
+
+int g(realtype t, N_Vector y, realtype *gout, void *user_data)
+{
+
+  cdt *udataloc = (cdt *)user_data;
+  realtype temper = NV_Ith_S(y,0) ;
+
+  gout[0] = temper-(udataloc->Tign) ;
+  udataloc->ncalls += 1;
+
+  return(0);
+}
+
+
+
+int Check_CVflag(void *flagvalue, char *funcname, int opt)
+{
+
+  int *errflag;
+
+  /* Check if SUNDIALS function returned NULL pointer - no memory allocated */
+  if ( ( opt == 0 ) && ( flagvalue == NULL ) )
+  {
[…]

### 2018-06-11 Codes/Kinetics/TChem/example/ign-c/src/setup.c

@@ -1,0 +1,141 @@
+#include "ign.h"
+
+#define FNAMEMAX 100
+
+void setup(tadvInfo *ad, ioInfo *iod, unsigned int *withTab,
+           char *SpecName, double *SpecMsFr, int *specinno,
+           char *mechfile, char *thermofile)
+{
+  int i,lsnm ;
+  char filDeltatSeq[FNAMEMAX] ;
+
+  lsnm = LENGTHOFSPECNAME;
+  /*
+      _       __             _ _
+   __| | ___ / _| __ _ _   _| | |_ ___
+  / _` |/ _ \ |_ / _` | | | | | __/ __|
+ | (_| |  __/  _| (_| | |_| | | |_\__ \
+  \__,_|\___|_|  \__,_|\__,_|_|\__|___/
+
+  */
+  ad->NiterMax  = 100000    ; /* Maximum no. of iterations */
+  ad->oFreq     = 10        ; /* Output frequency          */
+  ad->Tini      = 1000.0    ; /* Initial temperature  [K]  */
+  ad->Temp_id   = 1500.0    ; /* Threshold temperature for ignition delay [K]  */
+  ad->deltat    = 1.e-10    ; /* Initial time step size [s]  */
+  ad->deltatMax = 1.e-4     ; /* Maximum time step size [s]  */
+  ad->tend      = 2.0e0     ; /* End integration time   [s]  */
+  ad->deltaTemp = 1.0       ; /* Maximum temperature change per time step [K]  */
+  ad->pressure  = 1.01325e5 ; /* Pressure [Pa] */
+  ad->pfac      = 1.0       ; /* Pressure scale factor [ ]  */
+
+  ad->getDeltatSeq = 0      ; /* Do not use a sequence of dt  */
+  ad->deltatSeq    = NULL   ;
+
+  ad->CVrelt        = 1.e-8  ;
+  ad->CVsmall       = 1.e-17 ;
+  ad->CVmaxord      = 5      ;
+  ad->CVmaxnumsteps = 10000  ;
+
+  strcpy(mechfile  ,"chem.inp" ) ;
+  strcpy(thermofile,"therm.dat") ;
+
+  *withTab = 0 ;  /* no tabulation           */
+  ad->getIgnDel = 0 ;/* no ignition delay stop  */
+  ad->getSens   = 0 ;/* no sensitivity analysis */
+
[…]

### 2018-06-11 Codes/Kinetics/TChem/include/TC_defs.h

@@ -1,0 +1,421 @@
+#ifndef _TCdefsHSeen_
+#define _TCdefsHSeen_
+
+/*! #
+ * \file TC_defs.h
+ * \brief Definitions of variables names used by the library.
+*/
+#include "copyright.h"
+#include <stdio.h>
+#include "TC_params.h"
+
+/* --------------------------------------------
+   numbers, lengths, etc.
+   -------------------------------------------- */
+/** \var static int TC_maxSpecInReac_
+ *  \ingroup maxpar
+ *  \brief Maximum number of species in a reaction */
+static int TC_maxSpecInReac_ ;
+/** \var static int TC_maxTbInReac_
+ *  \ingroup maxpar
+    \brief Max # of third-body efficiencies in a reaction */
+static int TC_maxTbInReac_   ;
+/** \var static int TC_nNASAinter_
+ *  \ingroup maxpar
+    \brief # of temperature regions for thermo fits */
+static int TC_nNASAinter_    ;
+/** \var static int TC_nCpCoef_
+ *  \ingroup maxpar
+    \brief # of polynomial coefficients for thermo fits */
+static int TC_nCpCoef_       ;
+/** \var static int TC_nArhPar_
+ *  \ingroup maxpar
+    \brief # of Arrhenius parameters */
+static int TC_nArhPar_       ;
+/** \var static int TC_nLtPar_
+ *  \ingroup maxpar
+    \brief # of parameters for Landau-Teller reactions */
+static int TC_nLtPar_        ;
+/** \var static int TC_nFallPar_
+ *  \ingroup maxpar
+    \brief # of parameters for pressure-dependent reactions */
+static int TC_nFallPar_      ;
+/** \var static int TC_nJanPar_
+ *  \ingroup maxpar
+    \brief # of parameters for Jannev-Langer fits (JAN) */
+static int TC_nJanPar_       ;
+/** \var static int TC_maxOrdPar_
+ *  \ingroup maxpar
+    \brief # of parameters for arbitrary order reactions */
+static int TC_maxOrdPar_     ;
+/** \var static int TC_nFit1Par_
+ *  \ingroup maxpar
+    \brief # of parameters for FIT1 fits */
+static int TC_nFit1Par_      ;
+
+/** \var static int TC_Nvars_
+ *  \ingroup nospec
+    \brief # of variables = no. of species + 1 */
[…]

### 2018-06-11 Codes/Kinetics/TChem/include/TC_interface.h

@@ -1,0 +1,387 @@
+/*! \file TC_interface.h
+    \brief Header file to be included in user's code. Contains function definitions.
+*/ 
+#ifndef _TCinterfHSeen_
+#define _TCinterfHSeen_
+
+#include "copyright.h"
+
+/* This is a C library, not C++ */
+#ifdef __cplusplus
+extern "C"
+{
+#endif
+
+/*
+     __       __                        _       __            ____              
+    / /______/ /_  ___  ____ ___       (_)___  / /____  _____/ __/___ _________ 
+   / __/ ___/ __ \/ _ \/ __ `__ \     / / __ \/ __/ _ \/ ___/ /_/ __ `/ ___/ _ \
+  / /_/ /__/ / / /  __/ / / / / /    / / / / / /_/  __/ /  / __/ /_/ / /__/  __/
+  \__/\___/_/ /_/\___/_/ /_/ /_/____/_/_/ /_/\__/\___/_/  /_/  \__,_/\___/\___/ 
+                              /_____/                                           
+*/
+#define TCSMALL 1.e-30
+
+int TC_getReacStr(int ireac, int lenstr,char *rstr);
+/*
+
+       _____ ____         _                 
+      |_   _/ ___|    ___| |__   __ _   ___ 
+        | || |       / __| '_ \ / _` | / __|
+        | || |___   | (__| | | | (_| || (__ 
+        |_| \____|___\___|_| |_|\__, (_)___|
+                |_____|         |___/       
+
+*/
+int TC_chgArhenFor( int ireac, int ipos, double newval ) ;
+int TC_chgArhenRev( int ireac, int ipos, double newval ) ;
+int TC_chgArhenPresDepFor( int ireac, int ipos, double newval) ;
+int TC_chgArhenForBack( int ireac, int ipos) ;
+int TC_chgArhenRevBack( int ireac, int ipos) ;
+
+int TC_chgReacOrd( int ireac, int iForRev, int ispec, double newval );
+
+/*
+       _____ ____                _         
+      |_   _/ ___|     __ _  ___| |_   ___ 
+        | || |        / _` |/ _ \ __| / __|
+        | || |___    | (_| |  __/ |_ | (__ 
+        |_| \____|____\__, |\___|\__(_)___|
+                |_____|___/                
+*/
+int TC_getArhenRev( int ireac, int ipos, double* val ) ;
[…]

### 2018-06-11 Codes/Kinetics/TChem/include/TC_kmodint.h

@@ -1,0 +1,243 @@
+#ifndef TCkmodintHSeen
+#define TCkmodintHSeen
+
+#include "copyright.h"
+#include "TC_params.h"
+
+/* Length of filenames */
+#define lenfile 100
+
+/* Lengths of character strings */
+#define lenstr01 2000
+#define lenstr02 200
+#define lenstr03 20
+#define lenread  512
+
+/* Reallocation factors for element, species, and reaction lists */
+#define nelemalloc 1
+#define nspecalloc 1
+#define nreacalloc 5
+
+/* -------------------------------------------------------------------------
+                           Structure definitions
+   ------------------------------------------------------------------------- */
+
+/**
+ * \brief Entry in the table of periodic elements
+ */
+typedef struct {
+  char    name[LENGTHOFELEMNAME] ;
+  double  mass                   ;
+} elemtable ;
+
+/**
+ * \brief Element data
+ */
+typedef struct {
+  char   name[LENGTHOFELEMNAME] ;
+  int    hasmass                ;
+  double mass                   ;
+} element ;
+
+/**
+ * \brief Species data
+ */
+typedef struct {
+  char   name[LENGTHOFSPECNAME]          ;
+  int    hasthermo                       ;
+  int    hasmass                         ;
+  double mass                            ;
+  int    charge                          ;
+  int    phase                           ;
+  int    numofelem                       ;
+  int    elemindx[NUMBEROFELEMINSPEC]    ;
+  int    elemcontent[NUMBEROFELEMINSPEC] ;
+  double nasapoltemp[3]                  ;
+  double nasapolcoefs[14]                ;
+  /* new NASA polynomials */
+  int    Nth9rng                         ;
+  double Nth9Temp[2*NTH9RNGMAX]          ;
+  double Nth9coefs[9*NTH9RNGMAX]         ;
+} species ;
+
+/**
+ * \brief Reaction data
+ */
+typedef struct {
+  int isdup     ; /* Duplicate reactions */
+  int isreal    ; /* Real stoichiometric coefficients */
+  int isrev     ; /* Is reversible */
+  int isfall    ; /* Is pressure dependent */
+  int specfall  ; /* Type of concetration used for pressure dependency */
+  int isthrdb   ; /* Uses third body */
+  int nthrdb    ; /* Number of third body coefficients */
+  int iswl      ; /* Is photon activation */
+  int isbal     ; /* Is balanced */
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_chg.c

@@ -1,0 +1,257 @@
+/*! \file TC_chg.c
+    \brief Functions for changing Arrhenius rate factors
+*/ 
+/**
+ * \brief Change parameters for forward rate constants
+ */
+int TC_chgArhenFor( int ireac, int ipos, double newval )
+{
+/**
+ * \param ireac : reaction index
+ * \param ipos : index of parameter to be changed (0) pre-exponential factor
+                 (1) temperature exponent, (2) activation energy
+ * \param newval : new parameter value
+ */
+
+  if ( TC_ArhenForChg_ == 0 )
+  {
+
+    /* Save original factors */
+    TC_reacArhenForSave_ = (double *) malloc( TC_Nreac_*3*sizeof(double) ) ;
+    memcpy(TC_reacArhenForSave_, TC_reacArhenFor_, 3*TC_Nreac_*sizeof(double) );
+    TC_ArhenForChg_ = 1 ;
+
+  }
+
+  if ( ( ireac < 0 ) || ( ireac >= TC_Nreac_ ))
+  {
+    printf("TC_chgArhenFor() : reaction index is wrong -> %d\n", ireac) ;
+    exit(1) ;
+  }
+  if ( ( ipos < 0 ) || ( ipos >= 3 ))
+  {
+    printf("TC_chgArhenFor() : index of Arrhenius parameter is wrong -> %d\n", ipos) ;
+    exit(1) ;
+  }
+
+  TC_reacArhenFor_[ireac*3+ipos] = newval ;
+
+  return ( 0 ) ;
+
+}
+
+/**
+ * \brief Change parameters for forward rate constants of low/high pressure limits for Pressure-dependent reactions
+ */
+int TC_chgArhenPresDepFor( int ireac, int ipos, double newval)
+{
+/**
+ * \param ireac : Pressure-dependent reaction index
+ * \param ipos : index of parameter to be changed (0) pre-exponential factor
+                 (1) temperature exponent, (2) activation energy
+ * \param newval : new parameter value
+ */
+
+  if ( ( ireac < 0 ) || ( ireac >= TC_nFallReac_ ))
+  {
+    printf("TC_chgArhenPresDepFor() : reaction index is wrong -> %d\n", ireac) ;
+    exit(1) ;
+  }
+  if ( ( ipos < 0 ) || ( ipos >= TC_nFallPar_ ))
+  {
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_dnd.c

@@ -1,0 +1,240 @@
+/**
+ * \ingroup srcs
+ * \brief Returns dimensional/non-dimensional source term for 
+ * \f[\frac{\partial T}{\partial t}=\omega_0,\frac{\partial Y_i}{\partial t}=\omega_i,\f]
+ *  based on temperature T and species mass fractions Y's
+ */
+
+int TCDND_getSrc(double *scal,int Nvars,double *omega)
+{
+
+/**
+   \param scal : array of Nspec+1 doubles \f$(T,Y_1,Y_2,...,Y_{N_{spec}})\f$
+	        temperature T [K], mass fractions Y [] 
+   \param Nvars : no. of variables \f$ N_{vars}= N_{spec}+1\f$ 
+   \return omega : array of N<sub>spec</sub>+1 source terms (possibly normalized) for temperature and 
+                   species mass fractions equations: 
+		   omega[0] : [(K/s)], omega[1...N<sub>spec</sub>] : [(1/s)]
+*/
+
+  int ans, i ;
+
+  if ( Nvars != TC_Nvars_ ) 
+    TC_errorMSG( 20, "TCDND_getSrc", Nvars, TC_Nvars_ ) ;
+
+  if ( TC_nonDim_ == 1 ) scal[0] *= TC_Tref_ ;
+
+  ans = TC_getSrc(scal, Nvars, omega) ;
+
+  if ( TC_nonDim_ == 1 ) 
+  {
+    scal[0] /= TC_Tref_ ;
+    omega[0] *= (TC_timref_/TC_Tref_) ;
+    for ( i = 1 ; i < TC_Nspec_+1 ; i++ ) omega[i] *= TC_timref_ ;
+  }
+
+  return ( ans ) ;
+ 
+}
+/*
+                _   ____            ____                
+      __ _  ___| |_/ ___| _ __ ___ / ___|___  _ __  ___ 
+     / _` |/ _ \ __\___ \| '__/ __| |   / _ \| '_ \/ __|
+    | (_| |  __/ |_ ___) | | | (__| |__| (_) | | | \__ \
+     \__, |\___|\__|____/|_|  \___|\____\___/|_| |_|___/
+     |___/                                              
+
+*/
+/**
+ * \ingroup srcs
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_edit.c

@@ -1,0 +1,797 @@
+/** 
+  \brief Frees all memory and sets variables to 0 so that TC_initChem can be called
+         again without a memory leak.  Not designed for use with tables.   
+*/
+void TC_reset()
+{
+  /* For straightforward error checking, arrays are freed in the same order as 
+  allocation in TC_init.c */
+
+  /* From TC_initChem() */
+  free(TC_eNames_);       TC_eNames_       = 0;
+  free(TC_eMass_);        TC_eMass_        = 0;
+  free(TC_sNames_);       TC_sNames_       = 0;
+  free(TC_sMass_);        TC_sMass_        = 0;
+  free(TC_elemcount_);    TC_elemcount_    = 0;
+  free(TC_sCharge_);      TC_sCharge_      = 0;
+  free(TC_sTfit_);        TC_sTfit_        = 0;
+  free(TC_sPhase_);       TC_sPhase_       = 0;
+  free(TC_Tlo_);          TC_Tlo_          = 0;
+  free(TC_Tmi_);          TC_Tmi_          = 0;
+  free(TC_Thi_);          TC_Thi_          = 0;
+  free(TC_cppol_);        TC_cppol_        = 0;
+  free(TC_sNion_);        TC_sNion_        = 0;
+  free(TC_isRev_);        TC_isRev_        = 0;
+  free(TC_reacNrp_);      TC_reacNrp_      = 0;
+  free(TC_reacNreac_);    TC_reacNreac_    = 0;
+  free(TC_reacNprod_);    TC_reacNprod_    = 0;
+  free(TC_reacNuki_);     TC_reacNuki_     = 0;
+  free(TC_reacNukiDbl_);  TC_reacNukiDbl_  = 0;
+  free(TC_reacSidx_);     TC_reacSidx_     = 0;
+  free(TC_reacScoef_);    TC_reacScoef_    = 0;
+  free(TC_reacArhenFor_); TC_reacArhenFor_ = 0;
+  free(TC_reacRev_);      TC_reacRev_      = 0;
+  free(TC_reacArhenRev_); TC_reacArhenRev_ = 0;
+  free(TC_reacPfal_);     TC_reacPfal_     = 0;
+  free(TC_reacPtype_);    TC_reacPtype_    = 0;
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_for.c

@@ -1,0 +1,833 @@
+
+int tcsplitfr_(char *mechfile, int *lmech, int *rlist) {
+  memset(&mechfile  [*lmech], 0, 1) ;
+  TC_splitFR(mechfile,rlist);
+  return (0);
+}
+
+/*
+    _____ ____     _        __
+   |_   _/ ___|   (_)_ __  / _| ___
+     | || |       | | '_ \| |_ / _ \
+     | || |___    | | | | |  _| (_) |
+     |_| \____|___|_|_| |_|_|  \___/
+             |_____|
+
+*/
+int tcgetnreac_() { return ( TC_getNreac() ) ; }
+int tcgetnpresdepreac_() { return ( TC_getNPresDepReac() ) ; }
+int tcgetnthbreac_() { return ( TC_getNThbReac() ) ; }
+
+int tcgetstoicoef_( int *Nspec, int *Nreac, double *stoicoef ) {
+  return (TC_getStoiCoef( *Nspec, *Nreac, stoicoef ) ) ;
+}
+int tcgetstoicoeffr_( int *Nspec, int *Nreac, double *stoicoef ) {
+  return ( TC_getStoiCoefFR( *Nspec, *Nreac, stoicoef ) ) ;
+}
+int tcgetstoicoefreac_( int *Nspec, int *Nreac, int *ireac, int *idx, double *stoicoef ) {
+  return ( TC_getStoiCoefReac( *Nspec, *Nreac, *ireac, *idx, stoicoef ) ) ;
+}
+int tcgetstoicoefij_( int *Nspec, int *Nreac, int *ireac, int *kspec, double *stoicoef ) {
+  return ( TC_getStoiCoefIJ( *Nspec, *Nreac, *ireac, *kspec, stoicoef ) );
+}
+
+int tcgetreacrev_(int *ireac)  { return ( TC_getReacRev(*ireac)  ) ; }
+int tcgetreacthb_(int *ireac)  { return ( TC_getReacThb(*ireac)  ) ; }
+int tcgetreaclow_(int *ireac)  { return ( TC_getReacLow(*ireac)  ) ; }
+int tcgetreachigh_(int *ireac) { return ( TC_getReacHIGH(*ireac) ) ; }
+
+int tcgetreacptype_(int *ireac) { return ( TC_getReacPtype(*ireac) ) ; }
+int tcgetthbreaceff_(int *ireac,int *specidx, double *effs) {
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_getthc9.c

@@ -1,0 +1,269 @@
+/* ------------------------------------------------------------------------- */
+/**
+ * \brief Reads thermodynamic properties (NASA polynomials) from the 
+ *        mechanism input file or from a separate file
+*/
+int TCKMI_readValidLine(FILE *filein, char* linein)
+{
+  int len1 = 0;
+  while ( (len1==0) && (feof(filein) == 0))
+  {
+    fgets(linein,200,filein) ;
+    TCKMI_cleancharstring(linein,&len1) ;
+  }
+  return ( 0 ) ;
+}
+int TCKMI_getthermo9(char *singleword, FILE *thermoin,
+              element *listelem,int *Nelem,species *listspec,int *Nspec,
+              int *ithermo,int *iread,int *ierror)
+{
+
+  char linein1[200],linein2[200],linein3[200] ;
+  double dtemp ;
+  int    itemp, Nth9rng, Nth9npow, pows[7] ;
+  FILE   *thermofile ;
+  int i, irng, ip, len1 ;
+
+  /* Exit if the error flag is not zero */
+  if ( *ierror > 0 ) return (1) ;
+
+  /* Exit if value of iread flag is not appropriate (4) */
+  if (*iread != 4) { (*ierror) = 300 ; return ( 1 ) ; }
+
+  /* Set up the input file */
+  thermofile = thermoin ;
+
+  /* Check if file pointer is null or if file is empty */
+  if ( thermofile == NULL  ) { (*ierror) = 320 ; return ( 1 ) ; }
+  if ( feof(thermofile) > 0) { (*ierror) = 338 ; return ( 1 ) ; }
+
+  len1 = 0 ;
+  while ( len1 == 0 )
+  {
+    /* Reading the first line in the file */
+    fgets(linein1,200,thermofile) ;
+    if ( feof(thermofile) > 0) { (*ierror) = 340 ; return ( 1 ) ; }
+    TCKMI_cleancharstring(linein1,&len1) ;
+  }
+
+  len1 = 0 ;
+  while (len1==0)
+  {
+    /* Reading the second line in the file, hopefully the temperature range */
+    fgets(linein1,200,thermofile) ;
+    if ( feof(thermofile) > 0) { (*ierror) = 342 ; return ( 1 ) ; }
+    TCKMI_cleancharstring(linein1,&len1) ;
+  }
+
+  /* Start reading properties */
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_info.c

@@ -1,0 +1,763 @@
+/*! \file TC_info.c
+ *  \brief Various functions providing info about the kinetic model
+ */ 
+
+/**
+ * \brief Returns number of reactions \f$N_{reac}\f$
+*/
+int TC_getNreac() { return ( TC_Nreac_ ) ; }   
+
+/**
+ * \brief Returns number of reactions with low/high pressure limit
+ * rate constants
+*/
+int TC_getNPresDepReac() { return ( TC_nFallReac_ ) ; }
+
+/**
+ * \brief Returns number of reactions with reaction rates enhanced 
+ * by third-body efficiencies
+*/
+int TC_getNThbReac() { return ( TC_nThbReac_ ) ; }
+
+/**
+ * \brief Returns number of reactions with reaction rates in PLOG format
+ */
+int TC_getNplogReac() { return ( TC_nPlogReac_ ) ; }
+
+
+/**
+ * \brief Returns 1 if a reaction is reversible, 0 otherwise
+*/
+int TC_getReacRev(int ireac) { return (TC_isRev_[ireac]) ; }
+
+/**
+ * \brief Returns 1 if a reaction employs third-body efficiencies, 0 otherwise
+*/
+int TC_getReacThb(int ireac) { 
+
+  int i, ithb ;
+
+  if ( TC_nThbReac_ <= 0 ) return (0);
+
+  ithb = 0;
+  for ( i=0; i<TC_nThbReac_; i++) {
+    if (TC_reacTbdy_[i] == ireac) {
+      ithb = 1; /* found match */
+      break ;
+    }
+  }
+  return (ithb) ;
+
+}
+
+/**
+ * \brief Returns 1 if a reaction is of "LOW" type, 0 otherwise
+*/
+int TC_getReacLow(int ireac) { 
+/**
+   \param ireac : reaction index
+*/
+
+  int i, ipfal;
+
+  if ( TC_nFallReac_ <= 0 ) return (0);
+
+  ipfal = 0;
+  for ( i=0; i<TC_nFallReac_; i++) {
+    if (TC_reacPfal_[i] == ireac) {
+      if (TC_reacPlohi_[i] == 0) ipfal = 1; /* found match, check if LOW */
+      break ;
+    }
+  }
+  return (ipfal) ;
+
+}
+
+/**
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_init.c

@@ -1,0 +1,1581 @@
+/*!
+ * \file TC_init.c
+ * \brief Initialize chemical library
+*/
+/**
+ * \ingroup init
+ * \brief Initialize library
+*/
+
+int icomp (const void * a, const void * b)
+{
+  return ( *(int*)a - *(int*)b );
+}
+int TC_initChem(char *mechfile,char *thermofile, int tab, double delT)
+{
+  /**
+    \param mechfile : name of file containing kinetic model in chemkin format
+    \param thermofile : name of file containing coefficients for NASA polynomials
+    \param tab : flag to tabulate temperature dependent terms (tab=1 -> create tables)
+    \param delT : temperature step size [K] for the tables; used only tab=1
+  */
+
+  /* loop variables */
+  int i, j, k, ir, ij ;
+
+  int  lmech, lthrm, ierr, itemp ;
+  double sml, reacbalance ;
+  char charvar4[4] ;
+
+  FILE *chemfile, *echofile, *errfile ;
+
+  /* zero-out variables */
+  TC_isInit_   = 0 ;
+  TC_pressure_ = 0.0 ;
+  TC_prescgs_  = 0.0 ;
+  TC_rho_      = 0.0 ;
+  TC_rhocgs_   = 0.0 ;
+  TC_rhoset_   = 0   ;
+  TC_Runiv_    = 0.0 ;
+  TC_Rcal_     = 0.0 ;
+  TC_Rcgs_     = 0.0 ;
+
+  /* integers */
+  TC_Nvars_ = TC_Nvjac_ = 0 ;
+  TC_maxSpecInReac_ = TC_maxTbInReac_ = TC_nNASAinter_ = TC_nCpCoef_ = TC_nArhPar_ = TC_nLtPar_ = 0 ;
+  TC_nFallPar_ = TC_nJanPar_ = TC_maxOrdPar_ = TC_nFit1Par_  = 0;
+  TC_Nelem_ = TC_Nspec_ = TC_Nreac_ = TC_nRevReac_ = TC_nFallReac_ = TC_nPlogReac_ = TC_nThbReac_ = 0 ;
+  TC_nLtReac_ = TC_nRltReac_ = TC_nHvReac_  = TC_nIonSpec_ = TC_nJanReac_ = TC_nFit1Reac_ = 0 ;
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_jac.c

@@ -1,0 +1,1242 @@
+/*! \file TC_src.c
+ *    \brief Jacobian functions
+ */
+
+/*
+           _                 _     _                 
+          | | __ _  ___ ___ | |__ (_) __ _ _ __  ___ 
+       _  | |/ _` |/ __/ _ \| '_ \| |/ _` | '_ \/ __|
+      | |_| | (_| | (_| (_) | |_) | | (_| | | | \__ \
+       \___/ \__,_|\___\___/|_.__/|_|\__,_|_| |_|___/
+
+ */
+/**
+ * \ingroup jacs
+ * \brief Computes analytical Jacobian for the system 
+ * \f$(T,Y_1,Y_2,\ldots,Y_{N-1})\f$ 
+ * based on T and Y's
+ */
+int TC_getJacTYNm1anl(double *scal, int Nspec, double *jac)
+{
+/**
+ *   \param scal : array of \f$N_{spec}+1\f$ doubles \f$(T,Y_1,Y_2,...,Y_{N_{spec}})\f$
+ *                 temperature T [K], mass fractions Y [] 
+ *  \param Nspec : no. of species \f$N_{spec}\f$ 
+ *  \return jac  : Jacobian array 
+ */
+
+  int ans, i, k, iJacR,iJacF ;
+  double rhomix, Wmix, drhodT, *Yspec ;
+
+  if ( Nspec != TC_Nspec_ ) 
+    TC_errorMSG( 10, "TC_getJacTYNm1anl", Nspec, TC_Nspec_ ) ;
+
+  ans   = 0 ;
+  Yspec = &scal[1] ;
+
+  /* first, get full Jacobian */
+  ans = TC_getJacRPTYNanl(scal, Nspec, TC_jacFull) ;
+  if ( ans != 0 ) return ( ans ) ;
+
+  /* assemble reduced Jacobian */
+  ans = TC_getRhoMixMs(  scal, TC_Nvars_, &rhomix ) ;
+  if ( ans != 0 ) return ( ans ) ;
+  ans = TC_getMs2Wmix ( Yspec, TC_Nspec_, &Wmix   ) ;
+  if ( ans != 0 ) return ( ans ) ;
+
+  /* first column */
+  drhodT = -rhomix/scal[0] ;
+  for ( i = 0, iJacR=0, iJacF = TC_Nvjac_*2 ; 
+	i < Nspec ; 
+	i++,iJacR++,iJacF+=TC_Nvjac_ )
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_kmodint.c

@@ -1,0 +1,6007 @@
+/*! \file TC_kmodint.c
+
+    \brief Collection of functions used to parse kinetic models from files
+
+    \details
+
+       TC_kmodint - utility used to parse kinetic models
+       ----------------------------------------------
+
+       Usage: TC_kmodint_(char *mechfile,int *lmech,char *thermofile,int *lthrm)
+       <ul>
+       <li> mechfile: file containing the kinetic model
+       <li> lmech: length of the character string above (introduced to
+                    enable passing of character strings from Fortran to C)
+       <li> thermofile: file containing thermodynamic properties (NASA polynomials)
+       <li> lmech: length of the character string thermofile (introduced to
+                    enable passing of character strings from Fortran to C)
+       </ul>
+       Output:
+       <ul>
+       <li>kmod.out - ascii file containing kinetic model info formatted
+                      for visual inspection
+       <li>kmod.list - ascii file containing unformatted data for tchem
+       </ul>
+
+       <b> Brief description of kinetic model input format  </b>
+       ( For a detailed description of the kinetic model format and keywords see:
+       Robert J. Kee, Fran M. Rupley, Ellen Meeks, and James A. Miller
+       "CHEMKIN-III:A Fortran Chemical Kinetics Package for the Analysis of Gas-phase
+       Chemical and Pllasma Kinetics", Sandia Report, SAND96-8216, (1996) )
+
+       \b Elements :
+                 - Number of elements is "unlimited"
+                 - Elements not present in file periodictable.dat must
+                     be followed by their atomic weight, e.g.
+                     N+ /14.0010/
+                 - Element names are one or two characters long
+                 - Any duplicate listing of an element is ignored
+
+       \b Species :
+                 - Number of species is "unlimited"
+                 - Species need to be formed only of elements declared in the
+                     list of elements
+                 - Species names are "LENGTHOFSPECNAME" characters long
+                 - Any duplicate listing of an species is ignored
+                 - A species can contain at most "NUMBEROFELEMINSPEC"
+                     distinct elements
+
+       <b> Thermodynamic data </b>:
+                 - Data can be provided in the kinetic model file and/or
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_mlms.c

@@ -1,0 +1,352 @@
+/*! \file TC_mlms.c
+    \brief Mass fractions - Mole fractions - Molar concetrations - Molecular weight
+*/ 
+
+/*
+                 _   __  __     ____   ____     
+       __ _  ___| |_|  \/  |___|___ \ / ___|___ 
+      / _` |/ _ \ __| |\/| / __| __) | |   / __|
+     | (_| |  __/ |_| |  | \__ \/ __/| |__| (__ 
+      \__, |\___|\__|_|  |_|___/_____|\____\___|
+      |___/                                     
+
+*/
+/**
+ * \brief Computes molar concentrations based on temperature and species mass fractions. 
+ *        Input temperature is normalized, output concentrations are also normalized before exit.
+ *        \f[ \overline{[X_k]}=[X_k]\cdot\frac{W_{ref}}{\rho_{ref}}=Y_k\cdot\frac{\rho}{W_k}\cdot\frac{W_{ref}}{\rho_{ref}} \f]
+ */
+int TCDND_getMs2Cc(double *scal,int Nvars,double *concX)
+{
+/**
+  \param scal : array of N<sub>spec</sub>+1 doubles (T,Y<sub>1</sub>,Y<sub>2</sub>,...,Y<sub>Nspec</sub>), temperature T [K], mass fractions Y [] 
+  \param Nvars : no. of variables = N<sub>spec</sub>+1 
+  \return concX : array of doubles containing species molar concentrations [kmol/m<sup>3</sup>]
+*/
+
+  int ans, i ;
+
+  if ( Nvars != TC_Nvars_ )
+  {
+    printf("TCDND_getMs2Cc() : disagreement in Nvars : %d vs %d\n",Nvars,TC_Nvars_) ;
+    printf("                   -> Abort !!!\n") ;
+    exit(1) ;
+  }
+
+  if ( TC_nonDim_ == 1 ) scal[0] *= TC_Tref_ ;
+
+  ans = TC_getMs2Cc(scal,Nvars,concX) ;
+
+  if ( TC_nonDim_ == 1 ) 
+  {
+    double makeND = TC_Wref_ / TC_rhoref_ ;
+    scal[0] /= TC_Tref_ ;
+    for ( i = 0 ; i < TC_Nspec_ ; i++ ) concX[i] *= makeND ;
+  }
+
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_reduce.cpp

@@ -1,0 +1,815 @@
+#include "stdlib.h"
+#include <iostream>
+#include <fstream>
+#include <algorithm>
+#include <vector>
+#include <cstring>
+#include <boost/algorithm/string.hpp>
+
+using namespace boost::algorithm;
+using namespace std;
+using std::ifstream;
+
+const int MAX_CHARS_PER_LINE = 1024;
+
+/* 
+  Local functions 
+*/
+
+/* Parse a text file into a vector of strings, with each line as a
+   separate string */
+void getTextFile(char *filein, vector<string> &ftext) ;
+/* Determine the start line and end line for a specific section in a
+   kinetic model */
+void getSection(vector<string> mech, string sname, int *sst, int *sen) ;
+
+void getReacLines(vector<string> mech, int rst, int ren, vector<int> &reacIdx) ;
+
+void checkSpecInList(string sline, vector<string> specDelList, vector<string> &validSpec) ;
+
+void checkSpecInMech(vector<string> &mechfile, vector<int> reacIdx, vector<int> reacFR, 
+		     int ispec, vector<string> &specList, vector<string> &delList) ;
+
+void getReacString(string reacline, vector<string> &rcomp) ;
+
+bool checkValidReac(vector<string> mechfile, int ireac, vector<string> specDelList) ;
+
+string delSpecFromReac(string mline, vector<string> specDelList) ;
+
+bool isSpecInVecStr(vector<string> rcomp, vector<string> specDelList) ;
+
+bool isSpecNameInVecStr(string rcomp, vector<string> specDelList) ;
+
+/* Returns the position of the first upper case letter in a string */
+size_t firstCap(string strin);
+
+void checkDup(vector<string> mechfile, vector<int> reacIdx, vector<int> reacFR, 
+              vector<int> &reacDup);
+
+#ifdef __cplusplus
+extern "C" {
+#endif
+
+void TC_reduce (char *mechIn, char *slist, char *mechOut) ;
+void TC_splitFR(char *minp, int *rlist) ;
+int  TC_parseFG(char *minp);
+
+#ifdef __cplusplus
+}
+#endif
+
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_rr.c

@@ -1,0 +1,2223 @@
+/*! \file TC_rr.c
+ *  \brief Reaction rate functions
+ */
+/* #define DEBUGMSG */
+
+/*
+    ______                _   _              ______      _
+    | ___ \              | | (_)             | ___ \    | |
+    | |_/ /___  __ _  ___| |_ _  ___  _ __   | |_/ /__ _| |_ ___  ___
+    |    // _ \/ _` |/ __| __| |/ _ \| '_ \  |    // _` | __/ _ \/ __|
+    | |\ \  __/ (_| | (__| |_| | (_) | | | | | |\ \ (_| | ||  __/\__ \
+    \_| \_\___|\__,_|\___|\__|_|\___/|_| |_| \_| \_\__,_|\__\___||___/
+*/
+
+/**
+   \brief Returns forward and reverse rate constants for all reactions
+   at a specified temperature
+*/
+int TC_getkFR(double t, double *kF, double *kR)
+{
+
+  int i, ans ;
+
+  double t_1, tln;
+  t_1 = 1.0/t;
+  tln = log(t) ;
+
+  /* compute (-ln(T)+dS/R-dH/RT) for each species */
+  ans = TC_getgk(t,t_1,tln) ;
+
+  /* compute forward and reverse rate constants */
+  ans = TC_getkForRev(t,t_1,tln) ;
+
+  for ( i = 0 ; i<TC_Nreac_; i++) kF[i] = TC_kfor[i] ;
+  for ( i = 0 ; i<TC_Nreac_; i++) kR[i] = TC_krev[i] ;
+
+  return (ans) ;
+
+}
+
+/**
+ \brief Returns forward and reverse rate constants for all reactions
+ at a specified temperature
+ */
+int TC_getkFRp(double t, double *kF, double *kR)
+{
+
+  int i, ans ;
+
+  double t_1, tln;
+  t_1 = 1.0/t;
+  tln = log(t) ;
+
+  /* compute (-ln(T)+dS/R-dH/RT) for each species */
+  ans = TC_getgkp(t,t_1,tln) ;
+
+  /* compute forward and reverse rate constants */
+  ans = TC_getkForRevPFcn(t_1) ;
+
+  for ( i = 0 ; i<TC_Nreac_; i++) kF[i] = TC_kforP[i] ;
+  for ( i = 0 ; i<TC_Nreac_; i++) kR[i] = TC_krevP[i] ;
+
+  return (ans) ;
+
+}
+
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_spec.c

@@ -1,0 +1,178 @@
+/*! \file TC_spec.c
+    \brief Species info
+*/ 
+/*
+	            _   _   _      
+	  __ _  ___| |_| \ | |_/\__
+	 / _` |/ _ \ __|  \| \    /
+	| (_| |  __/ |_| |\  /_  _\
+	 \__, |\___|\__|_| \_| \/  
+	 |___/                     
+*/
+/**
+  \brief Returns no. of species N<sub>spec</sub>
+*/
+int TC_getNspec() { return ( TC_Nspec_ ) ; }
+
+/**
+  \brief Returns no. of elements N<sub>elem</sub>
+*/
+int TC_getNelem() { return ( TC_Nelem_ ) ; }
+
+/**
+  \brief Returns no. of variables (N<sub>spec</sub>+1)
+*/
+int TC_getNvars() { return ( TC_Nvars_ ) ; }
+
+/*
+                 _   ____                                  
+       __ _  ___| |_/ ___| _ __   __ _ _ __ ___   ___  ___ 
+      / _` |/ _ \ __\___ \| '_ \ / _` | '_ ` _ \ / _ \/ __|
+     | (_| |  __/ |_ ___) | | | | (_| | | | | | |  __/\__ \
+      \__, |\___|\__|____/|_| |_|\__,_|_| |_| |_|\___||___/
+      |___/                                                
+*/
+/**
+  \brief Returns species names 
+*/
+int TC_getSnames(int Nspec,char *snames)
+{
+/**
+  \param Nspec : no. of species 
+  \return snames: array of characters containing species names, each name 
+                  is LENGTHOFSPECNAME characters
+*/
+
+  if ( Nspec != TC_Nspec_ )
+  {
+    printf("Error : TC_getSnames - disagreement in the number of species : %d vs %d\n",
+	   Nspec, TC_Nspec_ ) ;
+    exit( -1 ) ;
+  }
+
+  memcpy( snames, TC_sNames_, LENGTHOFSPECNAME * TC_Nspec_ *sizeof(char)) ;
+  
+  return ( 0 ) ;
+  
+}
+
+/**
+  \brief Returns element names 
+*/
+int TC_getEnames(int Nelem,char *enames)
+{
+/**
+  \param Nspec : no. of species 
+  \return snames: array of characters containing species names, each name 
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_src.c

@@ -1,0 +1,510 @@
+/*! \file TC_src.c
+ *    \brief Source term and Jacobian functions
+ */
+
+/*
+      _____              _
+     /  ___|            | |
+     \ `--. _ __ ___    | |_ ___ _ __ _ __ ___  ___
+      `--. \ '__/ __|   | __/ _ \ '__| '_ ` _ \/ __|
+     /\__/ / | | (__ _  | ||  __/ |  | | | | | \__ \
+     \____/|_|  \___(_)  \__\___|_|  |_| |_| |_|___/
+
+*/
+/*
+                          _   ____
+                __ _  ___| |_/ ___| _ __ ___
+               / _` |/ _ \ __\___ \| '__/ __|
+              | (_| |  __/ |_ ___) | | | (__
+               \__, |\___|\__|____/|_|  \___|
+               |___/
+
+*/
+/**
+ * \ingroup srcs
+ * \brief Returns source term for
+ * \f[\frac{\partial T}{\partial t}=\omega_0,\frac{\partial Y_i}{\partial t}=\omega_i,\f]
+ *  based on temperature T and species mass fractions Y's
+ */
+//#define DEBUGMSG
+
+int TC_getSrc(double *scal,int Nvars,double *omega)
+{
+
+/**
+   \param scal : array of Nspec+1 doubles \f$(T,Y_1,Y_2,...,Y_{N_{spec}})\f$
+	        temperature T [K], mass fractions Y []
+   \param Nvars : no. of variables \f$ N_{vars}= N_{spec}+1\f$
+   \return omega : array of N<sub>spec</sub>+1 source terms for temperature and species
+                   mass fractions: omega[0] : [(K/s)], omega[1...N<sub>spec</sub>] : [(1/s)]
+*/
+
+  int i, ans ;
+  double temperature, *Yspec, *omegaspec, rhomix, orho, cpmix ;
+
+  if ( Nvars != TC_Nvars_ )
+    TC_errorMSG( 20, "TC_getSrc", Nvars, TC_Nvars_ ) ;
+
+  ans         = 0 ;
+  temperature =  scal[0] ;
+  Yspec       = &scal[1] ;
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_thermo.c

@@ -1,0 +1,1775 @@
+/*! \file TC_thermo.c
+    \brief Equation of state and thermodynamic functions
+*/
+/*
+                  _   ____  _           __  __ _
+        __ _  ___| |_|  _ \| |__   ___ |  \/  (_)_  __
+       / _` |/ _ \ __| |_) | '_ \ / _ \| |\/| | \ \/ /
+      | (_| |  __/ |_|  _ <| | | | (_) | |  | | |>  <
+       \__, |\___|\__|_| \_\_| |_|\___/|_|  |_|_/_/\_\
+       |___/
+
+*/
+/**
+ * \ingroup eqstate
+ * \brief Computes density based on temperature and species mass fractions using the equation of state.
+ * Input temperature is normalized, output density also normalized before exit.
+*/
+int TCDND_getRhoMixMs(double *scal,int Nvars,double *rhomix)
+{
+/**
+   \param scal : array of N<sub>spec</sub>+1 doubles (T,Y<sub>1</sub>,Y<sub>2</sub>,...,Y<sub>Nspec</sub>),
+                 temperature T [K], mass fractions Y []
+   \param Nvars : no. of variables = N<sub>spec</sub>+1
+   \return rhomix : pointer to mixture density [kg/m<sup>3</sup>]
+*/
+
+  int ans ;
+
+  if ( Nvars != TC_Nvars_ )
+    TC_errorMSG( 20, "TCDND_getRhoMixMs", Nvars, TC_Nvars_ ) ;
+
+  if ( TC_nonDim_ == 1 ) scal[0] *= TC_Tref_ ;
+
+  ans = TC_getRhoMixMs(scal, Nvars, rhomix) ;
+
+  if ( TC_nonDim_ == 1 )
+  {
+    *rhomix /= TC_rhoref_ ;
+    scal[0] /= TC_Tref_   ;
+  }
+
+  return ( ans ) ;
+
+}
+/**
+ * \ingroup eqstate
+ * \brief Computes density based on temperature and species mass fractions using the equation of state.
+ */
+int TC_getRhoMixMs( double *scal, int Nvars, double *rhomix)
+{
+/**
+  \param scal : array of N<sub>spec</sub>+1 doubles (T,Y<sub>1</sub>,Y<sub>2</sub>,...,Y<sub>Nspec</sub>),
[…]

### 2018-06-11 Codes/Kinetics/TChem/src/TC_utils.c

@@ -1,0 +1,36 @@
+/*! \file TC_utils.c
+ *  \brief Various utilities used by other functions
+ */ 
+/** 
+ * \brief Much faster version of pow for small integers 
+ *  (considering that reactions are generally no more than 3rd order).
+ *  The C version of pow requires a double exponent; pow is the slowest part of the 
+ *  code when used instead of fastIntPow. 
+ */
+static double fastIntPow(double val, int exponent)
+{
+  switch(exponent)
+  {
+    case 0:
+      return ( 1.0 );
+    case 1:
+      return ( val );
+    case 2:
+      return ( val*val );
+    case 3:
+      return ( val*val*val );
+    case 4:
+      return ( val*val*val*val );
+    case 5:
+      return ( val*val*val*val*val );
+    case -1:
+      return ( 1.0/val );
+    case -2:
+      return ( 1.0/(val*val) );
+    case -3:
+      return ( 1.0/(val*val*val) );
+    default:
+      return ( pow(val,exponent) );
+  }
+}
+

### 2018-06-11 Codes/Kinetics/TChem/step1.sh

@@ -1,0 +1,3 @@
+./configure CC=/usr/bin/gcc       \
+                   CXX=/usr/bin/g++      \
+                   F77=/usr/bin/gfortran    

### 2018-06-11 Codes/Kinetics/TChem/step4.sh

@@ -1,0 +1,8 @@
+./configure CC=/usr/bin/gcc                   \
+                   CXX=/usr/bin/g++                  \
+                   F77=/usr/bin/gfortran             \
+                   --with-examples=yes                                      \
+                   --with-sundials-dir=$PWD/lib/cvode-2.7.0-install         \
+                   --with-dvode-dir=$PWD/lib                                \
+                   --with-boost-dir=/usr/lib/x86_64-linux-gnu
+

### 2018-06-11 Codes/Kinetics/compute_dgsm.m

@@ -1,0 +1,47 @@
+close all;
+clear all;
+
+dim = 19;
+L = zeros(1,dim); U = zeros(1,dim); dX = zeros(1,dim);
+pc = zeros(1,dim); mu = zeros(1,dim); ub = zeros(1,dim);
+id_data_rng10 = load('record_id_rng10.txt');
+id_data_rng20 = load('record_id_rng20.txt');
+id_data_rng30 = load('record_id_rng30.txt');
+id_data_rng40 = load('record_id_rng40.txt');
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1,:) = 0.9.*nom(1,:); U(1,:) = 1.1.*nom(1,:);
+
+for j = 1:dim
+  dX(1,j) = 1e-3.*(U(1,j) - L(1,j));
+  pc(1,j) = ((U(1,j)-L(1,j)).^2)./(pi.^2);
+end
+
+nsams = 20;
+G = zeros(nsams,1); Gdx = zeros(nsams,dim);
+G(1:5,1) = id_data_rng10(1:5,1);
+G(6:10,1) = id_data_rng20(1:5,1);
+G(11:15,1) = id_data_rng30(1:5,1);
+G(16:20,1) = id_data_rng40(1:5,1);
+%save('id_7D_20pts.dat','G','-ASCII')
+
+for j = 1:dim
+  Gdx(1:5,j) = id_data_rng10(j*5+1:(j+1)*5,1);
+  Gdx(6:10,j) = id_data_rng20(j*5+1:(j+1)*5,1);
+  Gdx(11:15,j) = id_data_rng30(j*5+1:(j+1)*5,1);
+  Gdx(16:20,j) = id_data_rng40(j*5+1:(j+1)*5,1);
+  dGdx = (Gdx(:,j) - G(:,1))./dX(1,j);
+  dGdx2 = dGdx.^2;
+  T = sum(dGdx2);
+  mu(1,j) = T./nsams;
+  ub(1,j) = pc(1,j).*mu(1,j);
+end
+
+ub(1,1:dim) = ub(1,1:dim)./sum(ub);
[…]

### 2018-06-11 Codes/Kinetics/gen_plots.m

@@ -1,0 +1,62 @@
+close all
+clear all
+
+%plot_ub();
+
+%function pub = plot_ub()
+ub5 = load('new_lean_mix/ub5.mat');
+ub10 = load('new_lean_mix/ub10.mat');
+ub15 = load('new_lean_mix/ub15.mat');
+ub20 = load('new_lean_mix/ub20.mat');
+mu5 = load('new_lean_mix/mu5.mat');
+mu10 = load('new_lean_mix/mu10.mat');
+mu15 = load('new_lean_mix/mu15.mat');
+mu20 = load('new_lean_mix/mu20.mat');
+xp = linspace(1,19,19);
+
+figure;
+hold on;
+h = plot(xp,ub5.ub,'--o','MarkerFaceColor','r');
+plot(xp,ub10.ub,'--o','MarkerFaceColor','b');
+plot(xp,ub15.ub,'--o','MarkerFaceColor','g');
+plot(xp,ub20.ub,'--o','MarkerFaceColor','k');
+xticklabels({'$\mathrm{A_1}$','$\mathrm{A_2}$','$\mathrm{A_3}$','$\mathrm{A_4}$',...
+             '$\mathrm{A_5}$','$\mathrm{A_6}$','$\mathrm{A_7}$','$\mathrm{A_8}$',...
+             '$\mathrm{A_9}$','$\mathrm{A_{10}}$','$\mathrm{A_{11}}$','$\mathrm{A_{12}}$',...
+             '$\mathrm{A_{13}}$','$\mathrm{A_{14}}$','$\mathrm{A_{15}}$','$\mathrm{A_{16}}$',...
+             '$\mathrm{A_{17}}$','$\mathrm{A_{18}}$','$\mathrm{A_{19}}$'});
+set(gca,'xtick',1:19,'fontsize',10,'TickLabelInterpreter','latex');
+ax = ancestor(h, 'axes');
+yrule = ax.YAxis;
+yrule.FontSize = 16;
+xlabel('$$\mathrm{Parameter}$$','interpreter','latex','fontsize',20);
+ylabel('$$\mathrm{\widehat{\mathcal{C}_i\mu_i}}$$','interpreter','latex','fontsize',20);
+set(gcf,'color',[1,1,1]);
+leg = legend({'$\mathrm{N~=~5}$','$\mathrm{N~=~10}$','$\mathrm{N~=~15}$',...
+              '$\mathrm{N~=~20}$','location','best'});
[…]

### 2018-06-11 Codes/Kinetics/gen_samples.m

@@ -1,0 +1,35 @@
+close all;
+clear all;
+rng(40);
+
+dim = 19;
+L = zeros(1,dim); U = zeros(1,dim); dX = zeros(1,dim);
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1,:) = 0.9.*nom(1,:); U(1,:) = 1.1.*nom(1,:);
+nsams = 10; pts = zeros(nsams*(dim+1),dim);
+
+for j = 1:dim
+  pts(1:nsams,j) = unifrnd(L(1,j),U(1,j),nsams,1);
+  dX(1,j) = 1e-3.*(U(1,j) - L(1,j));
+end
+
+for i = 1:dim
+  pts(i*nsams+1:(i+1)*nsams,:) = pts(1:nsams,:);
+  pts(i*nsams+1:(i+1)*nsams,i) = pts(i*nsams+1:(i+1)*nsams,i) + dX(1,i);
+end
+
+f1 = fopen('pts_pce19D_10.txt','w');
+%fmt = '%15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f\n';
+fmt = '%10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e\n';
+
+for i = 1:nsams*(dim+1)
+  fprintf(f1,fmt,pts(i,1),pts(i,2),pts(i,3),pts(i,4),pts(i,5),pts(i,6),pts(i,7),pts(i,8),pts(i,9),pts(i,10),pts(i,11),pts(i,12),pts(i,13),pts(i,14),pts(i,15),pts(i,16),pts(i,17),pts(i,18),pts(i,19));
+end
+
+fclose(f1);

### 2018-06-11 Codes/Kinetics/gen_samples_pdf.m

@@ -1,0 +1,30 @@
+close all;
+clear all;
+rng(100);
+
+dim = 19;
+L = zeros(1,dim); U = zeros(1,dim); 
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1,:) = 0.9.*nom(1,:); U(1,:) = 1.1.*nom(1,:);
+nsams = 1000; pts = zeros(nsams,dim);
+
+% Generate 50 samples in the 19D space
+for j = 1:dim
+  pts(1:nsams,j) = unifrnd(L(1,j),U(1,j),nsams,1);
+end
+
+f1 = fopen('pts_val.txt','w');
+%fmt = '%15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f\n';
+fmt = '%10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e\n';
+
+for i = 1:nsams
+  fprintf(f1,fmt,pts(i,1),pts(i,2),pts(i,3),pts(i,4),pts(i,5),pts(i,6),pts(i,7),pts(i,8),pts(i,9),pts(i,10),pts(i,11),pts(i,12),pts(i,13),pts(i,14),pts(i,15),pts(i,16),pts(i,17),pts(i,18),pts(i,19));
+end
+
+fclose(f1);

### 2018-06-11 Codes/Kinetics/new_lean_mix/PCE3D/build_pce.m

@@ -1,0 +1,83 @@
+close all
+clearvars
+uqlab
+
+% Input data
+X = dlmread(fullfile('pts_pce3D_3D.dat')) ;
+Y = dlmread(fullfile('record_id_pce3D.dat')) ;
+MetaOpts.ExpDesign.X = X;
+MetaOpts.ExpDesign.Y = Y;
+
+L = [1.7235e14 5.5530e19 1.082e17];
+U = [2.1065e14 6.7870e19 1.322e17];
+
+nom = [1.915e14 6.170e19 1.202e17];
+
+for ii = 1:3
+    IOpts.Marginals(ii).Type = 'Uniform';
+    IOpts.Marginals(ii).Parameters = [L(ii), U(ii)];
+end
+
+my_Input = uq_createInput(IOpts);
+
+% Set-up PCE
+MetaOpts.Type = 'Metamodel';
+MetaOpts.MetaType = 'PCE';
+MetaOpts.Degree = 1:30;
+MetaOpts.Method = 'LARS';
+
+myPCE = uq_createModel(MetaOpts);
+uq_print(myPCE);
+
+nsams = 1000;
+qoi = load('record_id_val.txt');
+E1 = verify_L2(nsams,qoi);
+save('rel_L2.txt','E1','-ASCII');
+verify_pdf(qoi,L,U);
+%
+%% Function Definitions
+function errl = verify_L2(nsams,qoi)
+pts = load('pts_val.txt');
+pts3D = zeros(nsams,3);
+pts3D(:,1) = pts(:,1); pts3D(:,2) = pts(:,9);
+pts3D(:,3) = pts(:,15);
+
+Y_PCE = uq_evalModel(pts3D);
+Y_Model = qoi;
+NR = sum(((Y_Model-Y_PCE).^2)).^(0.5);
+DR = sum((Y_Model.^2)).^(0.5);
+errl = double(NR)./double(DR);
+end
+%
+function errp = verify_pdf(qoi,L,U)
+pts = zeros(1e6,3);
+pts(:,1) = unifrnd(L(1),U(1),1e6,1);
+pts(:,2) = unifrnd(L(2),U(2),1e6,1);
+pts(:,3) = unifrnd(L(3),U(3),1e6,1);
+
+Y_PCE = uq_evalModel(pts);
+Y_Model = qoi;
+step = (max(Y_PCE) - min(Y_PCE)).*(1e-4);
+pts_PCE = 0.95.*min(Y_PCE):step:1.05.*max(Y_PCE);
[…]

### 2018-06-11 Codes/Kinetics/new_lean_mix/PCE3D/gen_samples3D.m

@@ -1,0 +1,46 @@
+close all;
+clear all;
+rng(50);
+
+dim = 3;
+L = zeros(1,dim); U = zeros(1,dim);
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1) = 0.9.*nom(1); U(1) = 1.1.*nom(1);
+L(2) = 0.9.*nom(9); U(2) = 1.1.*nom(9);
+L(3) = 0.9.*nom(15); U(3) = 1.1.*nom(15);
+
+nsams = 100; pts = zeros(nsams,19);
+
+pts(:,1) = unifrnd(L(1),U(1),nsams,1);
+pts(:,9) = unifrnd(L(2),U(2),nsams,1);
+pts(:,15) = unifrnd(L(3),U(3),nsams,1);
+
+for j = 2:8
+  pts(:,j) = nom(j);
+end
+
+for j = 10:14
+  pts(:,j) = nom(j);
+end
+
+for j = 16:19
+  pts(:,j) = nom(j);
+end
+
+%save('pts_pce2D.mat','pts');
+
+f1 = fopen('pts_pce3D.txt','w');
+%fmt = '%15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f\n';
+fmt = '%10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e\n';
+
+for i = 1:nsams
+  fprintf(f1,fmt,pts(i,1),pts(i,2),pts(i,3),pts(i,4),pts(i,5),pts(i,6),pts(i,7),pts(i,8),pts(i,9),pts(i,10),pts(i,11),pts(i,12),pts(i,13),pts(i,14),pts(i,15),pts(i,16),pts(i,17),pts(i,18),pts(i,19));
+end
+
+fclose(f1);

### 2018-06-11 Codes/Kinetics/new_lean_mix/PCE3D/gen_smooth.m

@@ -1,0 +1,63 @@
+close all;
+clear all;
+rng(50);
+
+dim = 2;
+L = zeros(1,dim); U = zeros(1,dim);
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1) = 0.9.*nom(1); U(1) = 1.1.*nom(1);
+L(2) = 0.9.*nom(9); U(2) = 1.1.*nom(9);
+
+nsams = 100; pts = zeros(nsams,19);
+
+x = linspace(L(1),U(1),10);
+y = linspace(L(2),U(2),10);
+
+[X,Y] = meshgrid(x,y);
+
+f1 = fopen('pts_smooth_rich.txt','w');
+fmt = '%10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e\n';
+
+for j = 2:8
+  pts(:,j) = nom(j);
+end
+
+for j = 10:19
+  pts(:,j) = nom(j);
+end
+
+c = 1;
+for j = 1:10
+  for i = 1:10
+   pts(c,1) = X(j,i);
+   pts(c,9) = Y(j,i);
+   fprintf(f1,fmt,pts(c,1),pts(c,2),pts(c,3),pts(c,4),pts(c,5),pts(c,6),pts(c,7),pts(c,8),pts(c,9),pts(c,10),pts(c,11),pts(c,12),pts(c,13),pts(c,14),pts(c,15),pts(c,16),pts(c,17),pts(c,18),pts(c,19));
+   c = c + 1;    
+  end
+end
+
+fclose(f1);
+
+ig = load('record_id_smooth_rich.txt');
+ig_surf = reshape(ig,size(X));
+save('X.mat','X');
+save('Y.mat','Y');
+save('ig_surf.mat','ig_surf');
+
+figure;
+pcolor(X,Y,ig_surf);
+shading interp;
+%surf(X,Y,ig_surf);
+c = colorbar();
[…]

### 2018-06-11 Codes/Kinetics/new_rich_mix/PCE4D/build_pce.m

@@ -1,0 +1,84 @@
+close all
+clearvars
+uqlab
+
+% Input data
+X = dlmread(fullfile('pts_pce4D_4D.dat')) ;
+Y = dlmread(fullfile('record_id_pce4D_19D.dat')) ;
+MetaOpts.ExpDesign.X = X;
+MetaOpts.ExpDesign.Y = Y;
+
+L = [1.7235e14 5.5530e19 1.082e17 4.338e13];
+U = [2.1065e14 6.7870e19 1.322e17 5.302e13];
+
+nom = [1.915e14 6.170e19 1.202e17 4.820e13];
+
+for ii = 1:4
+    IOpts.Marginals(ii).Type = 'Uniform';
+    IOpts.Marginals(ii).Parameters = [L(ii), U(ii)];
+end
+
+my_Input = uq_createInput(IOpts);
+
+% Set-up PCE
+MetaOpts.Type = 'Metamodel';
+MetaOpts.MetaType = 'PCE';
+MetaOpts.Degree = 1:30;
+MetaOpts.Method = 'LARS';
+
+myPCE = uq_createModel(MetaOpts);
+uq_print(myPCE);
+
+nsams = 1000;
+qoi = load('record_id_val.txt');
+E1 = verify_L2(nsams,qoi);
+save('rel_L2.txt','E1','-ASCII');
+verify_pdf(qoi,L,U);
+%
+%% Function Definitions
+function errl = verify_L2(nsams,qoi)
+pts = load('pts_val.txt');
+pts4D = zeros(nsams,4);
+pts4D(:,1) = pts(:,1); pts4D(:,2) = pts(:,9);
+pts4D(:,3) = pts(:,15); pts4D(:,4) = pts(:,17);
+
+Y_PCE = uq_evalModel(pts4D);
+Y_Model = qoi;
+NR = sum(((Y_Model-Y_PCE).^2)).^(0.5);
+DR = sum((Y_Model.^2)).^(0.5);
+errl = double(NR)./double(DR);
+end
+%
+function errp = verify_pdf(qoi,L,U)
+pts = zeros(1e6,4);
+pts(:,1) = unifrnd(L(1),U(1),1e6,1);
+pts(:,2) = unifrnd(L(2),U(2),1e6,1);
+pts(:,3) = unifrnd(L(3),U(3),1e6,1);
+pts(:,4) = unifrnd(L(4),U(4),1e6,1);
+
+Y_PCE = uq_evalModel(pts);
+Y_Model = qoi;
[…]

### 2018-06-11 Codes/Kinetics/new_rich_mix/PCE4D/gen_samples4D.m

@@ -1,0 +1,50 @@
+close all;
+clear all;
+rng(50);
+
+dim = 4;
+L = zeros(1,dim); U = zeros(1,dim);
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1) = 0.9.*nom(1); U(1) = 1.1.*nom(1);
+L(2) = 0.9.*nom(9); U(2) = 1.1.*nom(9);
+L(3) = 0.9.*nom(15); U(3) = 1.1.*nom(15);
+L(4) = 0.9.*nom(17); U(4) = 1.1.*nom(17);
+
+nsams = 100; pts = zeros(nsams,19);
+
+pts(:,1) = unifrnd(L(1),U(1),nsams,1);
+pts(:,9) = unifrnd(L(2),U(2),nsams,1);
+pts(:,15) = unifrnd(L(3),U(3),nsams,1);
+pts(:,17) = unifrnd(L(4),U(4),nsams,1);
+
+for j = 2:8
+  pts(:,j) = nom(j);
+end
+
+for j = 10:14
+  pts(:,j) = nom(j);
+end
+
+pts(:,16) = nom(16);
+
+for j = 18:19
+  pts(:,j) = nom(j);
+end
+
+%save('pts_pce2D.mat','pts');
+
+f1 = fopen('pts_pce4D.txt','w');
+%fmt = '%15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f\n';
+fmt = '%10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e\n';
+
+for i = 1:nsams
[…]

### 2018-06-12 Paper/disc.tex
..

@@
 
-In this work, we have presented a systematic approach for constructing a reduced-space
+In this work, we have presented a systematic and efficient approach for constructing
+a reduced-space
 surrogate for scientific and engineering applications. Dimension reduction is accomplished
@@
 surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
-as well as a probabilistic sense using a validation test suite. In the proposed framework,
+as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
 a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
@@
 implemented  to a relatively higher dimensional application involving kinetics
-of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction was
+of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
+dimensions to 3 or 4 dimensions) was
 accomplished for two different scenarios involving a fuel-rich and a fuel-lean
@@
 constructed using samples from the correlated space or preferably,
-the input-output relationship could be represented using a Gaussian process
+the input-output relationship in this case could be represented as a Gaussian process
 that provides a means for incorporating the correlation between inputs.  

### 2018-06-12 Paper/intro.tex
..

@@
 situations involving complex physical models and computationally intensive
-simulations surrogate modeling often provides orders of magnitude speedups in
+simulations, surrogate modeling often provides orders of magnitude speedups in
 statistical studies. This is done by replacing repeated evaluations of
@@
 indices, constructing them in the case of models with high-dimensional inputs
-can be as expensive as computing the Sobol indices via sampling. This is
-clearly a ``catch-22" situation. In this paper, we aim to address this
-problem in a systematic and efficient manner. Specifically, we reduce
+can be as expensive as computing the Sobol indices via sampling. 
+In this paper, we propose a systematic, practical, and an efficient
+approach to address this commonly observed ``catch-22" situation
+in surrogate modelling for engineering applications.
+Specifically, we reduce
 the dimensionality of the input space using derivative based global sensitivity
@@
 that enables a more tractable approach for global sensitivity
-analysis~\cite{Kucherenko:2016}.  Also, the links between derivative based
+analysis~\cite{Kucherenko:2016}. Moreover, the links between derivative based
 global sensitivity measures (DGSMs) and total Sobol
@@
 model evaluations are performed iteratively, and convergence of our DGSM based
-screening metric is tested successively. Moreover, the verification steps built
-in our method enable monitoring the accuracy of the parameter-screening and the
-constructed surrogate model.  Our approach is agnostic to the choice of
+screening metric is tested successively. Moreover, a series of verification steps
+incorporated in our method enable monitoring the accuracy of the parameter-screening
+and the resulting surrogate model.  Our approach is agnostic to the choice of
 methodology for constructing the surrogate. However, in the present work, we
@@
 The contributions of this article are as follows: (i) We establish a robust and
-practical framework for dimension reduction and surrogate modeling.  Our
+practical framework for dimension reduction in surrogate modeling using
+derivate-based global sensitivity measures. Our
 approach is general in that it is applicable to a wide range of applications.

### 2018-06-12 Paper/method.tex
..

@@
 parameter, $\theta_i$, and use it as a metric to screen 
-parameters that are relatively unimportant. A general
-methodology for parameter screening is provided below in
+parameters that are relatively unimportant.
+
+The metric is initially computed using model evaluations at say, $n_1$ samples
+in the full space. 
+In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically,
+we could use finite-difference to approximate its value as shown in
+Eq.~\ref{eq:partial}. However, as discussed earlier in~\ref{sub:dgsm},
+estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires
+model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in case
+the derivative is available analytically. Hence, computational effort when
+using finite differences is expected to increase by a factor of $(N_p+1)$.
+Another possible approach, suitable in certain cases, is the use of
+adjoint-based gradient computation. In particular, for PDE-based
+problems with scalar QoIs, but high-dimensional uncertain parameters, 
+adjoint-based gradient computation is much more efficient than finite differences.
+In the adjoint approach, each gradient evaluation requires 
+a solution of the state equation (forward solve) and that of the 
+corresponding adjoint equation; 
+see e.g.,~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011}.
+The adjoint method, however, requires the availability of an adjoint solver.
+
+Based on the associated metric value, an initial
+rank ($\mathcal{R}_i^{old}$) is assigned to each parameter. At each iteration,
+a new set of Latin Hypercube samples is generated and corresponding model
+output at each sample point is computed. The new set of model evaluations
+combined with prior evaluations is used to update parameter ranks. Additionally,
+deviation in the derivative-based sensitivity measure between successive iterations
+normalized by the measure in the previous iteration is recorded for each parameter.
+The iterative process is continued until parameter ranks between successive iterations
+are observed to be consistent as well as the maximum deviation among all parameters
+($\Delta\mu_s$) is below a certain tolerance ($\tau$). The amount of computational
+effort associated with the screening process is limited
+by the choice of maximum number of iterations, $s_\text{max}$. 
+Key inputs to the screening procedure
+are as follows: (1) 
+a limiting value $\tau$ of the maximum relative change in the sensitivity
+measure between successive iterations; (2) 
+a limiting ratio $\tau_\text{screen}$ of the sensitivity metric 
+relative to its maximum value;
+(3) a real number $\beta \in (0, 1)$ to 
+guide the number of new samples $\lceil \beta n_1 \rceil$ 
+at each iteration ($\lceil \beta n_1
+\rceil$ 
+is the smallest integer greater than or equal to $\beta n_1$); 
+(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
+for the initial screening step in
+the algorithm and the corresponding gradient evaluations 
+$\{ \bm{g}^k \}_{k=1}^{n_0}$, where
+$\bm{g}^k = \nabla_{\bm{\theta}} G(\bm{\theta}_k)$. 
+The outputs are the set of active
+indices $\mathcal{I}_\text{active}$ corresponding to the 
+\emph{important parameters}, the total number of available model 
+evaluations $N_\text{total}$, and the enriched set of gradient evaluations 
+$\{ \bm{g}^k\}_{k=1}^{N_\text{total}}$. 
+A general methodology for parameter screening is provided below in
 Algorithm~\ref{alg:screen}.
@@
                \left(\frac{|\mu_{s,i} - \mu_{s-1,i}|}{ \mu_{s-1,i}}\right)$.
-      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
+      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$
+                {\bf AND} $s \geq s_\text{min}$}
          \State $\mathrm{done} = \mathrm{true}$
@@
 
-In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically,
-we could use finite-difference to approximate its value as shown in
-Eq.~\ref{eq:partial}. However, as discussed earlier in~\ref{sub:dgsm},
-estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires
-model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in case
-the derivative is available analytically. Hence, computational effort when
-using finite differences is expected to increase by a factor of $(N_p+1)$.
-Another possible approach, suitable in certain cases, is the use of
-adjoint-based gradient computation. In particular, for PDE-based
-problems with scalar QoIs, but high-dimensional uncertain parameters, 
-adjoint-based gradient computation is much more efficient than finite differences.
-In the adjoint approach, each gradient evaluation requires 
-a solution of the state equation (forward solve) and that of the 
-corresponding adjoint equation; 
-see e.g.,~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011}.
-The adjoint method, however, requires the availability of an adjoint solver.
+\textbf{Adaptive surrogate model construction.}
+Parameter screening is an integral part of an overall framework for adaptive
+surrogate model construction. Key attributes of the framework are discussed 
+as follows.
 
-Based on the steps outlined in the above algorithm, it can be said that the set
-of sample points used for estimating the screening metricd
-$\widehat{\mathcal{C}_i\mu_i}$ is enriched until consistency in ranks between
-successive iterations as well as a certain degree of convergence in estimates
-of the screening metric for each uncertain parameter is accomplished. However,
-the amount of computational effort associated with the screening process is limited
-by the choice of maximum number of iterations, $s_\text{max}$. 
-Key inputs
-are as follows: (1) 
-a limiting value $\tau$ of the maximum relative change in the sensitivity
-measure between successive iterations; (2) 
-a limiting ratio $\tau_\text{screen}$ of the sensitivity metric 
-relative to its maximum value;
-(3) a real number $\beta \in (0, 1)$ to 
-guide the number of new samples $\lceil \beta n_1 \rceil$ 
-at each iteration ($\lceil \beta n_1
-\rceil$ 
-is the smallest integer greater than or equal to $\beta n_1$); 
-(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
-for the initial screening step in
-the algorithm and the corresponding gradient evaluations 
-$\{ \bm{g}^k \}_{k=1}^{n_0}$, where
-$\bm{g}^k = \nabla_{\bm{\theta}} G(\bm{\theta}_k)$. 
-The outputs are the set of active
-indices $\mathcal{I}_\text{active}$ corresponding to the 
-\emph{important parameters}, the total number of available model 
-evaluations $N_\text{total}$, and the enriched set of gradient evaluations 
-$\{ \bm{g}^k\}_{k=1}^{N_\text{total}}$. 
-Parameter screening is an integral part of the
-overall surrogate model construction framework 
-detailed below.
+We begin by setting aside computational resources for constructing a cross-validation
+test suite to be used for assessing the accuracy of the resulting surrogate.
+Naturally, the resources allocated for this purpose depend upon the application
+as well as total amount of available resources. 
+The set of required inputs for parameter screening are initialized,
+and model evaluations at $n_1$ random samples in the full-space are computed.
+These evaluations are used to construct a surrogate in the full-space (FSS)
+using regression-based techniques. If the surrogate is found to be sufficiently
+accurate for the given application, the process is terminated. However, it is
+likely that a full-space surrogate constructed using a 
+small number of model evaluations would not provide a 
+faithful representation of the input-output relationship.
+
+The available set of model evaluations are utilized and further enhanced during
+parameter screening as discussed earlier.  At the end of screening, the set of
+active indices, $\mathcal{I}_\text{active}$, is used to evaluate $\alpha$, referred
+to as the degree of dimension reduction:
+%
+\be
+\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p},
+\label{eq:alpha}
+\ee
+%
+where $|\mathcal{I}_\text{active}|$ denotes the cardinality of
+$\mathcal{I}_\text{active}$.  Scope for dimension-reduction increases as
+$\alpha$ decreases.  Hence, if $\alpha$ is considered to be small and
+computational gains are expected owing to dimension reduction, the RSS is
+constructed and verified for accuracy using a combination of model evaluations
+used for screening and those associated with the cross-validation test suite.  On the
+other hand, if $\alpha$ is close to 1, the set of inputs required for screening are
+ updated as needed, and a
+new set of $n_1$ samples and corresponding model evaluations are generated. The
+FSS is re-constructed using the enriched set of evaluations and the
+aforementioned analysis is repeated as illustrated in the flow-diagram
+in Figure~\ref{fig:flow} that shows the overall 
+parameter screening and surrogate model construction method.
 
@@
 
-\textbf{Adaptive surrogate model construction.}
-We begin by setting aside computational resources for constructing a cross-validation
-test suite to be used for assessing the accuracy of the resulting surrogate.
-Naturally, the resources allocated for this purpose depend upon the application
-as well as total amount of available resources. 
-The set of required inputs for parameter screening are initialized,
-and model evaluations at $n_0$ random samples in the full-space are computed.
-These evaluations are used to construct a surrogate in the full-space (FSS)
-using regression-based techniques. If the surrogate is found to be sufficiently
-accurate for the given application, the process is terminated. However, it is
-likely that a full-space surrogate constructed using a 
-small number of model evaluations would not provide a 
-faithful representation of the input-output relationship.
-
-The available set of model evaluations are utilized and further enhanced during
-parameter screening as discussed earlier.  At the end of screening, the set of
-active indices, $\mathcal{I}_\text{active}$, is used to evaluate $\alpha$ in the
-following equation: 
-%
-\be
-\alpha = \frac{|\mathcal{I}_\text{active}|}{N_p},
-\label{eq:alpha}
-\ee
-%
-where $|\mathcal{I}_\text{active}|$ denotes the cardinality of
-$\mathcal{I}_\text{active}$.  Scope for dimension-reduction increases as
-$\alpha$ decreases.  Hence, if $\alpha$ is considered to be small and
-computational gains are expected owing to dimension reduction, the RSS is
-constructed and verified for accuracy using a combination of model evaluations
-used for screening and those associated with the validation test suite.  On the
-other hand, if $\alpha$ is close to 1, the set of inputs required for screening are
- updated as needed, and a
-new set of $n_0$ samples and corresponding model evaluations are generated. The
-FSS is re-constructed using the enriched set of evaluations and the
-aforementioned analysis is repeated as illustrated in the flow-diagram
-in Figure~\ref{fig:flow} that shows the overall 
-parameter screening and surrogate model construction method.
-
 \textbf{Assessment of the surrogate.}
@@
 disadvantage. We suggest using a small number of samples in the initial
-screening step (say, $n_0$ = 5) and a relatively large $\tau$ (say,
+screening step (say, $n_1$ = 5) and a relatively large $\tau$ (say,
 $\mathcal{O}(10^{-1})$) as a starting point with possible reduction in $\tau$

### 2018-06-12 Paper/app.tex
..

@@
 and in 3D for
-the fuel-lean case. Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the 
+the fuel-lean case. Figure~\ref{fig:err_samples_kinetics} illustrates a
+comparison of convergence characteristics for the PCEs constructed in the
+full-space and the reduced-space for the fuel-rich case.
+%
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_kinetics}
+\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
+number of model evaluations in the full-space (19D) and the reduced-space (4D)
+for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0.}
+\label{fig:err_samples_kinetics}
+\end{center}
+\end{figure}
+%
+
+Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the 
 cross-validation set, the RSS was found to be accurate within 1.8$\%$ in the

### 2018-06-12 Paper/app.tex
..

@@
 comparison of convergence characteristics for the PCEs constructed in the
-full-space and the reduced-space for the fuel-rich case.
+full-space and the reduced-space for the fuel-rich case. Note that the
+plot is generated using the implementation of least angle regression (LAR)
+for sparse PCEs in UQLab.  
 %
@@
 %
+The leave-one-out cross validation error is observed to drop initially
+and plateau with the increase in training points for the 19-dimensional
+PCE. However, in the case of 4-dimensional PCE, the error exhibits a
+monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
+at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
+Similar trends (not included) were observed in the fuel-lean case.
 

### 2018-06-12 Paper/bg.tex
..

@@
 Notice that this formulation assumes that the function $\GG$ is differentiable
-with respect to $\theta_i$, $i = 1, \ldots, \Np$, almost surely~\manavnote {What do
-we mean by ``almost surely"}.
+with respect to $\theta_i$, $i = 1, \ldots, \Np$.
 

### 2018-06-12 Paper/disc.tex
..

@@
 include inverse problems involving parameter estimation in a Bayesian setting.
+
+\item Dimension reduction based on the proposed methodology could help reduce the
+effort required for model calibration wherein only the important parameters
+are calibrated. 
 \end{enumerate}
@@
 could be reasonable at least in initial screening using DGSMs. On the other
-hand, if approximate correlations are known, the PCE could still be 
-constructed using samples from the correlated space or preferably,
-the input-output relationship in this case could be represented as a Gaussian process
-that provides a means for incorporating the correlation between inputs.  
+hand, if approximate correlations are known, we recommend using a Gaussian 
+process or Kriging-based surrogate since it 
+provides a means for incorporating the correlation between inputs.  
 Additionally, the quantity of interest is required to be differentiable with

### 2018-06-12 Paper/intro.tex
..

@@
 In this paper, we propose a systematic, practical, and an efficient
-approach to address this commonly observed ``catch-22" situation
+approach to address this commonly observed ``chicken-and-egg" problem
 in surrogate modelling for engineering applications.
 Specifically, we reduce
-the dimensionality of the input space using derivative based global sensitivity
+the dimensionality of the input space using derivative-based global sensitivity
 analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016}
@@
 indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
-basis for their use in identifying unimportant parameters.
+basis for their use in identifying unimportant parameters. In addition
+to the construction of an efficient surrogate in the reduced space,
+dimension reduction highlights key features of the input-output relationship
+encapsulated by the model, and allows for an efficient approach to calibration
+of the important inputs.
 

### 2018-06-12 Paper/abstract.tex
..

\section*{Abstract}

In this effort, we develop a systematic approach to constructing a surrogate
in a reduced input space using derivative-based global sensitivity
measures~(DGSMs)~\cite{Sobol:2010}. A sparse set of model evaluations in
the original input space is used for an approximate evaluation of DGSMs
for individual uncertain inputs of the model. An iterative screening
procedure is developed to exploit DGSM estimates in order to identify
the `unimportant' inputs. The screening procedure forms an integral part
of an overall framework for adaptive construction of a surrogate in the
reduced-space. The framework is tested for computational efficiency through
an initial implementation in simple test cases such as the classic Borehole
function, and a semilinear elliptic PDE with a random source term. 
Motivated by these experiences, the framework is further implemented to
a 19-dimensional problem with uncertain rate constants associated with
the H$_2$/O$_2$ reaction mechanism~\cite{Yetter:1991}. It is observed
that significant computational gains can be accomplished by constructing
reliable and accurate low-dimensional surrogates using the proposed 
framework for practical problems.

### 2018-06-13 Paper/abstract.tex
abstract and intro ...

@@
 \section*{Abstract}
-
-In this effort, we develop a systematic approach to constructing a surrogate
-in a reduced input space using derivative-based global sensitivity
-measures~(DGSMs)~\cite{Sobol:2010}. A sparse set of model evaluations in
-the original input space is used for an approximate evaluation of DGSMs
-for individual uncertain inputs of the model. An iterative screening
-procedure is developed to exploit DGSM estimates in order to identify
-the `unimportant' inputs. The screening procedure forms an integral part
-of an overall framework for adaptive construction of a surrogate in the
-reduced-space. The framework is tested for computational efficiency through
-an initial implementation in simple test cases such as the classic Borehole
-function, and a semilinear elliptic PDE with a random source term. 
-Motivated by these experiences, the framework is further implemented to
-a 19-dimensional problem with uncertain rate constants associated with
-the H$_2$/O$_2$ reaction mechanism~\cite{Yetter:1991}. It is observed
-that significant computational gains can be accomplished by constructing
-reliable and accurate low-dimensional surrogates using the proposed 
-framework for practical problems.
+We develop a systematic approach for surrogate model
+construction in reduced input parameter spaces.
+%using derivative-based global sensitivity measures~(DGSMs)~\cite{Sobol:2010}. 
+%
+A sparse set of model evaluations in the original input space is used to  
+approximate derivative based global sensitivity measures (DGSMs) 
+for individual uncertain inputs of the model.
+An iterative screening procedure is developed that exploits DGSM estimates in
+order to identify the \emph{unimportant} inputs. The screening procedure forms
+an integral part of an overall framework for adaptive construction of a
+surrogate in the reduced space. The framework is tested for computational
+efficiency through an initial implementation in simple test cases such as the
+classic Borehole function, and a semilinear elliptic PDE with a random source
+term. 
+%Motivated by these experiences, the framework is fully implemented to
+The framework is then deployed for a realistic application from chemical
+kinetics, where we study the ignition delay time in an H$_2$/O$_2$ reaction
+mechanism with 19 uncertain rate constants.  It is observed that significant
+computational gains can be attained by constructing accurate low-dimensional
+surrogates using the proposed framework.

### 2018-06-13 Paper/intro.tex
abstract and intro ...

@@
 central importance in enabling efficient uncertainty quantification for
-systems with computationally intensive models.
+computationally intensive models.
 
@@
 identifying model inputs that are inessential to variability in model output is
-a key step that can help reduce the dimension and hence, the effort
+a key step that can help reduce the input parameter dimension and hence the effort
 associated with surrogate model construction.
@@
 geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
-and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014},
+and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
 to name a few.
@@
 can be as expensive as computing the Sobol indices via sampling. 
-In this paper, we propose a systematic, practical, and an efficient
-approach to address this commonly observed ``chicken-and-egg" problem
+In this article, we propose a practical and efficient
+approach to address this commonly observed ``chicken-and-egg'' problem
 in surrogate modelling for engineering applications.
@@
 the dimensionality of the input space using derivative-based global sensitivity
-analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016}
-that enables a more tractable approach for global sensitivity
+analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
+which enables a tractable approach for global sensitivity
 analysis~\cite{Kucherenko:2016}. Moreover, the links between derivative based
@@
 methodology for constructing the surrogate. However, in the present work, we
-rely on sparse PCEs to demonstrate the suitability of the proposed strategy.
+rely on sparse polynomial chaos expansions (PCEs) 
+to demonstrate the suitability of the proposed strategy.
 
@@
 our strategy using motivating applications: the classic borehole
-function, and a semilinear elliptic PDE.  (iii) We further
+function, and a semilinear elliptic PDE.  (iii) We 
 deploy our strategy in an application problem from chemical kinetics with 19
-uncertain parameters. The application problem is studied in multiple regimes.
+uncertain parameters. The problem is studied in multiple regimes.
 It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
@@
 brief introduction to DGSMs as well as the polynomial chaos methodology used in
-the present work.  In Section~\ref{sec:method} we present our proposed
+the present work.  In section~\ref{sec:method}, we present our proposed
 approach. There we also provide a detailed numerical algorithm and a flow
 diagram to aid practitioners in implementing the presented framework.
-Section~\ref{sec:examples} is devoted to a number of numerical examples
+Section~\ref{sec:examples} is devoted to numerical examples
 examining various aspects of our approach. This is followed by implementation

### 2018-06-15 Paper/ack.tex
..

@@
 M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
-National Science Foundation (Grant No. 1404823, CDSE Program). M. Vohra
-would also like to sincerely thank Dr. Xun Huan at Sandia National Labs for
+National Science Foundation (Grant No. 1404823, CDSE Program). 
+C. Safta was supported by the U.S. Department of Energy, Office of Science,
+Basic Energy Sciences, as part of the Computational Chemical Sciences Program.
+M. Vohra would also like to sincerely thank Dr. Xun Huan at Sandia National Labs for
 his guidance pertaining to the usage of TChem for the chemical kinetics application
-in this work.
+in this work. Sandia National Laboratories is a multimission laboratory managed 
+and operated by National Technology \& Engineering Solutions of Sandia, LLC, 
+a wholly owned subsidiary of Honeywell International Inc., for the 
+U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525. 
+The views expressed in the article do not necessarily represent the
+views of the U.S. Department Of Energy or the United States Government.

### 2018-06-15 Paper/app.tex
..

@@
 the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
+The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
+source of clean energy for applications such as 
+transportation~\cite{Das:1996}. 
 The mechanism comprises of 19 reactions including chain reactions,
 dissociation/recombination reactions, and formation and consumption
-of intermediate species: HO$_2$ and H$_2$O$_2$, as provided below
-in Table~\ref{tab:kinetics}.
+of intermediate species as provided below in Table~\ref{tab:kinetics}.
 
@@
 activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
-universal gas constant. We focus on quantifying the uncertainty in the
-\emph{ignition delay} due to uncertainty associated with the pre-exponent,
-$A_i$ for each reaction. Hence, the total number of uncertain parameters in the
+universal gas constant. 
+The TChem~\cite{Safta:2011} software package is used to model homogenous
+ignition at constant pressure for a range of initial conditions for the
+fuel-oxidizer mixture. During the simulation, the fuel-oxidizer mixture goes 
+through a radical build-up phase followed by a sharp increase in temperature
+as heat is realeased during the thermal runaway. We focus on quantifying the 
+uncertainty in the \emph{ignition delay} due to uncertainty associated 
+with the pre-exponent, $A_i$, for each reaction. The ignition delay 
+is defined as the inflection point on the temperature profile during the thermal
+runaway. The total number of uncertain parameters in the
 present case is 19.  The $A_i$'s are considered to be uniformly distributed in
 the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
-estimate corresponding to the $i^{th}$ reaction. TChem~\cite{Safta:2011}, an
-open source C package was used for simulating temperature and concentration
-evolution during the progress of reactions $\mathcal{R}_1$--$\mathcal{R}_{19}$,
-and determining the ignition delay. The set of nominal values used in the
-computations, for parameters in~\eqref{eq:rate} are provided
+estimate corresponding to the $i^{th}$ reaction.
+The set of nominal values used in the computations, for parameters 
+in~\eqref{eq:rate} are provided
 in~\cite{Yetter:1991}.

### 2018-06-15 Paper/bg.tex
changes on bg from yesterday ...

@@
 is measuring the influence of each component of the input vector 
-$\bm{\theta}$ on the model output. 
+$\bm{\theta} = \begin{bmatrix}\theta_1 & \theta_2 & 
+\ldots & \theta_\Np\end{bmatrix}^T$ on the model output. 
 In the present work, we consider the case where the inputs are statistically 
@@
 
-Derivative-based global sensitivity analysis (DGSA) is performed by 
+Derivative-based global sensitivity analysis is performed by 
 computing derivative based global sensitivity measures (DGSMs)~\cite{Sobol:2009} 
@@
 If an analytic expression for $\GG$ is available the derivative in the above
-expression can be computed directly. In many applications, however, $\GG$ is often
-defined in terms of a solution of a mathematical model. In some cases, 
+expression can be computed directly. In many applications, however, $\GG$ is
+often defined in terms of a solution of a mathematical model.  In some cases,
 one has access to appropriate adjoint solvers that enable efficient
-adjoint-based gradient computations. In the present work, we consider
-a generic computational model and only assume that the model
-output depends differentiably on the parameter $\bm{\theta}$. Thus, 
-we consider finite-difference gradient computation: 
+adjoint-based gradient computations. This is discussed further below.  In the
+present work, we consider a generic computational model and only assume that
+the model output depends differentiably on the parameter $\bm{\theta}$. A
+simple approach to computing the gradient is to use finite-differences: 
 \be
@@
 %using large increments.  
-It is noted by many authors~[REFS], and also observed
-in the numerical experiments in the present work, that a modest Monte Carlo
-sample size is often sufficient for computing~\eqref{eq:mu} with reasonable
-accuracy.
+It is noted by many authors~\alennote{Need to give some references}, and also
+observed in the numerical experiments in the present work, that a modest Monte
+Carlo sample size is often sufficient for computing~\eqref{eq:mu} with
+sufficient accuracy to indentify the unimportant inputs.
 
@@
 for parameters with continuous distributions, an upper bound on $\mathcal{T}_i$  
-can be expressed in terms of $\mu_i$, the Poincar\'e constant ($\mathcal{C}_i$) and the total 
-variance of the model output ($\mathbb{V}(\GG)$)~\cite{Lamboni:2013}:
+can be expressed in terms of $\mu_i$ as follows: 
 \be
-\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)}~(\propto \widehat{\mathcal{C}_i\mu_i})
+\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)},
+%~(\propto \widehat{\mathcal{C}_i\mu_i})
 \label{eq:bound}
 \ee
-The upper bound in the above inequality is proportional to the product of
-$\mathcal{C}_i$ and $\mu_i$. However, for the purpose of parameter screening as
-discussed later in Section~\ref{sec:method}, we consider a normalized product,
-$\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies between 0 and 1:
-
+where $\mathcal{C}_i$ is the corresponding ``Poincar\'e constant''
+and
+$\mathbb{V}(\GG)$ is the total variance of the model
+output~\cite{Lamboni:2013}.  The upper bound in the above inequality is
+proportional to the product of $\mathcal{C}_i$ and $\mu_i$.  For the purpose of
+parameter screening as discussed later in Section~\ref{sec:method}, we consider
+a normalized product, $\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies
+between 0 and 1:
 \be
@@
 where $f_i$ are probability density functions of $\xi_i$, $i = 1, \ldots, \Np$.
-We consider a square integrable random variable $\GG:\R^\Np \to \R$; 
-that is,
-\[
-\int_{\mathcal{D}} \GG(\bm{\xi})^2 \, \bm{f}(\bm{\xi})d\bm{\xi} < \infty,
-\]
-where $\mathcal{D}$ is the support of the distribution law of the random vector
-$\bm{\xi}$.
 
+Consider a square integrable random variable $\GG:\R^\Np \to \R$. 
+%that is,
+%\[
+%\int_{\mathcal{D}} \GG(\bm{\xi})^2 \, \bm{f}(\bm{\xi})d\bm{\xi} < \infty,
+%\]
+%where $\mathcal{D}$ is the support of the distribution law of the random vector
+%$\bm{\xi}$. 
 % for representing the
@@
 %\ee
-
 %\noindent where $\mathcal{D}_{\bm{\theta}}$ is the domain of the input parameter space. 
-
+%
 As mentioned in Section~\ref{sec:intro}, the 

### 2018-06-15 Paper/abstract.tex
..

@@
 The framework is then deployed for a realistic application from chemical
-kinetics, where we study the ignition delay time in an H$_2$/O$_2$ reaction
+kinetics, where we study the ignition delay in an H$_2$/O$_2$ reaction
 mechanism with 19 uncertain rate constants.  It is observed that significant

### 2018-06-15 Paper/app.tex
..

@@
 universal gas constant. 
-The TChem~\cite{Safta:2011} software package is used to model homogenous
+The TChem~\cite{Safta:2011} software package is used to model homogeneous
 ignition at constant pressure for a range of initial conditions for the
@@
 through a radical build-up phase followed by a sharp increase in temperature
-as heat is realeased during the thermal runaway. We focus on quantifying the 
+as heat is released during the thermal runaway. We focus on quantifying the 
 uncertainty in the \emph{ignition delay} due to uncertainty associated 

### 2018-06-15 Paper/bg.tex
..

@@
 expression can be computed directly. In many applications, however, $\GG$ is
-often defined in terms of a solution of a mathematical model.  In some cases,
-one has access to appropriate adjoint solvers that enable efficient
-adjoint-based gradient computations. This is discussed further below.  In the
+often defined in terms of a solution of a mathematical model.  In the
 present work, we consider a generic computational model and only assume that
@@
 \ee
-Then,~\eqref{eq:mu} can be evaluated by Monte Carlo sampling in
+Then,~\eqref{eq:mu} can be evaluated by Monte Carlo (MC) sampling in
 the uncertain parameter space. 
@@
 %using large increments.  
-It is noted by many authors~\alennote{Need to give some references}, and also
-observed in the numerical experiments in the present work, that a modest Monte
-Carlo sample size is often sufficient for computing~\eqref{eq:mu} with
-sufficient accuracy to indentify the unimportant inputs.
+It is noted in previous studies~\cite{Kucherenko:2016,Kucherenko:2009},
+and also
+observed in the numerical experiments in the present work, that a modest MC sample size is often sufficient for computing~\eqref{eq:mu} with
+reasonable accuracy to indentify the unimportant inputs. Moreover, the
+computational efficiency for estimating $\mu_i$ can be enhanced by using
+techniques such as the automatic differentiation
+algorithm~\cite{Kiparissides:2009}.
 
@@
 \be
-\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
+\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}.
 \label{eq:cmu}
@@
 \left[\left(\sum_{k=0}^\Npc c_k \Psi_k(\bm\xi(\bm\theta)) -
-\GG(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
+\GG(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}},
 \label{eq:reg}

### 2018-06-15 Paper/disc.tex
..

@@
 
-In this work, we have presented a systematic and efficient approach for constructing
+In this work, we have presented an efficient and practical approach for constructing
 a reduced-space
@@
 in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
-using a screening metric~(\eqref{eq:cmu}) involving derivative-based sensitivity
+using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
 measures. Initially, the metric is estimated
@@
 the available set of model evaluations. Both, RSS and FSS are
-constructed using regression-based sparse basis methods. Simultaneous construction
+constructed using regression-based sparse PCEs. Simultaneous construction
 of the FSS ensures that the computational effort associated with the proposed framework
@@
 \begin{enumerate}
-\item The proposed framework is agnostic to the choice of the surrogate although PCE's were used
-in this work. 
-\item The scope for dimension reduction and associated computational gains are
-dependent upon the application as well as the quantity of interest. 
+\item Although PCEs were used in this work, the proposed framework is
+agnostic to the choice of the surrogate model construction method.
 %\item The quantity of interest must be differentiable with respect to each uncertain parameter
@@
 
-Based on the results presented for a variety of test problems, and a
-higher-dimensional chemical kinetics application in this work, it can be said
-that the proposed framework seems quite promising in its potential for
-identifying favorable scenarios for constructing a reduced-space surrogate in a
-computationally efficient manner.  However, it is important to remain cognizant
-about the limitations of the framework as well. For instance, it does not
+Based on the results presented for the test problems and the kinetics
+application, the proposed framework seems quite promising in its
+potential for identifying the unimportant model inputs. These
+observations could be exploited to construct efficient model surrogates
+in a reduced input space. However, it is important to remain cognizant
+about the limitations of the framework as well. 
+For instance, the quantity of interest is required to be differentiable with
+respect to each parameter in the considered domain. This condition once
+satisfied, helps improve the DGSM estimates and enhances the accuracy
+of the PCE-based surrogates as well.  
+Additionally, the proposed framework does not
 account for the existence of possible correlations between the uncertain
@@
 provides a means for incorporating the correlation between inputs.  
-Additionally, the quantity of interest is required to be differentiable with
-respect to each parameter in the considered domain. This condition, however,
-must anyways be satisfied for the resulting surrogate to be able to represent
-the input-output relationship for a given model with reasonable accuracy.
-Finally, careful assessment and decision-making is required with regards to
-proceeding with the construction of a reduced-space surrogate based on the
-outcome of parameter screening, and accuracy of the most recent full-space
-surrogate as well as allocation of computational resources for parameter
-screening, and constructing the validation test suite. Implementation to more
-advanced applications in the future would enable further development of the
-proposed framework.
+Implementation to applications involving strongly correlated parameters
+could enhance the applicability of the proposed framework. 
+We consider that to be a potential direction for future studies related
+to this work.

### 2018-06-15 Paper/examples.tex
..

@@
 enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
-sampling, with a sufficiently large Monte Carlo sample size.  Shown in
+sampling, with a sufficiently large MC sample size.  Shown in
 Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
@@
 Once again, we verify the accuracy of the RSS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
-using model evaluations at 1000 independent Monte-Carlo samples in the 10D parameter
+using model evaluations at 1000 independent MC samples in the 10D parameter
 space. The RSS was found to be accurate

### 2018-06-15 Paper/intro.tex
..

@@
 regression splines (MARS)~\cite{friedman93}, Gaussian processes
-(GPs)~\cite{Rasmussen:2004}, or kriging~\cite{Stein:2012}.  Many real-world
+(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}.  Many real-world
 applications involve a large number of model inputs. This makes
@@
 practical framework for dimension reduction in surrogate modeling using
-derivate-based global sensitivity measures. Our
+derivative-based global sensitivity measures. Our
 approach is general in that it is applicable to a wide range of applications.

### 2018-06-15 Paper/method.tex
changes on bg from yesterday ...
..

@@
 further below.  The term reduced-space implies that the surrogate is
-constructed in a subspace that sufficiently captures the uncertainty in the
+constructed in a reduced parameter space that sufficiently captures the uncertainty in the
 model output. We begin by outlining an algorithm for parameter screening
@@
 reduction and construction of an RSS. The overall adaptive framework 
-which incorporates parameter screening as an integral step is thereafter
+that incorporates parameter screening as an integral step is thereafter
 presented. Finally, we present metrics used for assessing the
@@
 \textbf{Parameter screening.}
-Dimension reduction is guided by global sensitivity analysis (GSA).  A typical
-approach to GSA involves estimating the Sobol sensitivity
-indices~\cite{Sobol:2001} in the case of non-linear mathematical models.
-However, as discussed earlier in sections~\ref{sec:intro} and~\ref{sec:bg},
-determining accurate estimates of Sobol sensitivity indices typically requires
-tens of thousands of model evaluations. Consequently, the exercise becomes
-prohibitive for expensive-to-evaluate models.  In the proposed framework, we
+In the proposed framework, we
 adopt a novel approach for constructing an RSS based on estimating the
@@
 
-The metric is initially computed using model evaluations at say, $n_1$ samples
-in the full space. 
-In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically,
-we could use finite-difference to approximate its value as shown in
-Eq.~\ref{eq:partial}. However, as discussed earlier in~\ref{sub:dgsm},
-estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires
-model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in case
-the derivative is available analytically. Hence, computational effort when
-using finite differences is expected to increase by a factor of $(N_p+1)$.
-Another possible approach, suitable in certain cases, is the use of
-adjoint-based gradient computation. In particular, for PDE-based
-problems with scalar QoIs, but high-dimensional uncertain parameters, 
-adjoint-based gradient computation is much more efficient than finite differences.
-In the adjoint approach, each gradient evaluation requires 
-a solution of the state equation (forward solve) and that of the 
-corresponding adjoint equation; 
-see e.g.,~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011}.
-The adjoint method, however, requires the availability of an adjoint solver.
+%The metric is initially computed using model evaluations at say, $n_1$ samples
+%in the full space. 
+%In situations where $\nabla_{\bm{\theta}}G_k$ cannot be evaluated analytically,
+%we could use finite-difference to approximate its value as shown in
+%Eq.~\ref{eq:partial}. However, as discussed earlier in~\ref{sub:dgsm},
+%estimating $\bm{\mu}$  using $M$ samples in the full parameter space requires
+%model evaluations at $(N_p+1)M$ samples, compared to only $M$ samples in case
+%the derivative is available analytically. Hence, computational effort when
+%using finite differences is expected to increase by a factor of $(N_p+1)$.
+%Another possible approach, suitable in certain cases, is the use of
+%adjoint-based gradient computation. In particular, for PDE-based
+%problems with scalar QoIs, but high-dimensional uncertain parameters, 
+%adjoint-based gradient computation is much more efficient than finite differences~\cite{Griewank:2008}.
+%In the adjoint approach, each gradient evaluation requires 
+%a solution of the state equation (forward solve) and that of the 
+%corresponding adjoint equation; 
+%see e.g.,~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011}.
+%The adjoint method, however, requires the availability of an adjoint solver.
 
+An initial set of say, $n_1$ samples is used to obtain a rough estimate
+of the metric.  
 Based on the associated metric value, an initial
 rank ($\mathcal{R}_i^{old}$) is assigned to each parameter. At each iteration,
-a new set of Latin Hypercube samples is generated and corresponding model
+a new set of samples is generated based on the joint probability distribution
+of $\bm{\theta}$ and corresponding model
 output at each sample point is computed. The new set of model evaluations
@@
 by the choice of maximum number of iterations, $s_\text{max}$.
+
 Key inputs to the screening procedure
@@
 
-We begin by setting aside computational resources for constructing a cross-validation
+We begin by allocating computational resources for constructing a cross-validation
 test suite to be used for assessing the accuracy of the resulting surrogate.
@@
 \frac{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - G^{\mbox{\tiny {PC}\textbackslash i}}(\bm{\xi(\theta}_i))\right)^2}
-{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - \widetilde{\mu}\right)^2}
+{\sum\limits_{i=1}^{N_l}\left(G(\bm{\theta}_i) - \widetilde{\mu}\right)^2},
 \label{eq:loo}
@@
 G^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
-{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}
+{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}},
 \label{eq:l2}
@@
 
-\textbf{Remarks.}
+\textbf{Discussion on the proposed methodology.}
 The amount of computational effort associated with the presented methodology
@@
 evaluations used in parameter screening to simultaneously construct the FSS
-while keeping a track of its accuracy using the validation test suite. This
-would help address situations where significant dimension reduction is not
-possible, and hence, constructing the RSS might result in a computational
+while keeping a track of its accuracy using the cross-validation test suite.
+This would help address situations where significant dimension reduction 
+is not possible, and hence, constructing the RSS might result in a 
+computational
 disadvantage. We suggest using a small number of samples in the initial
@@
 $\mathcal{O}(10^{-1})$) as a starting point with possible reduction in $\tau$
-during subsequent screenings.
+during subsequent screenings. Pseudo-random sampling approaches such as
+Latin hypercube sampling (LHS) and quasi Monte Carlo (QMC) could be used to
+generate samples in the input space.
+
+Careful assessment and decision-making is required on whether or not to
+proceed with the construction of the RSS at the end of each screening step.
+The user should account for factors such as the possible degree of 
+dimension reduction, accuracy of the concurrent FSS, and availability of
+computational resources.
 
@@
 assess the nature of the input-output relationship for a given model prior to
-implementing the present framework.
+implementing the present framework. Additionally, in some cases, the partial
+derivative of the output with respect to each uncertain input is not available
+analytically. In these cases, one could use finite difference (FD) to approximate
+the gradient as illustrated in~\ref{eq:partial}. However, since FD requires
+model evaluations at neighboring points, the underlying computational cost is
+expected to increase by a factor, $N_p+1$; $N_p$ being the number of inputs. 
+A possible, more efficient alternative to FD involves the use of adjoints for
+gradient computation~\cite{Griewank:2008}. In the adjoint approach, each
+gradient evaluation requires 
+a solution of the state equation (forward solve) and that of the 
+corresponding adjoint equation; 
+see e.g.,~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011}.
+The adjoint method, however, requires the availability of an adjoint solver.
 
@@
 surrogate in the most efficient manner within the constraints of the computational
-budget. However, it is likely that for a given application, the RSS is not
+budget. However, it might be possible that for a given application, the RSS is not
 found to be sufficiently accurate. In such a scenario, we suggest enriching the

### 2018-06-15 Paper/examples.tex
edits ...

@@
 an RSS (if deemed advantageous) by identifying unimportant parameters based on 
-estimates of the screening metric, $\widehat{\mathcal{C}_i\mu_i}$
+estimates of the screening metric, $\widehat{\mathcal{C}_i\mu_i}$,
 for individual parameters.
-In this section, we motivate the underlying methodology by applying it to three
+In this section, we motivate the proposed methodology by applying it to two
 test problems,
 namely, the borehole function, and a semilinear elliptic PDE.
-Since model evaluations in all these test
-problems are inexpensive, we are able to compare the relative importance of
-model parameters based
-on the screening metric, obtained using model evaluations with 
-converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate constructed in the
-full parameter space (FSS). Additionally, to illustrate the computational gains, 
+Model evaluations in these test
+problems are inexpensive. Therefore, we are able to compare the 
+relative importance of model parameters based
+on the screening metric (computed by sampling the model) with 
+those obtained from converged estimates of $\mathcal{T}(\theta_i)$ (computed
+using the surrogate constructed in the
+full parameter space (FSS)). Additionally, to illustrate the computational gains, 
 we compare
@@
 Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
-PDFs of the model output, obtained using the RSS and the full-space surrogate for
+PDFs of the model output, obtained using the RSS, the FSS,
+as well as true model evaluations, for
 the purpose of verification.
@@
 The borehole function is a benchmark reference problem in sensitivity analysis.
+\alennote{Give references}
 It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
@@
 \frac{2LT_u}{
-\ln({r}/{r_w})r_w^2K_w} + \frac{T_u}{T_l}\Big]}
+\ln({r}/{r_w})r_w^2K_w} + \frac{T_u}{T_l}\Big]}.
 \label{eq:bore}
@@
 as uncertain. Hence, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
- $\vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T$, a vector of
+\[
+\vec{\theta} = \begin{bmatrix}r_w & L & T_u & H_u & T_l & H_l & 
+K_w\end{bmatrix}^T, 
+\]
+being the vector of
 uncertain parameters. Table~\ref{tab:bore} provides distributions of the
@@
 
-\begin{table}[htbp]
+\begin{table}[ht]
 \renewcommand*{\arraystretch}{1.2}
@@
 %
-Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ using
+Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ 
 enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
@@
 Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
-the dimensionality of the problem by 
-discounting the variabilities in $T_u$, $T_l$, and $K_w$ by fixing 
+the dimensionality of the problem: we can 
+discount the variabilities in $T_u$, $T_l$, and $K_w$ by fixing 
 them at their respective nominal values.
@@
 validation test suite were
-found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other
+found to be 0.0551 and 0.0112 for the 4D and 5D PCE's, respectively. In other
 words, the 4D PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within
@@
 $u$ is the state variable, and $\kappa$ and $c$ are coefficients of the diffusion term
-and the nonlinear term in the above equation respectively. 
+and the nonlinear term in the above equation, respectively. 
 We consider uncertainties in $\kappa$, $c$, and the source term. 
@@
 %
-Hence, $u~=~u(\vec{\theta})$, where $\vec{\theta} = 
-(\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$ is the vector
+Hence, $u~=~u(\vec{\theta})$, where 
+\[\vec{\theta} = 
+\begin{bmatrix} \kappa & c & \alpha_1 & \alpha_2 & \cdots & \alpha_{8}
+\end{bmatrix}^T
+\] 
+is the vector
 of uncertain parameters. Distributions of the uncertain
@@
 \be
-\mathcal{F}(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
+\mathcal{F}(\vec\theta) = \frac{1}{|D|} \int_D u(\vec{x}; \vec\theta) \, d\vec{x}, 
 \label{eq:qoi}
@@
 The equation was discretized using finite differences, and Newton's method
-was used to solve the resulting nonlinear system on a (100$\times$100) 2D
+was used to solve the resulting nonlinear system on a $100 \times 100$ 2D
 cartesian grid.
@@
 PCEs constructed in 10 and 5 dimensions to compare their convergence characteristics. 
-Right: PDF of the QoI, $\mathcal{F}(\kappa, c, \theta)$ in~\eqref{eq:semilinear} is
+Right: PDF of the QoI, $\mathcal{F}(\vec\theta)$ in~\eqref{eq:semilinear} is
 plotted using the full-surrogate and the reduced-space PC surrogate.}
@@
 by them. Hence, the RSS could be used with a reasonable degree of confidence to
-quantify the uncertainty in $\mathcal{F}(\kappa, c, \theta)$ thereby leading to
+quantify the uncertainty in $\mathcal{F}(\vec\theta)$ thereby leading to
 a computational advantage in this case.

### 2018-06-16 Paper/examples.tex
..

@@
 Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ 
-enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
-sampling, with a sufficiently large MC sample size.  Shown in
+enables construction of the FSS with minimal effort. FSS predictions at
+a large set of MC samples in the input space are used to obtain converged
+estimates of $\mathcal{T}(\theta_i)$. Shown in
 Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
-uncertain parameters in the borehole function using 10$^6$ pseudo-random
+uncertain parameters in the borehole function using 10$^6$ MC
 samples in the input parameter space. 
@@
 words, the 4D PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within
-1.12$\%$ of predictions based on the borehole function. We note  that although
-the convergence in the case of a 5D PCE is slower (Figure~\ref{fig:conv_bore}),
-its predictive accuracy is higher than the 4D PCE. This illustrates the
+1.12$\%$ of predictions based on the borehole function. Note that $\epsilon_\text{\tiny{LOO}}$
+however, is lower in the case of 4D PCE (Figure~\ref{fig:conv_bore}).
+This illustrates the
 trade-off between accuracy and computational efficiency for the present 
@@
 total-effect index $\mathcal{T}(\theta_i)$, reported 
-in Figure~\ref{fig:sense_elliptic}~(left) by solving the above non-linear
-system at 500 samples in the 10-dimensional parameter space. 
+in Figure~\ref{fig:sense_elliptic}~(left) using FSS predictions at 10$^6$
+MC samples in the input space. The FSS was 
+constructed using model predictions at 500 training points in the 10-dimensional
+input space. Corresponding value of $\epsilon_\text{\tiny{LOO}}$ was 
+found to be 9.729$\times 10^{-4}$. 
 %

### 2018-06-28 Codes/Kinetics/active_subspace/free_grad/lean/init_1D.m
..

@@ -1,0 +1,179 @@
+function [rn1,gsa_t1] = init_1D(eta,xpr,G,dim,L,U);
+
+% 1D Surrogate
+y = eta(:,1)'*xpr'; % active var
+Y_surr = get_polyfit_surr(y,G,eta(:,1),2);
+
+% Compute rel L-2 norm of error at MD data for kappa
+np = size(xpr,1); % number of points at which MD data is available
+Y_surr_data = zeros(np,1);
+
+for i = 1:np
+  Y_surr_data(i,1) = Y_surr(xpr(i,:)');
+end
+
+Nr = (sum((G-Y_surr_data).^2)).^(0.5);
+Dr = (sum((G).^2)).^(0.5);
+rn1 = Nr./Dr;
+
+
+% SSP 1D
+ssp1D(eta,xpr,G);
+
+% Generate a million random samples in the 7D space
+%ts = 1e5;
+%samples = zeros(ts,dim);
+%
+%for j = 1:dim
+%  samples(:,j) = unifrnd(L(j,1),U(j,1),ts,1);
+%end
+%
+%% project those samples in [-1,1]
+%
+%xrand = zeros(ts,dim);
+%
+%for i = 1:ts
+%  for j = 1:dim
+%    xrand(i,j) = 2.0.*(samples(i,j)-L(j))./(U(j)-L(j)) - 1.0;
+%  end
+%end
+%
+%% Estimate k using 1D surrogate for the million projected samples
+%Y_surr_rs = zeros(ts,1);
+%
+%for i = 1:ts
+%  Y_surr_rs(i,1) = Y_surr(xrand(i,:)');
+%end
+%
+%% compare pdf of kappa using 1D surrogate
+%pdf_comp_ssp1D(G,Y_surr_rs);
+[gsa_t1] = sobol(L,U,dim);
+
+% Function Definitions
+
+% 1D polyfit
+function surr = get_polyfit_surr(y,G,eta,deg)
+p = polyfit(y(:),G,deg);
+surr = @(x)(polyval(p,eta'*x));
+end
+
+function [gsa_t1] = sobol(L,U,dim)
+N = 1e5; % number of samples
[…]

### 2018-06-28 Codes/Kinetics/active_subspace/free_grad/rich/free_grad_sub.m

@@ -1,0 +1,206 @@
+close all;
+clear all;
+rng(100);
+%set(0,'DefaultFigureVisible','off');
+
+dim = 19;
+dX = zeros(dim,1); 
+L = zeros(dim,1); U = zeros(dim,1);
+id_data = load('record_id_as.txt');
+params = load('pts_as.txt');
+
+% Nominal values of the parameters
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(:,1) = 0.9.*nom(:,1); U(:,1) = 1.1.*nom(:,1);
+
+% Project params in [-1,1]
+
+nrows = size(params,1); % number of rows
+ncols = size(params,2); % number of cols
+
+xp = zeros(nrows,ncols);
+
+for i = 1:nrows
+  for j = 1:ncols
+    xp(i,j) = 2.0.*(params(i,j)-L(j))./(U(j)-L(j)) - 1.0;
+  end
+end
+
+nsams = 153;
+% refine xp as xpr
+xpr = zeros(nsams,ncols);
+xpr(:,:) = xp(1:nsams,:);
+
+N = nsams;
+p = N-1;
+d_matrix = zeros(N,1);
+M = 471;
+% model realizations
+G = zeros(nsams,1); Gdx = zeros(nsams,dim);
+G(:,1) = id_data(1:nsams,1);
+
+% Draw M independent samples
+samples = zeros(M,ncols); ypr = zeros(M,ncols);
+for j = 1:dim
+  samples(:,j) = unifrnd(L(j,1),U(j,1),M,1);
+end
+
+% project samples in [-1,1]
+for i = 1:M
+  for j = 1:dim
+    ypr(i,j) = 2.0.*(samples(i,j)-L(j))./(U(j)-L(j)) - 1.0;
+  end
+end
+
+for i = 1:M
+  for j = 1:N
+    d_matrix(j) = 0;
+    for k = 1:dim
+      d_matrix(j) = d_matrix(j) + norm(ypr(i,k) - xpr(j,k));
+    end
+  end
+  [z,index(i,:)] = sort(d_matrix);
+  for j = 1:p
[…]

### 2018-06-28 Codes/Kinetics/active_subspace/grad/lean/grad_sub.m

@@ -1,0 +1,163 @@
+close all;
+clear all;
+rng(100);
+set(0,'DefaultFigureVisible','off');
+
+dim = 19;
+dX = zeros(dim,1); 
+L = zeros(dim,1); U = zeros(dim,1);
+id_data = load('record_id_as.txt');
+params = load('pts_as.txt');
+
+% Nominal values of the parameters
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(:,1) = 0.9.*nom(:,1); U(:,1) = 1.1.*nom(:,1);
+
+% Project params in [-1,1]
+
+nrows = size(params,1); % number of rows
+ncols = size(params,2); % number of cols
+
+xp = zeros(nrows,ncols);
+
+for i = 1:nrows
+  for j = 1:ncols
+    xp(i,j) = 2.0.*(params(i,j)-L(j))./(U(j)-L(j)) - 1.0;
+  end
+end
+
+nsams = 60;
+
+
+for j = 1:dim
+  dX(j) = 1e-3.*(U(j,1)-L(j,1));
+end
+
+G = zeros(nsams,1); Gdx = zeros(nsams,dim);
+G(:,1) = id_data(1:nsams,1);
+dGdx = zeros(nsams,dim);
+
+for j = 1:dim
+  Gdx(:,j) = id_data(j*nsams+1:(j+1)*nsams,1);
+  dGdx(:,j) = (Gdx(:,j) - G(:,1))./dX(j);
+end
+
+% Computing the C matrix (Eq. 1.2)
+
+C = zeros(dim,dim);
+grad_f = zeros(dim,1);
+
+for i = 1:nsams
+  grad_f(:,1) = dGdx(i,:);
+  C = C + grad_f*transpose(grad_f);
+end
+
+C = (1./nsams).*(C);
+[W,D] = eig(C);
+
+[lambda, idx] = sort(diag(D), 'descend');
+W = W(:,idx);
+
+eta = zeros(dim,3);
+eta(:,1) = W(:,1);
+eta(:,2) = W(:,2);
+eta(:,3) = W(:,3);
+
+
+% Computing activity scores
+
+as = zeros(dim,1);
+
+for i = 1:dim
[…]

### 2018-06-28 Codes/Kinetics/active_subspace/kinetics_test/active_subspace.m

@@ -1,0 +1,100 @@
+m = 19;
+k = m + 1;
+alpha = 3;
+rng(123);
+nsamp = floor(alpha * k * log(m));
+
+L = zeros(1,m); U = zeros(1,m);
+
+% Nominal values for pre-factors a1 to a19 for the 19 reactions
+
+nom = [1.915e14,5.080e04,2.160e08,1.230e04,4.577e19,6.165e15,4.714e18,2.240e22,6.170e19,...
+       6.630e13,1.690e14,1.810e13,1.450e16,3.020e12,1.202e17,1.000e13,4.820e13,9.550e06,...
+       7.000e12];
+
+L(1,:) = 0.9.*nom(1,:); U(1,:) = 1.1.*nom(1,:);
+
+% draw samples in [-1,1]
+xi = -1 + 2 * rand(nsamp, m);
+%pts_xi = zeros(nsamp*(m+1),m);
+%pts_xi(1:nsamp,:) = xi;
+%
+%% perturb the points
+dxi = 2e-5;
+%for i = 1:m
+%  pts_xi(i*nsamp+1:(i+1)*nsamp,:) = pts_xi(1:nsamp,:);
+%  pts_xi(i*nsamp+1:(i+1)*nsamp,i) = pts_xi(i*nsamp+1:(i+1)*nsamp,i) + dxi;
+%end
+%
+%% Project points to the physical space
+%pts_x = zeros(size(pts_xi,1),size(pts_xi,2));
+%for i = 1:size(pts_x,1)
+%  for j = 1:size(pts_x,2)
+%    pts_x(i,j) = L(1,j) + 0.5*(U(1,j)-L(1,j)).*(pts_xi(i,j)+1);
+%  end
+%end
+%
+%% Save physical points to a file
+%save('pts_grad.txt','pts_x','-ASCII');
+
+id = load('record_id_grad.txt');
+G = zeros(nsamp,1); Gdxi = zeros(nsamp,m);
+G(:,1) = id(1:nsamp,1);
+dGdxi = zeros(nsamp,m);
+%
+for j = 1:m
+  Gdxi(:,j) = id(j*nsamp+1:(j+1)*nsamp,1);
+  dGdxi(:,j) = (Gdxi(:,j) - G(:,1))./dxi;
+end
+%
+C = zeros(m,m);
+grad_f = zeros(m,1);
+
+for i = 1:nsamp
+  grad_f(:,1) = dGdxi(i,:);
+  C = C + grad_f*transpose(grad_f);
+end
+
[…]

### 2018-06-28 Codes/Kinetics/gen_samples.m

@@ -24,7 +24,7 @@ for i = 1:dim
   pts(i*nsams+1:(i+1)*nsams,i) = pts(i*nsams+1:(i+1)*nsams,i) + dX(1,i);
 end
 
-f1 = fopen('pts_pce19D_10.txt','w');
+f1 = fopen('pts_test.txt','w');
 %fmt = '%15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f %15.4f\n';
 fmt = '%10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e %10.6e\n';
 

### 2018-06-28 Codes/Kinetics/new_rich_mix/PCE4D/build_pce.m

@@ -3,8 +3,8 @@ clearvars
 uqlab
 
 % Input data
-X = dlmread(fullfile('pts_pce4D_4D.dat')) ;
-Y = dlmread(fullfile('record_id_pce4D_19D.dat')) ;
+X = dlmread(fullfile('pts_pce4D_4D_60.dat')) ;
+Y = dlmread(fullfile('record_id_pce4D_19D_60.dat')) ;
 MetaOpts.ExpDesign.X = X;
 MetaOpts.ExpDesign.Y = Y;
 
@@ -29,11 +29,11 @@ MetaOpts.Method = 'LARS';
 myPCE = uq_createModel(MetaOpts);
 uq_print(myPCE);
 
-nsams = 1000;
-qoi = load('record_id_val.txt');
-E1 = verify_L2(nsams,qoi);
-save('rel_L2.txt','E1','-ASCII');
-verify_pdf(qoi,L,U);
+%nsams = 1000;
+%qoi = load('record_id_val.txt');
+%E1 = verify_L2(nsams,qoi);
+%save('rel_L2.txt','E1','-ASCII');
+%verify_pdf(qoi,L,U);
 %
 %% Function Definitions
 function errl = verify_L2(nsams,qoi)

### 2018-06-28 Paper/bg.tex

@@
 derivative-based global sensitivity measures and surrogate modeling 
-using polynomial chaos expansion.
+using polynomial chaos expansions.
 
@@
 
-If an analytic expression for $\GG$ is available the derivative in the above
-expression can be computed directly. In many applications, however, $\GG$ is
+If an analytic expression for $\GG$ is available, the derivative in the above
+expression can be computed directly. In real-world applications, 
+however, $\GG$ is
 often defined in terms of a solution of a mathematical model.  In the
@@
 computational efficiency for estimating $\mu_i$ can be enhanced by using
-techniques such as the automatic differentiation
-algorithm~\cite{Kiparissides:2009}.
+techniques such as automatic differentiation
+~\cite{Kiparissides:2009} or adjoint-based gradient computation~\cite{jameson1988aerodynamic,gunzburger2003perspectives,Borzi2011,AlexanderianPetraStadlerEtAl17}.
 
@@
 
-Consider a square integrable random variable $\GG:\R^\Np \to \R$. 
-%that is,
-%\[
-%\int_{\mathcal{D}} \GG(\bm{\xi})^2 \, \bm{f}(\bm{\xi})d\bm{\xi} < \infty,
-%\]
-%where $\mathcal{D}$ is the support of the distribution law of the random vector
-%$\bm{\xi}$. 
+Consider a square integrable random variable $\GG:\R^\Np \to \R$; 
+i.e.,
+$\int_{\mathcal{D}} \GG(\bm{\xi})^2 \, \bm{f}(\bm{\xi})d\bm{\xi} < \infty$,
+where $\mathcal{D}$ is the support of the distribution law of the random vector
+$\bm{\xi}$. 
 % for representing the
@@
 %
-As mentioned in Section~\ref{sec:intro}, the 
-polynomial chaos expansion
-(PCE) is a commonly used tool for surrogate modeling. 
+%As mentioned in Section~\ref{sec:intro}, the 
+%polynomial chaos expansion
+%(PCE) is a commonly used tool for surrogate modeling. 
 The PCE of
@@
 and selection operator (LASSO)~\cite{Tibshirani:1996} aim to construct a sparse PCE~\cite{Blatman:2008}
-by solving a regularized optimization problem. Specifically in the case of LAR, a penalty term comprising the L-1
-norm of the PC coefficients is used:
-
+by solving a penalized least-squares problem. Specifically in the case of LAR, a penalty term comprising the $\ell_1$-norm of the PC coefficients is used:
 \be
@@
 where $\normone{\bm{c}}$ = $\sum_{k=0}^\Npc |c_k |$.
-The regularization term forces the minimization towards sparse coefficient vectors resulting
-in sparse PC representations.
-In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
-a general purpose uncertainty quantification software developed at ETH Zurich.
+The penalty term forces the minimization towards sparse coefficient vectors
+resulting in sparse PC representations.  In this work, we construct sparse PCEs
+with LAR using UQLab~\cite{Marelli:2014}, a general purpose uncertainty
+quantification software developed at ETH Zurich.
 % in Switzerland.

### 2018-06-28 Paper/disc.tex

@@
 measures. Initially, the metric is estimated
-using model evaluations at a small set of samples in the parameter domain. However, these
+using model evaluations at a small set of samples in the parameter domain. These
 estimates are refined by subsequent enrichment of the sample set during the screening
@@
 
-\item Exponential gains can be realized in situations where multiple surrogates need to be
+\item Significant gains can be realized in situations where multiple surrogates need to be
 constructed as illustrated in the kinetics application. Other possible scenarios may
@@
 respect to each parameter in the considered domain. This condition once
-satisfied, helps improve the DGSM estimates and enhances the accuracy
-of the PCE-based surrogates as well.  
+satisfied, enhances the accuracy of the PCE-based surrogates as well.  
 Additionally, the proposed framework does not

### 2018-06-28 Paper/intro.tex

@@
 
-Variance based global sensitivity analysis based on Sobol indices~\cite{Sobol93,
+Variance based global sensitivity analysis based on Sobol' indices~\cite{Sobol93,
 Sobol:2001,
@@
 uncertainty in predictions. Specifically, such analysis can help reduce the
-dimensionality of the problem.  Computing Sobol indices, however, is a
+dimensionality of the problem.  Computing Sobol' indices, however, is a
 computationally demanding task.  
@@
 enables efficient computation 
-of Sobol indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
+of Sobol' indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
 on a wide range of applications including in ocean 
@@
 indices, constructing them in the case of models with high-dimensional inputs
-can be as expensive as computing the Sobol indices via sampling. 
+can be as expensive as computing the Sobol' indices via sampling. 
 In this article, we propose a practical and efficient
@@
 which enables a tractable approach for global sensitivity
-analysis~\cite{Kucherenko:2016}. Moreover, the links between derivative based
-global sensitivity measures (DGSMs) and total Sobol
+analysis~\cite{Kucherenko:2016}. The links between derivative based
+global sensitivity measures (DGSMs) and total Sobol'
 indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
@@
 The contributions of this article are as follows: (i) We establish a robust and
-practical framework for dimension reduction in surrogate modeling using
+practical framework for dimension reduction and surrogate modeling using
 derivative-based global sensitivity measures. Our
@@
 the present work.  In section~\ref{sec:method}, we present our proposed
-approach. There we also provide a detailed numerical algorithm and a flow
+approach, where we also provide a detailed numerical algorithm and a flow
 diagram to aid practitioners in implementing the presented framework.

### 2018-06-28 Paper/method.tex

@@
 %
-%1. Goal is to estimate the upper bound on Sobol total-effect index using DGSM. 
+%1. Goal is to estimate the upper bound on Sobol' total-effect index using DGSM. 
 %2. QoI should be differentiable w.r.t all the parameters. 
@@
 upper-bound $\widehat{\mathcal{C}_i\mu_i}$, given in~\eqref{eq:bound}, on 
-Sobol total effect index ($\mathcal{T}(\theta_i)$) for each 
-parameter, $\theta_i$, and use it as a metric to screen 
+total Sobol' index ($\mathcal{T}(\theta_i)$) for each 
+parameter $\theta_i$; the \emph{screening metrics}, 
+$\{\widehat{\mathcal{C}_i\mu_i}\}_{i=1}^\Np$,  
+are used to identify
 parameters that are relatively unimportant.
@@
 
-An initial set of say, $n_1$ samples is used to obtain a rough estimate
+An initial set of $n_1$ samples is used to obtain a rough estimate
 of the metric.  
@@
 is the smallest integer greater than or equal to $\beta n_1$); 
-(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
+(4) a set of samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
 for the initial screening step in
@@
 \textbf{Adaptive surrogate model construction.}
-Parameter screening is an integral part of an overall framework for adaptive
-surrogate model construction. Key attributes of the framework are discussed 
-as follows.
-
+%Parameter screening is an integral part of an overall framework for adaptive
+%surrogate model construction. Key attributes of the framework are discussed 
+%as follows. 
+%
 We begin by allocating computational resources for constructing a cross-validation
@@
 new set of $n_1$ samples and corresponding model evaluations are generated. The
-FSS is re-constructed using the enriched set of evaluations and the
+FSS is reconstructed using the enriched set of evaluations and the
 aforementioned analysis is repeated as illustrated in the flow-diagram
@@
 
-%\node (counter) [process, below of=sam0, text width=9.5em, yshift=-0.21cm] {\vspace{-6mm}\be N_\text{total} = N_\text{total} + n_0 \nonumber\ee};
+%\node (counter) [process, below of=sam0, text width=9.5em, yshift=-0.21cm] {\vspace{-6mm}\be N_\text{total} = N_\text{total} + n_1 \nonumber\ee};
 
@@
 \textbf{Assessment of the surrogate.}
-To assess convergence of the resulting surrogate, one could estimate the
+To assess accuracy of the resulting surrogate, one could estimate the
 leave-one-out cross validation error as follows:
@@
 G^{\mbox{\tiny {PC}}}(\bm{\xi(\theta}_i))\right)^2\right]^{\frac{1}{2}}}
-{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}},
+{\left[\sum\limits_{i=1}^{N_v}\left(G(\bm{\theta}_i)\right)^2\right]^{\frac{1}{2}}}.
 \label{eq:l2}
 \ee
-where $N_v$ is the number of sampling points in the full parameter space at
-which model evaluations are available. In the case of an RSS, it is the
+Here $N_v$ is the number of sampling points in the full parameter space at
+which model evaluations are available; this, in the case of an RSS, is 
+given by the
 augmented set of model evaluations used for validation and screening.  
@@
 evaluations would be infeasible.  A practical alternative would be to compare
-a histogram based on sparse model evaluations with the surrogate-based PDF in
-order to gain some insight into the quality of the comparison.
+a (normalized) histogram based on sparse model evaluations with the surrogate-based PDF in
+order to gain some insight into the statistical quality of the surrogate.
 
@@
 assess the nature of the input-output relationship for a given model prior to
-implementing the present framework. Additionally, in some cases, the partial
+implementing the present framework.
+
+Additionally, in some cases, the partial
 derivative of the output with respect to each uncertain input is not available
@@
 model evaluations at neighboring points, the underlying computational cost is
-expected to increase by a factor, $N_p+1$; $N_p$ being the number of inputs. 
-A possible, more efficient alternative to FD involves the use of adjoints for
+expected to increase by a factor, $N_p+1$, with $N_p$ being the number of inputs. 
+A possible, more efficient alternative to FD, which might be suitable in some cases, involves the use of adjoints for
 gradient computation~\cite{Griewank:2008}. In the adjoint approach, each
@@
 The adjoint method, however, requires the availability of an adjoint solver.
+Another alternative for efficient gradient computation is the use of 
+automatic differentiation.
 

### 2018-06-28 Codes/Kinetics/new_rich_mix/PCE4D/convert_19D_4D.m
..

@@ -1,0 +1,41 @@
+close all;
+clear all;
+
+d19_10 = load('pts_pce4D_19D_10.txt');
+d19_20 = load('pts_pce4D_19D_20.txt');
+d19_30 = load('pts_pce4D_19D_30.txt');
+d19_40 = load('pts_pce4D_19D_40.txt');
+d19_50 = load('pts_pce4D_19D_50.txt');
+d19_60 = load('pts_pce4D_19D_60.txt');
+
+d4_10 = zeros(size(d19_10,1),4);
+d4_20 = zeros(size(d19_20,1),4);
+d4_30 = zeros(size(d19_30,1),4);
+d4_40 = zeros(size(d19_40,1),4);
+d4_50 = zeros(size(d19_50,1),4);
+d4_60 = zeros(size(d19_60,1),4);
+
+d4_10(:,1) = d19_10(:,1); d4_10(:,2) = d19_10(:,9);
+d4_10(:,3) = d19_10(:,15); d4_10(:,4) = d19_10(:,17);
+
+d4_20(:,1) = d19_20(:,1); d4_20(:,2) = d19_20(:,9);
+d4_20(:,3) = d19_20(:,15); d4_20(:,4) = d19_20(:,17);
+
+d4_30(:,1) = d19_30(:,1); d4_30(:,2) = d19_30(:,9);
+d4_30(:,3) = d19_30(:,15); d4_30(:,4) = d19_30(:,17);
+
+d4_40(:,1) = d19_40(:,1); d4_40(:,2) = d19_40(:,9);
+d4_40(:,3) = d19_40(:,15); d4_40(:,4) = d19_40(:,17);
+
+d4_50(:,1) = d19_50(:,1); d4_50(:,2) = d19_50(:,9);
+d4_50(:,3) = d19_50(:,15); d4_50(:,4) = d19_50(:,17);
+
+d4_60(:,1) = d19_60(:,1); d4_60(:,2) = d19_60(:,9);
+d4_60(:,3) = d19_60(:,15); d4_60(:,4) = d19_60(:,17);
+
+save('pts_pce4D_4D_10.dat','d4_10','-ASCII');
+save('pts_pce4D_4D_20.dat','d4_20','-ASCII');
+save('pts_pce4D_4D_30.dat','d4_30','-ASCII');
+save('pts_pce4D_4D_40.dat','d4_40','-ASCII');
[…]

### 2018-06-28 Codes/Kinetics/new_rich_mix/PCE4D/gen_plots.m

@@ -1,0 +1,34 @@
+close all
+clear all
+
+err_samples();
+
+function err = err_samples()
+filename = 'nsams_eloo.txt';
+delimiterIn = ' ';
+headerlinesIn = 1;
+A = importdata(filename,delimiterIn,headerlinesIn);
+
+figure
+semilogy(A.data(:,1),A.data(:,2),'-o','color','k','linewidth',2,'MarkerFaceColor','k');
+hold on;
+semilogy(A.data(:,1),A.data(:,3),'--o','color','b','linewidth',2,'MarkerFaceColor','b');
+ylabel('$$\mathrm{\log_{10}(\epsilon_{LOO})}$$','interpreter','latex','fontsize',20);
+
+%yyaxis right
+%plot(A.data(:,1),A.data(:,3),'--o','color','k','linewidth',2);
+%plot(A.data(:,1),A.data(:,5),'--o','color','b','linewidth',2);
+%ylabel('$$\mathrm{CPU~Time}$$','interpreter','latex');
+
+xlabel('$$\mathrm{Number~of~Training~Points}$$','interpreter','latex','fontsize',20);
+xlim([0,70]);
+leg = legend({'$\mathrm{19D~PCE}$','$\mathrm{4D~PCE}$'},'location','southwest');
+set(leg,'Interpreter','latex');
+
+set(gca,'fontsize',18);
+set(gca,'TickLabelInterpreter','latex');
+set(gcf,'color',[1,1,1]);
+box on;
+grid on;
+print -depsc err_samples_kinetics.eps
+end

### 2018-07-30 Paper/intro.tex
..

@@
 
-The emerging field of uncertainty quantification (UQ) aims at methodologies for
-incorporating, characterizing, quantifying, propagating, and reducing the
-uncertainties associated with predictive models and simulations.  For
-situations involving complex physical models and computationally intensive
-simulations, surrogate modeling often provides orders of magnitude speedups in
-statistical studies. This is done by replacing repeated evaluations of
-computationally expensive models by inexpensive evaluations of a surrogate
-model.  Thus, an efficient approach to construction of surrogate models is of
-central importance in enabling efficient uncertainty quantification for
-computationally intensive models.
-
-Commonly used surrogate modeling approaches use polynomial chaos expansions
+\paragraph{Motivation}
+Surrogate modeling has become a critical component of scientific computing
+owing to the emergence of the field of uncertainty quantification for
+scientific and engineering applications. Commonly used approaches for
+surrogate modeling include polynomial chaos expansions
 (PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
 regression splines (MARS)~\cite{friedman93}, Gaussian processes
-(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}.  Many real-world
-applications involve a large number of model inputs. This makes
-the construction of surrogate models difficult or impossible in some cases.
-However, in many situations, the variability in model observables of interest
-is sensitive to only a small subset of the uncertain inputs.  Hence,
-identifying model inputs that are inessential to variability in model output is
-a key step that can help reduce the input parameter dimension and hence the effort
-associated with surrogate model construction.
+(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A 
+pertinent challenge associated with surrogate construction involves the
+process of \textit{training} that typically requires a large number of model runs.
+In situations involving large-dimensional systems,
+and computationally intensive simulations, the training of a surrogate
+becomes remarkably challenging and even prohibitive in some cases. A possible
+approach for mitigating this challenge involves computation of sensitivity
+measures (e.g. Sobol' indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08})
+to ascertain important parameters that predominantly contribute towards the variability
+of the model output. Sensitivity-based dimension reduction could thus help
+reduce the computational effort significantly. However, numerically estimating
+the Sobol' indices that involve multi-dimensional integrals can be a demanding task
+in itself. In fact, surrogate models are constructed to estimate the 
+Sobol sensitivity indices for a variety of applications including in ocean 
+modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
+geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
+and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
+to name a few. Hence, this common practical issue in scientific computing can
+be characterized as a ``chicken-and-egg" problem.
+
+In this article, we propose a practical and efficient approach that focuses on
+optimal use of computational resources for surrogate construction in a 
+reduced-input space. Specifically, we reduce the dimensionality of the
+input space by using the derivative-based global sensitivity
+analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
+which enables a tractable approach for global sensitivity
+analysis~\cite{Kucherenko:2016}. The links between derivative based
+global sensitivity measures (DGSMs) and total Sobol'
+indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
+basis for their use in identifying unimportant parameters. In addition
+to the construction of an efficient surrogate in the reduced space,
+dimension reduction highlights key features of the input-output relationship
+encapsulated by the model, and allows for an efficient approach to calibration
+of the important inputs.
+
+%The emerging field of uncertainty quantification (UQ) aims at methodologies for
+%incorporating, characterizing, quantifying, propagating, and reducing the
+%uncertainties associated with predictive models and simulations.  For
+%situations involving complex physical models and computationally intensive
+%simulations, surrogate modeling often provides orders of magnitude speedups in
+%statistical studies. This is done by replacing repeated evaluations of
+%computationally expensive models by inexpensive evaluations of a surrogate
+%model.  Thus, an efficient approach to construction of surrogate models is of
+%central importance in enabling efficient uncertainty quantification for
+%computationally intensive models. 
+%
+%
+%Commonly used surrogate modeling approaches use polynomial chaos expansions
+%(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
+%regression splines (MARS)~\cite{friedman93}, Gaussian processes
+%(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}.  Many real-world
+%applications involve a large number of model inputs. This makes
+%the construction of surrogate models difficult or impossible in some cases.
+%However, in many situations, the variability in model observables of interest
+%is sensitive to only a small subset of the uncertain inputs.  Hence,
+%identifying model inputs that are inessential to variability in model output is
+%a key step that can help reduce the input parameter dimension and hence the effort
+%associated with surrogate model construction.
 
@@
 
-Variance based global sensitivity analysis based on Sobol' indices~\cite{Sobol93,
-Sobol:2001,
-Owen13,
-SaltelliRattoAndresEtAl08} provides
-insight into the relative contributions of the uncertain model inputs to the
-uncertainty in predictions. Specifically, such analysis can help reduce the
-dimensionality of the problem.  Computing Sobol' indices, however, is a
-computationally demanding task.  
-Availability of a surrogate model typically
-enables efficient computation 
-of Sobol' indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
-on a wide range of applications including in ocean 
-modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
-geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
-and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
-to name a few.
-
-While surrogate models provide an efficient way of computing sensitivity
-indices, constructing them in the case of models with high-dimensional inputs
-can be as expensive as computing the Sobol' indices via sampling. 
-In this article, we propose a practical and efficient
-approach to address this commonly observed ``chicken-and-egg'' problem
-in surrogate modelling for engineering applications.
-Specifically, we reduce
-the dimensionality of the input space using derivative-based global sensitivity
-analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
-which enables a tractable approach for global sensitivity
-analysis~\cite{Kucherenko:2016}. The links between derivative based
-global sensitivity measures (DGSMs) and total Sobol'
-indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
-basis for their use in identifying unimportant parameters. In addition
-to the construction of an efficient surrogate in the reduced space,
-dimension reduction highlights key features of the input-output relationship
-encapsulated by the model, and allows for an efficient approach to calibration
-of the important inputs.
+%Variance based global sensitivity analysis based on Sobol' indices~\cite{Sobol93,
+%Sobol:2001,Owen13,SaltelliRattoAndresEtAl08} provides
+%insight into the relative contributions of the uncertain model inputs to the
+%uncertainty in predictions. Specifically, such analysis can help reduce the
+%dimensionality of the problem.  Computing Sobol' indices, however, is a
+%computationally demanding task.  
+%Availability of a surrogate model typically
+%enables efficient computation 
+%of Sobol' indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
+%on a wide range of applications including in ocean 
+%modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
+%geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
+%and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
+%to name a few.
+%
+%While surrogate models provide an efficient way of computing sensitivity
+%indices, constructing them in the case of models with high-dimensional inputs
+%can be as expensive as computing the Sobol' indices via sampling. 
+%In this article, we propose a practical and efficient
+%approach to address this commonly observed ``chicken-and-egg'' problem
+%in surrogate modelling for engineering applications.
+%Specifically, we reduce
+%the dimensionality of the input space using derivative-based global sensitivity
+%analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
+%which enables a tractable approach for global sensitivity
+%analysis~\cite{Kucherenko:2016}. The links between derivative based
+%global sensitivity measures (DGSMs) and total Sobol'
+%indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
+%basis for their use in identifying unimportant parameters. In addition
+%to the construction of an efficient surrogate in the reduced space,
+%dimension reduction highlights key features of the input-output relationship
+%encapsulated by the model, and allows for an efficient approach to calibration
+%of the important inputs.
 

### 2018-07-30 Codes/MD/active_subspace/from_Alen/manav_codes/compute_active_subspace.m
..

@@ -50,7 +50,7 @@ eta2 = W(:,2);
 % plot of eigenvalues
 %
 semilogy(lambda./lambda(1), '-o');
-
+print -depsc lam.eps
 
 %
 % univariate SSP
@@ -61,7 +61,7 @@ plot(y, f, 'ko', 'markerfacecolor', 'k')
 set(gca, 'fontsize', 20);
 xlabel('y = <eta1, x>');
 ylabel('f(x)');
-print -dpng uni_SSP.png
+print -depsc uni_SSP.eps
 
 %
 % bivariate SSP

### 2018-07-30 Codes/MD/active_subspace/from_Alen/manav_codes/driver_routine.m

@@ -28,19 +28,19 @@ end
 % figures
 %
 %close all;
-%figure(1);
-%plot(ff, ff_hat, '*');
-%set(gca, 'fontsize', 20);
-%xlabel('true model');
-%ylabel('surrogate');
-%
-%figure(2)
-%hold on;
-%histnorm(ff);
-%plot(xi, pdf, 'r', 'linewidth',2);
-%xlabel('parameter x');
-%ylabel('distribution');
-%legend('true model evals', 'surrogate');
-%set(gca, 'fontsize', 20);
+figure(1);
+plot(ff, ff_hat, '*');
+set(gca, 'fontsize', 20);
+xlabel('true model');
+ylabel('surrogate');
+print -depsc surr.eps
 
-
+figure(2)
+hold on;
+histnorm(ff);
+plot(xi, pdf, 'r', 'linewidth',2);
+xlabel('parameter x');
+ylabel('distribution');
+legend('true model evals', 'surrogate');
+set(gca, 'fontsize', 20);
+print -depsc pdf_comp.eps

### 2018-07-30 Paper/intro.tex
...

@@
 
-\paragraph{Motivation}
-Surrogate modeling has become a critical component of scientific computing
-owing to the emergence of the field of uncertainty quantification for
-scientific and engineering applications. Commonly used approaches for
-surrogate modeling include polynomial chaos expansions
-(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
-regression splines (MARS)~\cite{friedman93}, Gaussian processes
-(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A 
-pertinent challenge associated with surrogate construction involves the
-process of \textit{training} that typically requires a large number of model runs.
-In situations involving large-dimensional systems,
-and computationally intensive simulations, the training of a surrogate
-becomes remarkably challenging and even prohibitive in some cases. A possible
-approach for mitigating this challenge involves computation of sensitivity
-measures (e.g. Sobol' indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08})
-to ascertain important parameters that predominantly contribute towards the variability
-of the model output. Sensitivity-based dimension reduction could thus help
-reduce the computational effort significantly. However, numerically estimating
-the Sobol' indices that involve multi-dimensional integrals can be a demanding task
-in itself. In fact, surrogate models are constructed to estimate the 
-Sobol sensitivity indices for a variety of applications including in ocean 
+%\paragraph{Motivation}
+Computing statistical properties of 
+complex systems containing uncertain parameters is
+challening due to the need for a large number of expensive model evaluations. 
+Surrogate models make such computations possible by replacing 
+expensive model runs with cheap evaluations of an approximate model.
+%
+%Surrogate modeling has become a critical component of scientific computing
+%owing to the emergence of the field of uncertainty quantification for
+%scientific and engineering applications. 
+%
+Commonly used approaches for surrogate modeling include polynomial chaos
+expansions (PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate
+adaptive regression splines (MARS)~\cite{friedman93}, Gaussian processes
+(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A pertinent
+challenge associated with surrogate construction involves the process of
+\textit{training} that typically requires a large number of model runs.  In
+situations involving large-dimensional systems, and computationally intensive
+simulations, the training of a surrogate becomes challenging and
+even prohibitive in some cases. A possible approach for mitigating this
+challenge involves computation of global sensitivity measures such as Sobol'
+indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08} to identify
+the \emph{important parameters}---i.e., parameters that predominantly
+contribute towards the variability of the model output.
+
+Sensitivity-based
+dimension reduction can help reduce the computational effort
+significantly. However, numerically estimating the Sobol' indices, which
+involve multi-dimensional integrals, can be a demanding task in itself. In
+fact, often surrogate models are constructed to estimate the Sobol' sensitivity
+indices; this has been done for a variety of applications including in ocean
 modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
 geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
-and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
-to name a few. Hence, this common practical issue in scientific computing can
-be characterized as a ``chicken-and-egg" problem.
+and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014} to
+name a few. 
+We are thus, faced with a ``chicken-and-egg'' problem: on the one hand,
+computing global sensitivity measures enable dimension reduction, which in turn
+enable efficient surrogate model construction.  On the other hand, computing
+sensitivity measures is expensive and is often made possible by using
+surrogate models. Development of an approach for 
+overcoming this chicken-and-egg problem is a major goal of this article.
+
+%Hence, this common practical issue in scientific computing can
+%be characterized as a ``chicken-and-egg" problem.
 

### 2018-07-31 Paper/bg.tex
..

@@
 observed in the numerical experiments in the present work, that a modest MC sample size is often sufficient for computing~\eqref{eq:mu} with
-reasonable accuracy to indentify the unimportant inputs. Moreover, the
+reasonable accuracy to identify the unimportant inputs. Moreover, the
 computational efficiency for estimating $\mu_i$ can be enhanced by using

### 2018-07-31 Paper/cover.tex
..

@@
 \textsc{
-Derivative-based global sensitivity approach to efficient surrogate modelling
-with Polynomial Chaos
+Sensitivity-driven adaptive construction of reduced-space surrogates
 }
@@
 \\
-Submitted to: \> \textit{Reliability Engineering and System Safety} \\
-\>  May 2018\\
+Submitted to: \> \textit{Journal of Scientific Computing} \\
+\>  July 2018\\
 

### 2018-07-31 Paper/examples.tex
..

@@
 
-The borehole function is a benchmark reference problem in sensitivity analysis.
-\alennote{Give references}
+The borehole function~\cite{Morris:1993} is a benchmark reference problem in sensitivity analysis.
 It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of

### 2018-07-31 Paper/method.tex
..

@@
 of $\bm{\theta}$ and corresponding model
-output at each sample point is computed. The new set of model evaluations
+output at each sample point is computed. The new set of gradient evaluations
 combined with prior evaluations is used to update parameter ranks. Additionally,
@@
 Another alternative for efficient gradient computation is the use of 
-automatic differentiation.
+automatic differentiation~\cite{Kiparissides:2009}.
 

### 2018-07-31 Paper/abstract.tex
..

@@
 \section*{Abstract}
+Surrogate modeling has become a critical component of scientific computing
+in situations involving expensive model evaluations. However, training a
+surrogate model can be remarkably challenging and even computationally
+prohibitive in the case of intensive simulations and large-dimensional
+systems.
 We develop a systematic approach for surrogate model
@@
 surrogates using the proposed framework.
+\vspace{2mm}
+
+\noindent
+\textbf{Keywords}: Derivative-based global sensitivity,
+polynomial chaos, parameter screening, reduced-space surrogate

### 2018-07-31 Paper/intro.tex
..

@@
 complex systems containing uncertain parameters is
-challening due to the need for a large number of expensive model evaluations. 
+challenging due to the need for a large number of expensive model evaluations. 
 Surrogate models make such computations possible by replacing 
@@
 adaptive regression splines (MARS)~\cite{friedman93}, Gaussian processes
-(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A pertinent
+(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}, and neural
+networks~\cite{Funahashi:1989,Specht:1990}. A pertinent
 challenge associated with surrogate construction involves the process of
 \textit{training} that typically requires a large number of model runs.  In
-situations involving large-dimensional systems, and computationally intensive
+situations involving large-dimensional systems and computationally intensive
 simulations, the training of a surrogate becomes challenging and
@@
 challenge involves computation of global sensitivity measures such as Sobol'
-indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08} to identify
+indices~\cite{Sobol93} to identify
 the \emph{important parameters}---i.e., parameters that predominantly
@@
 Sensitivity-based
-dimension reduction can help reduce the computational effort
+dimension reduction can help reduce the computational effort associated with
+surrogate construction,
 significantly. However, numerically estimating the Sobol' indices, which
 involve multi-dimensional integrals, can be a demanding task in itself. In
-fact, often surrogate models are constructed to estimate the Sobol' sensitivity
-indices; this has been done for a variety of applications including in ocean
+fact, because of the large number of samples required, computation of Sobol'
+indices is often done using surrogate models, as shown in a variety of 
+applications including in ocean
 modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
@@
 optimal use of computational resources for surrogate construction in a 
-reduced-input space. Specifically, we reduce the dimensionality of the
-input space by using the derivative-based global sensitivity
+reduced input space. Specifically, we reduce the dimensionality of the
+input space by using derivative-based global sensitivity
 analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
 which enables a tractable approach for global sensitivity
-analysis~\cite{Kucherenko:2016}. The links between derivative based
+analysis~\cite{Kucherenko:2016}. The links between derivative-based
 global sensitivity measures (DGSMs) and total Sobol'
 indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
-basis for their use in identifying unimportant parameters. In addition
+basis for their use in identifying important uncertainty contributors. 
+In addition
 to the construction of an efficient surrogate in the reduced space,
@@
 encapsulated by the model, and allows for an efficient approach to calibration
-of the important inputs.
+of the important model parameters.
 
@@
 
-\paragraph{Our approach}
-We present a strategy for identifying and screening uncertain model parameters
+We present a strategy for identifying and screening uncertain model inputs
 that are significantly less important than the rest, thereby reducing the
@@
 iterative manner.  To make optimum use of computational resources, batches of
-model evaluations are performed iteratively, and convergence of our DGSM based
+model evaluations are performed iteratively, and convergence of our DGSM-based
 screening metric is tested successively. Moreover, a series of verification steps
-incorporated in our method enable monitoring the accuracy of the parameter-screening
+incorporated in our method enable monitoring the accuracy of the parameter 
+screening
 and the resulting surrogate model.  Our approach is agnostic to the choice of
@@
 
-\paragraph{Contributions}
 The contributions of this article are as follows: (i) We establish a robust and
@@
 
-\paragraph{Paper outline}
-This article is structured as follows. In section~\ref{sec:bg}, we provide a
+The remainder of this article is structured as follows. 
+In section~\ref{sec:bg}, we provide a
 brief introduction to DGSMs as well as the polynomial chaos methodology used in

### 2018-07-31 Paper/intro.tex
..

@@
 expansions (PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate
-adaptive regression splines (MARS)~\cite{friedman93}, Gaussian processes
-(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}, and neural
+adaptive regression splines (MARS)~\cite{friedman93}, Gaussian process
+(GP) and Kriging models~\cite{Rasmussen:2004,Stein:2012}, and neural
 networks~\cite{Funahashi:1989,Specht:1990}. A pertinent

### 2018-10-14 Paper/revision/reviewer_replies.tex
replies ...

\documentclass[11pt,final]{article}
\renewcommand*\familydefault{\sfdefault}
%\usepackage{amssymb,amsmath,amsfonts,comment}
%\usepackage{amsmath,amssymb,graphicx,subfigure,psfrag}
\usepackage{amsmath,amssymb,graphicx,subfigure,psfrag,upgreek}
\usepackage{algorithm,algorithmic}
\usepackage{amssymb,mathrsfs}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{color,pdfcolmk}
\newcommand{\todo}[1]{\noindent\emph{\textcolor{red}{Todo: #1\:}}}
%\newcommand{\alennote}[1]{\noindent\emph{\vspace{1ex}\textcolor{cyan}{Alen: #1\:}}\\[1ex]}
\newcommand{\referee}[1]{\vspace{.1ex}\noindent{\textcolor{blue}{#1}}}

\begin{document}

We thank the reviewers for their careful reading of our article 
and the helpful comments and suggestions.
Please find below point-by-point replies (in black) to your comments and
questions (which are reprinted in blue). To give you an overview of all the
changes in the paper, we also provide a diff-document that highlights the
changes between the initial submission and this re-submission.\\[1ex]

\section{Replies to reviewer \#1}
\referee{This draft proposed a systematic approach for surrogate model construction in
reduced input parameter spaces in order to reduce the number of model
evaluations. The key idea is to approximate the screening parameter iteratively
in order to identify the unimportant inputs. The screening procedure also
integrates with the adaptive construction of a surrogate in the reduced space
to improve the efficiency of the methods. Several numerical examples are used
to demonstrate the efficiency and accuracy of the proposed framework.}

Comments and Questions:
\begin{enumerate}

\item \referee{P16, Figure.2,  the estimated screening parameters eq (5) based on eq(1)
quickly converge with a small number of samples (5-10 samples). It seems that
if $\mu_i$ is based on eq(1), it will still require a reasonable amount of
samples, can authors comment on why this example converges with a small number
of samples? The same question applies to Figure 5 and Figure 7.}

\item 
\referee{P17, Figure 3, what's the degree of the PCE used in the example? The same
question applies to Figure 6 and Figure 8.}

\item
\referee{
P25, Figure 7, it seems that the rank of the parameters and the difference of
$\mu_s$ doesn't change too much over iterations. Does it indicate the initial
parameter screening  (line 1-6 in Algorithm 1) is good enough for ranking the
parameters? Can the authors plot the similar figure for other examples to see
if the iterative screening procedure does make a difference on the ranking the
parameters compared with the initial parameter screening step?}
\end{enumerate}

\section{Replies to reviewer \#2}

\referee{
An adaptive surrogate model construction approach in reduced input parameter
space is proposed in this paper. Instead of variance based sensitivity indices,
derivative based global sensitivity measures are employed to calibration of the
important model inputs, upon which surrogate models are constructed. To
demonstrate the computational advantage, the proposed approach is then
validated against three examples.  The reviewer’s recommendation is ``major
revision''.}

Major comments:
\begin{enumerate}

\item
\referee{
In this paper, the constructed surrogate model is either a RSS or a FSS. Based
on the diagram on page 12, the resulting RSS is built upon the not sufficiently
accurate FSS model (which could lead the accuracy to decrease further), or
is the RSS constructed directly from the original model with reduced input
parameters? The diagram is ambigous on this issue.}

\item
\referee{The reviewer would also like to see the comparison of the computational cost
(not just the numerical results) of DGSMs to variance based sensitivity indices
with increasing parameter dimension, e.g. Sobol’ indices incorporated with
sparse grid, since the difference decreases with increasing number of parameters.}

\item 
\referee{In section 4 and 5, no predictive convergence using the test data sample is
presented, only the convergence of $\epsilon_\text{LOO}$, which reuses the training data as
the validation set, is shown. This shows only the convergence of the model,
and does not necessarily indicate the (predictive) accuracy of the constructed
model, hence could lead to false conclusion. The reviewer would like to see the
convergence of $\epsilon_{L_2}$.}

\item 
\referee{How would the proposed approach behave when presented with severe nonlinearity
or rare events where the screening metrics could misrepresent the significance
of parameters?}

\item 
\referee{The reviewer would like to see some comments on the change of computational
cost of the proposed approach with respect to the increase of parameter dimensions.}
\end{enumerate}

Minor comments have been addressed in the revised draft. Thanks for pointing them out.

\end{document}

### 2018-10-16 Paper/revision/reviewer_replies.tex
..

@@
 
-We thank the reviewers for their careful reading of our article 
-and the helpful comments and suggestions.
-Please find below point-by-point replies (in black) to your comments and
-questions (which are reprinted in blue). To give you an overview of all the
-changes in the paper, we also provide a diff-document that highlights the
-changes between the initial submission and this re-submission.\\[1ex]
+%We thank the reviewers for their careful reading of our article 
+%and the helpful comments and suggestions.
+%Please find below point-by-point replies (in black) to your comments and
+%questions (which are reprinted in blue). To give you an overview of all the
+%changes in the paper, we also provide a diff-document that highlights the
+%changes between the initial submission and this re-submission.\\[1ex]
+\begin{center}
+{\bf Summary of Modifications to JOMP-D-18-00403}\\[6pt]
+{\bf Sensitivity-driven Adaptive Construction of Reduced-space Surrogates}\\[6pt]
+By \\
+Manav Vohra, Alen Alexanderian, Cosmin Safta, Sankaran Mahadevan 
+\end{center}
+
+\baselineskip=22pt
+
+\vspace*{1in}
+
+We thank the reviewers for their assessment of our manuscript. Please find
+below point-by-point replies (in black) to your comments and questions
+(reprinted in blue). Where possible, key modifications have been highlighted
+in blue in the revised manuscript. We sincerely hope that with these
+modifications, the paper is found suitable for publication in the
+{\it Journal of Scientific Computing}.
+
+\clearpage
 
@@
 of samples? The same question applies to Figure 5 and Figure 7.}
+
+Convergence behavior in this case depends upon the variability in the gradient of
+$G(\theta)$ with respect to individual parameters, $\theta_i$ in their respective
+domains. For the numerical tests and the application considered in this work, the
+gradient is not observed to vary significantly in the considered domain of the
+parameters. In other words, the variance of the estimator is low. 
+Hence, a small number of Monte Carlo samples are able to estimate
+the screening parameters. This is a common observation in many practical
+applications, and therefore the proposed methodology involving an iterative
+approach can yield significant computational savings.
+
+These points have been emphasized in the discussion in Section~6 (Summary and
+Conclusion) in the revised manuscript.
 

### 2018-10-16 Paper/disc.tex
..

@@
 application, the proposed framework seems quite promising in its
-potential for identifying the unimportant model inputs. These
-observations could be exploited to construct efficient model surrogates
+potential for identifying the unimportant model inputs. \rebut{In fact, in 
+the numerical tests and the chemical kinetics application presented in this
+work, reasonable estimates of the screening metric are obtained during the
+initial screening step with only 5 samples. This is indicative of a small
+degree of
+variability in the gradient of the model output with respect to individual
+parameters, and therefore, a low variance of the Monte Carlo estimator.}
+These observations could be exploited to construct efficient model surrogates
 in a reduced input space. However, it is important to remain cognizant

### 2018-10-17 Paper/revision/reviewer_replies.tex
..

@@
 
+In the borehole test case, the degree of the PCE was found to be 3 in the reduced space (4D)
+and 5 in the full space (7D). In the case of semilinear elliptic PDE, the degree of the PCE was 
+found to be 3 in the reduced space (5D) as well as the original space (10D). For the reaction
+kinetics application, the degree of the PCE was found to be 3 in the reduced space (4D) and 
+2 in the full space (19D).
+
+The captions of Figures 3, 6, and 8 have been updated to include this information.
+
 \item
@@
 parameters compared with the initial parameter screening step?}
+
+The reviewer is correct in pointing out from Figure 7 that the initial screening step
+reasonably approximates the screening metric. The is also observed in
+Figure 5 for the semilinear elliptic PDE test case. It is also true in the borehole test
+case and a similar figure has been included for this example in the revised manuscript
+(Figure 2c) as suggested by the reviewer. The reason for this observation has already
+been discussed in response to Comment~1 above and included in the revised manuscript.
+
 \end{enumerate}
@@
 
+The reviewer correctly points out that the resulting surrogate model is either an RSS or
+an FSS. However, we would like to clarify that the main purpose of the proposed
+methodology is to construct an RSS based on estimates of the screening metric.
+However, since estimating the metric requires model evaluations, we further exploit these
+evaluations to construct an FSS (free of cost) using regression-based approaches 
+mentioned in the paper. Note that the FSS construction is performed simultaneously to 
+ensure that the computational effort associated with obtaining converged estimates of
+the screening metric and RSS construction does not overshoot that required for
+constructing a sufficiently accurate FSS.
+
+The above points are already included in the paragraph on the discussion of the proposed
+methodology in Section 3. Nevertheless, based on the reviewer's feedback, we have tried to
+clarify and emphasize these points in the first paragraph in Section 6 (Summary and Conclusion)
+in the revised manuscript.
+
 \item
@@
 
+As suggested by the reviewer, the plots and related discussion pertaining to the convergence 
+of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 and 
+the chemical kinetics application presented in Section 4.
+
 \item 
@@
 of parameters?}
+
+Severe non-linearity in the model output as a function of uncertain inputs could potentially lead
+to a significantly large variability in its gradient. Hence, a large number of Monte Carlo samples might be
+required to estimate the screening metrics with reasonable accuracy in this case depending upon the
+application. Therefore, the computational effort is expected to increase in such cases. In the presence
+of rare events, the variance-based approaches typically lead to inaccurate estimates of 
+parametric sensitivities. Since the proposed methodology in this work aims to reduce the computational
+effort pertaining to total-effect Sobol index which is a variance-based measure, it might lead to
+inaccurate estimates of the screening metric and therefore, the relative importance of the. uncertain
+inputs.
+
+A brief discussion based on the above points has been included in Section 6 (Summary and Discussion).
 
@@
 
-Minor comments have been addressed in the revised draft. Thanks for pointing them out.
+Minor comments have also been addressed in the revised manuscript. The authors thank
+the reviewer for pointing those out as well.
 

### 2018-10-17 Paper/app.tex
..

@@
 and in 3D for
-the fuel-lean case. Figure~\ref{fig:err_samples_kinetics} illustrates a
+the fuel-lean case. Figure~\ref{fig:err_samples_kinetics}~(left) illustrates a
 comparison of convergence characteristics for the PCEs constructed in the
@@
  \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_kinetics}
-\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
+  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics}
+   \includegraphics[width=0.44\textwidth]{./Figures/errL2_samples_kinetics}
+\caption{Left: A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
 number of model evaluations in the full-space (19D) and the reduced-space (4D)
-for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0.}
+for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
+the resulting PCE was found to be 3 and 2 in the 4D and the 19D case respectively.
+Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
+for the PCEs constructed in 4D and 19D.}}
 \label{fig:err_samples_kinetics}
@@
 at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
+\rebut{Additionally, the
+convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
+Figure~\ref{fig:err_samples_kinetics}~(right) indicates that for the case of 10
+samples, the 4D PCE is observed to be more accurate. However, the 19D PCE
+is observed to be more accurate by an order of magnitude as the sample size
+increases. Specifically, the 4D PCE was found to be accurate within 1.8$\%$ in the
+fuel-rich case, and within 3.1$\%$ in the fuel-lean case. Therefore, the 4D PCE
+is still observed to be reasonably accurate in this case. Moreover, its faster convergence
+as mentioned earlier should help reduce computational effort associated with
+surrogate model construction.}
 Similar trends (not included) were observed in the fuel-lean case.
 
-Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the 
-cross-validation set, the RSS was found to be accurate within 1.8$\%$ in the
-fuel-rich case, and
-within 3.1$\%$ in the fuel-lean case. Model evaluations at 1000 samples in the test suite
+Model evaluations at 1000 samples in the test suite
 are further used to plot a normalized histogram of the ignition time in 

### 2018-10-17 Paper/disc.tex
..

@@
 the available set of model evaluations. Both, RSS and FSS are
-constructed using regression-based sparse PCEs. Simultaneous construction
-of the FSS ensures that the computational effort associated with the proposed framework
-does not overshoot the effort required to construct the FSS directly.
-Hence, the RSS is constructed only in situations where computational gains are
-expected.
+constructed using regression-based sparse PCEs. \rebut{Note however that the FSS is
+constructed in an independent manner to ensure that the computational effort associated
+with the proposed methodology does not overshoot the effort required to construct the 
+FSS directly. Therefore, it does not impact the accuracy of the RSS which is only
+constructed in situations where computational gains are expected.}
 
@@
 satisfied, enhances the accuracy of the PCE-based surrogates as well.  
+\rebut{Moreover, in the presence of severe non-linearities in the model output
+leading to significant variability in its gradient in the considered input domain,
+the number of samples and hence, the computational effort associated with
+the estimation of screening metrics would expectedly 
+increase. The extent of increase in the effort would of course depend upon the
+application. In the case of rare events, the variance-based methods typically
+lead to inaccurate estimates of the uncertainty in the model output. Since the
+methodology proposed in this work is based on reducing computational
+effort associated with variance-based sensitivity analysis, specifically, the
+total-effect Sobol' index, it might lead to erroneous estimates of the
+screening metrics and consequently the relative importance of the
+uncertain parameters.}
 Additionally, the proposed framework does not

### 2018-10-17 Paper/examples.tex
..

@@
 estimates of $\mathcal{T}(\theta_i)$. Shown in
-Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
+Figure~\ref{fig:sense_bore}(a) are estimates of these indices corresponding to the
 uncertain parameters in the borehole function using 10$^6$ MC
@@
  \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
-  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
+ \begin{tabular}{cc}
+  \includegraphics[width=0.45\textwidth]{./Figures/sense_borehole}
+  &
+  \includegraphics[width=0.49\textwidth]{./Figures/ub_conv_borehole}
+  \\ (a) & (b)
+  \end{tabular}
+  \\
+  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_borehole2}
+  \\ (c)
 \caption{
-Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain
+(a) Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain
 parameters in the
-borehole discharge function in~\eqref{eq:bore}. Right: 
+borehole discharge function in~\eqref{eq:bore}; (b)
 Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
 against number of samples. Also included in the legend are estimates of
-$\mathcal{T}(\theta_i)$ in each case in the legend.}
+$\mathcal{T}(\theta_i)$ in each case in the legend; \rebut{and (c) Estimates of
+$\widehat{\mathcal{C}_i\mu_i}$ for individual parameters using $N$ = 5, 10,
+15, and 20 samples in the full parameter space.}}
 \label{fig:sense_bore}
@@
 
-In Figure~\ref{fig:sense_bore}~(right), we plot estimates of the screening parameter 
+In Figure~\ref{fig:sense_bore}(b), we plot estimates of the screening parameter 
 $\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
-samples used for approximating $\mu_i$ using~\eqref{eq:mu}.
+samples used for approximating $\mu_i$ using~\eqref{eq:mu}. \rebut{Additionally,
+to illustrate a comparison of the estimates of $\widehat{\mathcal{C}_i\mu_i}$ obtained
+at the end of the initial screening step, i.e. $N$~=~5, with subsequent steps, we plot
+them for individual parameters at $N$~=`5, 10, 15, and 20 samples in Figure~\ref{fig:sense_bore}(c).}
 Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement
@@
 fixing $K_w$ in the latter at their respective mean values. In
-Figure~\ref{fig:conv_bore}~(left), we compare convergence of PCEs constructed in the
+Figure~\ref{fig:conv_bore}(a), we compare convergence of PCEs constructed in the
 full space (7D) with those constructed in the two reduced spaces (4D and 5D)
@@
  \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_borehole}
-  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_borehole}
-\caption{Left: A comparison of order of the leave-one-out-error 
+ \begin{tabular}{cc}
+  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
+  &
+  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
+  \\ (a) & (b)
+  \end{tabular}
+  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
+  \\ (c)
+\caption{(a) A comparison of order of the leave-one-out-error 
 ($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
-used for constructing the PCE in 4, 5, and 7 dimensions. Right: A comparison of
+used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
+the resulting PCE was found to be 3, 2,and 5 in the 4D, 5D, and 7D case respectively;
+(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
+for the PCEs constructed in 4D, 5D, and 7D};
+and (c) A comparison of
 PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
@@
 space seems much higher. Latin hypercube sampling (LHS) was used in
-each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}~(left)
+each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
 is not expected to decrease monotonically with the increase in sample size
 owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
+\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
+size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
+clearly demonstrates the trade-off between
+computational effort associated with surrogate construction and its predictive 
+accuracy. For a small sample size of 20, the relative  error in the case of 4D
+PCE is found to be the smallest. However, as the sample size increases, the higher
+order PCE becomes more accurate. Note that the same set of 50 samples in the
+validation test suite were used in each case. Hence, when limited computational resources
+are available, the proposed methodology could yield substantial gains due to fast
+convergence as well as higher accuracy of the surrogate in the reduced space.
+The gains are expected to increase exponentially as the dimensionality of the 
+input space increases.}
 
-As discussed earlier in this section, the reduced-space PCE's are verified for
-predictive accuracy in a least-squares sense and a probabilistic sense.
-Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$ based on 50 samples in the
-validation test suite were
+Specifically, the estimates for $\epsilon_{\mbox{\tiny{L-2}}}$ were
 found to be 0.0551 and 0.0112 for the 4D and 5D PCE's, respectively. In other
@@
 however, is lower in the case of 4D PCE (Figure~\ref{fig:conv_bore}).
-This illustrates the
-trade-off between accuracy and computational efficiency for the present 
-problem. Generally, the required level of accuracy is problem dependent. 
+Generally, the required level of accuracy is problem dependent. 
 The present framework allows for moving towards higher fidelity 
@@
 
-Figure~\ref{fig:conv_bore}~(right) illustrates a comparison of the PDFs
+Figure~\ref{fig:conv_bore}(c) illustrates a comparison of the PDFs
 of the
@@
 illustrate the comparison of convergence characteristics of the PCEs constructed in the
-full parameter space (10D) and the reduced space (5D) in Figure~\ref{fig:conv_elliptic} (left). 
+full parameter space (10D) and the reduced space (5D) in Figure~\ref{fig:conv_elliptic}(a). 
 As expected, the RSS converges considerably faster. Using model evaluations at 90
@@
  \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_elliptic}
-  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_elliptic}
-\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
-PCEs constructed in 10 and 5 dimensions to compare their convergence characteristics. 
-Right: PDF of the QoI, $\mathcal{F}(\vec\theta)$ in~\eqref{eq:semilinear} is
-plotted using the full-surrogate and the reduced-space PC surrogate.}
+ \begin{tabular}{cc}
+  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_elliptic}
+  &
+  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_elliptic}
+  \\ (a) & (b)
+  \end{tabular}
+  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_elliptic}
+  \\ (c)
+\caption{(a) Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample 
+size for PCEs constructed in 10 and 5 dimensions to compare their convergence 
+characteristics. \rebut{The degree of
+the resulting PCE was found to be 3 in both cases; 
+(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
+for the PCEs constructed in 5D and 7D}; 
+and (c) PDF of the QoI, $\mathcal{F}(\vec\theta)$ in~\eqref{eq:semilinear}
+is plotted using the full-surrogate and the reduced-space PC surrogate.}
 \label{fig:conv_elliptic}
@@
 \end{figure}
+%
+\rebut{The comparison of convergence characteristics of $\epsilon_{\mbox{\tiny{L-2}}}$
+illustrated in Figure~\ref{fig:conv_elliptic}(b) indicates that for a small sample size of 20,
+the surrogate constructed in the reduced space performs better in terms of
+predictability. However, as the sample size increases, the full space is observed to
+be slightly more accurate. However, the order of the accuracy is found to be 
+consistent in both cases until the sample size is less than 80. When the sample size
+increases to 90, the 19D PCE is observed to be more accurate by an order of magnitude.
+However, the corresponding value of $\epsilon_{\mbox{\tiny{LOO}}}$ is~$\mathcal{O}(10^{-1})$.
+Hence, the 19D PCE does not seem to have fully  converged and requires additional 
+model evaluations. Therefore, considering
+fast convergence of the surrogate in the 5D space and predictive accuracy comparable
+to the 19D PCE,
+the proposed methodology significantly reduces computational effort in this case.}
 
@@
 validation test-suite, in 
-Figure~\ref{fig:conv_elliptic}~(right). While the two PDFs are in favorable agreement,
+Figure~\ref{fig:conv_elliptic}(c). While the two PDFs are in favorable agreement,
 the modal estimate and the spread in the QoI based on the histogram is also captured

### 2018-10-17 Paper/revision/reviewer_replies.tex
..

@@
 The reviewer is correct in pointing out from Figure 7 that the initial screening step
-reasonably approximates the screening metric. The is also observed in
+reasonably approximates the screening metric. The same is observed in
 Figure 5 for the semilinear elliptic PDE test case. It is also true in the borehole test
@@
 As suggested by the reviewer, the plots and related discussion pertaining to the convergence 
-of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 and 
-the chemical kinetics application presented in Section 4.
+of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 (Figures 3b
+and 6b) and 
+the chemical kinetics application presented in Section 4 (Figure 8, right).
 

### 2018-10-24 Paper/revision/reviewer_replies.tex
..

@@
 
-In the borehole test case, the degree of the PCE was found to be 3 in the reduced space (4D)
-and 5 in the full space (7D). In the case of semilinear elliptic PDE, the degree of the PCE was 
-found to be 3 in the reduced space (5D) as well as the original space (10D). For the reaction
-kinetics application, the degree of the PCE was found to be 3 in the reduced space (4D) and 
-2 in the full space (19D).
+Sparse PCEs were constructed using least angle regression by means of UQLab software
+for the two numerical tests (Borehole and the semilinear elliptic PDE),
+and the reaction kinetics application in this work.  
+In the borehole test case, the PCE constructed using 50 training points for the 7D, 5D, and
+4D cases was found to be of degree 2, 2, and 3 respectively.  
+In the semilinear elliptic PDE example, the PCE constructed using 90 training
+points for the 10D and 5D cases was found to be of degree 2 and 3 respectively.
+For the reaction kinetics application, the PCE constructed using 60 training points
+for the 19D and 4D cases was found to be of degree 1 and 3 respectively.
 

### 2018-10-24 Paper/app.tex
..

@@
 source of clean energy for applications such as 
-transportation~\cite{Das:1996}. 
+transportation~\cite{Das:1996} and fuel cell 
+applications~\cite{Loges:2008,Cosnier:2016}. \rebut{We begin by providing
+the necessary background information for setting up the problem
+in~\ref{sub:setup}. Results and discussion based on the implementation
+of the proposed framework are provided in~\ref{sub:imp}. Finally, 
+in~\ref{sub:cost}, we
+provide a comparative analysis of the computational cost involved
+in determining relative parameter importance using DGSMs and the
+total-effect Sobol index as the dimensionality increases from 19 to 33
+for the present application.}
+
+\subsection{Problem Set-up}
+\label{sub:setup}  
 The mechanism comprises of 19 reactions including chain reactions,
@@
 
+\subsection{DGSM-guided surrogate construction}
+\label{sub:imp}
 We apply the parameter screening algorithm with the following
@@
  \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_kinetics_rich}
-  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_kinetics_lean}
+  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_rich}
+  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_lean}
   \\ \vspace{2mm}
-  \includegraphics[width=0.48\textwidth]{./Figures/mu_rich}
-  \includegraphics[width=0.48\textwidth]{./Figures/mu_lean}
+  \includegraphics[width=0.45\textwidth]{./Figures/mu_rich}
+  \includegraphics[width=0.45\textwidth]{./Figures/mu_lean}
 \caption{Top: Estimates of $\widehat{\mathcal{C}_i\mu_i}$ for $A_i$'s in the case
@@
 for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
-the resulting PCE was found to be 3 and 2 in the 4D and the 19D case respectively.
+the PCE constructed using 60 training points was found to be 1 and 3 in the 19D and the 4D cases respectively.
 Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
@@
  \begin{center}
-  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_rich}
-  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_lean}
+  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_rich}
+  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_lean}
 \caption{A normalized histogram based on model evaluations at 1000 samples is plotted
@@
 mechanism.
+
+\rebut{
+\subsection{Comparative cost analysis}
+\label{sub:cost}
+
+In this section, we perform a comparative analysis of the computational cost
+associated with obtaining converged estimates of parametric sensitivities
+using DGSM, and the total-effect Sobol indices ($\mathcal{T}(\theta_i)$). The former is computed
+using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
+estimated analytically using a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
+using a PCE has been shown to be more efficient compared to sampling techniques.
+Moreover, a sparse-basis PCE is expected to require fewer training points which
+enhances computational savings. To investigate the impact of the dimensionality, the
+analysis is performed with 19 uncertain parameters, i.e.
+the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
+33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are also considered to
+be uncertain. The $E_{a,i}$'s are also considered to be uniformly distributed in the
+interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
+for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
+$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therfore the
+total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.
+
+The 33-dimensional sparse basis PCE was assessed for its convergence characteristics
+and its predictive accuracy using $\epsilon_{\mbox{\tiny LOO}}$~(see~\eqref{eq:loo}) and
+$\epsilon_{\mbox{\tiny{L-2}}}$~(see~\eqref{eq:l2}) respectively as shown in
+Figure~\ref{fig:err_samples}.  
+%
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics33D}
+\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$  and $\epsilon_{\mbox{\tiny{L-2}}}$
+as a function of the number of training points in the 33D parameter space 
+for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. The degree of
+the PCE constructed using 500 training points was found to be 3.}
+\label{fig:err_samples}
+\end{center}
+\end{figure}
+%
+The sparse-basis PCEs constructed in the 19 and the 33 dimensional parameter
+space are considered to have converged once $\epsilon_\text{\tiny LOO}$ is found to be
+smaller than 6.0$\times$10$^{-3}$. As observed in Figures~\ref{fig:err_samples_kinetics}
+and~\ref{fig:err_samples}, the number of training points required in the 19D
+and the 33D cases are found to be 60 and 500 respectively. As expected, the predictive
+accuracy is observed to increase with increase in the number of training points in both cases.
+The estimate of $\epsilon_{\mbox{\tiny{L-2}}}$ was found to be 7.22$\times$10$^{-2}$ using the
+converged 33D PCE and an independent set of model evaluations at 1000 samples.
+
+Sensitivity estimates for the 33 uncertain parameters are hence determined
+using the DGSM-based strategy and by evaluating $\mathcal{T}(\theta_i)$ analytically
+using the sparse-basis PCE as discussed earlier in this section. The estimates based
+on the two approaches were plotted separately and placed side-by-side for comparison
+in Figure~\ref{fig:sense33D}.
+%
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.42\textwidth]{./Figures/ub33D}
+  \includegraphics[width=0.40\textwidth]{./Figures/sens_kinetics33D}
+\caption{
+Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each 
+uncertain parameter, obtained using $N$ = 5, 10, 15, and 20 samples in the full parameter space.
+Right: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
+semilinear elliptic PDE~\eqref{eq:semilinear}.}
+\label{fig:sense33D}
+\end{center}
+\end{figure}
+%
+
+}

### 2018-10-24 Paper/examples.tex
..

@@
 used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
-the resulting PCE was found to be 3, 2,and 5 in the 4D, 5D, and 7D case respectively;
+the PCE using 50 training points was found to be 3, 2,and 2 in the 4D, 5D, and 7D case respectively;
 (b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
@@
 characteristics. \rebut{The degree of
-the resulting PCE was found to be 3 in both cases; 
+the PCE constructed using 90 training points was found to be 2 and 3 in the
+10D and 5D cases respectively; 
 (b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 

### 2018-10-25 Paper/revision/reviewer_replies.tex
..

@@
 These points have been emphasized in the discussion in Section~6 (Summary and
-Conclusion) in the revised manuscript.
+Conclusion, Page 34) in the revised manuscript.
 
@@
 an FSS. However, we would like to clarify that the main purpose of the proposed
-methodology is to construct an RSS based on estimates of the screening metric.
+methodology is to construct an RSS based on estimates of a screening metric that
+involves derivative-based global sensitivity measure (DGSM) for each uncertain parameter.
 However, since estimating the metric requires model evaluations, we further exploit these
-evaluations to construct an FSS (free of cost) using regression-based approaches 
-mentioned in the paper. Note that the FSS construction is performed simultaneously to 
+evaluations to construct an FSS (free of cost) using a sparse regression-based approach
+as mentioned in the paper. Note that the FSS construction is performed simultaneously to 
 ensure that the computational effort associated with obtaining converged estimates of
@@
 sparse grid, since the difference decreases with increasing number of parameters.}
+
+As suggested by the reviewer, the computational cost pertaining to the estimation of DGSM-based
+sensitivity indices is compared with the cost associated with estimating the total-effect Sobol' indices
+for the 19-dimensional reaction kinetics application in this work. Additionally, the comparison is 
+performed for the same application with 33 uncertain rate-controlling parameters to investigate
+the impact of dimensionality.
+
+A new sub-section (5.3) on ``comparative cost analysis" has been included in the revised
+manuscript.
 
@@
 effort pertaining to total-effect Sobol index which is a variance-based measure, it might lead to
-inaccurate estimates of the screening metric and therefore, the relative importance of the. uncertain
+inaccurate estimates of the screening metric and therefore to erroneous relative importance of the uncertain
 inputs.
 
-A brief discussion based on the above points has been included in Section 6 (Summary and Discussion).
+A brief discussion based on the above points has been included in the last paragraph in
+Section 6 (Summary and Discussion).
 
@@
 cost of the proposed approach with respect to the increase of parameter dimensions.}
+
+As mentioned earlier in the response to Comment $\#$ 2, a comparative analysis of the
+computational cost with increasing parameter dimensions has been included for the reaction
+kinetics application in Section 5.3 in the revised manuscript. Additional comments pertaining
+to the increase in computational cost and expected gains with dimensionality, based on
+our findings have been included in Section 6 (Summary and Discussion).
+
 \end{enumerate}

### 2018-10-25 Paper/app.tex
..

@@
 in determining relative parameter importance using DGSMs and the
-total-effect Sobol index as the dimensionality increases from 19 to 33
+total-effect Sobol' index as the dimensionality increases from 19 to 33
 for the present application.}
@@
 expected, the surrogate is found to be highly inaccurate. Moreover, unlike the
-test problems in section~\ref{sec:examples}, we do not estimate the Sobol
+test problems in section~\ref{sec:examples}, we do not estimate the Sobol'
 total-effect sensitivity indices in the interest of following the overall framework
@@
 associated with obtaining converged estimates of parametric sensitivities
-using DGSM, and the total-effect Sobol indices ($\mathcal{T}(\theta_i)$). The former is computed
+using DGSM, and the total-effect Sobol' indices ($\mathcal{T}(\theta_i)$). The former is computed
 using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
-estimated analytically using a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
-using a PCE has been shown to be more efficient compared to sampling techniques.
-Moreover, a sparse-basis PCE is expected to require fewer training points which
-enhances computational savings. To investigate the impact of the dimensionality, the
+estimated analytically by constructing a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
+using a PCE has been shown to be more efficient compared to sampling 
+techniques~\cite{Crestaux:2009,BlatmanSudret10}.
+Moreover, a sparse-basis PCE requires fewer training points which
+enhances computational savings~\cite{Sudret:2008,Blatman:2009}. 
+To investigate the impact of the dimensionality, the
 analysis is performed with 19 uncertain parameters, i.e.
 the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
-33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are also considered to
-be uncertain. The $E_{a,i}$'s are also considered to be uniformly distributed in the
+33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are considered to
+be uncertain in addition to the $A_i$'s. The $E_{a,i}$'s are also considered to be uniformly distributed in the
 interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
 for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
-$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therfore the
+$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therefore the
 total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.
@@
 The sparse-basis PCEs constructed in the 19 and the 33 dimensional parameter
-space are considered to have converged once $\epsilon_\text{\tiny LOO}$ is found to be
+space were considered to have converged once $\epsilon_\text{\tiny LOO}$ was found to be
 smaller than 6.0$\times$10$^{-3}$. As observed in Figures~\ref{fig:err_samples_kinetics}
 and~\ref{fig:err_samples}, the number of training points required in the 19D
-and the 33D cases are found to be 60 and 500 respectively. As expected, the predictive
+and the 33D cases are found to be 20 and 500 respectively. As expected, the predictive
 accuracy is observed to increase with increase in the number of training points in both cases.
@@
 
-Sensitivity estimates for the 33 uncertain parameters are hence determined
-using the DGSM-based strategy and by evaluating $\mathcal{T}(\theta_i)$ analytically
-using the sparse-basis PCE as discussed earlier in this section. The estimates based
-on the two approaches were plotted separately and placed side-by-side for comparison
+Before comparing the computational cost pertaining to the two approaches (DGSM-based and 
+Sobol'-based) and the impact of dimensionality, we verify that the parametric sensitivities are
+consistent in both cases. Sensitivity estimates for the 33 uncertain parameters obtained
+using the DGSM-based strategy, and by evaluating $\mathcal{T}(\theta_i)$ analytically
+using the sparse-basis PCE are plotted and placed adjacent to each other for comparison
 in Figure~\ref{fig:sense33D}.
@@
 \caption{
-Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each 
-uncertain parameter, obtained using $N$ = 5, 10, 15, and 20 samples in the full parameter space.
-Right: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
-semilinear elliptic PDE~\eqref{eq:semilinear}.}
+Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), 
+obtained using $N$ = 5, 10 samples in the full parameter space; and
+Right: Total-effect Sobol' indices, $\mathcal{T}(\theta_i)$ for the 33 uncertain rate-controlling
+parameters ($A_i$'s and $E_{a,i}$'s).}
 \label{fig:sense33D}
@@
 %
+The plots clearly indicate that the relative importance of the uncertain parameters is
+consistent in both cases. Specifically, both approaches reveal that the uncertainty in
+the ignition delay is predominantly due to the uncertainty in $E_{a,1}$ and $E_{a,10}$ with a 
+minor contribution from $E_{a,12}$, whereas, contributions from other parameters is either zero
+or negligible. These results are clearly indicative of the potential for dimension reduction in this
+case using the proposed sensitivity-driven approach. A reasonably accurate RSS in a 2D
+parameter space could potentially capture the uncertainty in the ignition delay due to the
+uncertainty in the 33 rate-controlling parameters.
+
+The computational cost is estimated in terms of the number of function evaluations or model runs,
+denoted by $\mathcal{M}$ in each case. In the case of DGSM-based approach presented in this work, 
+$\mathcal{M}$ = $N(N_p+1)$ ($N$: number of samples, $N_p$: number of parameters)
+as discussed earlier in~\ref{sub:dgsm}. In the case of PCE-based computation of $\mathcal{T}(\theta_i)$,
+$\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
+PCE and the number of evaluations used for its verification, denoted by $N_v$. In Table~\ref{tab:cost},
+we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
+parameters for the H$_2$/O$_2$ reaction kinetics application. 
+%
+\begin{table}[htbp]
+\renewcommand{\arraystretch}{1.5}
+\caption{A comparison of computational cost for the DGSM-based and Sobol'-based parametric 
+sensitivity analysis in the case of 19 and 33 uncertain rate-controlling parameters.}
+\begin{center}
+\begin{tabular}{c|c|c|}
+\cline{2-3}
+& \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
+& \textbf{19D} & \textbf{33D} \\  \hhline{===}
+\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, $\widehat{\mathcal{C}_i\mu_i}$} & 5(19+1) = 100 & 5(33+1) = 170 \\ 
+\cline{1-3}
+\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & 20 + $N_v$ & 
+500 + $N_v$ \\ \cline{1-3}  
+\end{tabular}
+\end{center}
+\label{tab:cost}
+\end{table}
+%
+For the 19D case, estimating the converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$)
+required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
+model output, a total of 100 model runs were required. However, as mentioned earlier in~\ref{sub:dgsm}, depending
+upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
+adjoint computation and automatic differentiation. Hence, there is scope for reduction in the computational cost
+associated with the DGSM-based approach. Constructing the sparse-basis PCE requires only 20 samples in
+the 19D parameter space with uncertain pre-exponents. However, additional model runs typically ranging from
+$\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
+accuracy of the PCE. The DGSM-based approach could thus yield computational gains especially when 
+efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
+proposed DGSM-based framework in the higher dimensional case involving 33 uncertain parameters. 
+Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
+using only 5 samples in the 33D parameter space. Hence, a total of 170 model runs are needed in this case
+including for gradient computation using finite difference. Whereas,
+constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
+model runs are required to further verify the accuracy of the resulting PCE. Note that the analysis was performed
+for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
+for brevity.
+
+In addition to the potential for computational cost reduction using the proposed framework, the comparative 
+analysis also reveals the significant increase in computational effort pertaining to the estimation of the total-effect
+Sobol' indices as the dimensionality increases from 19 to 33 despite using an efficient approach involving
+sparse-basis PCEs. It can thus be understood that for higher dimensional problems involving hundreds of 
+parameters, conventional approaches can quickly become prohibitive and the proposed framework could help
+reduce the computational effort by several orders of magnitude.
 

### 2018-10-25 Paper/disc.tex
..

@@
 relationship as well as the uncertainty in the quantity of interest with
-reasonable accuracy. Additional highlights of the proposed framework are as
-follows:
+reasonable accuracy. \rebut{Moreover, it was shown that the parameter
+screening procedure (Algorithm~\ref{alg:screen}) was able to determine the
+relative importance of the
+parameters using only 5 samples in an even higher dimensional
+case involving 33 uncertain rate-controlling parameters. It was observed that
+the parameter dimension could be reduced from 33 to 2 in this case.}
+Additional highlights of the proposed framework are as follows:
 \begin{enumerate}
@@
 compute-intensive simulations even if the scope for dimension reduction is
-small. 
+small. \rebut{However, computational gains using the proposed framework
+are expected to increase significantly with the increase in dimensionality of the
+parameter space.}
 %Hence, careful judgment pertaining to the construction of a reduced-order

### 2018-10-25 Paper/examples.tex
..

@@
 used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
-the PCE using 50 training points was found to be 3, 2,and 2 in the 4D, 5D, and 7D case respectively;
+the PCE constructed using 50 training points was found to be 
+3, 2,and 2 in the 4D, 5D, and 7D case respectively;
 (b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
@@
 %\end{figure}
-%We note that the total Sobol sensitivity indices are in excellent agreement
+%We note that the total Sobol' sensitivity indices are in excellent agreement
 %with the screening metric estimates. 
@@
 cartesian grid.
-We computed converged estimates of the Sobol
+We computed converged estimates of the Sobol'
 total-effect index $\mathcal{T}(\theta_i)$, reported 
@@
 %
-\rebut{The comparison of convergence characteristics of $\epsilon_{\mbox{\tiny{L-2}}}$
-illustrated in Figure~\ref{fig:conv_elliptic}(b) indicates that for a small sample size of 20,
+\rebut{The comparison of predictive accuracy of the PCEs using $\epsilon_{\mbox{\tiny{L-2}}}$
+is illustrated in Figure~\ref{fig:conv_elliptic}(b). It is observed that for a small sample size of 20,
 the surrogate constructed in the reduced space performs better in terms of
 predictability. However, as the sample size increases, the full space is observed to
-be slightly more accurate. However, the order of the accuracy is found to be 
+be slightly more accurate although the order of the accuracy is found to be 
 consistent in both cases until the sample size is less than 80. When the sample size
@@
 
-Once again, we verify the accuracy of the RSS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
-using model evaluations at 1000 independent MC samples in the 10D parameter
-space. The RSS was found to be accurate
+Using model evaluations at 1000 independent MC samples in the 10D parameter
+space, the RSS was found to be accurate
 within 5$\%$. In order to bolster confidence in the RSS, we compare PDFs of the QoI

### 2018-10-27 Paper/app.tex
..

@@
 using only 5 samples in the 33D parameter space. Hence, a total of 170 model runs are needed in this case
-including for gradient computation using finite difference. Whereas,
+including for gradient computation using finite difference. Whereas, as discussed earlier,
 constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
-model runs are required to further verify the accuracy of the resulting PCE. Note that the analysis was performed
+model runs ($\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$) are required to further verify the accuracy of the 
+resulting PCE. Note that the analysis was performed
 for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
@@
 In addition to the potential for computational cost reduction using the proposed framework, the comparative 
-analysis also reveals the significant increase in computational effort pertaining to the estimation of the total-effect
+analysis also reveals the significant increase in computational effort associated with the PCE-based approach for
+computing  the total-effect
 Sobol' indices as the dimensionality increases from 19 to 33 despite using an efficient approach involving
 sparse-basis PCEs. It can thus be understood that for higher dimensional problems involving hundreds of 
-parameters, conventional approaches can quickly become prohibitive and the proposed framework could help
+parameters, conventional approaches (even sparse-basis PCEs) can quickly become prohibitive and
+the proposed DGSM-based approach could help
 reduce the computational effort by several orders of magnitude.

### 2018-10-27 Paper/disc.tex
..

@@
 satisfied, enhances the accuracy of the PCE-based surrogates as well.  
-\rebut{Moreover, in the presence of severe non-linearities in the model output
+\rebut{Moreover, in the presence of severe non-linearity in the model output
 leading to significant variability in its gradient in the considered input domain,

### 2018-10-27 Paper/revision/reviewer_replies.tex
..

@@
 
-These points have been emphasized in the discussion in Section~6 (Summary and
+These points have been added in the discussion in Section~6 (Summary and
 Conclusion, Page 34) in the revised manuscript.
@@
 As suggested by the reviewer, the computational cost pertaining to the estimation of DGSM-based
-sensitivity indices is compared with the cost associated with estimating the total-effect Sobol' indices
-for the 19-dimensional reaction kinetics application in this work. Additionally, the comparison is 
+sensitivity indices using the approach presented in this work is compared with the cost associated 
+with estimating the total-effect Sobol' indices using a sparse-basis PCE
+for the 19-dimensional reaction kinetics application. Additionally, the comparison is 
 performed for the same application with 33 uncertain rate-controlling parameters to investigate
@@
 
-A new sub-section (5.3) on ``comparative cost analysis" has been included in the revised
+For the 19-dimensional case, the DGSM-based approach seems 
+slightly more efficient depending upon the model runs required for training and verifying the sparse-basis PCE
+used to compute the total-effect Sobol' indices. However, computational gains are observed to 
+be much more substantial in the case of DGSM-based approach for the 33-dimensional problem
+owing to the increase in the number of training points required to construct the PCE. Our analysis
+clearly indicates that with increasing dimensionality, the DGSM-based approach presented in this
+work is expected to yield a higher computational dividend especially when efficient gradient estimation
+techniques are employed.
+
+A new sub-section (5.3) on ``comparative cost analysis" comprising the results and
+discussion based on the above points has been included in the revised
 manuscript.
@@
 and 6b) and 
-the chemical kinetics application presented in Section 4 (Figure 8, right).
+the chemical kinetics application presented in Section 4 (Figure 8, right). As expected, the predictive
+accuracy of the surrogates is observed to increase with the number of training points in all cases. 
+Additionally, the RSS is observed to be more accurate when a small number of training samples, $N$=10
+is used. However, as $N$ increases the FSS is observed to be more accurate depending upon the
+application.
 
@@
 to a significantly large variability in its gradient. Hence, a large number of Monte Carlo samples might be
-required to estimate the screening metrics with reasonable accuracy in this case depending upon the
+required to estimate the screening metrics with reasonable accuracy in that case depending upon the
 application. Therefore, the computational effort is expected to increase in such cases. In the presence
@@
 parametric sensitivities. Since the proposed methodology in this work aims to reduce the computational
-effort pertaining to total-effect Sobol index which is a variance-based measure, it might lead to
+effort pertaining to total-effect Sobol' index which is a variance-based measure, it might lead to
 inaccurate estimates of the screening metric and therefore to erroneous relative importance of the uncertain

### 2018-10-28 Paper/app.tex
..

@@
 $\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
-PCE and the number of evaluations used for its verification, denoted by $N_v$. In Table~\ref{tab:cost},
+PCE and the number of evaluations used for its verification. In Table~\ref{tab:cost},
 we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
@@
 \begin{center}
-\begin{tabular}{c|c|c|}
+\begin{tabular}{c|p{4cm}|p{4cm}|}
 \cline{2-3}
 & \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
-& \textbf{19D} & \textbf{33D} \\  \hhline{===}
-\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, $\widehat{\mathcal{C}_i\mu_i}$} & 5(19+1) = 100 & 5(33+1) = 170 \\ 
+& \centering \textbf{19D} & \hspace{18mm} \textbf{33D} \\  \hhline{===}
+\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, 
+$\widehat{\mathcal{C}_i\mu_i}$} & \centering 100 + $N_{v_1}$ & \hspace{13mm} 170 + $N_{v_1}$ \\ 
 \cline{1-3}
-\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & 20 + $N_v$ & 
-500 + $N_v$ \\ \cline{1-3}  
+\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & \centering 20 + $N_{v_2}$ & 
+\hspace{13mm} 500 + $N_{v_2}$ \\ \cline{1-3}  
 \end{tabular}
@@
 required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
-model output, a total of 100 model runs were required. However, as mentioned earlier in~\ref{sub:dgsm}, depending
-upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
-adjoint computation and automatic differentiation. Hence, there is scope for reduction in the computational cost
-associated with the DGSM-based approach. Constructing the sparse-basis PCE requires only 20 samples in
-the 19D parameter space with uncertain pre-exponents. However, additional model runs typically ranging from
+model output, a total of 100 model runs were required. Additionally, the screening procedure is continued for
+one iteration using $N$ = 10 samples to ensure the convergence of $\widehat{\mathcal{C}_i\mu_i}$.
+Since these additional runs are essentially used for verification, we denote them as $N_{v_1}$.
+%As mentioned earlier in~\ref{sub:dgsm}, depending
+%upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
+%adjoint computation and automatic differentiation. Hence, there is scope for a significant
+%reduction in the computational cost
+%associated with the DGSM-based approach. 
+On the other hand, constructing the sparse-basis PCE requires only 20 samples in
+the 19D parameter space with uncertain pre-exponents. Additional model runs ($N_{v_2}$)
+ typically ranging from
 $\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
-accuracy of the PCE. The DGSM-based approach could thus yield computational gains especially when 
+accuracy of the PCE.  
+The DGSM-based approach could thus yield computational gains especially when 
 efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
@@
 Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
-using only 5 samples in the 33D parameter space. Hence, a total of 170 model runs are needed in this case
-including for gradient computation using finite difference. Whereas, as discussed earlier,
+using only 5 samples in the 33D parameter space. For verification, the screening procedure is
+continued for one iteration by evaluating the model output at 10 samples in 33 dimensions. 
+Therefore, a total of 340 model runs are needed in this case
+including for gradient computation using finite difference as well as verification. Whereas, as discussed earlier,
 constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
@@
 
-In addition to the potential for computational cost reduction using the proposed framework, the comparative 
-analysis also reveals the significant increase in computational effort associated with the PCE-based approach for
-computing  the total-effect
-Sobol' indices as the dimensionality increases from 19 to 33 despite using an efficient approach involving
-sparse-basis PCEs. It can thus be understood that for higher dimensional problems involving hundreds of 
+Based on our findings, it appears that the proposed DGSM-based approach can offer a significant
+computational advantage especially in higher dimensions due to multiple factors: (1) Computational
+effort required for estimating $\mathcal{T}(\theta_i)$ is observed to increase substantially with dimensionality even
+when using sparse-basis PCEs. Whereas, the DGSM-based estimates converge
+with only a few samples ($N$ = 5) even for a relatively higher-dimensional case. Moreover, it must be noted that
+the computational gains associated with the proposed DGSM-based approach could be enhanced
+significantly by employing efficient gradient computation techniques such as those involving adjoints
+and automatic differentiation as mentioned earlier in~\ref{sub:dgsm}; (2) The number of model runs
+needed to verify the convergence of $\widehat{\mathcal{C}_i\mu_i}$ can be controlled
+using the iterative strategy in this work
+and is expected to be much smaller than the number of runs needed for verifying the accuracy of  
+$\mathcal{T}(\theta_i)$ especially in high-dimensional settings. Specifically, for the 33D case,
+model runs at 5 additional samples (corresponding to the first iteration) were used to verify the
+convergence of $\widehat{\mathcal{C}_i\mu_i}$ as opposed to 1000 model evaluations used to verify
+the accuracy of the PCE. 
+It can thus be understood that for higher dimensional problems involving hundreds of 
 parameters, conventional approaches (even sparse-basis PCEs) can quickly become prohibitive and

### 2018-10-28 Paper/disc.tex
..

@@
 work, reasonable estimates of the screening metric are obtained during the
-initial screening step with only 5 samples. This is indicative of a small
+initial screening step with a few samples. This is indicative of a small
 degree of

### 2018-10-28 Paper/examples.tex
..

@@
 PCE is found to be the smallest. However, as the sample size increases, the higher
-order PCE becomes more accurate. Note that the same set of 50 samples in the
+order PCE becomes more accurate. This is expected since the higher order PCE
+inherently contains more information pertaining to the input-output relationship.
+Note that the same set of 50 samples in the
 validation test suite were used in each case. Hence, when limited computational resources
@@
 convergence as well as higher accuracy of the surrogate in the reduced space.
-The gains are expected to increase exponentially as the dimensionality of the 
+The gains are expected to increase significantly as the dimensionality of the 
 input space increases.}
@@
 the surrogate constructed in the reduced space performs better in terms of
-predictability. However, as the sample size increases, the full space is observed to
+predictability. However, as the sample size increases, the FSS is observed to
 be slightly more accurate although the order of the accuracy is found to be 

### 2018-10-30 Paper/revision/reviewer_replies.tex
..
update ...

@@
 For the reaction kinetics application, the PCE constructed using 60 training points
-for the 19D and 4D cases was found to be of degree 1 and 3 respectively.
+for the 19D and 4D cases was found to be of degree 1 and 3 respectively. Note that
+in each case, the degree refers to the maximal degree associated with the polynomial
+basis as reported by UQLab.
 
@@
 The reviewer is correct in pointing out from Figure 7 that the initial screening step
-reasonably approximates the screening metric. The same is observed in
+reasonably approximates the screening metric. However, as shown in Algorithm~1,
+the screening procedure involves atleast $s_\text{min}$ iterations to ensure that
+the screening metric has converged. The same is observed in
 Figure 5 for the semilinear elliptic PDE test case. It is also true in the borehole test
@@
 
-Severe non-linearity in the model output as a function of uncertain inputs could potentially lead
-to a significantly large variability in its gradient. Hence, a large number of Monte Carlo samples might be
-required to estimate the screening metrics with reasonable accuracy in that case depending upon the
-application. Therefore, the computational effort is expected to increase in such cases. In the presence
-of rare events, the variance-based approaches typically lead to inaccurate estimates of 
-parametric sensitivities. Since the proposed methodology in this work aims to reduce the computational
-effort pertaining to total-effect Sobol' index which is a variance-based measure, it might lead to
-inaccurate estimates of the screening metric and therefore to erroneous relative importance of the uncertain
-inputs.
+Severe non-linearity in the model output as a function of uncertain
+inputs could potentially lead to a significantly large variability in
+its gradient. Hence, a large number of Monte Carlo samples might be
+required to estimate the screening metrics with reasonable accuracy
+in that case depending upon the application. Therefore, the
+computational effort is expected to increase in such cases.
+Moreover, the proposed methodology aims to reduce the computational
+effort pertaining to the total-effect Sobol' index, which is a
+variance-based measure.  For severely nonlinear models, whose QoIs
+might exhibit heavy tailed or multimodal distributions, the 
+variance might not provide an adequate representation of uncertainty. 
+Possible remedies for such cases 
+include the so-called moment independent measures.
 
-A brief discussion based on the above points has been included in the last paragraph in
-Section 6 (Summary and Discussion).
+%it might lead to inaccurate estimates of
+%%the screening metric and therefore to erroneous relative importance
+%of the uncertain inputs.
+
+A brief discussion based on the above points has been included in the
+last paragraph in Section 6 (Summary and Discussion).
 

### 2018-10-30 Paper/disc.tex
update ...

@@
 Based on the results presented for the test problems and the kinetics
-application, the proposed framework seems quite promising in its
-potential for identifying the unimportant model inputs. \rebut{In fact, in 
-the numerical tests and the chemical kinetics application presented in this
-work, reasonable estimates of the screening metric are obtained during the
-initial screening step with a few samples. This is indicative of a small
-degree of
-variability in the gradient of the model output with respect to individual
-parameters, and therefore, a low variance of the Monte Carlo estimator.}
-These observations could be exploited to construct efficient model surrogates
-in a reduced input space. However, it is important to remain cognizant
+application, the proposed framework seems quite promising in its potential for
+identifying the unimportant model inputs. \rebut{In fact, in the numerical
+tests and the chemical kinetics application presented in this work, reasonable
+estimates of the screening metric are obtained during the initial screening
+step with a few samples. This is indicative of a small degree of variability in
+the gradient of the model output with respect to individual parameters, and
+therefore, a low variance of the Monte Carlo estimator.} These observations
+could be exploited to construct efficient model surrogates in a reduced input
+space.
+
+While the proposed approach has attractive features, it is important to remain cognizant
 about the limitations of the framework as well. 
@@
 increase. The extent of increase in the effort would of course depend upon the
-application. In the case of rare events, the variance-based methods typically
-lead to inaccurate estimates of the uncertainty in the model output. Since the
-methodology proposed in this work is based on reducing computational
-effort associated with variance-based sensitivity analysis, specifically, the
-total-effect Sobol' index, it might lead to erroneous estimates of the
-screening metrics and consequently the relative importance of the
-uncertain parameters.}
+application. 
+Also, we note that the proposed methodology aims to reduce the computational
+effort pertaining to the total-effect Sobol' index, which is a
+variance-based measure.  For severely nonlinear models, whose QoIs
+might exhibit heavy-tailed or multimodal distributions, the 
+variance might not provide an adequate representation of uncertainty.
+Possible remedies for such cases include the so-called moment independent
+measures; see e.g.,~\cite{BorgonovoIooss16,IoossLemaitre15}.}
+%In the case of rare events, the variance-based methods typically
+%lead to inaccurate estimates of the uncertainty in the model output. Since the
+%methodology proposed in this work is based on reducing computational
+%effort associated with variance-based sensitivity analysis, specifically, the
+%total-effect Sobol' index, it might lead to erroneous estimates of the
+%screening metrics and consequently the relative importance of the
+%uncertain parameters.
+
 Additionally, the proposed framework does not

### 2018-11-03 Paper/revision/reviewer_replies.tex
..

--- 2018-10-27 Paper/revision/reviewer_replies.tex
@@
 
-As suggested by the reviewer, the computational cost pertaining to the estimation of DGSM-based
+As suggested by the reviewer, the computational cost pertaining to the estimation of the DGSM-based
 sensitivity indices using the approach presented in this work is compared with the cost associated 
@@
 used to compute the total-effect Sobol' indices. However, computational gains are observed to 
-be much more substantial in the case of DGSM-based approach for the 33-dimensional problem
+be much more substantial in the case of the DGSM-based approach for the 33-dimensional problem
 owing to the increase in the number of training points required to construct the PCE. Our analysis

### 2018-11-03 Paper/abstract.tex
..
...

@@
 classic Borehole function, and a semilinear elliptic PDE with a random source
-term. 
+function. 
 %Motivated by these experiences, the framework is fully implemented to
@@
 \noindent
-\textbf{Keywords}: Derivative-based global sensitivity,
-polynomial chaos, parameter screening, reduced-space surrogate
+\textbf{Keywords}: Global sensitivity analysis,
+polynomial chaos, parameter screening, surrogate modeling

### 2018-11-03 Paper/app.tex
..
final revision

@@
 
-\subsection{Problem Set-up}
+\subsection{Problem Setup}
 \label{sub:setup}  
@@
 of intermediate species as provided below in Table~\ref{tab:kinetics}.
-
+%
 \begin{table}[htbp]
@@
 \end{table}
-
+%
 The reaction rate for the $i^{th}$ reaction as a function of temperature
@@
 %
-where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
-activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
+where $A_i$, $n_i$, and $E_{a,i}$ denote the pre-exponent, the index of $T$, and
+and the activation energy corresponding to the $i^{th}$ reaction; and $R$ is the
 universal gas constant. 
@@
 
-While the dimensionality of the problem is relatively moderate,
+While the dimensionality of the problem is moderate,
 constructing a surrogate in the 19-dimensional parameter space could still be
@@
 \rebut{
-\subsection{Comparative cost analysis}
+\subsection{Comparative cost analysis: higher-dimensional setting}
 \label{sub:cost}
@@
 using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
-estimated analytically by constructing a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
+estimated using a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
 using a PCE has been shown to be more efficient compared to sampling 
@@
 consistent in both cases. Sensitivity estimates for the 33 uncertain parameters obtained
-using the DGSM-based strategy, and by evaluating $\mathcal{T}(\theta_i)$ analytically
+using the DGSM-based strategy, and by evaluating $\mathcal{T}(\theta_i)$ 
 using the sparse-basis PCE are plotted and placed adjacent to each other for comparison
@@
 \begin{center}
-\begin{tabular}{c|p{4cm}|p{4cm}|}
+\begin{tabular}{c|p{4.2cm}|p{4.2cm}|}
 \cline{2-3}
@@
 & \centering \textbf{19D} & \hspace{18mm} \textbf{33D} \\  \hhline{===}
-\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, 
-$\widehat{\mathcal{C}_i\mu_i}$} & \centering 100 + $N_{v_1}$ & \hspace{13mm} 170 + $N_{v_1}$ \\ 
+\multicolumn{1}{ |l|| }{$\widehat{\mathcal{C}_i\mu_i}$ (\textbf{DGSM-based)}} & \centering 5(19+1) = 100 + $N_{v_1}$ & \hspace{3mm} 5(33+1) = 170 + $N_{v_1}$ \\ 
 \cline{1-3}
-\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & \centering 20 + $N_{v_2}$ & 
+\multicolumn{1}{ |l|| }{$\mathcal{T}(\theta_i)$ (\textbf{PCE-based})} & \centering 20 + $N_{v_2}$ & 
 \hspace{13mm} 500 + $N_{v_2}$ \\ \cline{1-3}  
@@
 resulting PCE. Note that the analysis was performed
-for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
-for brevity.
+for the fuel-rich case.
 
@@
 when using sparse-basis PCEs. Whereas, the DGSM-based estimates converge
-with only a few samples ($N$ = 5) even for a relatively higher-dimensional case. Moreover, it must be noted that
+with only a few samples, $\mathcal{O}(10^1)$ even for a relatively higher-dimensional case. Moreover, it must be noted that
 the computational gains associated with the proposed DGSM-based approach could be enhanced

### 2018-11-03 Paper/disc.tex
final revision

@@
 by identifying uncertain parameters that contribute relatively less towards the uncertainty
-in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
+in the QoI. These parameters deemed as \textit{unimportant} are determined
 using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
@@
 mixture. In both cases, the resulting RSS was able to capture the input-output
-relationship as well as the uncertainty in the quantity of interest with
+relationship as well as the uncertainty in the QoI with
 reasonable accuracy. \rebut{Moreover, it was shown that the parameter
@@
 about the limitations of the framework as well. 
-For instance, the quantity of interest is required to be differentiable with
+For instance, the QoI is required to be differentiable with
 respect to each parameter in the considered domain. This condition once

### 2018-11-03 Paper/examples.tex
final revision

@@
 
-The borehole function~\cite{Morris:1993} is a benchmark reference problem in sensitivity analysis.
+The borehole function~\cite{Morris:1993,Marelli:2014} is a benchmark reference problem in sensitivity analysis.
 It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
@@
   &
-  \includegraphics[width=0.49\textwidth]{./Figures/ub_conv_borehole}
+  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_borehole}
   \\ (a) & (b)
@@
 and $|D|$ denotes the area of $D$. 
-While this model is considerably more complex than the previous numerical
-examples, it can still be solved efficiently.
+While this model is considerably more complex than the borehole 
+example, it can still be solved efficiently.
 The equation was discretized using finite differences, and Newton's method
@@
 consistent in both cases until the sample size is less than 80. When the sample size
-increases to 90, the 19D PCE is observed to be more accurate by an order of magnitude.
+increases to 90, the 10D PCE is observed to be more accurate by an order of magnitude.
 However, the corresponding value of $\epsilon_{\mbox{\tiny{LOO}}}$ is~$\mathcal{O}(10^{-1})$.
-Hence, the 19D PCE does not seem to have fully  converged and requires additional 
+Hence, the 10D PCE does not seem to have fully  converged and requires additional 
 model evaluations. Therefore, considering
 fast convergence of the surrogate in the 5D space and predictive accuracy comparable
-to the 19D PCE,
+to the 10D PCE,
 the proposed methodology significantly reduces computational effort in this case.}

### 2018-11-03 Paper/intro.tex
final revision

@@
 We are thus, faced with a ``chicken-and-egg'' problem: on the one hand,
-computing global sensitivity measures enable dimension reduction, which in turn
-enable efficient surrogate model construction.  On the other hand, computing
+computing global sensitivity measures enables dimension reduction, which in turn
+enables efficient surrogate model construction.  On the other hand, computing
 sensitivity measures is expensive and is often made possible by using
@@
 deploy our strategy in an application problem from chemical kinetics with 19
-uncertain parameters. The problem is studied in multiple regimes.
+uncertain rate-controlling parameters. The problem is studied in multiple regimes.
 It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
-or 4-dimensional problem.
+or 4-dimensional problem. \rebut{The strategy is further implemented to a
+higher dimensional problem involving 33 uncertain rate-controlling parameters.
+In this case, it is shown that only 2 out of 33 parameters predominantly 
+contribute to the uncertainty in the quantity of interest (QoI). Moreover, 
+computational gains using the proposed strategy are shown to increase significantly
+with dimensionality.}
 

### 2018-11-03 Paper/method.tex
..
final revision

@@
 \textbf{Parameter screening.}
-In the proposed framework, we
-adopt a novel approach for constructing an RSS based on estimating the
+Dimension reduction and subsequent construction of the RSS is enabled by
+identifying key contributors to the uncertainty in the QoI. For this purpose,
+we estimate the 
 upper-bound $\widehat{\mathcal{C}_i\mu_i}$, given in~\eqref{eq:bound}, on 
@@
 the algorithm and the corresponding gradient evaluations 
-$\{ \bm{g}^k \}_{k=1}^{n_0}$, where
+$\{ \bm{g}^k \}_{k=1}^{\rebut{n_1}}$, where
 $\bm{g}^k = \nabla_{\bm{\theta}} G(\bm{\theta}_k)$. 
@@
         \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
-                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
+                  $\bm{\theta}_k$, $k = \rebut{N_\text{total} + 1, \ldots, N_\text{total} + n_s}$
        \State $N_\text{total} = N_\text{total} + n_s$.
@@
 of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used; for an easy reference,
-see~\cite[Eq.~(1.27)]{Marelli:2014}.  Accuracy of the surrogate could also 
-be assessed by evaluating the relative $\ell_2$-norm of the difference in
+see~\cite[Eq.~(1.27)]{Marelli:2014}.  Predictive accuracy of the surrogate is 
+assessed by evaluating the relative $\ell_2$-norm of the difference in
 predictions between the model and the surrogate ($\epsilon_{\mbox{\tiny{L-2}}}$), as follows:
@@
 dimension reduction, accuracy of the concurrent FSS, and availability of
-computational resources.
+computational resources. Moreover, the stopping criterion for the
+screening procedure i.e. the choice of $\Delta\mu_s$
+should be based on the application.
 

### 2018-12-10 Paper/revision/source_files/abstract.tex
..

--- 2018-11-03 Paper/abstract.tex
@@
 kinetics, where we study the ignition delay in an H$_2$/O$_2$ reaction
-mechanism with 19 uncertain rate constants.  It is observed that significant
+mechanism with 19 and 33 uncertain rate-controlling parameters.  
+It is observed that significant
 computational gains can be attained by constructing accurate low-dimensional

### 2018-12-10 Paper/revision/source_files/app.tex
..

--- 2018-11-03 Paper/app.tex
@@
 transportation~\cite{Das:1996} and fuel cell 
-applications~\cite{Loges:2008,Cosnier:2016}. \rebut{We begin by providing
+applications~\cite{Loges:2008,Cosnier:2016}. We begin by providing
 the necessary background information for setting up the problem
@@
 total-effect Sobol' index as the dimensionality increases from 19 to 33
-for the present application.}
+for the present application.
 
@@
 number of model evaluations in the full-space (19D) and the reduced-space (4D)
-for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
+for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. The degree of
 the PCE constructed using 60 training points was found to be 1 and 3 in the 19D and the 4D cases respectively.
 Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
-for the PCEs constructed in 4D and 19D.}}
+for the PCEs constructed in 4D and 19D.}
 \label{fig:err_samples_kinetics}
@@
 at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
-\rebut{Additionally, the
+Additionally, the
 convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
@@
 as mentioned earlier should help reduce computational effort associated with
-surrogate model construction.}
+surrogate model construction.
 Similar trends (not included) were observed in the fuel-lean case.
@@
 
-\rebut{
 \subsection{Comparative cost analysis: higher-dimensional setting}
@@
 reduce the computational effort by several orders of magnitude.
-
-}

### 2018-12-10 Paper/revision/source_files/bg.tex
..

--- 2018-07-31 Paper/bg.tex
@@
 Notice that this formulation assumes that the function $\GG$ is differentiable
-with respect to $\theta_i$, $i = 1, \ldots, \Np$.
+with respect to $\theta_i$, $i = 1, \ldots, \Np$ and the partial derivatives,
+$\left(\frac{\partial \GG(\bm{\bm{\theta}})}{\partial \theta_i}\right)$ are 
+square integrable.
 
@@
 $\mathcal{C}_i = (b-a)^{2}/\pi^2$, and for  
-$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$. 
+$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$
+(see~\cite{Lamboni:2013} for more details). 
 Here $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with mean $\mu$

### 2018-12-10 Paper/revision/source_files/disc.tex
..

--- 2018-11-03 Paper/disc.tex
@@
 the available set of model evaluations. Both, RSS and FSS are
-constructed using regression-based sparse PCEs. \rebut{Note however that the FSS is
+constructed using regression-based sparse PCEs. Note however that the FSS is
 constructed in an independent manner to ensure that the computational effort associated
@@
 FSS directly. Therefore, it does not impact the accuracy of the RSS which is only
-constructed in situations where computational gains are expected.}
+constructed in situations where computational gains are expected.
 
@@
 relationship as well as the uncertainty in the QoI with
-reasonable accuracy. \rebut{Moreover, it was shown that the parameter
+reasonable accuracy. Moreover, it was shown that the parameter
 screening procedure (Algorithm~\ref{alg:screen}) was able to determine the
@@
 case involving 33 uncertain rate-controlling parameters. It was observed that
-the parameter dimension could be reduced from 33 to 2 in this case.}
+the parameter dimension could be reduced from 33 to 2 in this case.
 Additional highlights of the proposed framework are as follows:
@@
 compute-intensive simulations even if the scope for dimension reduction is
-small. \rebut{However, computational gains using the proposed framework
+small. However, computational gains using the proposed framework
 are expected to increase significantly with the increase in dimensionality of the
-parameter space.}
+parameter space.
 %Hence, careful judgment pertaining to the construction of a reduced-order
@@
 application, the proposed framework seems quite promising in its potential for
-identifying the unimportant model inputs. \rebut{In fact, in the numerical
+identifying the unimportant model inputs. In fact, in the numerical
 tests and the chemical kinetics application presented in this work, reasonable
@@
 the gradient of the model output with respect to individual parameters, and
-therefore, a low variance of the Monte Carlo estimator.} These observations
+therefore, a low variance of the Monte Carlo estimator. These observations
 could be exploited to construct efficient model surrogates in a reduced input
@@
 satisfied, enhances the accuracy of the PCE-based surrogates as well.  
-\rebut{Moreover, in the presence of severe non-linearity in the model output
+Moreover, in the presence of severe non-linearity in the model output
 leading to significant variability in its gradient in the considered input domain,
@@
 Possible remedies for such cases include the so-called moment independent
-measures; see e.g.,~\cite{BorgonovoIooss16,IoossLemaitre15}.}
+measures; see e.g.,~\cite{BorgonovoIooss16,IoossLemaitre15}.
 %In the case of rare events, the variance-based methods typically

### 2018-12-10 Paper/revision/source_files/examples.tex
..

--- 2018-11-03 Paper/examples.tex
@@
 against number of samples. Also included in the legend are estimates of
-$\mathcal{T}(\theta_i)$ in each case in the legend; \rebut{and (c) Estimates of
+$\mathcal{T}(\theta_i)$ in each case in the legend; and (c) Estimates of
 $\widehat{\mathcal{C}_i\mu_i}$ for individual parameters using $N$ = 5, 10,
-15, and 20 samples in the full parameter space.}}
+15, and 20 samples in the full parameter space.}
 \label{fig:sense_bore}
@@
 $\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
-samples used for approximating $\mu_i$ using~\eqref{eq:mu}. \rebut{Additionally,
+samples used for approximating $\mu_i$ using~\eqref{eq:mu}. Additionally,
 to illustrate a comparison of the estimates of $\widehat{\mathcal{C}_i\mu_i}$ obtained
 at the end of the initial screening step, i.e. $N$~=~5, with subsequent steps, we plot
-them for individual parameters at $N$~=`5, 10, 15, and 20 samples in Figure~\ref{fig:sense_bore}(c).}
+them for individual parameters at $N$~=`5, 10, 15, and 20 samples in Figure~\ref{fig:sense_bore}(c).
 Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement
@@
 ($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
-used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
+used for constructing the PCE in 4, 5, and 7 dimensions. The degree of
 the PCE constructed using 50 training points was found to be 
@@
 (b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
-for the PCEs constructed in 4D, 5D, and 7D};
+for the PCEs constructed in 4D, 5D, and 7D;
 and (c) A comparison of
@@
 owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
-\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
+However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
 size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
@@
 The gains are expected to increase significantly as the dimensionality of the 
-input space increases.}
+input space increases.
 
@@
 size for PCEs constructed in 10 and 5 dimensions to compare their convergence 
-characteristics. \rebut{The degree of
+characteristics. The degree of
 the PCE constructed using 90 training points was found to be 2 and 3 in the
@@
 and (c) PDF of the QoI, $\mathcal{F}(\vec\theta)$ in~\eqref{eq:semilinear}
-is plotted using the full-surrogate and the reduced-space PC surrogate.}
+is plotted using the full-surrogate and the reduced-space PC surrogate.
 \label{fig:conv_elliptic}
@@
 %
-\rebut{The comparison of predictive accuracy of the PCEs using $\epsilon_{\mbox{\tiny{L-2}}}$
+The comparison of predictive accuracy of the PCEs using $\epsilon_{\mbox{\tiny{L-2}}}$
 is illustrated in Figure~\ref{fig:conv_elliptic}(b). It is observed that for a small sample size of 20,
@@
 to the 10D PCE,
-the proposed methodology significantly reduces computational effort in this case.}
+the proposed methodology significantly reduces computational effort in this case.
 

### 2018-12-10 Paper/revision/source_files/intro.tex
..

--- 2018-11-03 Paper/intro.tex
@@
 It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
-or 4-dimensional problem. \rebut{The strategy is further implemented to a
+or 4-dimensional problem. The strategy is further implemented to a
 higher dimensional problem involving 33 uncertain rate-controlling parameters.
@@
 computational gains using the proposed strategy are shown to increase significantly
-with dimensionality.}
+with dimensionality.
 
